### 2015-03-23 MUSES_vs_BYOD_solutions.tex
Artículo enviado
Para empezar a trabajar

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

\begin{document}

\begin{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   AUTHORS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{P. de las Cuevas, A.M. Mora, J.J. Merelo}
\ead{\{paloma, amorag, jmerelo\}@geneura.ugr.es}
\address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
%\author{A. M. Mora}
%\ead{amorag@geneura.ugr.es}
%\address{Departamento de Arquitectura y Tecnología de Computadores. Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación. CITIC. University of Granada, Spain}

%\maketitle

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and their Chief Security Officers (CSOs) particularly, want to be sure that their Security Policies are complied. This goal turned hard to achieve since employees are able to use their own devices (laptops, smartphones, and tablets) at work, or at home but for work purposes. As this is part of the Bring Your Own Device (BYOD) philosophy and is being adopted by many companies everyday, a number of solutions have arisen in order to adapt it securely. In this paper, a novel system to deal with this situation is introduced, named  MUSES (Multiplatform Usable Endpoint Security). It is a system able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, still in development, is compared with the most relevant solutions offered by other companies to deal with the same issues as MUSES, remarking the advantages that our system will offer with respect to them.
\end{abstract}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   KEYWORDS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{keyword}
Corporate mobile security \sep End-to-end security solutions \sep User-centric systems \sep Self-adaptation \sep Multiplatform \sep Security Policies \sep Data security and data privacy \sep BYOD
\end{keyword}

\end{frontmatter}

%-------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   INTRODUCTION   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------------------------------

\section{Introduction}
\label{sec:intro}

The way on how data has been stored and accessed in the companies has completely changed along the years. The use of owned servers being accessed by desktop PCs (and maybe laptops) from inside the company facilities has been transformed into the distribution of these data among a number of machines, even not all belonging to the company, and working over the famous Cloud Computing environment. Besides, being stored in the cloud or not, data are being consulted and modified through a wide amount of devices, some of them owned by the company's users. This is the so-called Bring Your Own Device (BYOD) philosophy. It is becoming highly successful due to the impact that portable devices (such as smartphones and tablets) are having in the market.
Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies. Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems, for instance the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).

In this scenario several solutions have arisen in order to manage the corporate security. Some solutions are focused only in smartphones, while others are thought for laptops; also some are implemented for a certain platform, but others consider multiplatform. However most of them try to be non-intrusive (regarding the users' personal data), friendly and easy to use.

Moreover, it has been demonstrated that people are the main hazard regarding the company security \cite{Adams_Users05}, so in this situation, some monitorization and security-aimed applications are arising, aiming to cope with the concept of seamless working experience on different devices. 
This concept is a methodology of work which allows users to start/continue a working session over multiple devices and locations without any significant loss of data. This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company's data borders have changed in the last years so now the users can access significant data from outside the enterprise, and possibly through a non absolutely secure channel.

Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a device-independent end-to end user-centric tool, based in a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt, even inferring new ones, the set of rules in order to deal with potential future security incidents due to the user's. Then the system will react, in a non-intrusive way, to the potentially dangerous sequence of actions (events) that he or she is conducting at any time.

To this end MUSES will analyse the users' behaviour by means of Data Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning (ML) methods \cite{MachineLearning_Bishop06}, extracting a set of patterns which will be later processed by means of Computational Intelligence (CI) algorithms, namely Evolutionary Computation methods \cite{EAs_Back96,GP_Koza92}.

MUSES will include some important modules in the loop, such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset.

In the paper the system architecture is presented, in addition to a deep description of the soft computing methods the system will apply.

But first, this work presents a brief overview of the main existing solutions in this environment. Then a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) will bring.

The rest of the paper is organized as follows. First, some background situation about enterprise security is presented in Section \ref{sec:preliminaryconcepts}, explaining how BYOD philosophy affects it. Then, the main tools/solutions are detailed in Section \ref{sec:toolsreview}, even if they are still in development.  
Then, in Section \ref{sec:muses}, the Multiplatform Usable Endpoint Security System is presented (architecture + soft computing techniques). Its advantages and benefits in comparison with the other solutions are commented in Section \ref{sec:comparison}.
Finally, the reached conclusions are discussed in Section \ref{sec:conclusions}.

%----------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   BACKGROUND  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------

\section{Preliminary concepts and background about enterprise security}
\label{sec:preliminaryconcepts}

Until these days, enterprises used to follow a static Security Policy devoted to controlling a certain structure \cite{BYOD13}, where the Information Assets and the devices were purchased and maintained by the company. Now that corporate networks are becoming dynamic for being adapted to the BYOD philosophy, there is an additional risk because the devices that the employees use are not always company-owned. A needed security policy, or in this case, an Information Security Policy (ISP from now on) should deal with the way of protecting a certain organization's information against a security breach. Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}; an ISP is built depending on the characteristics of the community/organisation that they are built for.

On the other hand, employee-owned devices like smartphones, are not just for work purposes anymore. As the name says, smartphones are more than simple old cellular phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life. For this reason, the risk of uncontrolled devices accessing to corporate access in unsafe conditions, due to the number of risky applications is bigger.

Normally, the enterprise network architecture was being adapted to cope with external attackers \cite{MIT05}. With the incorporation of BYOD, the threat is about corporate assets being compromised due to employees' devices with vulnerabilities \cite{android11}, or leaked because they are being accessed from a device connected through an insecure (public) network.

Thus now, more things should be considered than the usual ones when designing a company's network architecture. In Figure \ref{fig:proposed_diagram} there is a proposal which can be used for the beginning of the study of solutions that may secure such a dynamic environment. It includes the possibility of having employee-owned mobile (smartphones and tablets) and portable (laptops) devices, and also the opportunity that the employees have of connecting these devices either from inside or outside the company premises. Moreover, company's information assets are constantly accessed under these conditions, considering that an information asset means every \textit{piece of information} that has a \textit{value} (cost depending on the risk of being lost or leaked) for the company. It can be referred to files with sensitive information to certain mails, or even to company applications.

\begin{figure}[ht]
	\begin{center}
		\includegraphics[scale=0.4]{img/proposed_diagram.eps}
		\caption{Architecture approach of an Enterprise Network assuming that the Company has adopted the BYOD philosophy.}
	\label{fig:proposed_diagram}
	\end{center}
\end{figure}

The other issue to cope with is the elaboration of a good ISP, understandable for every user of the company, and more importantly, non-intrusive for him. A lot of researchers have studied the natural tendency of employees to comply with the ISP \cite{SecPolComp07,SecPolComp10,SecPolComp12}, reaching conclusions such as the employees compliance with the security policies increases educating/training them in information security awareness  \cite{SecPolComp09}, and decreases applying too much sanctions when a misuse or abuse occurs \cite{SecPolPenalty09}. Thus, in this paper, for each tool in Section \ref{sec:toolsreview} it is specified if the developers have taken into account the construction of ISPs, or even if they give some guidelines for building them.

This situation leads to a need of protecting the organisation's side, but also the users' side, making non-interfering easy-to-follow ISPs, and leaving them to use their devices for personal purposes while working, without putting organisation's information assets under risk. The compliance of these requirements would compose an End-to-End Security Solution (protecting both enterprise and employee), which is the motivation of the commented tools and, as presented in Section \ref{sec:muses}, is the aim of the MUSES project.

%------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TOOLS REVIEW  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------------------------------------------------------

\section{Tools for corporate mobile security}
\label{sec:toolsreview}

Now that BYOD philosophy is becoming a tendency, a number of tools appeared by now, and others are under development but expected to be released soon. They were specifically designed for Chief Security Officers (CSOs) and Chief Information Security Officers (CISOs) to secure, monitor, and act over smartphones and other personal mobile or portable devices, when they become too risky. Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}). The present section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.

% Don't completely like the intro for being too focused to MUSES.

%----------------------------------------------------------------------------

\subsection{IBM Hosted Mobile Device Security Management}
\label{subsec:ibm}

One of the first companies who supported the BYOD model was IBM in 2011 \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace. To help organizations \cite{ibm11} embracing both company and employee owned mobile devices (as said, this practise is part of the BYOD model) in a security-rich environment, IBM developed a mobile device security management solution. For IBM, a mobile security strategy should focus on several key areas.

Thus, the organization should identify which business data the strategy will allow to be stored and processed on which mobile devices. This helps to determine what needs to be protected and to what degree. Then, since different mobile platforms have different native security mechanisms, the organization needs to define which mobile device platforms will be allowed in the business environment and, thus, which need to be supported in the mobile security strategy and plan. That means, to define the scope of the security plan. Also it is needed to decide the responsibility for mobile security management work, whether using the current IT security team to handle mobile devices, or outsourcing them to a managed security service provider. And no matter what the mobile environments are, a number of mobile ISPs and best-practise procedures need to be put in place and should also be identified in the company's mobile security strategic plan.

Taking into account these considerations, IBM developed a framework that specifies security domains and levels for applying various security technologies. When applied to mobile devices (not portable ones, so that laptops are not considered), the features of this framework depend on the deployment:

\begin{itemize}
	\item \textit{Identity and access}: Not only the use of strong passwords when accessing the devices, but also supply two way authentication and VPN access control, by supervising the authorised IP addresses and adding re-authentication for accessing resources (assets) with high value.
	\item \textit{Data protection}: Data security stored in the devices, related to professional life, is encrypted, also during the transmission. Moreover, when a device is lost, data can be removed remotely, and the device located or locked out (locking out a device is also made after a modifiable timeout). Finally, back ups are performed periodically once the device has been recovered.
	\item \textit{Application security}: This is related to the requirement of being connected from a controlled location for authorising the download of business applications, and those applications must be certified (also the currently running on the device). Actually, IBM's tool can monitor and remove applications which are identified as untrustworthy or unsafe.
	\item \textit{Fundamental integrity control}: Running both anti-malware software and personal firewall, and making the result of these tests as dependency for VPN's intranet access. 
	\item \textit{Governance and compliance}: Taking into consideration the mobile security as an important point in the overall risk management program of the company, and extend the periodic security audits to mobile devices too.
\end{itemize}

This solution is based on a client-server architecture, where the controlling center is placed in the server, and the client would be installed on the mobile devices. This way, the client/device would communicate with the server as regularly as possible, to enforce policies, execute commands, and report status. With these features, and by analysing in the server the incoming data from the devices, this IBM's solution would be able to help enterprises to support ISPs compliance and to recognise (consequently acting over) mobile threat landscapes.

%Regarding IBM hosted mobile device security solution's architecture, the solution is built on a sound client-server architecture in which the server centrally controls and manages security policies and settings for various security features. The client would be installed on the mobile device and regularly communicate with the server to enforce policies, execute commands and report status. Also, IBM's solution contains reporting and analysis capabilities, with information that helps the company to support ISP compliance, recognize the mobile threat landscape and evaluate the solution's effectiveness in countering threats.

%----------------------------------------------------------------------------

\subsection{Sophos Mobile Control}
\label{subsec:sophos}

Sophos is a company founded in 1985 focused on IT security and data protection for businesses. Their \textit{Mobile Device Management} main product \cite{Sophos_tool} is Sophos Mobile Control. It is oriented to IT administration for mobile devices, trying to offer to the users the possibility of choosing the delivery model to suit their needs, i.e., between on-premise and Software as a Service (SaaS).

The tool offers the possibility of managing all workers and co-workers smartphones and tablets from a single-based console. The console monitors the devices throughout their full life cycle: from the initial set up and enrolment, right through to decommissioning. Other features are similar to IBM's product, adding some new like being able to connect to an existing user directory using Lightweight Directory Access Control (LDAP)\footnote{LDAP is an application protocol for accessing and maintaining distributed directory information services over an Internet Protocol (IP) network.}.

Additional security is provided by the incorporation of \textit{Malware and Web protection}, so that the user does not need to install anti-malware software by him or herself. Regarding the compliance enforcement, the main goal is not to sacrifice company's security in favour of flexibility for the users, which has been demonstrated \cite{SecPolPenalty09} that could result in bad (unwilling or not) users' behaviour. Thus, company's BYOD initiative should include an acceptable use policy to ensure the users are aware of any measures the company may take if a device breaches any ISPs. Sophos aims to reach this by doing three main tasks: First, by enforcing IPSs, i.e. allowing setting up user and group-based security policies separately. The security settings can also vary from one platform to another, thus looking to support all of them is necessary to set task bundles and individual actions for many different violations. Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of a breach. For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe may be the chosen option. As previously stated, the actions vary for each platform, but the most common platforms such as Android and iOS allow blocking email access, notifying the admin, performing a remote lock or wiping, locating a device using 3D maps, triggering a remote alarm, transferring a task bundle combining a number of actions, and Sophos's solution adds the possibility of trigger a scan. Finally, compliance check, i.e. though some of the most widely used features include allow or disallow root rights or jailbreaking, require encryption, and whitelist or blacklist apps. Sophos also allows disabling malware apps, setting maximum intervals since last \textit{Mobile Security scan}, and allowing or disallowing suspicious apps and potentially unwanted apps (named PUAs).

Then, the Enterprise App Store included in Sophos Mobile Control allows the company to supply the users with recommended and/or required apps directly on their devices. Both company's in-house and app store apps are suggested directly on the user's mobile device, so they can click to trigger the installation. Also, for keeping the employees working without increasing the burden for the IT department, the self-service portal built-in included in Sophos's solution has many features. Among others, it shall be mentioned that, wanting the employees to use their personal devices at work, they can register them (with a provided step-by-step process) and agree to an acceptable company-defined use policy. All profiles, including email access, would be available after registration, and the portal may be accessed from any PC with Internet access, or even from a mobile device itself. Furthermore, when a device is eventually stolen, users can choose to remotely locate, lock or wipe their devices and reset their passcode without having to contact the company help desk. From the company side, they can define which features are available in a self-service portal from the administrator console.

%----------------------------------------------------------------------------

\subsection{Samsung's Knox Mobile Security Suite}
\label{subsec:samsungknox}

As part of its SAFE (Samsung for enterprise) brand, Samsung revealed at the Barcelona Mobile World Congress 2013 the Knox application \cite{Samsung_tool}, which was expected to be available on its last Galaxy smartphone generation. The solution is available since December 2013.
The main feature of this security package is the use of different containers, or environments, for business and personal sides. Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
There will be needed introducing a password to enter into the business side and, once \textit{logged in} this container, no more passwords will be required for the business applications. The applications approved by the company IT department must meet Samsung's security standards and allow single sign-on. A Knox API will also be provided for the company to be capable of accessing over almost 205 predefined IT policies (the SAFE API grows this number to 475). Also, Knox would allow different VPNs for individual apps.
Regarding the information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files. In the same way, the user won't be able to share data between the two environments, e.g. creating separate contact lists so the user cannot send a contact from one side to the other, or if the user copies data to the clipboard in the Knox container, it won't be there in the personal container.

There are three main components in the device architecture:

\begin{itemize}
	\item \textit{Customizable Secure Boot}: This ensures that only verified and authorized software can run on the device. It is a primary component that forms the first line of defence against malicious attacks on devices with Samsung KNOX. In addition, Samsung Knox's Secure Boot technology allows the switch of the secure boot root certificate in a secure manner after the devices are shipped.
	\item \textit{TrustZone-based Integrity Measurement Architecture (TIMA)}: By a continuous integrity monitoring of the Linux kernel, it is possible to detect that the integrity of the kernel or the boot loader is violated, and to take a policy-driven action in response. One of these policy actions disables the kernel and powers down the device.
	\item \textit{Security Enhancements for Android}: This feature is the one referred to the separation of information based on confidentiality and integrity requirements. It isolates applications and data into different domains so that threats of tampering and bypassing of application security mechanisms are reduced while the amount of damage that can be caused by malicious or flawed applications is minimized.
\end{itemize}

It is important to take into account that if an enterprise decides to deploy this solution to secure its BYOD environment, it must yet work with certain Mobile Device Management (MDM) services, either cloud or server based. Samsung offers a list\footnote{\url{https://www.samsungknox.com/en/knox-mdm-feature-list}} of the MDM which Knox supports, each one with the number of supported policies.

%----------------------------------------------------------------------------

\subsection{Good's Bring Your Own Device solution}
\label{subsec:goodsbyod}

Good Technology is a company that was founded in 1996 in California. The philosophy followed by Good is similar to Samsung's Knox one: to create a secure container that places an unreachable partition between personal and business data in order to protect company's assets. The solutions that they offer \cite{Good_tool} are similar than the previous ones. They have focused in mobile (not laptops) devices, though they support a different of Operating Systems (OSs), and in separating personal and company data. A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, PIM, calendar), intranet, and in-house or third-party mobile applications. Finally, Good offers best practise recommendations to help the company's BYOD policies such as reimbursements and stipends. There is a document available at Good's webpage\footnote{\url{http://www1.good.com/mobility-management-solutions/bring-your-own-device}} which contains several questions about Information Security Policies and how to cope with all of them.

%----------------------------------------------------------------------------

\subsection{BlackBerry Balance}
\label{subsec:blackberrybalance}

This security package was announced as a feature of BlackBerry 10 \cite{Blackberry_tool}. Nevertheless, it is available with BlackBerry Enterprise Service 10, which is a device management, security and app management for BlackBerry, iOS and Android devices. It is necessary to activate BlackBerry Balance for having available some security features, all related or similar to the aforementioned. For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps. Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.

On the other side, employees are able to access information and applications related to their personal lives, while staying connected to important work information when they need to perform. Finally, another known feature is also offered by Blackberry, so if the device gets lost or is stolen, or if the employee leaves the organization, there will be an option to wipe just work information which can be done remotely.

%----------------------------------------------------------------------------

\subsection{Android Work}
\label{subsec:androidwork}

This tool is the Google's approach in the mobile enterprise security area, and  will run on Android 5.0 ``Lollipop''. It follows the idea of containers, previously presented in the Samsung Knox description. Thus the container will be used to manage (encrypted) corporate data, and also to restrict what the users can do with them, but the environment will be as usual, i.e. there will not be a separate workspace for doing this.

This system will be strongly related with the Google Play market, as the applications will be `categorized' as \textit{managed}\footnote{ A concept previously introduced in Apple devices}. Thus Android Work will provide the CSOs with a tool to define which apps would be managed, i.e. which ones could be installed by the users and considered as corporate-related applications. Moreover the enterprise IT department could define specific security policies on these apps, in addition to the inherent protection that the container provides.

Several enterprise-security aimed applications will be offered in the market, so the IT would decide which ones will be installed (even as a bundle) in the employees' devices, and also, they can manage the updates of these apps, in order to ensure that all the employees are up to date. For instance one app could manage the creation of personal/work profiles, so the user just could access corporate assets after login in into the app.

Thus, the system will provide a framework for IT staff to manage business devices but also, importantly, personal devices being used in a BYOD context (The CSO would give you an activation code in order to `connect' the smartphone to the enterprise and use this Android Work).
Thus, IT admins will be able to specify which Google Play apps will be available for users to install through this work profile, including being able to provision apps to specific individuals or groups (inside the company).

In addition to the work profiles, there will be considered other high-level ones with the ability to administrate the device from the corporate-security point of view, or as the owner, with all the privileges on the device.

%----------------------------------------------------------------------------

\subsection{Other tools}
\label{subsec:othertools}

There have arisen several other corporate-security aimed tools inside the BYOD philosophy, such as:

\subsubsection{WSO2 - Enterprise Mobility Manager \cite{WSO2_tool}}
An open source platform aimed to manage the corporate and personal mobile devices in the enterprise. Its main features are:
\begin{itemize}
\item Mobile Device Management: a console to manage the corporate/personal devices, adding policies online, role-based permissions, etc.
\item Mobile Application Management: tool designed to manage the apps to be enrolled on the system (in the devices).
\item Enterprise App Store: specific apps for the enterprise environment.
\item Mobile Data Security: containerization and encryption of data.
\end{itemize}

\subsubsection{Blackphone  \cite{Blackphone}}
A phone designed to be used as a corporate device (in addition to personal uses). It includes an own OS, named PrivatOS, including useful tools to this end. The features of this OS are:
\begin{itemize}
\item It is built on Android.
\item It uses anonymous searching.
\item It includes a few bundled apps, all of them privacy-enabled.
\item It lets a smart disabling of all Wi-Fi connections except trusted hotspots.
\item It permits a fine-grained control on app permissions in a single interface.
\item It offers a total control on private calls, texting, video chat, file exchange (up to 100MB), browsing, and conference calls.
\item There are frequent security updates from Blackphone directly.
\item It permits an anonymous remote wipe and anti theft (in Android it requires use of centralized cloud account).
\end{itemize}

\subsubsection{Azzurri - Icon Mobilise \cite{AzurriMDM}}
It is a cloud-based service to manage enterprise devices from the BYOD point of view (protecting sensitive corporate data and also letting the users enjoy them privately), by outsourcing the management of those devices to Azzurri. 
\begin{itemize}
\item It offers a centrally deployment, administration and securing of all mobile devices regardless of their OS.
\item It manages and enforces security policies `over the air' for both corporate and employee owned mobile devices.
\item It does it by enforcing passwords and providing mechanisms for remote lock.
\item It offers the ability to wipe/selective wipe corporate data email/contacts on the device if lost or stolen.
\end{itemize}

\subsubsection{Citrix - XenMobile}
It is a tool implemented with Worx App SDK \cite{WorxSDK}:
\begin{itemize}
\item It Includes the concept of framework-enabled app.
\item There can be defined fine-grained policies associated to the apps by means of a specific graphical user interface.
\item It offers a dedicated micro VPN to connect to Citrix-protected backend services.
\item All Worx-enabled apps can interact with each other for a seamless experience. It covers native and HTML5 apps.
\item It separates business and personal applications inside a secure mobile container.
\end{itemize}

Once the main tools and systems in this area have been introduced, in the following section our own system (still in development) is presented, giving an overview on its general architecture. Moreover we devote a subsection to describe its main features: the use of Data Mining + Machine Learning techniques, and also its self-adaptation ability using Computational Intelligence methods, which compose the real difference with all these tools.

%----------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   MUSES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------

\section{Multiplatform Usable Endpoint Security System}
\label{sec:muses}

The MUSES system overview is presented in Figure \ref{fig:system_overview}. As it can be seen, in this system, the user interacts with the devices, own or corporate, through the MUSES graphical interface inside his or her own context (situation, connection, status).

\begin{figure}[ht]
\centering
\includegraphics[scale=0.2]{img/system_overview.eps}
\caption{MUSES system overview. Conceptual model designed by S2 Grupo.  http://www.s2grupo.es/.\label{fig:system_overview}}
\end{figure}

As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}. The first one monitors the environment (context) and the user's behaviour, translating his/her actions into a sequence of events. These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module. Then, a decision is taken in the corporate security operations centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context. The corresponding feedback is communicated to the user through the \textit{actuator}, which is also in charge of triggering the recommended actions to stop the user's or application's doings, in case it is required.

The designed MUSES architecture is shown in Figure \ref{fig:architecture}. It is a \textit{client/server} approach in which the \textit{client} program will be installed in every user's mobile or portable device, independently of the platform (operating system and type of device). The \textit{server} side would be installed in the corporate SOC. Both sides are connected through a secure channel (using HTTPS) over Internet. In that figure just the high-level components in each part are shown, along with the information flows labelled as 'Info XX'.

\begin{figure}[ht]
%\begin{center}
\hspace{-0.7in}
\includegraphics[scale=0.45]{img/architecture_modules.eps}
%\includegraphics[scale=0.45]{img/muses_architecture.eps}
\caption{Design of the MUSES architecture (art by S2 Grupo). \label{fig:architecture}}
%\end{center}
\end{figure}

The rationale for this approach is based on two main reasons: 1) there is need for a high computational power in order to perform the event correlation and self-adaptation processes, so a quite powerful machine should be used (server); 2) there are two clearly separated parts in the system, namely the users (client) and the enterprise (server).

The system considers two working modes for every device: online and offline. In the \textit{online} mode the device can connect with the MUSES server, so it can request the server to make a decision. On the other hand, in \textit{offline} mode the server cannot be reached by the device (there is not an available connection between them), so all the decisions should be made locally.
This will be done using an up-to-date copy on the Decision Table inside the Local database, which will contain decisions for any type of detected event, along with default actions to be performed if no rule is met. Anyway, in this mode, the gathered information by the sensors in the device will be stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
Moreover, when switching from offline to online mode, the device will receive an updated copy of the Decision Rules (the so-called Device Policies), as a kind of antivirus database, in order to work again perfectly in offline mode (if the connection is lost).

All data in MUSES will be encrypted.

% ----------------------------------------------------------

\subsection{Client/Device architecture}

There are three main components in this side:
\begin{itemize}
 	 \item \textit{Local Database}: it is a local security-based storage, which includes the set of security rules to be applied locally (Device Policies), user authentication data, and a cache of gathered events and information. The latter will be useful when the device is in offline mode, so these data are stored to be later submitted to the server side. 
%It contains the so-called \textit{Decision Table}, a set of rules in which the antecedents are high-level events, and the consequents are the corresponding decisions/actions, namely `allow', `deny' or `request' (the decision must be made in the server side).
 	 \item \textit{Device Monitor (MusDM)}: module which gathers the events and information produced by the user. It also acts following the decisions made by the system, in order to allow or deny the controlled application (or the user) for doing something. It is composed by a monitoring and an actuator submodules.
 	 \item \textit{Access Control System (MusACS)}: module in charge of making the decisions considering the gathered data. These decisions can be made locally (if possible), or can be requested to the server (if there is no rule which matches with the occurred events).

%The subcomponents are the \textit{Decision Maker}, which performs the decision process; the \textit{User, Context, Event Handler}, which processes the events and information to be used for making the decision or stored for further submission (depending on the mode and on the gathered data); and the \textit{Security Policy Receiver} that updates the set of decisions (or Device Policies) in the Decision Table with those received from the server side, after an update or decision process.
\end{itemize}

The rest of the components are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides. 
In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring and acting). This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API will be defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}. On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with. Usually it will be accessed through the operating system (OS). So the type of information to gather from them and also the type of actions to do over them will vary depending on the OS. In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user). This is due to the usual forbiddance or limitation of interactions with other applications that the OSs have.

% ----------------------------------------------------------

\subsection{Server architecture}

As in the client, there are three main components:
\begin{itemize}
	 \item \textit{System Database}: it stores all the information that the system will manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (regarding the security policies).

	 \item \textit{Continuous Real-Time Event Processor (MusCRTEP)}: this component is the core of the MUSES system with respect to the decision making process. It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{EventProcessing_Luckham02,SurveyEventCorrelation_Tiffany02}, gathering the set of occurred events and doing a rule-based threat identification. The output of this module is taken by the \textit{RT2AE}, which also considering information such as trust data and profiles, assets' values, user reputation, or opportunity, performs a risk and trust analysis task \cite{RT2AE_SOTICS13}, and extracts the set of potential rules to consider in the analysed situation. Then, these rules are transformed into decisions (or Device Policies) and submitted to those devices to which they apply.

	 \item \textit{Knowledge Refinement System (MusKRS)}: this module is in charge of analysing the information stored in the system database, identifying relevant data, such as important patterns, key features, or security incidents. These are later processed for tuning up the existing set of rules or for inferring new ones.

\end{itemize}

There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company's chief security officer (CSO) to define and manage Security Policies and Rules in a friendly way. It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values. The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system. The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, user-related, etc) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task). Finally, there is another \textit{Connection Manager} which controls the communication with the device side.

% ----------------------------------------------------------

\subsection{Self-Adaptation in MUSES: The Knowledge Refinement System}

As previously stated, one of the main features of this system will be the self-adaptation (to the user and context), of the set of Corporate Security Rules (specification of the ISPs), that it will be able to perform. 
To this end, the \textit{MusKRS} module will be run asynchronously in the server (once a day or every X hours) and will be in charge of analysing all the gathered information (events, context, user-related data), and adapting/refining the security rules. The refinement (improvement) will have as aim to better deal with these events, optimizing the current set of rules (removing redundant or non-useful rules, for instance), and even trying to predict future threats due to the user's behaviour.

This procedure will be composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process will be performed (in the \textit{Data Miner} sub-component);  second, a refinement and inference process will be done (in the \textit{Knowledge Compiler} sub-component), considering the data `extracted' in the first step, by means of Computational Intelligence (CI) techniques.
It should be noticed that part of the refinement (or adaptation) of the security rules will be made using simpler methods, such as generalisation or specialisation of rules, for instance. Then, other parts of the process would be conducted using CI.

Another important fact is that MUSES will count with a human controller, normally the Chief Security Officer (CSO) of the company, who will supervise the system activity by means of logs or feedback messages. Thus, adapted and inferred security rules will not be, in principle, directly added to the current set of rules. Instead, they will be proposed as draft rules to this controller, in order that he/she will accept them if they are interesting and correct. It is planned that the system will be able to `learn' from this decisions so, after a so-called training or `warm up' period, the rules would be directly accepted (included in the set) or rejected autonomously by the MusKRS.

The following sections describe these processes: first focusing on DM techniques to be used both automatically by the MusKRS, and as a kind of decision-aid/monitoring tool for the CSO; second, the CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches, since these methods perform very well, and have been widely used in security-based environments for solving security issues, such as the intrusion detection \cite{GA_intrusion-majeed}, the design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.

% ------------------------------------------------------------------
%
\subsubsection{Data Mining + Machine Learning}
\label{subsubsec:dm_ml}

This task will be performed by the \textit{Data Miner} module. It will take the `raw' data from the database and will process the information, in order to yield a set of relevant data for the Knowledge Compiler module or for the human controller. In the first case, this sub-component will take them as a reference in order to refine or adapt the current set of security rules (for instance, to deal with anomalous situations).

The process will be mainly non-supervised. Moreover, eventually, the datasets can be huge (depending on the company's data flows), so Big Data processing methods \cite{BigData_11} will be applied.

The DM/ML techniques will process the so-called patterns, which in this context correspond to events (and their related information) produced by the users' interactions with the system. As stated, these events will be captured by the sensors in the users' devices and transmitted to the server to be processed and stored in the system database. The methods to be applied are:

\begin{itemize}

\item \textit{Pattern Mining} \cite{PatternMining_Han07}: 
This process will try to identify frequent or, on the contrary, anomalous patterns, in order to process them lately. The idea is that non-frequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO or to serve as a reference for the rule-refinement process.

\item \textit{Classification} \cite{classification_67}: 
This technique tries to train a model (classifier) able to associate every pattern in the dataset to a class, so that the model could be used for assign a class for further incoming patterns with an unknown category.
For instance, it could look for events (patterns) that had been previously  marked as `allowed' or `denied' (according to the ISPs). When a new event arises, if it has not an assigned decision, the classifier should provide one based on the similarity with previous (and already labelled) patterns.

\item \textit{Clustering} \cite{Clustering_Jain99}: 
The aim of this method is grouping the patterns considering some similarity criteria, in order to manage them as a set. This could be used for providing data visualisation mechanisms, in order to make it easier to interpret the data interaction and the distribution in clusters with respect to the different properties/features of the patterns.

\item \textit{Feature Selection} \cite{FeatureSelection_Guyon03}: 
It consists on extract the most important features/variables from the data. This could be useful if we want to discard non-key features, which could be interesting in order to reduce the database weight, for improving the performance of other techniques (such as classification or clustering), and even to improve the performance of whole the system, since less information would be gathered and transmitted.

\item \textit{Data Analysis}: 
This will provide the CSO with mechanisms to visualise interesting facts about the data, such as more frequent events, dangerous or suspicious users (according to their behaviour), more triggered rules, etc.

\end{itemize}

%\pagebreak

% ------------------------------------------------------------------
%
\subsubsection{Computational Intelligence: Evolutionary Computation Methods}
\label{subsec:ci}

MUSES will use different EC approaches, initially, two in the DM/ML part of the process, and three in the rule-refinement/adaptation phase. They are based in Genetic Programming (GP) \cite{GP_Koza92}, and Genetic Algorithms (GAs) \cite{GAs_Goldberg89}.

The first evolutionary-based approach will be a \textit{GP-based classification} method. This will be useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems inside real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features/variables and information gathered from the events take these kind of values.

Thus, this approach will be able to manage unbalanced datasets considering a fitness function in which a cost can be associated to the classifier accuracy at every epoch, having a penalty cost when the classifier makes a false negative (an element from the minority class which is classified as belonging to the majority class) \cite{cost_adjustment_07}.
Regarding the type of data, since GP algorithms can manage rule- or tree-based models, it will work perfectly with any categorical variable, yielding a good classifier as it has been made in other works (such as the aforementioned \cite{cost_adjustment_07}).

The second approach will be a Feature Selection process, conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features/variables in the classification. Thus, the algorithm can optimize the group of features to be considered in the classification task, improving both the computational time of this task and also the obtained accuracy of the method.

The second set of EC techniques are, as stated, part of the rule-refinement (or adaptation) process, to be performed by the \textit{Knowledge Compiler} module. These methods will be used for inference and optimisation, and will consider this data as a part of the process:

\begin{itemize}

\item The information extracted from the Data Miner sub-component, mainly concerning the anomalous, unclassified or misclassified patterns. These are those patterns which did not match with any of the existing classes (they are quite different from the patterns belonging to those classes), so they cannot be included in any of the classes and thus they should be taken into account for a potential inference or update in the set of security rules, in order to `cover' them.

\item User-related information corresponding to those anomalous or unlabelled patterns (events). Thus, the user's ID, location and role, for instance, will be considered in order to select the applicable set of rules for that conditions.

\item Context information for the same patterns, in order to also restrict the applicable set of rules considering this information.

\end{itemize}

Another useful information to consider in the refinement/ adaptation process will be:

\begin{itemize}

\item Risk information extracted from the user profile (reputation), e.g. "Did the user received a lot of `denies'/`allows' before?", i.e. "Is he/she trustworthy?". In case the user is not, more restrictive rules would be created for him, otherwise the corresponding rules could be `relaxed' for that user.

\item The information stored in logs along the system, which can, for instance, tell about how the user responds to system messages (either an action or if he gives feedback). This could result in the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignore warning messages.
Moreover, important log information regarding the parameters used or the decisions made in the different modules will be used for further tests of new inferred rules, as it is explained below.

\end{itemize}

Given this, the approaches that will be implemented are:

\begin{itemize}

\item \textit{GP rule inference} method, which will generate/create new rules in order to `cover' those situations non contemplated in the current set of rules. Thus, for instance, a new rule could be created in order to deal with the patterns to which the classifier could not assign a class.
The generation will be done considering the so-called \textit{dictionary}, i.e. a set of terms corresponding to all the possible inputs and actions in the system, which will be antecedents (conditions) and consequents in the security rules to be inferred.
The evaluation of these rules will be done considering the stored log information concerning the parameters along with the actions/decisions made in every component in the system. Thus, it will be possible to `simulate' the whole  system behaviour when the new rule is included and get a value of its performance.

\item \textit{GP rule refinement} approach, which will optimise the current set of rules, adjusting the values in the conditions (antecedents), for instance. Thus, some superfluous parts on the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
The evaluation (of the whole set of security rules) will be done considering the number of unlabelled patterns that will be `covered' after the adjustments.

\item \textit{GA optimisation} algorithm for setting up and adapting the assets' values. These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
If it is possible to evaluate the partial solutions proposed by the GA, this approach could be very useful for the CSO (who is in charge of assigning and adjusting these values over time).
The adaptation or adjustment concerns the change in value that an asset could have due to a loss of importance, once an event has passed (a project presentation, for instance).

\end{itemize}

%----------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   COMPARISON  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------

\section{MUSES Advantages over Other Solutions. Beyond the State of the Art}
\label{sec:comparison}

MUSES is mainly a free, open-source, platform independent solution, so these set of features make it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition most of the existing tools take into account only smartphones and tablets, but MUSES also will cover laptops and company PCs too, thus, it is not only for BYOD. Moreover the companies which desire work with those systems need specific operative system and server (such as Windows Server, for instance), being even more strict in some cases, as in Samsung Knox, in which companies must work with a specific (though they can choose from a list) MDM service for being able of deploy Knox in their environments, or in the use of the Blackphone. MUSES will be a good solution in these cases, since it will be a multiplatform system.

Another comparison concerns that the existing products are mostly policy-based, but MUSES makes its decisions not only considering policies, but also based on the terminals/users context (location, connected networks and so on), to really understand the real danger of a specific action, i.e. it adds a Risk Analysis Process (performed in the RT2AE).

Also related to this issue, a very big plus of the MUSES system (not present in the other solutions) is its self-adaptivity power. Thus, MUSES is able to adapt to changes, either regarding corporate security policies, newly discovered vulnerabilities or threats, different environments of use, or user profiles.

Moreover, another clear advantage over the rest is that MUSES can work in two connection modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.

Though these are clearly advantages of MUSES over the aforementioned products, they also establish a progress beyond the state of the art with respect to the existing solutions. Other issues that MUSES aims to progress on are related to risk and trust data analysis, human-computer interaction (or HCI), device monitoring, and legal compliance.

First, as mentioned previously, it will implement a self-adaptive event correlation, including a novel hybrid technique of rule refinement and rule adjustment extracting relevant information from processing huge amounts of data. Then, the project defines a new approach to risk management taking into account threats (with their costs) as well as the innovative concept of opportunity, i.e. the following beneficial outcome from a situation on which, for instance, a user is able to work while waiting at the airport if risk is low enough.

About HCI and usability of mobile devices, this will set up a significant advance in the state of the art because of the novelty of the BYOD philosophy, and trying to look for individual differences among the users in susceptibility to persuasive strategies for secure behaviour. Regarding device monitoring, MUSES will also take into account the so-called context observation, by which private or professional scenarios will be detected, or predicted, based on advanced machine learning techniques. Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it will contribute to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.

With regard to the scientific contribution of the system, one of the main differences with respect to previous works is the consideration of security threats `brought' by the user's behaviour inside the system, i.e. through interaction/events, rather than more general and external threats. Moreover, the techniques to be used in MUSES will work with real data (in a real system), as a difference to several research works (they consider simulated or artificial data).

Data Mining techniques have been used by the authors in some works, but usually aiming for a specific general objective, for instance the detection of threats (botnet) \cite{botnet_detection_clustering_09}, or the recognition of anomalies \cite{feature_selection_anomalies_08}, but they are not linked with a following process to improve the system (the refinement phase in MUSES).

There are some proposals in which security policies are inferred or refined \cite{inferring_policies_socialnetworks_09,policy_generation_clustering_10}, but they do not affect the ISPs as in MUSES, and they are not based in the user's behaviour in order to do this.

Genetic Programming has been previously used by several authors \cite{rule_generation_gp_09,sec_policy_evolution_gp_08}, even for creating new policies or rules in a security-aimed sense, but they do not affect the ISPs and moreover, our proposed evaluation functions (completely integrated in the system) for the refinement and inference approaches are novel.

With respect to Genetic Algorithms, they have been extensively used in this scope in the literature, mainly for the detection of anomalies and intrusions rather than for optimisation, as in our case. However, there are some examples that could be used as model for our approach, such as \cite{EAs_securitycosts-kirta,risk_reduction_ga_12}.

%*** Features:
%Concept of framework-enabled app (Citrix' Worx-enabled apps == MUSES-aware app)
%
%*** Azzurri includes several of the MUSES features

%----------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   CONCLUSIONS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------

\section{Conclusions}
\label{sec:conclusions}

In this work, there is introduced a self-adaptive user-centric end-to-end system, named MUSES, which is in development (it will be launched next year). The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.

MUSES has been compared with other existing solutions/tools with a similar aim: to ensure the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
The main advantages of MUSES with respect to the other solutions have been discussed, also remarking its advances beyond the state of the art that define these tools.

In addition, a scientific comparison between the techniques used in the presented system and those in the literature, in the same scope, has been done.

We can conclude that MUSES offers several advantages over the existing tools, both the some of its `technical' features, but also in the application of Data Mining, Machine Learning and Computational Intelligence methods to the events gathered by the system (users' behaviour), in order to adapt or refine the set of security rules.

Anyway, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  ACKNOWLEDGEMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}
This paper has been funded in part by European project MUSES (FP7-318508), along with Spanish National project TIN2011-28627-C04-02 (ANYSELF), and GENIL PYR-2014-17, awarded by the CEI-BioTIC UGR.

\bibliographystyle{elsarticle-num}

% Antonio - Poner la bibliografía en fichero .bib

\begin{thebibliography}{00}

%\bibitem{ids13}
%Sommestad T., Hunstad A.. \emph{Intrusion detection and the role of the system administrator.}, from Swedish Defence Research Agency (FOI), Linköping, Sweden, 2013.

%\bibitem{m2m12}
%NTT DOCOMO, \emph{DOCOMO to Launch Global M2M Platform}, in M2M Magazine, December 2012.
%http://www.machinetomachinemagazine.com/2012/12/05/docomo-to-launch-global-m2m-platform/.

%\bibitem{suites12}
%The Radicati Group Inc., report \emph{Microsoft Office 365 - Analysis and Forecast, 2012-2016}. June 2012.

\bibitem{Adams_Users05}
Adams, A. and Sasse, A.:
\newblock {\em Users are not the enemy}.
\newblock Security and Usability: Designing Systems That People Can Use.
  O\'Reilly Associations, 2005.

\bibitem{cost_adjustment_07}
Alfaro-Cid, E., Sharman, K. and Esparcia-Alcázar, A.I.:
\newblock A genetic programming approach for bankruptcy prediction using a
  highly unbalanced database.
\newblock In M.~Giacobini, editor, {\em Applications of Evolutionary
  Computing}, volume 4448 of {\em Lecture Notes in Computer Science}, pages
  169--178. Springer Berlin Heidelberg, 2007.

\bibitem{AzurriMDM}
Azurri Communications.
\newblock Icon Mobilise.
\newblock \url{http://www.azzurricommunications.com/~/media/Resources/Brochures/Media/icon_mobilise_brochure_online.ashx}

\bibitem{SecPolComp12}
Al-Omari, A., El-Gayar, O., Deokar, A., and Walters, J.: \emph{Security Policy Compliance: User Acceptance Perspective}. 45th Hawaii International
Conference on System Sciences (pp. 3317-3326). IEEE, 2012.

\bibitem{BYOD13}
Bacik, S.: \emph{Security Implications of Bring Your Own Device, IT Consumerization, and Managing User Choices}, in Information Security Management Handbook, Sixth Edition, Volume 7, pp. 133-142, 2013.

\bibitem{EAs_Back96}
Back, T.:
\newblock {\em Evolutionary algorithms in theory and practice}.
\newblock Oxford University Press, 1996.

\bibitem{MachineLearning_Bishop06}
Bishop, C.:
\newblock {\em Pattern recognition and Machine Learning}.
\newblock Springer, 2006.

\bibitem{Blackberry_tool}
Blackberry.
\newblock Blackberry balance.
\newblock \url{http://es.blackberry.com/business/software/blackberry-balance.html}

\bibitem{Blackphone}
Blackphone.
\newblock \url{https://www.blackphone.ch/}

\bibitem{SecPolComp10}
Bulgurcu, B., Cavusoglu, H., and Benbasat, I.: \emph{Information security policy compliance: an empirical study of rationality-based beliefs and information security awareness}. MIS Quarterly, 34(3), 523-548. 2010.

\bibitem{botnet_detection_clustering_09}
Chang, S. and Daniels, T.E.:
\newblock P2P botnet detection using behavior clustering \& statistical tests.
\newblock In {\em Proceedings of the 2nd ACM Workshop on Security and
  Artificial Intelligence}, AISec '09, pages 23--30, New York, NY, USA, 2009.
  ACM.

\bibitem{SecPol09}
Cresson Wood, C. and Lineman, D.: \emph{Information Security Policies Made Easy Version 11}. Information Shield, Inc. 2009.

\bibitem{inferring_policies_socialnetworks_09}
Danezis, G.:
\newblock Inferring privacy policies for social networking services.
\newblock In {\em Proceedings of the 2Nd ACM Workshop on Security and
  Artificial Intelligence}, AISec '09, pages 5--10, New York, NY, USA, 2009.
  ACM.

\bibitem{Good_tool}
Good's Technology.
\newblock BYOD Solution.
\newblock
  \url{http://www1.good.com/secure-mobility-solution/bring-your-own-device.html}

\bibitem{GAs_Goldberg89}
Goldberg, D.E.:
\newblock {\em Genetic Algorithms in search, optimization and machine
  learning}.
\newblock Addison Wesley, 1989.

\bibitem{FeatureSelection_Guyon03}
Guyon, I.,  and Elisseeff, A.:
\newblock An introduction to variable and feature selection.
\newblock {\em J. Mach. Learn. Res.}, 3:1157--1182, 2003.

\bibitem{PatternMining_Han07}
Han, J., Cheng, H., Xin, D., and Yan, X.:
\newblock Frequent pattern mining: Current status and future directions.
\newblock {\em Data Min. Knowl. Discov.}, 15(1):55--86, 2007.

\bibitem{SecPolPenalty09}
Herath, T., and Rao, H.R.: \emph{Protection motivation and deterrence: a framework for security policy compliance in organisations}. European Journal of Information Systems, vol. 18, pp. 106-125, 2009.

\bibitem{IBM_tool}
IBM.
\newblock Hosted mobile device security management.
\newblock
\url{http://www-935.ibm.com/services/us/en/it-services/managed-security-services-cloud-computing} \url{ -hosted-mobile-device-security-management.html}

\bibitem{Clustering_Jain99}
Jain, A.K., Murty, M.N., and Flynn, P.~J.:
\newblock Data clustering: A review.
\newblock {\em ACM Comput. Surv.}, 31(3):264--323, Sept. 1999.

\bibitem{imbalance_techniques_02}
Japkowicz, N. and Stephen, S.:
\newblock The class imbalance problem: A systematic study.
\newblock {\em Intell. Data Anal.}, 6(5):429--449, Oct. 2002.

\bibitem{ibm11}
Kao, I-L.: \emph{IBM Security Services. Securing mobile devices in the business environment}, IBM, 2011.

\bibitem{feature_selection_anomalies_08}
Kloft, M., Brefeld, U., D\"{u}essel, P., Gehl, C. and Laskov, P.:
\newblock Automatic feature selection for anomaly detection.
\newblock In {\em Proceedings of the 1st ACM Workshop on Workshop on AISec},
  AISec '08, pages 71--76, New York, NY, USA, 2008. ACM.

\bibitem{GP_Koza92}
Koza, J.~R.:
\newblock {\em Genetic Programming: On the programming of computers by means of
  natural selection}.
\newblock MIT Press, Cambridge, MA, 1992.

\bibitem{EAs_securitycosts-kirta} 
Kirta, T., and Kivimaab, J.: Optimizing it security costs by evolutionary algorithms. In C. Czosseck and K. Podins, editors, Conference on Cyber Con ict,pages 145-160, CCD COE Publications, 2010.

\bibitem{DataMining_Lee01}
Lee, S.J. and Siau, K.:
\newblock A review of data mining techniques.
\newblock {\em Industrial Management \& Data Systems}, 101(1):41--46, 2001.

\bibitem{user_classification_ml_13}
Leontjeva, A., Goldszmidt, M., Xie, Y., Yu, F. and Abadi, M.:
\newblock Early security classification of skype users via machine learning.
\newblock In {\em Proceedings of the 2013 ACM Workshop on Artificial
  Intelligence and Security}, AISec '13, pages 35--44, New York, NY, USA, 2013.
  ACM.

\bibitem{sec_policy_evolution_gp_08}
Lim, Y.T., Cheng, P.C., Rohatgi, P. and Clark, J.A.:
\newblock Mls security policy evolution with genetic programming.
\newblock In {\em Proceedings of the 10th Annual Conference on Genetic and
  Evolutionary Computation}, GECCO '08, pages 1571--1578, New York, NY, USA,
  2008. ACM.

\bibitem{MIT05}
Lippmann, R.P., Ingols, K.W., Scott, C., Piwowarski, K., Kratkiewicz, K.J., Artz, M., and Cunningham, R.K.: \emph{Evaluating and Strengthening Enterprise
Network Security Using Attack Graphs}. Project Report IA-2. Lincoln Laboratory, Massachusetts Institute of Technology, October 2005.

\bibitem{GP_intrusion-lu} Lu, W. and Traore, L.: Detecting new forms of network intrusion using genetic programming. In Proceedings of the 2003 Congress on Evolutionary Computation, pages 2165-2172, 2003.

\bibitem{EventProcessing_Luckham02}
Luckham, D.:
\newblock {\em The Power of Events: An Introduction to Complex Event Processing
  in Distributed Enterprise Systems}.
\newblock Addison-Wesley, MA, USA, 2002.

\bibitem{classification_67}
MacQueen, J.:
\newblock Some methods for classification and analysis of multivariate
  observations.
\newblock In {\em Proceedings of the fifth Berkeley symposium on mathematical
  statistics and probability}, volume~1, page~14. California, USA, 1967.

\bibitem{GA_intrusion-majeed} Majeed, P.G. and Kumar, S. Genetic algorithms in intrusion detection systems: A survey. International Journal of Innovation and Applied Studies, 5(3):233-240, March 2014.

\bibitem{Opp_Security11}
Oppliger, R.:
\newblock Security and privacy in an online world.
\newblock {\em IEEE Computer}, 44(9):21--22, September 2011.

\bibitem{android11}
Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}. MobiSec Session on Smartphone Security, Aalborg 2011.

\bibitem{BigData_11}
Ratner, B.:
\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.

\bibitem{policy_generation_clustering_10}
Samak, T. and Al-Shaer, E.:
\newblock Synthetic security policy generation via network traffic clustering.
\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
  ACM.

\bibitem{Samsung_tool}
Samsung KNOX.
\newblock
  \url{https://www.samsungknox.com}

\bibitem{Schu_SecPatterns05}
Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
  Sommerlad, P.:
\newblock {\em Security Patterns: Integrating Security and Systems
  Engineering}.
\newblock John Wiley \& sons, 2005.

\bibitem{RT2AE_SOTICS13}
Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
\newblock A survey of trust and risk metrics for a BYOD mobile working world.
\newblock In {\em Third International Conference on Social Eco-Informatics
  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.

\bibitem{SecPolComp09}
Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.

\bibitem{SecPolComp07}
Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}. In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp. 133-144, 2007.

\bibitem{AAI_book_2009}
Solanas, A. and Martínez-bal, A.:
\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
  Security}.
\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.

\bibitem{Sophos_tool}
Sophos.
\newblock Mobile control.
\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}

\bibitem{rule_generation_gp_09}
Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
\newblock Automatic rule generation based on genetic programming for event
  correlation.
\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
  Computational Intelligence in Security for Information Systems}, volume~63 of
  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
  Berlin Heidelberg, 2009.

\bibitem{risk_reduction_ga_12}
Tamjidyamcholo, A.:
\newblock Genetic algorithm approach for risk reduction of information
  security.
\newblock {\em International Journal of Cyber-Security and Digital Forensics
  (IJCSDF)}, 1(1), 2012.

\bibitem{SurveyEventCorrelation_Tiffany02}
Tiffany, M.:
\newblock A survey of event correlation techniques and related topics.
\newblock Research paper, Georgia Institute of Technology, 2002.

\bibitem{WorxSDK}
Citrix.
\newblock Worx App SDK.
\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}

\bibitem{WSO2_tool}
WSO2.
\newblock Enterprise Mobility Manager.
\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}

\bibitem{GA_networksecurity-zarza} 
Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358. World Scientific, 2010.

\bibitem{GA_cryptographicprotocols-zarza2} 
Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques. In M. Malek, E. Fernández-Medina, and J. Hernando, editors, SECRYPT, pages 316-319. INSTICC Press, 2006.

\end{thebibliography}

\end{document}

### 2015-03-23 MUSES_vs_BYOD_solutions.tex
Añadiendo nueva estructura bibliografía

@@
 \section{Acknowledgements}
-This paper has been funded in part by European project MUSES (FP7-318508), along with Spanish National project TIN2011-28627-C04-02 (ANYSELF), and GENIL PYR-2014-17, awarded by the CEI-BioTIC UGR.
+This paper has been funded in part by European project MUSES
+(FP7-318508), along with Spanish National projects
+TIN2011-28627-C04-02
+(ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), and GENIL PYR-2014-17,
+awarded by the CEI-BioTIC UGR.
 
 \bibliographystyle{elsarticle-num}
-
-% Antonio - Poner la bibliografía en fichero .bib
-
-\begin{thebibliography}{00}
-
-%\bibitem{ids13}
-%Sommestad T., Hunstad A.. \emph{Intrusion detection and the role of the system administrator.}, from Swedish Defence Research Agency (FOI), Linköping, Sweden, 2013.
-
-%\bibitem{m2m12}
-%NTT DOCOMO, \emph{DOCOMO to Launch Global M2M Platform}, in M2M Magazine, December 2012.
-%http://www.machinetomachinemagazine.com/2012/12/05/docomo-to-launch-global-m2m-platform/.
-
-%\bibitem{suites12}
-%The Radicati Group Inc., report \emph{Microsoft Office 365 - Analysis and Forecast, 2012-2016}. June 2012.
-
-\bibitem{Adams_Users05}
-Adams, A. and Sasse, A.:
-\newblock {\em Users are not the enemy}.
-\newblock Security and Usability: Designing Systems That People Can Use.
-  O\'Reilly Associations, 2005.
-
-\bibitem{cost_adjustment_07}
-Alfaro-Cid, E., Sharman, K. and Esparcia-Alcázar, A.I.:
-\newblock A genetic programming approach for bankruptcy prediction using a
-  highly unbalanced database.
-\newblock In M.~Giacobini, editor, {\em Applications of Evolutionary
-  Computing}, volume 4448 of {\em Lecture Notes in Computer Science}, pages
-  169--178. Springer Berlin Heidelberg, 2007.
-
-\bibitem{AzurriMDM}
-Azurri Communications.
-\newblock Icon Mobilise.
-\newblock \url{http://www.azzurricommunications.com/~/media/Resources/Brochures/Media/icon_mobilise_brochure_online.ashx}
-
-\bibitem{SecPolComp12}
-Al-Omari, A., El-Gayar, O., Deokar, A., and Walters, J.: \emph{Security Policy Compliance: User Acceptance Perspective}. 45th Hawaii International
-Conference on System Sciences (pp. 3317-3326). IEEE, 2012.
-
-\bibitem{BYOD13}
-Bacik, S.: \emph{Security Implications of Bring Your Own Device, IT Consumerization, and Managing User Choices}, in Information Security Management Handbook, Sixth Edition, Volume 7, pp.
-133-142, 2013.
-
-\bibitem{EAs_Back96}
-Back, T.:
-\newblock {\em Evolutionary algorithms in theory and practice}.
-\newblock Oxford University Press, 1996.
-
-\bibitem{MachineLearning_Bishop06}
-Bishop, C.:
-\newblock {\em Pattern recognition and Machine Learning}.
-\newblock Springer, 2006.
-
-\bibitem{Blackberry_tool}
-Blackberry.
-\newblock Blackberry balance.
-\newblock \url{http://es.blackberry.com/business/software/blackberry-balance.html}
-
-\bibitem{Blackphone}
-Blackphone.
-\newblock \url{https://www.blackphone.ch/}
-
-\bibitem{SecPolComp10}
-Bulgurcu, B., Cavusoglu, H., and Benbasat, I.: \emph{Information security policy compliance: an empirical study of rationality-based beliefs and information security awareness}.
-MIS Quarterly, 34(3), 523-548.
-2010.
-
-\bibitem{botnet_detection_clustering_09}
-Chang, S. and Daniels, T.E.:
-\newblock P2P botnet detection using behavior clustering \& statistical tests.
-\newblock In {\em Proceedings of the 2nd ACM Workshop on Security and
-  Artificial Intelligence}, AISec '09, pages 23--30, New York, NY, USA, 2009.
-  ACM.
-
-\bibitem{SecPol09}
-Cresson Wood, C. and Lineman, D.: \emph{Information Security Policies Made Easy Version 11}. Information Shield, Inc. 2009.
-
-\bibitem{inferring_policies_socialnetworks_09}
-Danezis, G.:
-\newblock Inferring privacy policies for social networking services.
-\newblock In {\em Proceedings of the 2Nd ACM Workshop on Security and
-  Artificial Intelligence}, AISec '09, pages 5--10, New York, NY, USA, 2009.
-  ACM.
-
-\bibitem{Good_tool}
-Good's Technology.
-\newblock BYOD Solution.
-\newblock
-  \url{http://www1.good.com/secure-mobility-solution/bring-your-own-device.html}
-
-\bibitem{GAs_Goldberg89}
-Goldberg, D.E.:
-\newblock {\em Genetic Algorithms in search, optimization and machine
-  learning}.
-\newblock Addison Wesley, 1989.
-
-\bibitem{FeatureSelection_Guyon03}
-Guyon, I.,  and Elisseeff, A.:
-\newblock An introduction to variable and feature selection.
-\newblock {\em J. Mach. Learn. Res.}, 3:1157--1182, 2003.
-
-\bibitem{PatternMining_Han07}
-Han, J., Cheng, H., Xin, D., and Yan, X.:
-\newblock Frequent pattern mining: Current status and future directions.
-\newblock {\em Data Min. Knowl. Discov.}, 15(1):55--86, 2007.
-
-\bibitem{SecPolPenalty09}
-Herath, T., and Rao, H.R.: \emph{Protection motivation and deterrence: a framework for security policy compliance in organisations}.
-European Journal of Information Systems, vol.
-18, pp.
-106-125, 2009.
-
-\bibitem{IBM_tool}
-IBM.
-\newblock Hosted mobile device security management.
-\newblock
-\url{http://www-935.ibm.com/services/us/en/it-services/managed-security-services-cloud-computing} \url{ -hosted-mobile-device-security-management.html}
-
-\bibitem{Clustering_Jain99}
-Jain, A.K., Murty, M.N., and Flynn, P.~J.:
-\newblock Data clustering: A review.
-\newblock {\em ACM Comput. Surv.}, 31(3):264--323, Sept. 1999.
-
-\bibitem{imbalance_techniques_02}
-Japkowicz, N. and Stephen, S.:
-\newblock The class imbalance problem: A systematic study.
-\newblock {\em Intell. Data Anal.}, 6(5):429--449, Oct. 2002.
-
-\bibitem{ibm11}
-Kao, I-L.: \emph{IBM Security Services. Securing mobile devices in the business environment}, IBM, 2011.
-
-\bibitem{feature_selection_anomalies_08}
-Kloft, M., Brefeld, U., D\"{u}essel, P., Gehl, C. and Laskov, P.:
-\newblock Automatic feature selection for anomaly detection.
-\newblock In {\em Proceedings of the 1st ACM Workshop on Workshop on AISec},
-  AISec '08, pages 71--76, New York, NY, USA, 2008. ACM.
-
-\bibitem{GP_Koza92}
-Koza, J.~R.:
-\newblock {\em Genetic Programming: On the programming of computers by means of
-  natural selection}.
-\newblock MIT Press, Cambridge, MA, 1992.
-
-\bibitem{EAs_securitycosts-kirta} 
-Kirta, T., and Kivimaab, J.: Optimizing it security costs by evolutionary algorithms. In C. Czosseck and K. Podins, editors, Conference on Cyber Con ict,pages 145-160, CCD COE Publications, 2010.
-
-\bibitem{DataMining_Lee01}
-Lee, S.J. and Siau, K.:
-\newblock A review of data mining techniques.
-\newblock {\em Industrial Management \& Data Systems}, 101(1):41--46, 2001.
-
-\bibitem{user_classification_ml_13}
-Leontjeva, A., Goldszmidt, M., Xie, Y., Yu, F. and Abadi, M.:
-\newblock Early security classification of skype users via machine learning.
-\newblock In {\em Proceedings of the 2013 ACM Workshop on Artificial
-  Intelligence and Security}, AISec '13, pages 35--44, New York, NY, USA, 2013.
-  ACM.
-
-\bibitem{sec_policy_evolution_gp_08}
-Lim, Y.T., Cheng, P.C., Rohatgi, P. and Clark, J.A.:
-\newblock Mls security policy evolution with genetic programming.
-\newblock In {\em Proceedings of the 10th Annual Conference on Genetic and
-  Evolutionary Computation}, GECCO '08, pages 1571--1578, New York, NY, USA,
-  2008. ACM.
-
-\bibitem{MIT05}
-Lippmann, R.P., Ingols, K.W., Scott, C., Piwowarski, K., Kratkiewicz, K.J., Artz, M., and Cunningham, R.K.: \emph{Evaluating and Strengthening Enterprise
-Network Security Using Attack Graphs}. Project Report IA-2. Lincoln Laboratory, Massachusetts Institute of Technology, October 2005.
-
-\bibitem{GP_intrusion-lu} Lu, W.
-and Traore, L.: Detecting new forms of network intrusion using genetic programming.
-In Proceedings of the 2003 Congress on Evolutionary Computation, pages 2165-2172, 2003.
-
-\bibitem{EventProcessing_Luckham02}
-Luckham, D.:
-\newblock {\em The Power of Events: An Introduction to Complex Event Processing
-  in Distributed Enterprise Systems}.
-\newblock Addison-Wesley, MA, USA, 2002.
-
-\bibitem{classification_67}
-MacQueen, J.:
-\newblock Some methods for classification and analysis of multivariate
-  observations.
-\newblock In {\em Proceedings of the fifth Berkeley symposium on mathematical
-  statistics and probability}, volume~1, page~14. California, USA, 1967.
-
-\bibitem{GA_intrusion-majeed} Majeed, P.G. and Kumar, S. Genetic algorithms in intrusion detection systems: A survey. International Journal of Innovation and Applied Studies, 5(3):233-240, March 2014.
-
-\bibitem{Opp_Security11}
-Oppliger, R.:
-\newblock Security and privacy in an online world.
-\newblock {\em IEEE Computer}, 44(9):21--22, September 2011.
-
-\bibitem{android11}
-Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}.
-MobiSec Session on Smartphone Security, Aalborg 2011.
-
-\bibitem{BigData_11}
-Ratner, B.:
-\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
-  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
-\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.
-
-\bibitem{policy_generation_clustering_10}
-Samak, T. and Al-Shaer, E.:
-\newblock Synthetic security policy generation via network traffic clustering.
-\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
-  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
-  ACM.
-
-\bibitem{Samsung_tool}
-Samsung KNOX.
-\newblock
-  \url{https://www.samsungknox.com}
-
-\bibitem{Schu_SecPatterns05}
-Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
-  Sommerlad, P.:
-\newblock {\em Security Patterns: Integrating Security and Systems
-  Engineering}.
-\newblock John Wiley \& sons, 2005.
-
-\bibitem{RT2AE_SOTICS13}
-Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
-\newblock A survey of trust and risk metrics for a BYOD mobile working world.
-\newblock In {\em Third International Conference on Social Eco-Informatics
-  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.
-
-\bibitem{SecPolComp09}
-Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
-awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.
-
-\bibitem{SecPolComp07}
-Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}.
-In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp.
-133-144, 2007.
-
-\bibitem{AAI_book_2009}
-Solanas, A. and Martínez-bal, A.:
-\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
-  Security}.
-\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.
-
-\bibitem{Sophos_tool}
-Sophos.
-\newblock Mobile control.
-\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}
-
-\bibitem{rule_generation_gp_09}
-Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
-\newblock Automatic rule generation based on genetic programming for event
-  correlation.
-\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
-  Computational Intelligence in Security for Information Systems}, volume~63 of
-  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
-  Berlin Heidelberg, 2009.
-
-\bibitem{risk_reduction_ga_12}
-Tamjidyamcholo, A.:
-\newblock Genetic algorithm approach for risk reduction of information
-  security.
-\newblock {\em International Journal of Cyber-Security and Digital Forensics
-  (IJCSDF)}, 1(1), 2012.
-
-\bibitem{SurveyEventCorrelation_Tiffany02}
-Tiffany, M.:
-\newblock A survey of event correlation techniques and related topics.
-\newblock Research paper, Georgia Institute of Technology, 2002.
-
-\bibitem{WorxSDK}
-Citrix.
-\newblock Worx App SDK.
-\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}
-
-\bibitem{WSO2_tool}
-WSO2.
-\newblock Enterprise Mobility Manager.
-\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}
-
-\bibitem{GA_networksecurity-zarza} 
-Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358.
-World Scientific, 2010.
-
-\bibitem{GA_cryptographicprotocols-zarza2} 
-Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques.
-In M.
-Malek, E.
-Fernández-Medina, and J.
-Hernando, editors, SECRYPT, pages 316-319.
-INSTICC Press, 2006.
-
-\end{thebibliography}
+\bibliography{geneura-latin1,review_muses}
 
 \end{document}
+%%% Local Variables:
+%%% ispell-local-dictionary: "english"
+%%% hunspell-local-dictionary: "english"
+%%% End:

### 2015-03-24 MUSES_vs_BYOD_solutions.tex
Metiendo referencias en el bib
Van un puñao.
Sigo adelante.

--- 2015-03-23 MUSES_vs_BYOD_solutions.tex
@@
 The other issue to cope with is the elaboration of a good ISP, understandable for every user of the company, and more importantly, non-intrusive for him.
-A lot of researchers have studied the natural tendency of employees to comply with the ISP \cite{SecPolComp07,SecPolComp10,SecPolComp12}, reaching conclusions such as the employees compliance with the security policies increases educating/training them in information security awareness  \cite{SecPolComp09}, and decreases applying too much sanctions when a misuse or abuse occurs \cite{SecPolPenalty09}.
+A lot of researchers have studied the natural tendency of employees to comply with the ISP \cite{SecPolComp10,SecPolComp12,SecPolComp14}, reaching conclusions such as the employees compliance with the security policies increases educating/training them in information security awareness  \cite{SecPolComp09}, and decreases applying too much sanctions when a misuse or abuse occurs \cite{SecPolPenalty09}.
 Thus, in this paper, for each tool in Section \ref{sec:toolsreview} it is specified if the developers have taken into account the construction of ISPs, or even if they give some guidelines for building them.
@@
 
-\bibitem{android11}
-Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}.
+%\bibitem{android11}
+%Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}.
 MobiSec Session on Smartphone Security, Aalborg 2011.
 
-\bibitem{BigData_11}
-Ratner, B.:
-\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
-  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
-\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.
+%\bibitem{BigData_11}
+%Ratner, B.:
+%\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
+%  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
+%\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.
 
-\bibitem{policy_generation_clustering_10}
-Samak, T. and Al-Shaer, E.:
-\newblock Synthetic security policy generation via network traffic clustering.
-\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
-  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
-  ACM.
+%\bibitem{policy_generation_clustering_10}
+%Samak, T. and Al-Shaer, E.:
+%\newblock Synthetic security policy generation via network traffic clustering.
+%\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
+%  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
+%  ACM.
 
-\bibitem{Samsung_tool}
-Samsung KNOX.
-\newblock
-  \url{https://www.samsungknox.com}
+%\bibitem{Samsung_tool}
+%Samsung KNOX.
+%\newblock
+%  \url{https://www.samsungknox.com}
 
-\bibitem{Schu_SecPatterns05}
-Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
-  Sommerlad, P.:
-\newblock {\em Security Patterns: Integrating Security and Systems
-  Engineering}.
-\newblock John Wiley \& sons, 2005.
+%\bibitem{Schu_SecPatterns05}
+%Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
+%  Sommerlad, P.:
+%\newblock {\em Security Patterns: Integrating Security and Systems
+%  Engineering}.
+%\newblock John Wiley \& sons, 2005.
 
-\bibitem{RT2AE_SOTICS13}
-Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
-\newblock A survey of trust and risk metrics for a BYOD mobile working world.
-\newblock In {\em Third International Conference on Social Eco-Informatics
-  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.
+%\bibitem{RT2AE_SOTICS13}
+%Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
+%\newblock A survey of trust and risk metrics for a BYOD mobile working world.
+%\newblock In {\em Third International Conference on Social Eco-Informatics
+%  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.
 
-\bibitem{SecPolComp09}
-Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
-awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.
+%\bibitem{SecPolComp09}
+%Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
+%awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.
 
-\bibitem{SecPolComp07}
-Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}.
+%\bibitem{SecPolComp07}
+%Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}.
 In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp.
@@
 
-\bibitem{AAI_book_2009}
-Solanas, A. and Martínez-bal, A.:
-\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
-  Security}.
-\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.
+%\bibitem{AAI_book_2009}
+%Solanas, A. and Martínez-bal, A.:
+%\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
+%  Security}.
+%\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.
 
-\bibitem{Sophos_tool}
-Sophos.
-\newblock Mobile control.
-\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}
+%\bibitem{Sophos_tool}
+%Sophos.
+%\newblock Mobile control.
+%\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}
+%
+%\bibitem{rule_generation_gp_09}
+%Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
+%\newblock Automatic rule generation based on genetic programming for event
+%  correlation.
+%\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
+%  Computational Intelligence in Security for Information Systems}, volume~63 of
+%  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
+%  Berlin Heidelberg, 2009.
 
-\bibitem{rule_generation_gp_09}
-Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
-\newblock Automatic rule generation based on genetic programming for event
-  correlation.
-\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
-  Computational Intelligence in Security for Information Systems}, volume~63 of
-  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
-  Berlin Heidelberg, 2009.
+%\bibitem{risk_reduction_ga_12}
+%Tamjidyamcholo, A.:
+%\newblock Genetic algorithm approach for risk reduction of information
+%  security.
+%\newblock {\em International Journal of Cyber-Security and Digital Forensics
+%  (IJCSDF)}, 1(1), 2012.
 
-\bibitem{risk_reduction_ga_12}
-Tamjidyamcholo, A.:
-\newblock Genetic algorithm approach for risk reduction of information
-  security.
-\newblock {\em International Journal of Cyber-Security and Digital Forensics
-  (IJCSDF)}, 1(1), 2012.
+%\bibitem{SurveyEventCorrelation_Tiffany02}
+%Tiffany, M.:
+%\newblock A survey of event correlation techniques and related topics.
+%\newblock Research paper, Georgia Institute of Technology, 2002.
 
-\bibitem{SurveyEventCorrelation_Tiffany02}
-Tiffany, M.:
-\newblock A survey of event correlation techniques and related topics.
-\newblock Research paper, Georgia Institute of Technology, 2002.
+%\bibitem{WorxSDK}
+%Citrix.
+%\newblock Worx App SDK.
+%\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}
+%
+%\bibitem{WSO2_tool}
+%WSO2.
+%\newblock Enterprise Mobility Manager.
+%\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}
 
-\bibitem{WorxSDK}
-Citrix.
-\newblock Worx App SDK.
-\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}
-
-\bibitem{WSO2_tool}
-WSO2.
-\newblock Enterprise Mobility Manager.
-\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}
-
-\bibitem{GA_networksecurity-zarza} 
-Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358.
+%\bibitem{GA_networksecurity-zarza} 
+%Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358.
 World Scientific, 2010.
-
-\bibitem{GA_cryptographicprotocols-zarza2} 
-Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques.
+%
+%\bibitem{GA_cryptographicprotocols-zarza2} 
+%Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques.
 In M.

### 2015-03-24 MUSES_vs_BYOD_solutions.tex

@@
 \section{Acknowledgements}
-This paper has been funded in part by European project MUSES (FP7-318508), along with Spanish National project TIN2011-28627-C04-02 (ANYSELF), and GENIL PYR-2014-17, awarded by the CEI-BioTIC UGR.
+This paper has been funded in part by European project MUSES
+(FP7-318508), along with Spanish National projects
+TIN2011-28627-C04-02
+(ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), and GENIL PYR-2014-17,
+awarded by the CEI-BioTIC UGR.
 
@@
 
+\bibliography{geneura-latin1,review_muses}
+
 \end{document}
+%%% Local Variables:
+%%% ispell-local-dictionary: "english"
+%%% hunspell-local-dictionary: "english"
+%%% End:

### 2015-03-24 MUSES_vs_BYOD_solutions.tex
Bibliografía revisada, actualizada y puesta en BIB
Closes #1

--- 2015-03-23 MUSES_vs_BYOD_solutions.tex
@@
 
+% Antonio - Poner la bibliografía en fichero .bib
+
+%\begin{thebibliography}{00}
+
+%\bibitem{ids13}
+%Sommestad T., Hunstad A.. \emph{Intrusion detection and the role of the system administrator.}, from Swedish Defence Research Agency (FOI), Linköping, Sweden, 2013.
+
+%\bibitem{m2m12}
+%NTT DOCOMO, \emph{DOCOMO to Launch Global M2M Platform}, in M2M Magazine, December 2012.
+%http://www.machinetomachinemagazine.com/2012/12/05/docomo-to-launch-global-m2m-platform/.
+
+%\bibitem{suites12}
+%The Radicati Group Inc., report \emph{Microsoft Office 365 - Analysis and Forecast, 2012-2016}. June 2012.
+
+%\bibitem{Adams_Users05}
+%Adams, A. and Sasse, A.:
+%\newblock {\em Users are not the enemy}.
+%\newblock Security and Usability: Designing Systems That People Can Use.
+%  O\'Reilly Associations, 2005.
+
+%\bibitem{cost_adjustment_07}
+%Alfaro-Cid, E., Sharman, K. and Esparcia-Alcázar, A.I.:
+%\newblock A genetic programming approach for bankruptcy prediction using a
+%  highly unbalanced database.
+%\newblock In M.~Giacobini, editor, {\em Applications of Evolutionary
+%  Computing}, volume 4448 of {\em Lecture Notes in Computer Science}, pages
+%  169--178. Springer Berlin Heidelberg, 2007.
+
+%\bibitem{AzurriMDM}
+%Azurri Communications.
+%\newblock Icon Mobilise.
+%\newblock \url{http://www.azzurricommunications.com/~/media/Resources/Brochures/Media/icon_mobilise_brochure_online.ashx}
+
+%\bibitem{SecPolComp12}
+%Al-Omari, A., El-Gayar, O., Deokar, A., and Walters, J.: \emph{Security Policy Compliance: User Acceptance Perspective}. 45th Hawaii International
+%Conference on System Sciences (pp. 3317-3326). IEEE, 2012.
+
+%\bibitem{BYOD13}
+%Bacik, S.: \emph{Security Implications of Bring Your Own Device, IT Consumerization, and Managing User Choices}, in Information Security Management Handbook, Sixth Edition, Volume 7, pp.
+133-142, 2013.
+
+%\bibitem{EAs_Back96}
+%Back, T.:
+%\newblock {\em Evolutionary algorithms in theory and practice}.
+%\newblock Oxford University Press, 1996.
+
+%\bibitem{MachineLearning_Bishop06}
+%Bishop, C.:
+%\newblock {\em Pattern recognition and Machine Learning}.
+%\newblock Springer, 2006.
+
+%\bibitem{Blackberry_tool}
+%Blackberry.
+%\newblock Blackberry balance.
+%\newblock \url{http://es.blackberry.com/business/software/blackberry-balance.html}
+
+%\bibitem{Blackphone}
+%Blackphone.
+%\newblock \url{https://www.blackphone.ch/}
+
+%\bibitem{SecPolComp10}
+%Bulgurcu, B., Cavusoglu, H., and Benbasat, I.: \emph{Information security policy compliance: an empirical study of rationality-based beliefs and information security awareness}.
+MIS Quarterly, 34(3), 523-548.
+2010.
+
+%\bibitem{botnet_detection_clustering_09}
+%Chang, S. and Daniels, T.E.:
+%\newblock P2P botnet detection using behavior clustering \& statistical tests.
+%\newblock In {\em Proceedings of the 2nd ACM Workshop on Security and
+%  Artificial Intelligence}, AISec '09, pages 23--30, New York, NY, USA, 2009.
+%  ACM.
+
+%\bibitem{SecPol09}
+%Cresson Wood, C. and Lineman, D.: \emph{Information Security Policies Made Easy Version 11}. Information Shield, Inc. 2009.
+
+%\bibitem{inferring_policies_socialnetworks_09}
+%Danezis, G.:
+%\newblock Inferring privacy policies for social networking services.
+%\newblock In {\em Proceedings of the 2Nd ACM Workshop on Security and
+%  Artificial Intelligence}, AISec '09, pages 5--10, New York, NY, USA, 2009.
+%  ACM.
+
+%\bibitem{Good_tool}
+%Good's Technology.
+%\newblock BYOD Solution.
+%\newblock
+%  \url{http://www1.good.com/secure-mobility-solution/bring-your-own-device.html}
+
+%\bibitem{GAs_Goldberg89}
+%Goldberg, D.E.:
+%\newblock {\em Genetic Algorithms in search, optimization and machine
+%  learning}.
+%\newblock Addison Wesley, 1989.
+
+%\bibitem{FeatureSelection_Guyon03}
+%Guyon, I.,  and Elisseeff, A.:
+%\newblock An introduction to variable and feature selection.
+%\newblock {\em J. Mach. Learn. Res.}, 3:1157--1182, 2003.
+
+%\bibitem{PatternMining_Han07}
+%Han, J., Cheng, H., Xin, D., and Yan, X.:
+%\newblock Frequent pattern mining: Current status and future directions.
+%\newblock {\em Data Min. Knowl. Discov.}, 15(1):55--86, 2007.
+
+%\bibitem{SecPolPenalty09}
+%Herath, T., and Rao, H.R.: \emph{Protection motivation and deterrence: a framework for security policy compliance in organisations}.
+European Journal of Information Systems, vol.
+18, pp.
+106-125, 2009.
+
+%\bibitem{IBM_tool}
+%IBM.
+%\newblock Hosted mobile device security management.
+%\newblock
+%\url{http://www-935.ibm.com/services/us/en/it-services/managed-security-services-cloud-computing} \url{ -hosted-mobile-device-security-management.html}
+
+%\bibitem{Clustering_Jain99}
+%Jain, A.K., Murty, M.N., and Flynn, P.~J.:
+%\newblock Data clustering: A review.
+%\newblock {\em ACM Comput. Surv.}, 31(3):264--323, Sept. 1999.
+
+%\bibitem{imbalance_techniques_02}
+%Japkowicz, N. and Stephen, S.:
+%\newblock The class imbalance problem: A systematic study.
+%\newblock {\em Intell. Data Anal.}, 6(5):429--449, Oct. 2002.
+
+%\bibitem{ibm11}
+%Kao, I-L.: \emph{IBM Security Services. Securing mobile devices in the business environment}, IBM, 2011.
+
+%\bibitem{feature_selection_anomalies_08}
+%Kloft, M., Brefeld, U., D\"{u}essel, P., Gehl, C. and Laskov, P.:
+%\newblock Automatic feature selection for anomaly detection.
+%\newblock In {\em Proceedings of the 1st ACM Workshop on Workshop on AISec},
+%  AISec '08, pages 71--76, New York, NY, USA, 2008. ACM.
+
+%\bibitem{GP_Koza92}
+%Koza, J.~R.:
+%\newblock {\em Genetic Programming: On the programming of computers by means of
+%  natural selection}.
+%\newblock MIT Press, Cambridge, MA, 1992.
+
+%\bibitem{EAs_securitycosts-kirta} 
+%Kirta, T., and Kivimaab, J.: Optimizing it security costs by evolutionary algorithms. In C. Czosseck and K. Podins, editors, Conference on Cyber Con ict,pages 145-160, CCD COE Publications, 2010.
+
+%\bibitem{DataMining_Lee01}
+%Lee, S.J. and Siau, K.:
+%\newblock A review of data mining techniques.
+%\newblock {\em Industrial Management \& Data Systems}, 101(1):41--46, 2001.
+
+%\bibitem{user_classification_ml_13}
+%Leontjeva, A., Goldszmidt, M., Xie, Y., Yu, F. and Abadi, M.:
+%\newblock Early security classification of skype users via machine learning.
+%\newblock In {\em Proceedings of the 2013 ACM Workshop on Artificial
+%  Intelligence and Security}, AISec '13, pages 35--44, New York, NY, USA, 2013.
+%  ACM.
+
+%\bibitem{sec_policy_evolution_gp_08}
+%Lim, Y.T., Cheng, P.C., Rohatgi, P. and Clark, J.A.:
+%\newblock Mls security policy evolution with genetic programming.
+%\newblock In {\em Proceedings of the 10th Annual Conference on Genetic and
+%  Evolutionary Computation}, GECCO '08, pages 1571--1578, New York, NY, USA,
+%  2008. ACM.
+
+%\bibitem{MIT05}
+%Lippmann, R.P., Ingols, K.W., Scott, C., Piwowarski, K., Kratkiewicz, K.J., Artz, M., and Cunningham, R.K.: \emph{Evaluating and Strengthening Enterprise
+%Network Security Using Attack Graphs}. Project Report IA-2. Lincoln Laboratory, Massachusetts Institute of Technology, October 2005.
+
+%\bibitem{GP_intrusion-lu} Lu, W.
+and Traore, L.: Detecting new forms of network intrusion using genetic programming.
+In Proceedings of the 2003 Congress on Evolutionary Computation, pages 2165-2172, 2003.
+
+%\bibitem{EventProcessing_Luckham02}
+%Luckham, D.:
+%\newblock {\em The Power of Events: An Introduction to Complex Event Processing
+%  in Distributed Enterprise Systems}.
+%\newblock Addison-Wesley, MA, USA, 2002.
+
+%\bibitem{classification_67}
+%MacQueen, J.:
+%\newblock Some methods for classification and analysis of multivariate
+%  observations.
+%\newblock In {\em Proceedings of the fifth Berkeley symposium on mathematical
+%  statistics and probability}, volume~1, page~14. California, USA, 1967.
+
+%\bibitem{GA_intrusion-majeed} Majeed, P.G.
+and Kumar, S.
+Genetic algorithms in intrusion detection systems: A survey.
+International Journal of Innovation and Applied Studies, 5(3):233-240, March 2014.
+
+%\bibitem{Opp_Security11}
+%Oppliger, R.:
+%\newblock Security and privacy in an online world.
+%\newblock {\em IEEE Computer}, 44(9):21--22, September 2011.
+
+%\bibitem{android11}
+%Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}.
+MobiSec Session on Smartphone Security, Aalborg 2011.
+
+%\bibitem{BigData_11}
+%Ratner, B.:
+%\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
+%  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
+%\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.
+
+%\bibitem{policy_generation_clustering_10}
+%Samak, T. and Al-Shaer, E.:
+%\newblock Synthetic security policy generation via network traffic clustering.
+%\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
+%  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
+%  ACM.
+
+%\bibitem{Samsung_tool}
+%Samsung KNOX.
+%\newblock
+%  \url{https://www.samsungknox.com}
+
+%\bibitem{Schu_SecPatterns05}
+%Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
+%  Sommerlad, P.:
+%\newblock {\em Security Patterns: Integrating Security and Systems
+%  Engineering}.
+%\newblock John Wiley \& sons, 2005.
+
+%\bibitem{RT2AE_SOTICS13}
+%Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
+%\newblock A survey of trust and risk metrics for a BYOD mobile working world.
+%\newblock In {\em Third International Conference on Social Eco-Informatics
+%  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.
+
+%\bibitem{SecPolComp09}
+%Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
+%awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.
+
+%\bibitem{SecPolComp07}
+%Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}.
+In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp.
+133-144, 2007.
+
+%\bibitem{AAI_book_2009}
+%Solanas, A. and Martínez-bal, A.:
+%\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
+%  Security}.
+%\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.
+
+%\bibitem{Sophos_tool}
+%Sophos.
+%\newblock Mobile control.
+%\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}
+%
+%\bibitem{rule_generation_gp_09}
+%Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
+%\newblock Automatic rule generation based on genetic programming for event
+%  correlation.
+%\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
+%  Computational Intelligence in Security for Information Systems}, volume~63 of
+%  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
+%  Berlin Heidelberg, 2009.
+
+%\bibitem{risk_reduction_ga_12}
+%Tamjidyamcholo, A.:
+%\newblock Genetic algorithm approach for risk reduction of information
+%  security.
+%\newblock {\em International Journal of Cyber-Security and Digital Forensics
+%  (IJCSDF)}, 1(1), 2012.
+
+%\bibitem{SurveyEventCorrelation_Tiffany02}
+%Tiffany, M.:
+%\newblock A survey of event correlation techniques and related topics.
+%\newblock Research paper, Georgia Institute of Technology, 2002.
+
+%\bibitem{WorxSDK}
+%Citrix.
+%\newblock Worx App SDK.
+%\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}
+%
+%\bibitem{WSO2_tool}
+%WSO2.
+%\newblock Enterprise Mobility Manager.
+%\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}
+
+%\bibitem{GA_networksecurity-zarza} 
+%Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358.
+World Scientific, 2010.
+%
+%\bibitem{GA_cryptographicprotocols-zarza2} 
+%Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques.
+In M.
+Malek, E.
+Fernández-Medina, and J.
+Hernando, editors, SECRYPT, pages 316-319.
+INSTICC Press, 2006.
+
+%\end{thebibliography}
+
 \end{document}

### 2015-04-13 MUSES_vs_BYOD_solutions.tex
Changing SotA

@@
 
-Until these days, enterprises used to follow a static Security Policy devoted to controlling a certain structure \cite{BYOD13}, where the Information Assets and the devices were purchased and maintained by the company.
-Now that corporate networks are becoming dynamic for being adapted to the BYOD philosophy, there is an additional risk because the devices that the employees use are not always company-owned.
-A needed security policy, or in this case, an Information Security Policy (ISP from now on) should deal with the way of protecting a certain organization's information against a security breach.
-Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}; an ISP is built depending on the characteristics of the community/organisation that they are built for.
+One of the tasks of a Chief Security Officer (CSO) is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}.
+This means that, until the appearance of BYOD, enterprises used to follow static security policies devoted to control an environment where the company assets and the devices were purchased and maintained by the company.
+Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk because the devices that the employees use are not always company owned.
+This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying to avoid monitoring the users in a way that is against privacy.
+A needed security policy, or in this case, an ISP should deal with the way of protecting a certain organization's information against a security breach.
+Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community/organisation that they are built for.
+In this sense, MUSES stands up for a self-adaptation of the security policies of a company.
 
-On the other hand, employee-owned devices like smartphones, are not just for work purposes anymore.
-As the name says, smartphones are more than simple old cellular phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life.
-For this reason, the risk of uncontrolled devices accessing to corporate access in unsafe conditions, due to the number of risky applications is bigger.
+On the other hand, employee owned devices like smartphones, can be both used for personal matters at work, and for continue working outside of the workplace.
+As the name says, smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life.
+For this reason, the risk of uncontrolled devices accessing to corporate assets in unsafe conditions, due to the number of new risks which are linked to smartphones \cite{gangula2013survey}, is bigger.
 

### 2015-04-13 MUSES_vs_BYOD_solutions.tex
Changing intro to tools review

@@
 This means that, until the appearance of BYOD, enterprises used to follow static security policies devoted to control an environment where the company assets and the devices were purchased and maintained by the company.
-Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk because the devices that the employees use are not always company owned.
+Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk because the devices that the employees use are not always company-owned.
 This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying to avoid monitoring the users in a way that is against privacy.
@@
 
-On the other hand, employee owned devices like smartphones, can be both used for personal matters at work, and for continue working outside of the workplace.
+On the other hand, employee-owned devices like smartphones, can be both used for personal matters at work, and for continue working outside of the workplace.
 As the name says, smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life.
@@
 
-Thus now, more things should be considered than the usual ones when designing a company's network architecture.
+Thus now, more risky situations should be considered when designing a company's network architecture.
 In Figure \ref{fig:proposed_diagram} there is a proposal which can be used for the beginning of the study of solutions that may secure such a dynamic environment.
@@
 Moreover, company's information assets are constantly accessed under these conditions, considering that an information asset means every \textit{piece of information} that has a \textit{value} (cost depending on the risk of being lost or leaked) for the company.
-It can be referred to files with sensitive information to certain mails, or even to company applications.
+It can be referred to files with sensitive information, as well as confidential mails, or even to company applications.
 
@@
 		\includegraphics[scale=0.4]{img/proposed_diagram.eps}
-		\caption{Architecture approach of an Enterprise Network assuming that the Company has adopted the BYOD philosophy.}
+		\caption{Architecture approach of an enterprise network, assuming that it has adopted the BYOD philosophy.}
 	\label{fig:proposed_diagram}
@@
 
-Now that BYOD philosophy is becoming a tendency, a number of tools appeared by now, and others are under development but expected to be released soon.
-They were specifically designed for Chief Security Officers (CSOs) and Chief Information Security Officers (CISOs) to secure, monitor, and act over smartphones and other personal mobile or portable devices, when they become too risky.
-Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}).
+Many tools for companies, as well as for devices, which have adopted the BYOD have been released in the past four years. This way, and
+more focused on the enterprise, offer the CSO ways to control the devices which enter in the system, requiring users to employ strong passwords, for instance, and also to protect the employees data by means of data encryption and data protection by having strong and secure passwords.
+Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs.
+On the other hand, many solutions have been presented which are more focused on the device side, although they implement also the server side.
+Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art.
 The present section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.
@@
 One of the first companies who supported the BYOD model was IBM in 2011 \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace.
-To help organizations \cite{ibm11} embracing both company and employee owned mobile devices (as said, this practise is part of the BYOD model) in a security-rich environment, IBM developed a mobile device security management solution.
+To help organizations \cite{ibm11} embracing both company and employee-owned mobile devices (as said, this practise is part of the BYOD model) in a security-rich environment, IBM developed a mobile device security management solution.
 For IBM, a mobile security strategy should focus on several key areas.
@@
 \item It offers a centrally deployment, administration and securing of all mobile devices regardless of their OS.
-\item It manages and enforces security policies `over the air' for both corporate and employee owned mobile devices.
+\item It manages and enforces security policies `over the air' for both corporate and employee-owned mobile devices.
 \item It does it by enforcing passwords and providing mechanisms for remote lock.

### 2015-04-13 MUSES_vs_BYOD_solutions.tex
Updating and changing all IBM subsection, closes #3

@@
 Many tools for companies, as well as for devices, which have adopted the BYOD have been released in the past four years. This way, and
-more focused on the enterprise, offer the CSO ways to control the devices which enter in the system, requiring users to employ strong passwords, for instance, and also to protect the employees data by means of data encryption and data protection by having strong and secure passwords.
+more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter in the system, requiring users to employ strong passwords, for instance, and also to protect the employees data by means of data encryption and data protection by having strong and secure passwords.
 Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs.
@@
 
-\subsection{IBM Hosted Mobile Device Security Management}
+\subsection{IBM Mobile Security}
 \label{subsec:ibm}
 
-One of the first companies who supported the BYOD model was IBM in 2011 \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace.
-To help organizations \cite{ibm11} embracing both company and employee-owned mobile devices (as said, this practise is part of the BYOD model) in a security-rich environment, IBM developed a mobile device security management solution.
-For IBM, a mobile security strategy should focus on several key areas.
+One of the first companies who supported the BYOD model was IBM \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace \cite{ibm11}.
+IBM has different solutions divided into ``technology solutions'', and ``services'', and almost all are are mainly focused in the management of the devices in the system.
+Then, it might seem clear that the first disadvantage is not including all features in one system, but to make the companies to choose between one or another, or invest even more resources instead.
 
-Thus, the organization should identify which business data the strategy will allow to be stored and processed on which mobile devices.
-This helps to determine what needs to be protected and to what degree.
-Then, since different mobile platforms have different native security mechanisms, the organization needs to define which mobile device platforms will be allowed in the business environment and, thus, which need to be supported in the mobile security strategy and plan.
-That means, to define the scope of the security plan.
-Also it is needed to decide the responsibility for mobile security management work, whether using the current IT security team to handle mobile devices, or outsourcing them to a managed security service provider.
-And no matter what the mobile environments are, a number of mobile ISPs and best-practise procedures need to be put in place and should also be identified in the company's mobile security strategic plan.
-
-Taking into account these considerations, IBM developed a framework that specifies security domains and levels for applying various security technologies.
-When applied to mobile devices (not portable ones, so that laptops are not considered), the features of this framework depend on the deployment:
+Having a look into what IBM offer as ``services'', three services can be found:
 
 \begin{itemize} 
-	\item \textit{Identity and access}: Not only the use of strong passwords when accessing the devices, but also supply two way authentication and VPN access control, by supervising the authorised IP addresses and adding re-authentication for accessing resources (assets) with high value.
-	\item \textit{Data protection}: Data security stored in the devices, related to professional life, is encrypted, also during the transmission.
-Moreover, when a device is lost, data can be removed remotely, and the device located or locked out (locking out a device is also made after a modifiable timeout).
-Finally, back ups are performed periodically once the device has been recovered.
-	\item \textit{Application security}: This is related to the requirement of being connected from a controlled location for authorising the download of business applications, and those applications must be certified (also the currently running on the device).
-Actually, IBM's tool can monitor and remove applications which are identified as untrustworthy or unsafe.
-	\item \textit{Fundamental integrity control}: Running both anti-malware software and personal firewall, and making the result of these tests as dependency for VPN's intranet access. 
-	\item \textit{Governance and compliance}: Taking into consideration the mobile security as an important point in the overall risk management program of the company, and extend the periodic security audits to mobile devices too.
+	\item \textit{Mobile Enterprise Services}: Is offered as an integrated solution for smartphones, and tablets as well, but then it is divided in different subservices that the company has to acquire separately.
+Some of them are related to cloud computing, such as events and log management as a cloud security service, cloud backup, or the so-called `hosted vulnerability management'.
+The last one is specially interesting for the scope of this paper, given the fact that it seems to implement one of the most important advantages of the MUSES system, the self-adaptation.
+IBM, by performing deeper scans over the security incidents data, either if they were successful (computer forensics analysis) or not (the device was enough secure), they claim to be able to recognise new vulnerabilities - or threats - with enough accuracy.
+The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately, and configuring the different parts.
+	\item \textit{Hosted Mobile Device Security Management}: A particular service of the Mobile Enterprise Services.
+It includes itself a number of subservices, going from tools to make easy to develop secure mobile apps, to an interface for managing the devices in the system, check their configuration security level.
+Again, what is offered by IBM as `services', are included as default features in the MUSES system.
+	\item \textit{Enterprise Wireless Networks}: Devoted to provide secure channels for communications.
+This is related with ensuring employees that any connection they might perform to access company assets, is properly secured, at the time it delivers the expected performance.
+Thus, this service is, in some sense, adaptive to the situation, yet only in terms of a secure connection and not evolvind the security policies, like MUSES.
 \end{itemize}
-
-This solution is based on a client-server architecture, where the controlling center is placed in the server, and the client would be installed on the mobile devices.
-This way, the client/device would communicate with the server as regularly as possible, to enforce policies, execute commands, and report status.
-With these features, and by analysing in the server the incoming data from the devices, this IBM's solution would be able to help enterprises to support ISPs compliance and to recognise (consequently acting over) mobile threat landscapes.
-
-%Regarding IBM hosted mobile device security solution's architecture, the solution is built on a sound client-server architecture in which the server centrally controls and manages security policies and settings for various security features.
-The client would be installed on the mobile device and regularly communicate with the server to enforce policies, execute commands and report status.
-Also, IBM's solution contains reporting and analysis capabilities, with information that helps the company to support ISP compliance, recognize the mobile threat landscape and evaluate the solution's effectiveness in countering threats.
 

### 2015-04-14 MUSES_vs_BYOD_solutions.tex
Changing more things in state of the art, including section structure

@@
 
-% Don't completely like the intro for being too focused to MUSES.
-
 %----------------------------------------------------------------------------
@@
 
-Sophos is a company founded in 1985 focused on IT security and data protection for businesses.
-Their \textit{Mobile Device Management} main product \cite{Sophos_tool} is Sophos Mobile Control.
-It is oriented to IT administration for mobile devices, trying to offer to the users the possibility of choosing the delivery model to suit their needs, i.e., between on-premise and Software as a Service (SaaS).
+Contrarily to IBM's solution services, Sophos offer a whole product for securing BYOD environments, which is called Mobile Control \cite{Sophos_tool}.
+It is oriented to IT administration for mobile devices, and it can be deployed in two ways: on-premises, which means that all data and services remain in the servers of the company, and as Software as a Service (SaaS), so that the services are provided through Lightweight Directory Access Control (LDAP).
+LDAP is an application protocol for accessing and maintaining distributed directory information services over an Internet Protocol (IP) network.
 
-The tool offers the possibility of managing all workers and co-workers smartphones and tablets from a single-based console.
-The console monitors the devices throughout their full life cycle: from the initial set up and enrolment, right through to decommissioning.
-Other features are similar to IBM's product, adding some new like being able to connect to an existing user directory using Lightweight Directory Access Control (LDAP)\footnote{LDAP is an application protocol for accessing and maintaining distributed directory information services over an Internet Protocol (IP) network.}.
+The tool manages all employees' smartphones and tablets from a single-based console.
+This console monitors the devices since initial set up and registration, until they log off.
+Other features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.
 
-Additional security is provided by the incorporation of \textit{Malware and Web protection}, so that the user does not need to install anti-malware software by him or herself.
-Regarding the compliance enforcement, the main goal is not to sacrifice company's security in favour of flexibility for the users, which has been demonstrated \cite{SecPolPenalty09} that could result in bad (unwilling or not) users' behaviour.
-Thus, company's BYOD initiative should include an acceptable use policy to ensure the users are aware of any measures the company may take if a device breaches any ISPs.
-Sophos aims to reach this by doing three main tasks: First, by enforcing IPSs, i.e.
-allowing setting up user and group-based security policies separately.
-The security settings can also vary from one platform to another, thus looking to support all of them is necessary to set task bundles and individual actions for many different violations.
-Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of a breach.
+With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users.
+But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad (even not on purpose) users' behaviour.
+Thus, company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs.
+Sophos aims to reach this by doing three main tasks: First, by allowing setting up user and group-based security policies separately.
+Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of the breach.
 For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe may be the chosen option.
-As previously stated, the actions vary for each platform, but the most common platforms such as Android and iOS allow blocking email access, notifying the admin, performing a remote lock or wiping, locating a device using 3D maps, triggering a remote alarm, transferring a task bundle combining a number of actions, and Sophos's solution adds the possibility of trigger a scan.
-Finally, compliance check, i.e.
-though some of the most widely used features include allow or disallow root rights or jailbreaking, require encryption, and whitelist or blacklist apps.
-Sophos also allows disabling malware apps, setting maximum intervals since last \textit{Mobile Security scan}, and allowing or disallowing suspicious apps and potentially unwanted apps (named PUAs).
+Finally, compliance check, by constantly performing scans to detect malware and putting the devices in quarantine when they are found infected.
 
-Then, the Enterprise App Store included in Sophos Mobile Control allows the company to supply the users with recommended and/or required apps directly on their devices.
-Both company's in-house and app store apps are suggested directly on the user's mobile device, so they can click to trigger the installation.
-Also, for keeping the employees working without increasing the burden for the IT department, the self-service portal built-in included in Sophos's solution has many features.
-Among others, it shall be mentioned that, wanting the employees to use their personal devices at work, they can register them (with a provided step-by-step process) and agree to an acceptable company-defined use policy.
-All profiles, including email access, would be available after registration, and the portal may be accessed from any PC with Internet access, or even from a mobile device itself.
-Furthermore, when a device is eventually stolen, users can choose to remotely locate, lock or wipe their devices and reset their passcode without having to contact the company help desk.
-From the company side, they can define which features are available in a self-service portal from the administrator console.
+And given the fact that this tools is more focused in the company than in the user, it is worth mentioning that the MUSES tries to focus in the users, being user-centric.
+This means that letting the user know about a risky situation, instead of making them feel ``watched''.
 
@@
 
-\subsection{Samsung's Knox Mobile Security Suite}
-\label{subsec:samsungknox}
+\subsection{Samsung's KNOX and Blackberry Balance}
+\label{subsec:samsungblackberry}
+
+Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation.
+They are not being successful in spite of their features.
+On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.
 
@@
 
-\subsection{Good's Bring Your Own Device solution}
-\label{subsec:goodsbyod}
+\subsection{Blackphone}
+\label{subsec:blackphone}
 
-Good Technology is a company that was founded in 1996 in California.
-The philosophy followed by Good is similar to Samsung's Knox one: to create a secure container that places an unreachable partition between personal and business data in order to protect company's assets.
-The solutions that they offer \cite{Good_tool} are similar than the previous ones.
-They have focused in mobile (not laptops) devices, though they support a different of Operating Systems (OSs), and in separating personal and company data.
-A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, PIM, calendar), intranet, and in-house or third-party mobile applications.
-Finally, Good offers best practise recommendations to help the company's BYOD policies such as reimbursements and stipends.
-There is a document available at Good's webpage\footnote{\url{http://www1.good.com/mobility-management-solutions/bring-your-own-device}} which contains several questions about Information Security Policies and how to cope with all of them.
+On the device side, one of the most powerful solutions found in the BYOD state of the art seems to be to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone_site}.
+It has its own Android-based operating system, called \textit{PrivatOS}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}.
+This BlackPhone also allows a remote wiping of the data if the device is lost or stolen.
+The main disadvantage of this solution is either the enterprise having to make
+an investment and buy these smartphones to the employees (which, in fact, is against the BYOD philosophy), or to make employees buy them,
+so they cannot use the device they already have. On the contrary, the MUSES system proposed in this work is designed as device-independent.
 
@@
 
-There have arisen several other corporate-security aimed tools inside the BYOD philosophy, such as:
+There exist other corporate security-aimed tools inside the BYOD philosophy, such as:
 
 \subsubsection{WSO2 - Enterprise Mobility Manager \cite{WSO2_tool}}
-An open source platform aimed to manage the corporate and personal mobile devices in the enterprise. Its main features are:
-\begin{itemize}
-\item Mobile Device Management: a console to manage the corporate/personal devices, adding policies online, role-based permissions, etc.
-\item Mobile Application Management: tool designed to manage the apps to be enrolled on the system (in the devices).
-\item Enterprise App Store: specific apps for the enterprise environment.
-\item Mobile Data Security: containerization and encryption of data.
-\end{itemize}
 
-\subsubsection{Blackphone  \cite{Blackphone}}
-A phone designed to be used as a corporate device (in addition to personal uses). It includes an own OS, named PrivatOS, including useful tools to this end. The features of this OS are:
-\begin{itemize}
-\item It is built on Android.
-\item It uses anonymous searching.
-\item It includes a few bundled apps, all of them privacy-enabled.
-\item It lets a smart disabling of all Wi-Fi connections except trusted hotspots.
-\item It permits a fine-grained control on app permissions in a single interface.
-\item It offers a total control on private calls, texting, video chat, file exchange (up to 100MB), browsing, and conference calls.
-\item There are frequent security updates from Blackphone directly.
-\item It permits an anonymous remote wipe and anti theft (in Android it requires use of centralized cloud account).
-\end{itemize}
+WSO2 Enterprise Mobility Manager (WSO2 EMM) \citep{wso2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:
+
+\begin{description}
+  \item[Mobile Device Management] that is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
+It should be noted that this tool allowes the tracking of every enrolled device, as well as obtaining reports and analytics of their use.
+  \item[Mobile Application Management] With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
+  \item[Enterprise App Store] This store provides users with both enterprise and public applications approved by the company.
+  \item[Mobile Data Security] WSO2 also allows the user's data to be encrypted via password.
+\end{description}
+
+\subsubsection{Good's Bring Your Own Device solution}
+
+Good Technology is a company that was founded in 1996 in California.
+The philosophy followed by Good is similar to Samsung's Knox one: to create a secure container that places an unreachable partition between personal and business data in order to protect company's assets.
+The solutions that they offer \cite{Good_tool} are similar than the previous ones.
+They have focused in mobile (not laptops) devices, though they support a different of Operating Systems (OSs), and in separating personal and company data.
+A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, PIM, calendar), intranet, and in-house or third-party mobile applications.
+Finally, Good offers best practise recommendations to help the company's BYOD policies such as reimbursements and stipends.
+There is a document available at Good's webpage\footnote{\url{http://www1.good.com/mobility-management-solutions/bring-your-own-device}} which contains several questions about Information Security Policies and how to cope with all of them.
 
 \subsubsection{Azzurri - Icon Mobilise \cite{AzurriMDM}}
+
 It is a cloud-based service to manage enterprise devices from the BYOD point of view (protecting sensitive corporate data and also letting the users enjoy them privately), by outsourcing the management of those devices to Azzurri.
+
 \begin{itemize}
@@
 \subsubsection{Citrix - XenMobile}
-It is a tool implemented with Worx App SDK \cite{WorxSDK}:
-\begin{itemize}
-\item It Includes the concept of framework-enabled app.
-\item There can be defined fine-grained policies associated to the apps by means of a specific graphical user interface.
-\item It offers a dedicated micro VPN to connect to Citrix-protected backend services.
-\item All Worx-enabled apps can interact with each other for a seamless experience. It covers native and HTML5 apps.
-\item It separates business and personal applications inside a secure mobile container.
-\end{itemize}
+
+XenMobile with Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions (like using the mobile phone's camera, GPS or microphone) \cite{WorxSDK}.
+These policies can be turned on or off using its own GUI.
+Citrix is framework-enabled, and it is aware of some (or all) apps installed on the device.
+All the apps that are Worx-enable are capable of interacting, and thus offering the user a better experience.
+
+It is also important to point out that Citrix differenciates between apps used by the user privately and those used for business, locating both on a secure mobile container that is encrypted, and can be locked remotely for safety reasons.
+Another feature of Citrix is that it uses dedicated micro VPN to connect to Citrix-protected backend services.
 

### 2015-04-14 MUSES_vs_BYOD_solutions.tex
Comentario para Antares, refers #9
Comment for myself @unintendedbear, for not forgetting it

@@
 On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.
+On the other hand, %Antares needed
 
-As part of its SAFE (Samsung for enterprise) brand, Samsung revealed at the Barcelona Mobile World Congress 2013 the Knox application \cite{Samsung_tool}, which was expected to be available on its last Galaxy smartphone generation.
+With regard to their features, Samsung KNOX, as well as Blackberry Balance, are more focused on the device side, while the solutions mentioned in previous subsections were more centered in being tools for CSOs.
+This also means that they are not device-independent, as KNOX is only for Samsung devices and Balance is integrated in BlackBerry 10 \cite{Blackberry_tool}.
+
+As part of its SAFE (Samsung for enterprise) brand, Samsung revealed at the Barcelona Mobile World Congress 2013 the Knox application \cite{Samsung_mwc13}, which was expected to be available on its last Galaxy smartphone generation.
+It was also presented in the same congress in 2014 \cite{Samsung_mwc14}, but...
+%Completar cuando encuentre la noticia
+
 The solution is available since December 2013.

### 2015-04-14 MUSES_vs_BYOD_solutions.tex
Unifying KNOX and blackberry balance and re-writing

@@
 
-\subsection{Samsung's KNOX and Blackberry Balance}
+\subsection{Samsung KNOX and Blackberry Balance}
 \label{subsec:samsungblackberry}
@@
 
-The solution is available since December 2013.
 The main feature of this security package is the use of different containers, or environments, for business and personal sides.
 Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
-There will be needed introducing a password to enter into the business side and, once \textit{logged in} this container, no more passwords will be required for the business applications.
-The applications approved by the company IT department must meet Samsung's security standards and allow single sign-on.
-A Knox API will also be provided for the company to be capable of accessing over almost 205 predefined IT policies (the SAFE API grows this number to 475).
-Also, Knox would allow different VPNs for individual apps.
-Regarding the information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files.
-In the same way, the user won't be able to share data between the two environments, e.g.
-creating separate contact lists so the user cannot send a contact from one side to the other, or if the user copies data to the clipboard in the Knox container, it won't be there in the personal container.
+A password is required in order to enter into the business side and, once \textit{logged in} in this container, no more passwords are needed for the business applications.
+The applications approved by the company IT department must meet Samsung security standards and, though it has been said that KNOX is a device-focused solution, it offered an API.
+This API would allow the company to access to over almost 205 predefined IT policies.
+With regard to information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files.
+In the same way, the user is not allowed to share data between the two environments.
 
-There are three main components in the device architecture:
+Features in Blackberry Balance are similar.
+This security package was announced as a feature of BlackBerry 10.
+Nevertheless, it is available with BlackBerry Enterprise Service 10, which is a device management, security and app management for BlackBerry, iOS and Android devices.
+It is necessary to activate BlackBerry Balance for having available some security features, all related or similar to the aforementioned.
+For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps.
+Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.
 
-\begin{itemize}
-	\item \textit{Customizable Secure Boot}: This ensures that only verified and authorized software can run on the device.
-It is a primary component that forms the first line of defence against malicious attacks on devices with Samsung KNOX.
-In addition, Samsung Knox's Secure Boot technology allows the switch of the secure boot root certificate in a secure manner after the devices are shipped.
-	\item \textit{TrustZone-based Integrity Measurement Architecture (TIMA)}: By a continuous integrity monitoring of the Linux kernel, it is possible to detect that the integrity of the kernel or the boot loader is violated, and to take a policy-driven action in response.
-One of these policy actions disables the kernel and powers down the device.
-	\item \textit{Security Enhancements for Android}: This feature is the one referred to the separation of information based on confidentiality and integrity requirements.
-It isolates applications and data into different domains so that threats of tampering and bypassing of application security mechanisms are reduced while the amount of damage that can be caused by malicious or flawed applications is minimized.
-\end{itemize}
+On the other side, employees are able to access information and applications related to their personal lives, while staying connected to important work information when they need to perform.
+Finally, another known feature is also offered by Blackberry, so if the device gets lost or is stolen, or if the employee leaves the organization, there will be an option to wipe just work information which can be done remotely.
 
-It is important to take into account that if an enterprise decides to deploy this solution to secure its BYOD environment, it must yet work with certain Mobile Device Management (MDM) services, either cloud or server based.
-Samsung offers a list\footnote{\url{https://www.samsungknox.com/en/knox-mdm-feature-list}} of the MDM which Knox supports, each one with the number of supported policies.
+As a summary, Blackberry Balance has little opportunity if Blackberry sales continue to decrease, as well as Samsung KNOX, which is still out of the market.
+With this situation, MUSES could be a good choice, because is device-independent, and is available as an open source tool for both devices and servers.
 
@@
 so they cannot use the device they already have. On the contrary, the MUSES system proposed in this work is designed as device-independent.
-
-%----------------------------------------------------------------------------
-
-\subsection{BlackBerry Balance}
-\label{subsec:blackberrybalance}
-
-This security package was announced as a feature of BlackBerry 10 \cite{Blackberry_tool}.
-Nevertheless, it is available with BlackBerry Enterprise Service 10, which is a device management, security and app management for BlackBerry, iOS and Android devices.
-It is necessary to activate BlackBerry Balance for having available some security features, all related or similar to the aforementioned.
-For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps.
-Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.
-
-On the other side, employees are able to access information and applications related to their personal lives, while staying connected to important work information when they need to perform.
-Finally, another known feature is also offered by Blackberry, so if the device gets lost or is stolen, or if the employee leaves the organization, there will be an option to wipe just work information which can be done remotely.
 

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Good solution re-written

@@
 
-Good Technology is a company that was founded in 1996 in California.
-The philosophy followed by Good is similar to Samsung's Knox one: to create a secure container that places an unreachable partition between personal and business data in order to protect company's assets.
-The solutions that they offer \cite{Good_tool} are similar than the previous ones.
-They have focused in mobile (not laptops) devices, though they support a different of Operating Systems (OSs), and in separating personal and company data.
-A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, PIM, calendar), intranet, and in-house or third-party mobile applications.
-Finally, Good offers best practise recommendations to help the company's BYOD policies such as reimbursements and stipends.
-There is a document available at Good's webpage\footnote{\url{http://www1.good.com/mobility-management-solutions/bring-your-own-device}} which contains several questions about Information Security Policies and how to cope with all of them.
+The philosophy followed by Good is similar to Samsung KNOX one: to create a secure container that places an unreachable partition between personal and business data in order to protect company assets.
+The solutions that they offer \cite{Good_tool} are similar than in the already described solutions.
+Their solution has been developed for the main Operating Systems (OSs) (iOS, Android, and Windows phone), and also desktop computers with Windows.
+A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, documents, calendar), the intranet, and both in-house or third-party mobile applications.
+Finally, Good offers best practise recommendations to help the company developing BYOD policies.
+A document can be accessed from Good's webpage \cite{Good_tool}, which contains several questions about ISPs and how to cope with all of them.
 

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Another revision to section 3

@@
 Many tools for companies, as well as for devices, which have adopted the BYOD have been released in the past four years. This way, and
-more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter in the system, requiring users to employ strong passwords, for instance, and also to protect the employees data by means of data encryption and data protection by having strong and secure passwords.
+more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter in the system, for instance, and also to protect the employees' data by means of data encryption and data protection by requiring the use of strong and secure passwords.
 Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs.
@@
 The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately, and configuring the different parts.
+Also, the fact that IBM software is not open source as MUSES system is, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
 	\item \textit{Hosted Mobile Device Security Management}: A particular service of the Mobile Enterprise Services.
-It includes itself a number of subservices, going from tools to make easy to develop secure mobile apps, to an interface for managing the devices in the system, check their configuration security level.
+It includes itself a number of subservices, going from tools to make easy to develop secure mobile apps, to an interface for managing the devices in the system, checking their configuration security level.
 Again, what is offered by IBM as `services', are included as default features in the MUSES system.
@@
 This is related with ensuring employees that any connection they might perform to access company assets, is properly secured, at the time it delivers the expected performance.
-Thus, this service is, in some sense, adaptive to the situation, yet only in terms of a secure connection and not evolvind the security policies, like MUSES.
+Thus, this service is, in some sense, adaptive to the situation, yet only in terms of a secure connection and not evolving the security policies, like MUSES.
 \end{itemize}
@@
 
-And given the fact that this tools is more focused in the company than in the user, it is worth mentioning that the MUSES tries to focus in the users, being user-centric.
-This means that letting the user know about a risky situation, instead of making them feel ``watched''.
+Thus, given the fact that this tool is more focused in the company than in the user, it is worth to compare it to the MUSES system, as the latter tries to focus in the users, being user-centric.
+This means that is preferred to let the user know about a risky situation, rather than making them feel ``watched''.
 
@@
 
-On the device side, one of the most powerful solutions found in the BYOD state of the art seems to be to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone_site}.
+On the device side, one of the most powerful solutions found in the BYOD state of the art seems to be to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone}.
 It has its own Android-based operating system, called \textit{PrivatOS}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}.
@@
 
-This tool is the Google's approach in the mobile enterprise security area, and  will run on Android 5.0 ``Lollipop''.
+This tool is the Google approach in the mobile enterprise security area, and  will run on Android 5.0 ``Lollipop''.
 It follows the idea of containers, previously presented in the Samsung Knox description.
@@
 
-\subsubsection{WSO2 - Enterprise Mobility Manager \cite{WSO2_tool}}
+\subsubsection{WSO2 - Enterprise Mobility Manager}
 
-WSO2 Enterprise Mobility Manager (WSO2 EMM) \citep{wso2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:
+WSO2 Enterprise Mobility Manager (WSO2 EMM) \cite{WSO2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:
 
@@
 
-\subsubsection{Azzurri - Icon Mobilise \cite{AzurriMDM}}
+\subsubsection{Azzurri - Icon Mobilise}
 

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Integrating KNOX problems, contributed by @deantares, so this closes #9

@@
 On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.
-On the other hand, %Antares needed
+On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available on its last Galaxy smartphone generation.
+Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still semained delayed until it was apparently found insecure \cite{Samsung_insecure}.
+Finally, Samsung decided to collaborate with Google in Android Work (see Section \ref{subsec:androidwork}).
 
@@
 
-As part of its SAFE (Samsung for enterprise) brand, Samsung revealed at the Barcelona Mobile World Congress 2013 the Knox application \cite{Samsung_mwc13}, which was expected to be available on its last Galaxy smartphone generation.
-It was also presented in the same congress in 2014 \cite{Samsung_mwc14}, but...
-%Completar cuando encuentre la noticia
-
-The main feature of this security package is the use of different containers, or environments, for business and personal sides.
+The main feature of KNOX is the use of different containers, or environments, for business and personal sides.
 Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Re-writing and extending Android work, so this closes #8

@@
 Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still semained delayed until it was apparently found insecure \cite{Samsung_insecure}.
-Finally, Samsung decided to collaborate with Google in Android Work (see Section \ref{subsec:androidwork}).
+Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android} (see Section \ref{subsec:androidwork}).
 
@@
 This tool is the Google approach in the mobile enterprise security area, and  will run on Android 5.0 ``Lollipop''.
-It follows the idea of containers, previously presented in the Samsung Knox description.
-Thus the container will be used to manage (encrypted) corporate data, and also to restrict what the users can do with them, but the environment will be as usual, i.e.
-there will not be a separate workspace for doing this.
+It follows the idea of containers, previously presented in the Samsung KNOX description.
+Thus the container will be used to manage (encrypted) corporate data, and also to restrict what the users can do with them.
+This is called a ``dual-persona'' smartphone \cite{AndroidWork_review}.
 
-This system will be strongly related with the Google Play market, as the applications will be `categorized' as \textit{managed}\footnote{ A concept previously introduced in Apple devices}.
-Thus Android Work will provide the CSOs with a tool to define which apps would be managed, i.e.
-which ones could be installed by the users and considered as corporate-related applications.
-Moreover the enterprise IT department could define specific security policies on these apps, in addition to the inherent protection that the container provides.
+This system will be strongly related with the Google Play market, as the applications will be `categorized'.
+Thus, Android Work will provide the CSOs with a tool to define which apps would be allowed for being installed by the users and considered as corporate-related applications.
+Several enterprise-security aimed applications will be offered in the market, so the IT would decide which ones will be installed (even as a bundle) in the employees' devices, and also, they can manage the updates of these apps, in order to ensure that all the employees are up to date.
+For instance, one app could manage the creation of personal/work profiles, so the user just could access corporate assets after login in into the app.
+Moreover, the enterprise IT department could define specific security policies on these apps, in addition to the inherent protection that the container provides.
+However, the specifications of this tool \cite{AndroidWork_tool} do not include the ``self-adaptation'' as a feature, as the MUSES system does.
 
-Several enterprise-security aimed applications will be offered in the market, so the IT would decide which ones will be installed (even as a bundle) in the employees' devices, and also, they can manage the updates of these apps, in order to ensure that all the employees are up to date.
-For instance one app could manage the creation of personal/work profiles, so the user just could access corporate assets after login in into the app.
-
-Thus, the system will provide a framework for IT staff to manage business devices but also, importantly, personal devices being used in a BYOD context (The CSO would give you an activation code in order to `connect' the smartphone to the enterprise and use this Android Work).
-Thus, IT admins will be able to specify which Google Play apps will be available for users to install through this work profile, including being able to provision apps to specific individuals or groups (inside the company).
+Even though it does not analyse the system information for security rules evolution purposes, it offers policy management.
+Thus, the system will provide a framework for IT staff to manage business devices but also, and more importantly, personal devices being used in a BYOD context (The CSO would give the employee an activation code in order to `connect' the smartphone to the enterprise and use this Android Work).
+Therefore, IT admins will be able to specify which Google Play apps will be available for users to install through this work profile, including being able to provision apps to specific individuals or groups (inside the company).
 
 In addition to the work profiles, there will be considered other high-level ones with the ability to administrate the device from the corporate-security point of view, or as the owner, with all the privileges on the device.
+
+Android work has only one advantage over MUSES, and roughly over all solutions, which is the ability to act over the Android kernel.
+All the other tools only have permission for monitoring the running processes in the devices, while Android work has, for instance, the ability to provide a `work' version of its native apps.
+MUSES, instead, depends on if the developers adapt their applications through a MUSES API, transforming them to MUSES Aware apps (see Section \ref{subsec:client}).
+In any other case, and most of all with the ``self-adaptation'' feature of MUSES, it can be said that MUSES has more advantages than the Google solution.
 
@@
 \subsection{Client/Device architecture}
+\label{subsec:client}
 

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Last revision to section 3, so this closes #4

@@
 For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps.
-Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.
+Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions will not be permitted.
 

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Revisado el inglés
He cambiado muchos focus in->focus on, for verbo->for verboing, typos y cosillas de ese estilo. También muchas comas y cambiadas algunas frases.
He puesto algunas dudas en comentarios, pero aún no lo he leido en profundidad. Mañana sigo, así que @JJ @unintendedbear @amorag podéis seguir poniéndome issues si queréis :)

--- 2015-04-15 MUSES_vs_BYOD_solutions.tex
@@
 The way on how data has been stored and accessed in the companies has completely changed along the years.
-The use of owned servers being accessed by desktop PCs (and maybe laptops) from inside the company facilities has been transformed into the distribution of these data among a number of machines, even not all belonging to the company, and working over the famous Cloud Computing environment.
+The use of owned servers being accessed by desktop PCs (and maybe laptops) from inside the company facilities has been transformed into the distribution of these data between a number of machines, even not all belonging to the company, and working over the famous Cloud Computing environment.
 Besides, being stored in the cloud or not, data are being consulted and modified through a wide amount of devices, some of them owned by the company's users.
 This is the so-called Bring Your Own Device (BYOD) philosophy.
-It is becoming highly successful due to the impact that portable devices (such as smartphones and tablets) are having in the market.
+It is becoming highly successful due to the impact that portable devices (such as smartphones and tablets) are having on the market.
 Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies.
@@
 In this scenario several solutions have arisen in order to manage the corporate security.
-Some solutions are focused only in smartphones, while others are thought for laptops; also some are implemented for a certain platform, but others consider multiplatform.
-However most of them try to be non-intrusive (regarding the users' personal data), friendly and easy to use.
+Some solutions are focused only on smartphones, while others are thought for laptops; also some are implemented for a certain platform, but others consider multiplatform.
+However, most of them try to be non-intrusive (regarding the users' personal data), friendly and easy to use.
 
@@
 This concept is a methodology of work which allows users to start/continue a working session over multiple devices and locations without any significant loss of data.
-This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company's data borders have changed in the last years so now the users can access significant data from outside the enterprise, and possibly through a non absolutely secure channel.
+This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company's data borders have changed in the last years, so now the users can access significant data from outside the enterprise, and possibly through a non absolutely secure channel.
 
-Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a device-independent end-to end user-centric tool, based in a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt, even inferring new ones, the set of rules in order to deal with potential future security incidents due to the user's.
+Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a device-independent end-to end user-centric tool, based on a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt, even inferring new ones, the set of rules in order to deal with potential future security incidents due to the user's.
 Then the system will react, in a non-intrusive way, to the potentially dangerous sequence of actions (events) that he or she is conducting at any time.
@@
 
-On the other hand, employee-owned devices like smartphones, can be both used for personal matters at work, and for continue working outside of the workplace.
+On the other hand, employee-owned devices like smartphones, can be both used for personal matters at work, and for continuing working outside of the workplace.
 As the name says, smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life.
@@
 Many tools for companies, as well as for devices, which have adopted the BYOD have been released in the past four years. This way, and
-more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter in the system, for instance, and also to protect the employees' data by means of data encryption and data protection by requiring the use of strong and secure passwords.
+more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter into the system, for instance, and also to protect the employees' data by means of data encryption and data protection by requiring the use of strong and secure passwords.
 Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs.
@@
 One of the first companies who supported the BYOD model was IBM \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace \cite{ibm11}.
-IBM has different solutions divided into ``technology solutions'', and ``services'', and almost all are are mainly focused in the management of the devices in the system.
+IBM has different solutions divided into ``technology solutions'', and ``services'', and almost all are are mainly focused on the management of the devices in the system.
 Then, it might seem clear that the first disadvantage is not including all features in one system, but to make the companies to choose between one or another, or invest even more resources instead.
 
-Having a look into what IBM offer as ``services'', three services can be found:
+Having a look into what IBM offers as ``services'', three services can be found:
 
@@
 	\item \textit{Enterprise Wireless Networks}: Devoted to provide secure channels for communications.
-This is related with ensuring employees that any connection they might perform to access company assets, is properly secured, at the time it delivers the expected performance.
+This is related to ensuring employees that any connection they might perform to access company assets, is properly secured, at the time it delivers the expected performance.
 Thus, this service is, in some sense, adaptive to the situation, yet only in terms of a secure connection and not evolving the security policies, like MUSES.
@@
 
-Contrarily to IBM's solution services, Sophos offer a whole product for securing BYOD environments, which is called Mobile Control \cite{Sophos_tool}.
+Contrarily to IBM's solution services, Sophos offers a whole product for securing BYOD environments, which is called Mobile Control \cite{Sophos_tool}.
 It is oriented to IT administration for mobile devices, and it can be deployed in two ways: on-premises, which means that all data and services remain in the servers of the company, and as Software as a Service (SaaS), so that the services are provided through Lightweight Directory Access Control (LDAP).
@@
 The tool manages all employees' smartphones and tablets from a single-based console.
-This console monitors the devices since initial set up and registration, until they log off.
+This console monitors the devices since the initial set up and registration, until they log off.
 Other features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.
@@
 But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad (even not on purpose) users' behaviour.
-Thus, company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs.
+Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs.
 Sophos aims to reach this by doing three main tasks: First, by allowing setting up user and group-based security policies separately.
@@
 
-Thus, given the fact that this tool is more focused in the company than in the user, it is worth to compare it to the MUSES system, as the latter tries to focus in the users, being user-centric.
+Thus, given the fact that this tool is more focused on the company than in the user, it is worth to compare it to the MUSES system, as the latter tries to focus on the users, being user-centric.
 This means that is preferred to let the user know about a risky situation, rather than making them feel ``watched''.
@@
 The main feature of KNOX is the use of different containers, or environments, for business and personal sides.
-Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
+Each one even includes its own graphical configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
 A password is required in order to enter into the business side and, once \textit{logged in} in this container, no more passwords are needed for the business applications.
@@
 For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps.
-Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.
+Also, a user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions will not be permitted.
 
@@
 
-This system will be strongly related with the Google Play market, as the applications will be `categorized'.
+This system will be strongly related to the Google Play market, as the applications will be `categorized'.
 Thus, Android Work will provide the CSOs with a tool to define which apps would be allowed for being installed by the users and considered as corporate-related applications.
@@
 Even though it does not analyse the system information for security rules evolution purposes, it offers policy management.
-Thus, the system will provide a framework for IT staff to manage business devices but also, and more importantly, personal devices being used in a BYOD context (The CSO would give the employee an activation code in order to `connect' the smartphone to the enterprise and use this Android Work).
+Thus, the system will provide a framework for IT staff to manage business devices, but also, and more importantly, personal devices being used in a BYOD context (The CSO would give the employee an activation code in order to `connect' the smartphone to the enterprise and use this Android Work).
 Therefore, IT admins will be able to specify which Google Play apps will be available for users to install through this work profile, including being able to provision apps to specific individuals or groups (inside the company).
@@
   \item[Mobile Device Management] that is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
-It should be noted that this tool allowes the tracking of every enrolled device, as well as obtaining reports and analytics of their use.
+It should be noted that this tool allows the tracking of every enrolled device, as well as obtaining reports and analytics of their use.
   \item[Mobile Application Management] With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
@@
 \begin{itemize}
-\item It offers a centrally deployment, administration and securing of all mobile devices regardless of their OS.
+\item It offers a central deployment, administration and securing of all mobile devices regardless of their OS. %FERGU: securing como palabra no. security control mejor?
 \item It manages and enforces security policies `over the air' for both corporate and employee-owned mobile devices.
@@
 
-It is also important to point out that Citrix differenciates between apps used by the user privately and those used for business, locating both on a secure mobile container that is encrypted, and can be locked remotely for safety reasons.
+It is also important to point out that Citrix differentiates between apps used by the user privately and those used for business, locating both on a secure mobile container that is encrypted, and can be locked remotely for safety reasons.
 Another feature of Citrix is that it uses dedicated micro VPN to connect to Citrix-protected backend services.
@@
 Once the main tools and systems in this area have been introduced, in the following section our own system (still in development) is presented, giving an overview on its general architecture.
-Moreover we devote a subsection to describe its main features: the use of Data Mining + Machine Learning techniques, and also its self-adaptation ability using Computational Intelligence methods, which compose the real difference with all these tools.
+Moreover, we devote a subsection to describe its main features: the use of Data Mining + Machine Learning techniques, and also its self-adaptation ability using Computational Intelligence methods, which compose the real difference with all these tools.
 
@@
 As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}.
-The first one monitors the environment (context) and the user's behaviour, translating his/her actions into a sequence of events.
+The first one monitors the environment (context) and the user's behaviour, translating his/her actions in a sequence of events.
 These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module.
@@
 The \textit{server} side would be installed in the corporate SOC.
-Both sides are connected through a secure channel (using HTTPS) over Internet.
+Both sides are connected through a secure channel (using HTTPS) over the Internet.
 In that figure just the high-level components in each part are shown, along with the information flows labelled as 'Info XX'.
+%FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras
 
@@
 
-The rationale for this approach is based on two main reasons: 1) there is need for a high computational power in order to perform the event correlation and self-adaptation processes, so a quite powerful machine should be used (server); 2) there are two clearly separated parts in the system, namely the users (client) and the enterprise (server).
+The rationale for this approach is based on two main reasons: 1) there is a need for a high computational power in order to perform the event correlation and self-adaptation processes, so a quite powerful machine should be used (server); 2) there are two clearly separated parts in the system, namely the users (client) and the enterprise (server).
 
@@
 On the other hand, in \textit{offline} mode the server cannot be reached by the device (there is not an available connection between them), so all the decisions should be made locally.
-This will be done using an up-to-date copy on the Decision Table inside the Local database, which will contain decisions for any type of detected event, along with default actions to be performed if no rule is met.
+This will be done using an up-to-date copy on the Decision Table inside the Local database, which will contain decisions for any type of detected event, along with the default actions to be performed if no rule is met.
 Anyway, in this mode, the gathered information by the sensors in the device will be stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
@@
 
-All data in MUSES will be encrypted.
+All data in MUSES will be encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
 
@@
 This is due to the usual forbiddance or limitation of interactions with other applications that the OSs have.
+%FERGU: forbiddance parece que existe, pero el corrector me dice que no.
+Prohibition mejor?
 
@@
 The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
-The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, user-related, etc) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
+The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, user-related, etc.) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
 Finally, there is another \textit{Connection Manager} which controls the communication with the device side.
+%FERGU: no usar etc en artículos, mejor poner: (events, user-related LOQUESEA, among others)
 
@@
 Instead, they will be proposed as draft rules to this controller, in order that he/she will accept them if they are interesting and correct.
-It is planned that the system will be able to `learn' from this decisions so, after a so-called training or `warm up' period, the rules would be directly accepted (included in the set) or rejected autonomously by the MusKRS.
+It is planned that the system will be able to `learn' from this decisions, so after a so-called training or `warm up' period, the rules would be directly accepted (included in the set) or rejected autonomously by the MusKRS.
 
@@
 The DM/ML techniques will process the so-called patterns, which in this context correspond to events (and their related information) produced by the users' interactions with the system.
-As stated, these events will be captured by the sensors in the users' devices and transmitted to the server to be processed and stored in the system database.
+As stated, these events will be captured from the sensors in the users' devices and transmitted to the server to be processed and stored in the system database.
 The methods to be applied are:
@@
 \item \textit{Classification} \cite{classification_67}: 
-This technique tries to train a model (classifier) able to associate every pattern in the dataset to a class, so that the model could be used for assign a class for further incoming patterns with an unknown category.
+This technique tries to train a model (classifier) able to associate every pattern in the dataset to a class, so that the model could be used for assigning a class for further incoming patterns with an unknown category.
 For instance, it could look for events (patterns) that had been previously  marked as `allowed' or `denied' (according to the ISPs).
@@
 It consists on extract the most important features/variables from the data.
-This could be useful if we want to discard non-key features, which could be interesting in order to reduce the database weight, for improving the performance of other techniques (such as classification or clustering), and even to improve the performance of whole the system, since less information would be gathered and transmitted.
+This could be useful if we want to discard non-key features, which could be interesting in order to reduce the database weight, for improving the performance of other techniques (such as classification or clustering), and even to improve the performance of the whole system, since less information would be gathered and transmitted.
 
@@
 MUSES will use different EC approaches, initially, two in the DM/ML part of the process, and three in the rule-refinement/adaptation phase.
-They are based in Genetic Programming (GP) \cite{GP_Koza92}, and Genetic Algorithms (GAs) \cite{GAs_Goldberg89}.
+They are based on Genetic Programming (GP) \cite{GP_Koza92}, and Genetic Algorithms (GAs) \cite{GAs_Goldberg89}.
 
 The first evolutionary-based approach will be a \textit{GP-based classification} method.
-This will be useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems inside real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features/variables and information gathered from the events take these kind of values.
+This will be useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems in real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features/variables and information gathered from the events take these kind of values.
 
-Thus, this approach will be able to manage unbalanced datasets considering a fitness function in which a cost can be associated to the classifier accuracy at every epoch, having a penalty cost when the classifier makes a false negative (an element from the minority class which is classified as belonging to the majority class) \cite{cost_adjustment_07}.
+Thus, this approach will be able to manage unbalanced datasets considering a fitness function in which a cost can be associated with the classifier accuracy at every epoch, having a penalty cost when the classifier makes a false negative (an element from the minority class which is classified as belonging to the majority class) \cite{cost_adjustment_07}.
 Regarding the type of data, since GP algorithms can manage rule- or tree-based models, it will work perfectly with any categorical variable, yielding a good classifier as it has been made in other works (such as the aforementioned \cite{cost_adjustment_07}).
@@
 
-The second set of EC techniques are, as stated, part of the rule-refinement (or adaptation) process, to be performed by the \textit{Knowledge Compiler} module.
+The second set of EC techniques is, as stated, part of the rule-refinement (or adaptation) process, to be performed by the \textit{Knowledge Compiler} module.
 These methods will be used for inference and optimisation, and will consider this data as a part of the process:
@@
 
-Another useful information to consider in the refinement/ adaptation process will be:
+Other useful information to consider in the refinement/ adaptation process will be:
 
@@
 \item Risk information extracted from the user profile (reputation), e.g.
-"Did the user received a lot of `denies'/`allows' before?", i.e.
-"Is he/she trustworthy?".
+``Did the user received a lot of `denies'/`allows' before?'', i.e.
+``Is he/she trustworthy?''.
 In case the user is not, more restrictive rules would be created for him, otherwise the corresponding rules could be `relaxed' for that user.
@@
 \item \textit{GP rule refinement} approach, which will optimise the current set of rules, adjusting the values in the conditions (antecedents), for instance.
-Thus, some superfluous parts on the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
+Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
 The evaluation (of the whole set of security rules) will be done considering the number of unlabelled patterns that will be `covered' after the adjustments.
@@
 MUSES is mainly a free, open-source, platform independent solution, so these set of features make it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
-In addition most of the existing tools take into account only smartphones and tablets, but MUSES also will cover laptops and company PCs too, thus, it is not only for BYOD.
-Moreover the companies which desire work with those systems need specific operative system and server (such as Windows Server, for instance), being even more strict in some cases, as in Samsung Knox, in which companies must work with a specific (though they can choose from a list) MDM service for being able of deploy Knox in their environments, or in the use of the Blackphone.
+In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also will cover laptops and company PCs too, thus, it is not only for BYOD.
+Moreover the companies which desire work with those systems need a specific operating system and server (such as Windows Server, for instance), being even more strict in some cases, as in Samsung Knox, in which companies must work with a specific (though they can choose from a list) MDM service of being able of deploy Knox in their environments, or in the use of the Blackphone.
 MUSES will be a good solution in these cases, since it will be a multiplatform system.
@@
 Then, the project defines a new approach to risk management taking into account threats (with their costs) as well as the innovative concept of opportunity, i.e.
-the following beneficial outcome from a situation on which, for instance, a user is able to work while waiting at the airport if risk is low enough.
+the following beneficial outcome from a situation on which, for instance, a user is able to work while waiting at the airport if the risk is low enough.
 
@@
 
-There are some proposals in which security policies are inferred or refined \cite{inferring_policies_socialnetworks_09,policy_generation_clustering_10}, but they do not affect the ISPs as in MUSES, and they are not based in the user's behaviour in order to do this.
+There are some proposals in which security policies are inferred or refined \cite{inferring_policies_socialnetworks_09,policy_generation_clustering_10}, but they do not affect the ISPs as in MUSES, and they are not based on the user's behaviour in order to do this.
 
@@
 
-In this work, there is introduced a self-adaptive user-centric end-to-end system, named MUSES, which is in development (it will be launched next year).
+This work introduces a self-adaptive user-centric end-to-end system, named MUSES, which is in development (it will be launched next year).
 The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Justificación del uso del servidor
En el paper y en las respuestas a los revisores

@@
 
-\author{P. de las Cuevas, A.M. Mora, J.J. Merelo}
-\ead{\{paloma, amorag, jmerelo\}@geneura.ugr.es}
+\author{P. de las Cuevas, A.M. Mora, J.J. Merelo, P. García-Sánchez, A. Fernández-Ares}
+\ead{\{paloma, amorag, jmerelo, pgarcia, antares\}@geneura.ugr.es}
 \address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
@@
 Both sides are connected through a secure channel (using HTTPS) over the Internet.
-In that figure just the high-level components in each part are shown, along with the information flows labelled as 'Info XX'.
+In that figure just the high-level components in each part are shown, along with the information flows labelled as `Info XX'.
 %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras
@@
 
-The rationale for this approach is based on two main reasons: 1) there is a need for a high computational power in order to perform the event correlation and self-adaptation processes, so a quite powerful machine should be used (server); 2) there are two clearly separated parts in the system, namely the users (client) and the enterprise (server).
+The use of a server is mainly based in the need of a powerful machine, able to work with massive amounts of data (\textit{Big Data}) \ref{BigData_11}.
+Thus, part of the high computational cost methods to apply will be derived to this high-performance server, as the mobile devices do not count with enough computational power.
+These methods will include Data Mining \cite{Cios07DataMining} and Machine Learning \ref{MachineLearning_Bishop06} techniques.
+This server will also centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques will be applied.
 
@@
 All data in MUSES will be encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
+% Antonio - Sí, se va a comentar mejor en uno de los Issues. ;)
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambios sobre el servidor y referencias
Mejor justificación del servidor, nuevas refs, correcciones leves y
mejor respuesta al revisor

@@
 
-\author{P. de las Cuevas, A.M. Mora, J.J. Merelo, P. García-Sánchez, A. Fernández-Ares}
+\author{P. de las Cuevas, A.M. Mora, J.J. Merelo,\\ P. García-Sánchez, A. Fernández-Ares}
 \ead{\{paloma, amorag, jmerelo, pgarcia, antares\}@geneura.ugr.es}
@@
 
-The use of a server is mainly based in the need of a powerful machine, able to work with massive amounts of data (\textit{Big Data}) \ref{BigData_11}.
-Thus, part of the high computational cost methods to apply will be derived to this high-performance server, as the mobile devices do not count with enough computational power.
-These methods will include Data Mining \cite{Cios07DataMining} and Machine Learning \ref{MachineLearning_Bishop06} techniques.
-This server will also centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques will be applied.
+The use of a server is mainly based on the need of a powerful machine, able to work with massive amounts of data (\textit{Big Data}) \cite{BigData_11}, since the algorithms to apply to them require high computational costs \cite{Shirkhorshidi14Review}.
+Moreover, part of the high computational cost methods to apply will be derived to this high-performance server, as the mobile devices do not count with enough computational power.
+These methods will include Data Mining \cite{DataMining_Lee01} and Machine Learning \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
+This server will be also devoted to centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques will be applied.
 
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{geneura-latin1,review_muses}
+\bibliography{review_muses} %geneura-latin1
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Aceptando cambio de @fergunet
Extending (and improving) MusCRTEP description. Closes #17

@@
 \begin{itemize}
-\item It offers a central deployment, administration and securing of all mobile devices regardless of their OS. %FERGU: securing como palabra no. security control mejor?
+\item It offers a central deployment, administration and security control of all mobile devices regardless of their OS. %FERGU: securing como palabra no. security control mejor?
+%Cambiado
 \item It manages and enforces security policies `over the air' for both corporate and employee-owned mobile devices.
@@
 Prohibition mejor?
+% Yo diría que es forbidding...
 
@@
 \begin{itemize}
-	 \item \textit{System Database}: it stores all the information that the system will manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (regarding the security policies).
+	 \item \textit{System Database}: it stores all the information that the system will manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
 
 	 \item \textit{Continuous Real-Time Event Processor (MusCRTEP)}: this component is the core of the MUSES system with respect to the decision making process.
-It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{EventProcessing_Luckham02,SurveyEventCorrelation_Tiffany02}, gathering the set of occurred events and doing a rule-based threat identification.
-The output of this module is taken by the \textit{RT2AE}, which also considering information such as trust data and profiles, assets' values, user reputation, or opportunity, performs a risk and trust analysis task \cite{RT2AE_SOTICS13}, and extracts the set of potential rules to consider in the analysed situation.
-Then, these rules are transformed into decisions (or Device Policies) and submitted to those devices to which they apply.
+It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{deliverable21, deliverable52}.
+This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analyse them to look for an existing security rule that could be applied to the situation.
+The engine discovers that by analysing the context events which are sent with the user action event, so that a complete model of the risks can be built.
+The output of this module is an `access request' which is sent to the \textit{RT2AE}.
+It considers the information included in the access request, as well as other information such as trust data and profiles, assets' values, user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}.
+Finally, the RT2AE extracts the set of potential rules to consider in the analysed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.
 
-	 \item \textit{Knowledge Refinement System (MusKRS)}: this module is in charge of analysing the information stored in the system database, identifying relevant data, such as important patterns, key features, or security incidents.
-These are later processed for tuning up the existing set of rules or for inferring new ones.
+	 \item \textit{Knowledge Refinement System (MusKRS)}: this module is in charge of analysing the information stored in the system database by means of Data Mining techniques, identifying relevant data, such as important patterns, key features, or security incidents.
+These are later processed for tuning up the existing set of rules, or for inferring new ones.
+The KRS component, along with the CRTEP, are what represent the extension of the state of the art in security solutions for a BYOD environment.
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Aceptado otro cambio de @fergunet

@@
 The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
-The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, user-related, etc.) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
+The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
 Finally, there is another \textit{Connection Manager} which controls the communication with the device side.
 %FERGU: no usar etc en artículos, mejor poner: (events, user-related LOQUESEA, among others)
+% Cambiado
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Ampliando sobre la anonimización. Closes #18

--- 2015-04-16 MUSES_vs_BYOD_solutions.tex
@@
 
-There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company's chief security officer (CSO) to define and manage Security Policies and Rules in a friendly way.
+There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company's CSO to define and manage Security Policies and Rules in a friendly way.
 It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values.
 The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
-The \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, user-related, etc.) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
+There are three important points with relation to this matter \cite{deliverable72}.
+First, the data that the user provides to the system (such as name, or email) is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks.
+Then, the location of the device is never sent and stored in the database, but instead, there are a number of defined `zones'.
+What is checked is that the user is inside one of those zones of interest.
+For instance, a company might want to know if the user is inside or outside a zone defined as `company premises'.
+And finally, the use in MUSES of what is called as `soft limit' and `hard limit' \cite{deliverable72}.
+These limits exist to ensure the users that their data will not be kept longer than necessary.
+The soft limit is defined by the components that use the data (Event Processor, RT2AE, and Knowledge Refinement System) for decision making or rule refinement, but do not need that data anymore.
+In addition, the hard limit is provided by the law, in case that the employee leaves the company, or if there is a national law specifying a maximum data retention period.
+
+Then, the \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
 Finally, there is another \textit{Connection Manager} which controls the communication with the device side.
 %FERGU: no usar etc en artículos, mejor poner: (events, user-related LOQUESEA, among others)
+% Cambiado
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambiada estructura de algunos párrafos para leerlo más fácil, hyphenation y otros comentarios en la Introducción y abstract

@@
 In this paper, a novel system to deal with this situation is introduced, named  MUSES (Multiplatform Usable Endpoint Security).
-It is a system able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules.
+This system is able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules.
 MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
@@
 \end{abstract}
+
+%FERGU: seguro que ya lo habéis discutido, pero presentar MUSES como algo a hacer en el futuro es un poco... yasabesh xD
 
@@
 Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies.
-Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems, for instance the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).
+Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems.
+For instance, the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).
 
@@
 
-Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a device-independent end-to end user-centric tool, based on a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt, even inferring new ones, the set of rules in order to deal with potential future security incidents due to the user's.
+Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt the set of rules, or even inferring new ones, in order to deal with potential future security incidents due to the user's.
+%FERGU: The user's "algo que falta"?
+o eso hace referencia a su culpa?
 Then the system will react, in a non-intrusive way, to the potentially dangerous sequence of actions (events) that he or she is conducting at any time.
@@
 
-MUSES will include some important modules in the loop, such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset.
+MUSES will include some important modules in the loop, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
+ such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset.
 
-In the paper the system architecture is presented, in addition to a deep description of the soft computing methods the system will apply.
+In this paper, the system architecture is presented, in addition to a deep description of the soft computing methods the system will apply.
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Corrected abstract and title, @unintendedbear check it out

--- 2015-04-16 MUSES_vs_BYOD_solutions.tex
@@
 
-\title{Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System}
+\title{Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System}
 
@@
 \begin{abstract} 
-Enterprises, and their Chief Security Officers (CSOs) particularly, want to be sure that their Security Policies are complied.
-This goal turned hard to achieve since employees are able to use their own devices (laptops, smartphones, and tablets) at work, or at home but for work purposes.
-As this is part of the Bring Your Own Device (BYOD) philosophy and is being adopted by many companies everyday, a number of solutions have arisen in order to adapt it securely.
-In this paper, a novel system to deal with this situation is introduced, named  MUSES (Multiplatform Usable Endpoint Security).
-It is a system able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules.
+Enterprises, and particularly their Chief Security Officers (CSOs),
+want to ensure that their Security Policies are complied, but this
+goal turned hard to achieve since employees are able to use, or bring
+their own devices (in what is known as BYOD, bring your own device) at
+work, or at home but for work purposes. As this BYOD philosophy is
+adopted by many companies everyday, a number of solutions have arisen
+in order to adopt it securely. In this paper, a novel system named
+MUSES (Multiplatform Usable Endpoint Security) which should be able 
+to adapt Security Policies to a BYOD environment is introduced. MUSES
+has been designed to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules.
 MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
-This system, still in development, is compared with the most relevant solutions offered by other companies to deal with the same issues as MUSES, remarking the advantages that our system will offer with respect to them.
+This system, still in development, is compared with the most relevant
+solutions offered by other companies to deal with the same issues as
+MUSES, remarking the advantages that our system will offer with
+respect to them. % What do we do in this paper? Present the
+                 % architecture? The prototypes? - JJ
 \end{abstract}

### 2015-04-16 MUSES_vs_BYOD_solutions.tex

--- 2015-04-16 MUSES_vs_BYOD_solutions.tex
@@
 \begin{abstract} 
-Enterprises, and their Chief Security Officers (CSOs) particularly, want to be sure that their Security Policies are complied.
-This goal turned hard to achieve since employees are able to use their own devices (laptops, smartphones, and tablets) at work, or at home but for work purposes.
-As this is part of the Bring Your Own Device (BYOD) philosophy and is being adopted by many companies everyday, a number of solutions have arisen in order to adapt it securely.
-In this paper, a novel system to deal with this situation is introduced, named  MUSES (Multiplatform Usable Endpoint Security).
-This system is able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules.
+Enterprises, and particularly their Chief Security Officers (CSOs),
+want to ensure that their Security Policies are complied, but this
+goal turned hard to achieve since employees are able to use, or bring
+their own devices (in what is known as BYOD, bring your own device) at
+work, or at home but for work purposes. As this BYOD philosophy is
+adopted by many companies everyday, a number of solutions have arisen
+in order to adopt it securely. In this paper, a novel system named
+MUSES (Multiplatform Usable Endpoint Security) which should be able 
+to adapt Security Policies to a BYOD environment is introduced. MUSES
+has been designed to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules.
 MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
-This system, still in development, is compared with the most relevant solutions offered by other companies to deal with the same issues as MUSES, remarking the advantages that our system will offer with respect to them.
+This system, still in development, is compared with the most relevant
+solutions offered by other companies to deal with the same issues as
+MUSES, remarking the advantages that our system will offer with
+respect to them. % What do we do in this paper? Present the
+                 % architecture? The prototypes? - JJ
 \end{abstract}

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
First para intro with comments for @unintendedbear: more references

@@
 
-The way on how data has been stored and accessed in the companies has completely changed along the years.
-The use of owned servers being accessed by desktop PCs (and maybe laptops) from inside the company facilities has been transformed into the distribution of these data between a number of machines, even not all belonging to the company, and working over the famous Cloud Computing environment.
-Besides, being stored in the cloud or not, data are being consulted and modified through a wide amount of devices, some of them owned by the company's users.
-This is the so-called Bring Your Own Device (BYOD) philosophy.
-It is becoming highly successful due to the impact that portable devices (such as smartphones and tablets) are having on the market.
+The way on how data has been stored and accessed in companies has
+completely changed along the last years. The scenario where
+company-owned servers are being accessed by desktop PCs (and maybe
+laptops) from inside the company facilities has been transformed into
+another where data, increasingly a company asset, is distributed
+between a number of machines, maybe not all owned by the company, and
+working on the famous Cloud. Besides, being
+stored in the cloud or not, data is being consulted and modified
+through a wide variety of devices, some of them owned by the company's
+employees, in what is called the Bring Your Own Device (BYOD)
+philosophy. This philosophy has become highly successful due to the impact that
+portable devices (such as smartphones and tablets) are having on the
+market. % There should be a reference for this - JJ
 Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies.

### 2015-04-16 Response to reviewers.tex
Working on the response to reviewers, which I have moved to LaTeX

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System: Response to Reviewers\' comments}

\section{Editor's comments}
The referees made the following points about this paper.

Editor comments:\begin{enumerate}
\item The presentation/organisation of the paper needs some revision.
\item The authors should cite previous related work and explain the
  additional contribution of the current proposal.
\end{enumerate}

{\emph The paper has been throughly revised.

\section{Comments by Reviewer \#1}

\begin{verbatim}
The paper describes an ongoing European FP7 research project, MUSES. It mainly covers the concept behind MUSES, the description of the architecture, and a high level description of the soft computing methods to be used, as no actual results have been obtained so far.

A comparison to existing commercial applications is also included, but
this seems taken from their commercial brochures; it does not offer
any clues on how they differ from the functionality offered by MUSES.
\end{verbatim}

The reviewer is right, the state of the art in commercial solutions was quite brief and descriptive.
We have addressed this issue on the revised version of the paper, changing several sections in order to compose a State of the art in applications similar to MUSES, and going deeper in the features that can be compared with those of our system.

***COMPLETAR destacando lo que se haya cambiado para que el revisor perciba que el cambio ha sido gordo***

It is also unclear how this paper differs from previous work by the same authors (and others), which also aimed to describe the system; more specifically:
"Enforcing corporate security policies via computational intelligence techniques", GECCO Comp '14 Proceedings of the 2014 conference companion on Genetic and evolutionary computation Pages 1245-1252

>>> The paper has been improved in a number of ways, making it more distant with respect to our previous works. Moreover, we have remarked in ***Section X (Page Y) the contributions of the present work with respect to the previous ones***

***COMPLETAR UN POCO, JUSTIFICANDO LA IMPORTANCIA DE ESTE TRABAJO***

In this reviewer's opinion, the authors should wait till they have results to present.

>>> The aim of this paper is to present a state of the art... ***COMPLETAR***

The relationship between the scope of the special issue and the subjects dealt by MUSES is also unclear

>>> ***RESPONDER***

\section{Comments by Reviewer \#2}

= Global comments =

I'm concerned about the novelty of the information provided in the document. [REF1] and [REF2] are two already published papers by the same authors.

[REF1] A.M. Mora, P. De las Cuevas, J.J. Merelo, S. Zamarripa, M. Juan, A.I. Esparcia-Alcázar, M. Burvall, H. Arfwedson, and Z. Hodaie,  MUSES A corporate user-centric system which applies CI methods. Presented at the TRECK track at ACM-SAC 2014.
[REF2] A.M. Mora, P. de las Cuevas, J.J. Merelo, S. Zamarripa, A.I. Esparcia-Alcázar, Enforcing Corporate Security Policies via Computational Intelligence Techniques. Presented at the SecDef Workshop at ACM-GECCO 2014. July 2014

Comparing these references with the current article, which includes 21 pages:

- The introduction in page 2 is very similar to the introduction in [REF2]
- Pages 3-4 are the same than section 2 in [REF2]
- Pages 12-15 are strikingly similar to [REF1], even using the same figures.
- Pages 15-19 are a raw copy of [REF2], nearly word by word.
- Pages 19-21 are extremely similar to section 4 in [REF1] and section 5 in [REF2], put together.

>>> The reviewer is right in part, since some of the contents are the same when a system is being described.
We have followed his/her request and changed/improved several parts in the text, namely ***DECIR LAS SECCIONES QUE SE HAYAN CAMBIADO***

Hence, the only *new* research this reviewer is able to identify is section 3 (pages 5-11), which includes a very detailed state-of-the-art of current tools for corporate mobile security. Unfortunately, this is not really a paper focused on the state-of-the-art in this field.

>>> We have transformed the paper into a state-of-the-art of systems similar to MUSES.

***COMPLETAR***

The work is good and based on good ideas, and the fact that it is already accepted in two conferences proves this. This is why I will recommended a MAJOR REVIEW of the paper. In mi opinion, the authors should consider:

a) extending the state-of-the-art section, and converting the paper in a "state of the art" or tools for corporate mobile security. They already provide very detailed descriptions of IBM, Samsung, Sophos and a few other system, but only a hint about WSO2 and Blackphone, which are identified as the main competitors of MUSES in section 5. In this case, sections 4 and 5 are not really needed, but a description of MUSES as another system like the others could be a good idea.

>>> Following the reviewer's suggestions, we have transformed the paper into a state-of-the-art in tools for corporate mobile security. MUSES has been compared with the existing tools in a more detailed way and the description of the system has been reduced in the same way. 
***DECIR LAS SECCIONES CAMBIADAS***

b) reducing the length of the state-of-the-art section, currently too long in my opinion, and adding lots of new information and descriptions of new work, research and results to the sections 4 and 5.

>>> ***DECIR QUE HEMOS OPTADO POR LO PRIMERO AL NO HABER SUFICIENTES RESULTADOS SIN PUBLICAR ACTUALMENTE***

My preferences are for option b). In case the authors are interested, they will find next specific comments for a major revision of the work.

= Specific comments =

According to page 12, line 7 "the user interacts with the devices (...) through the MUSES graphical interface inside his or her own context". This is surprising. I have pictured MUSES as a hyper-visor module but, according to this sentence, MUSES is a GUI that contains every application the user has access to. I think further clarification are needed about how the user interacts with his applications and what this GUI the authors are describing is exactly. Contexts in this sentence "(situation, connection, status)" do not match contexts in figure 2 "(social, economical, political)".

>>> ***REESCRIBIR ESTO CORRECTAMENTE***

Page 13. The first reason to use a client/server architecture is that the event correlation and self-adaptation processes need a very powerful machine (a server), but this statement seems not be based on any real experiment run by the authors or any previous references. In addition, I find the second reason to user a client/server architecture quite surprising. Quoting: "there are two clearly separated parts in the system, namely the users (clients) and the enterprise (server)" I think this is a very weak justification. I can identify many other actors in the system: data providers (cloud system, databases...), other workers in the enterprise (for corporate applications), the friends of the user (for private applications), external application providers... Hence, if the "second reason" is of any real value, MUSES would have a P2P architecture. From my point of view, the reasons given by the authors are too week and, in any case, there is not really any necessity to justify
why MUSES has a client/server architecture.

>>> The reviewer is right. We have rewritten the paragraph justifying the use of a server machine due to its computational power, needed for applying Data Mining and Machine Learning techniques over Big Datasets, and also to centralise the data gathering of the system. We have removed the text explaining the consideration of two parts in the system.

Page 13, line 45 says all data in MUSES will be encrypted. It is not clear if the authors mean "the Decision Table and the even logger", or "all data in the devices, including personal data, contact list, emails..." If it is the latter, authors should explain how MUSES enforces this policy. Does it control all applications in the mobile phone? Does the mobile phone run only white-listed applications?

>>> ***EXPLICAR ESTO MEJOR***

Some specific examples about the kind of user activity MUSES monitors and the kind of actuators MUSES implements will be welcome. As is, sensors and actuators seem like a general idea and readers will understand the system better with specific examples.

>>> ***PONER EJEMPLOS DE SENSORES Y MONITORIZACIÓN***

Page 14, line 47 identifies the MusCRTEP as the core of the MUSES system and provides two references. Unfortunately, these references are not the implementation of MusCRTEP but a general definition of what a decision system does. These references are not really needed and a much more detailed description of MusCRTEP would be welcome since even the authors identify this module as the core of the system.

>>> The description of the performance of the CRTEP has been extended and improved, with references to two Project Reports which better fit to the contents.

Page 18, lines 20-37 hint about the importance of privacy enhancing technologies in a system that monitors the activity of the user and sends this activity to a centralized server to be "anonymously managed". Further information about how the system manages this information is needed (does private information ever leaves the personal devices? Which activity is monitored and collected?), as well as an explanation about how these data is anonymized. Is it anonymized at the mobile phone? Or in the server's database?

>>> The way user data is anonymised in the system, as long as other legal aspects about the data privacy, have been properly detailed, as well as complemented with a reference.

\end{document}

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Working on the response to reviewers, which I have moved to LaTeX

@@
 market. % There should be a reference for this - JJ
-Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies.
-Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems.
-For instance, the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).
+Data security and privacy are key factors for a company, thus, in
+order to protect them, it is usual to define Organisational Security
+Policies. Their definition is nowadays a very difficult problem, since
+the BYOD tendency means that several factors must be considered
+\cite{Opp_Security11}, most of them previously ignored or non
+considered in security systems. For instance, the current mixture
+between personal and professional information in these devices (the
+user could navigate inside social networks where there could be
+friends and also company partners or clients).
 

### 2015-04-16 Response to reviewers.tex
Moving stuff to the new LaTeX document. Still some formatting to do. Please @amorag @fergunet @unintendedbear update

@@
 \begin{verbatim}
-The paper describes an ongoing European FP7 research project, MUSES.
-It mainly covers the concept behind MUSES, the description of the architecture, and a high level description of the soft computing methods to be used, as no actual results have been obtained so far.
+The paper describes an ongoing European FP7 research project,
+MUSES. It mainly covers the concept behind MUSES, the description of
+the architecture, and a high level description of the soft computing
+methods to be used, as no actual results have been obtained so far.
 
@@
 The reviewer is right, the state of the art in commercial solutions was quite brief and descriptive.
-We have addressed this issue on the revised version of the paper, changing several sections in order to compose a State of the art in applications similar to MUSES, and going deeper in the features that can be compared with those of our system.
+We have addressed this issue on the revised version of the paper,
+changing several sections in order to compose a State of the art in
+applications similar to MUSES, and going deeper in the features that
+can be compared with those of our system.
 
@@
 
-It is also unclear how this paper differs from previous work by the same authors (and others), which also aimed to describe the system; more specifically:
-"Enforcing corporate security policies via computational intelligence techniques", GECCO Comp '14 Proceedings of the 2014 conference companion on Genetic and evolutionary computation Pages 1245-1252
+\begin{verbatim}
+It is also unclear how this paper differs from previous work by the
+same authors (and others), which also aimed to describe the system;
+more specifically: 
+"Enforcing corporate security policies via computational intelligence
+techniques", GECCO Comp '14 Proceedings of the 2014 conference
+companion on Genetic and evolutionary computation Pages 1245-1252  
+\end{verbatim}
 
->>> The paper has been improved in a number of ways, making it more distant with respect to our previous works.
-Moreover, we have remarked in ***Section X (Page Y) the contributions of the present work with respect to the previous ones***
+The paper has been improved in a number of ways, making it more
+distant with respect to our previous works. Moreover, we have remarked
+in ***Section X (Page Y) the contributions of the present work with
+respect to the previous ones***
 
@@
 
-In this reviewer's opinion, the authors should wait till they have results to present.
+\begin{verbatim}
+In this reviewer's opinion, the authors should wait till they have
+results to present. 
+\end{verbatim}
 
@@
 
-The relationship between the scope of the special issue and the subjects dealt by MUSES is also unclear
+\begin{verbatim}
+The relationship between the scope of the special issue and the
+subjects dealt by MUSES is also unclear
+\end{verbatim}
 
@@
 
+\begin{verbatim}
+
 = Global comments =
 
-I'm concerned about the novelty of the information provided in the document. [REF1] and [REF2] are two already published papers by the same authors.
+I'm concerned about the novelty of the information provided in the
+document. [REF1] and [REF2] are two already published papers by the
+same authors.
 
-[REF1] A.M.
-Mora, P.
-De las Cuevas, J.J.
-Merelo, S.
-Zamarripa, M.
-Juan, A.I.
-Esparcia-Alcázar, M.
-Burvall, H.
-Arfwedson, and Z.
-Hodaie,  MUSES A corporate user-centric system which applies CI methods.
-Presented at the TRECK track at ACM-SAC 2014.
-[REF2] A.M.
-Mora, P.
-de las Cuevas, J.J.
-Merelo, S.
-Zamarripa, A.I.
-Esparcia-Alcázar, Enforcing Corporate Security Policies via Computational Intelligence Techniques.
-Presented at the SecDef Workshop at ACM-GECCO 2014.
-July 2014
+[REF1] A.M. Mora, P. De las Cuevas, J.J. Merelo, S. Zamarripa,
+M. Juan, A.I. Esparcia-Alcázar, M. Burvall, H. Arfwedson, and
+Z. Hodaie,  MUSES A corporate user-centric system which applies CI
+methods. Presented at the TRECK track at ACM-SAC 2014. 
+[REF2] A.M. Mora, P. de las Cuevas, J.J. Merelo, S. Zamarripa,
+A.I. Esparcia-Alcázar, Enforcing Corporate Security Policies via
+Computational Intelligence Techniques. Presented at the SecDef
+Workshop at ACM-GECCO 2014. July 2014
 
@@
 
->>> The reviewer is right in part, since some of the contents are the same when a system is being described.
+\end{verbatim}
+
+The reviewer is right in part, since some of the contents are the same when a system is being described.
 We have followed his/her request and changed/improved several parts in the text, namely ***DECIR LAS SECCIONES QUE SE HAYAN CAMBIADO***
 
-Hence, the only *new* research this reviewer is able to identify is section 3 (pages 5-11), which includes a very detailed state-of-the-art of current tools for corporate mobile security.
-Unfortunately, this is not really a paper focused on the state-of-the-art in this field.
+\begin{verbatim}
+Hence, the only *new* research this reviewer is able to identify is
+section 3 (pages 5-11), which includes a very detailed
+state-of-the-art of current tools for corporate mobile
+security. Unfortunately, this is not really a paper focused on the
+state-of-the-art in this field.
+\end{verbatim}
 
@@
 
-The work is good and based on good ideas, and the fact that it is already accepted in two conferences proves this.
-This is why I will recommended a MAJOR REVIEW of the paper.
-In mi opinion, the authors should consider:
+\begin{verbatim}
+The work is good and based on good ideas, and the fact that it is
+already accepted in two conferences proves this. This is why I will
+recommended a MAJOR REVIEW of the paper. In mi opinion, the authors
+should consider:
 
-a) extending the state-of-the-art section, and converting the paper in a "state of the art" or tools for corporate mobile security.
-They already provide very detailed descriptions of IBM, Samsung, Sophos and a few other system, but only a hint about WSO2 and Blackphone, which are identified as the main competitors of MUSES in section 5.
-In this case, sections 4 and 5 are not really needed, but a description of MUSES as another system like the others could be a good idea.
+a) extending the state-of-the-art section, and converting the paper in
+a "state of the art" or tools for corporate mobile security. They
+already provide very detailed descriptions of IBM, Samsung, Sophos and
+a few other system, but only a hint about WSO2 and Blackphone, which
+are identified as the main competitors of MUSES in section 5. In this
+case, sections 4 and 5 are not really needed, but a description of
+MUSES as another system like the others could be a good idea. 
+\end{verbatim}
 
->>> Following the reviewer's suggestions, we have transformed the paper into a state-of-the-art in tools for corporate mobile security.
+Following the reviewer's suggestions, we have transformed the paper into a state-of-the-art in tools for corporate mobile security.
 MUSES has been compared with the existing tools in a more detailed way and the description of the system has been reduced in the same way.
@@
 
-b) reducing the length of the state-of-the-art section, currently too long in my opinion, and adding lots of new information and descriptions of new work, research and results to the sections 4 and 5.
+\begin{verbatim}
+b) reducing the length of the state-of-the-art section, currently too
+long in my opinion, and adding lots of new information and
+descriptions of new work, research and results to the sections 4 and
+5. 
+\end{verbatim}
 
@@
 
-My preferences are for option b). In case the authors are interested, they will find next specific comments for a major revision of the work.
+\begin{verbatim}
+My preferences are for option b). In case the authors are interested,
+they will find next specific comments for a major revision of the
+work.
+\end{verbatim}
 
+\begin{verbatim}
 = Specific comments =
 
-According to page 12, line 7 "the user interacts with the devices (...) through the MUSES graphical interface inside his or her own context".
-This is surprising.
-I have pictured MUSES as a hyper-visor module but, according to this sentence, MUSES is a GUI that contains every application the user has access to.
-I think further clarification are needed about how the user interacts with his applications and what this GUI the authors are describing is exactly.
-Contexts in this sentence "(situation, connection, status)" do not match contexts in figure 2 "(social, economical, political)".
+According to page 12, line 7 "the user interacts with the devices
+(...) through the MUSES graphical interface inside his or her own
+context". This is surprising. I have pictured MUSES as a hyper-visor
+module but, according to this sentence, MUSES is a GUI that contains
+every application the user has access to. I think further
+clarification are needed about how the user interacts with his
+applications and what this GUI the authors are describing is
+exactly. Contexts in this sentence "(situation, connection, status)"
+do not match contexts in figure 2 "(social, economical, political)".
+\end{verbatim}
 
@@
 
-Page 13.
-The first reason to use a client/server architecture is that the event correlation and self-adaptation processes need a very powerful machine (a server), but this statement seems not be based on any real experiment run by the authors or any previous references.
-In addition, I find the second reason to user a client/server architecture quite surprising.
-Quoting: "there are two clearly separated parts in the system, namely the users (clients) and the enterprise (server)" I think this is a very weak justification.
-I can identify many other actors in the system: data providers (cloud system, databases...), other workers in the enterprise (for corporate applications), the friends of the user (for private applications), external application providers...
-Hence, if the "second reason" is of any real value, MUSES would have a P2P architecture.
-From my point of view, the reasons given by the authors are too week and, in any case, there is not really any necessity to justify
+\begin{verbatim}
+Page 13. The first reason to use a client/server architecture is that
+the event correlation and self-adaptation processes need a very
+powerful machine (a server), but this statement seems not be based on
+any real experiment run by the authors or any previous references. In
+addition, I find the second reason to user a client/server
+architecture quite surprising. Quoting: "there are two clearly
+separated parts in the system, namely the users (clients) and the
+enterprise (server)" I think this is a very weak justification. I can
+identify many other actors in the system: data providers (cloud
+system, databases...), other workers in the enterprise (for corporate
+applications), the friends of the user (for private applications),
+external application providers... Hence, if the "second reason" is of
+any real value, MUSES would have a P2P architecture. From my point of
+view, the reasons given by the authors are too week and, in any case,
+there is not really any necessity to justify 
 why MUSES has a client/server architecture.
+\end{verbatim}
 
->>> The reviewer is right.
+The reviewer is right.
 We have rewritten the paragraph justifying the use of a server machine due to its computational power, needed for applying Data Mining and Machine Learning techniques over Big Datasets, and also to centralise the data gathering of the system.
@@
 
-Page 13, line 45 says all data in MUSES will be encrypted.
-It is not clear if the authors mean "the Decision Table and the even logger", or "all data in the devices, including personal data, contact list, emails..." If it is the latter, authors should explain how MUSES enforces this policy.
-Does it control all applications in the mobile phone?
-Does the mobile phone run only white-listed applications?
+\begin{verbatim}
+Page 13, line 45 says all data in MUSES will be encrypted. It is not
+clear if the authors mean "the Decision Table and the even logger", or
+"all data in the devices, including personal data, contact list,
+emails..." If it is the latter, authors should explain how MUSES
+enforces this policy. Does it control all applications in the mobile
+phone? Does the mobile phone run only white-listed applications? 
+\end{verbatim}
 
@@
 
-Some specific examples about the kind of user activity MUSES monitors and the kind of actuators MUSES implements will be welcome.
-As is, sensors and actuators seem like a general idea and readers will understand the system better with specific examples.
+\begin{verbatim}
+Some specific examples about the kind of user activity MUSES monitors
+and the kind of actuators MUSES implements will be welcome. As is,
+sensors and actuators seem like a general idea and readers will
+understand the system better with specific examples.
+\end{verbatim}
 
@@
 
-Page 14, line 47 identifies the MusCRTEP as the core of the MUSES system and provides two references.
-Unfortunately, these references are not the implementation of MusCRTEP but a general definition of what a decision system does.
-These references are not really needed and a much more detailed description of MusCRTEP would be welcome since even the authors identify this module as the core of the system.
+\begin{verbatim}
+Page 14, line 47 identifies the MusCRTEP as the core of the MUSES
+system and provides two references. Unfortunately, these references
+are not the implementation of MusCRTEP but a general definition of
+what a decision system does. These references are not really needed
+and a much more detailed description of MusCRTEP would be welcome
+since even the authors identify this module as the core of the
+system. 
+\end{verbatim}
 
->>> The description of the performance of the CRTEP has been extended and improved, with references to two Project Reports which better fit to the contents.
+The description of the performance of the CRTEP has been extended
+and improved, with references to two Project Reports which better fit
+to the contents.
 
-Page 18, lines 20-37 hint about the importance of privacy enhancing technologies in a system that monitors the activity of the user and sends this activity to a centralized server to be "anonymously managed".
-Further information about how the system manages this information is needed (does private information ever leaves the personal devices?
-Which activity is monitored and collected?), as well as an explanation about how these data is anonymized.
-Is it anonymized at the mobile phone?
-Or in the server's database?
+\begin{verbatim}
+Page 18, lines 20-37 hint about the importance of privacy enhancing
+technologies in a system that monitors the activity of the user and
+sends this activity to a centralized server to be "anonymously
+managed". Further information about how the system manages this
+information is needed (does private information ever leaves the
+personal devices? Which activity is monitored and collected?), as well
+as an explanation about how these data is anonymized. Is it anonymized
+at the mobile phone? Or in the server's database? 
+\end{verbatim}
 

### 2015-04-16 Response to reviewers.tex
Adds references to previous works
Checks what has been done to improve the paper in general and changes with respect to the old version. Closes #12 if @amorag or @unintendedbear do not say anything else.

@@
 The reviewer is right in part, since some of the contents are the same when a system is being described.
-We have followed his/her request and changed/improved several parts in the text, namely ***DECIR LAS SECCIONES QUE SE HAYAN CAMBIADO***
+We have followed his/her request and changed/improved several parts in
+the text, namely  \begin{itemize}
+\item The background has been corrected and expanded.
+\item References to papers mentioned by the reviwers and how they
+  compare with the current paper (and situation in the project) have
+  been added to the introduction.
+\item Many more papers have been reviewed and referenced. The
+  reference section has grown by half.
+\item BYOD solutions have been compared among themselves, and with
+  MUSES (section 5).
+\item The paper reflects the current, so far unpublished, state of
+  Muses architecture and implementation.
 
@@
 
->>> We have transformed the paper into a state-of-the-art of systems similar to MUSES.
-
-***COMPLETAR***
+As suggested by the reviewer, we have transformed the paper into a
+state-of-the-art of systems that offer functionalities that are
+similar to MUSES. The paper has been
+almost completely rewritten to reflect the state of the art including
+changes from the time the first paper was submitted (Samsung dropping
+KNOX, for instance).
 
@@
 
-Following the reviewer's suggestions, we have transformed the paper into a state-of-the-art in tools for corporate mobile security.
-MUSES has been compared with the existing tools in a more detailed way and the description of the system has been reduced in the same way.
+Following the reviewer's suggestions, we have transformed the paper
+into a state-of-the-art in tools for corporate mobile security. MUSES
+has been compared with the existing tools in a more detailed way and
+the description of the system has been reduced in the same way.  
 ***DECIR LAS SECCIONES CAMBIADAS***
@@
 
-The reviewer is right.
-We have rewritten the paragraph justifying the use of a server machine due to its computational power, needed for applying Data Mining and Machine Learning techniques over Big Datasets, and also to centralise the data gathering of the system.
-We have removed the text explaining the consideration of two parts in the system.
+The reviewer is right. We have rewritten the paragraph justifying the
+use of a server machine due to its computational power, needed for
+applying Data Mining and Machine Learning techniques over Big
+Datasets, and also to centralise the data gathering of the system. We
+have removed the text explaining the consideration of two parts in the
+system.
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Añadidas alguans anotaciones
Adds references to previous works
Checks what has been done to improve the paper in general and changes with respect to the old version. Closes #12 if @amorag or @unintendedbear do not say anything else.

@@
 MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
-This system, still in development, is compared with the most relevant
+This system, which has released its first prototypes this year, is compared with the most relevant
 solutions offered by other companies to deal with the same issues as
@@
 This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company's data borders have changed in the last years, so now the users can access significant data from outside the enterprise, and possibly through a non absolutely secure channel.
+%Antares - Yo quitaba lo de significant loss of data, ya que significant se repite después.
 
-Thus, this work introduces a novel (still in development) system named MUSES, from Multiplatform Usable Endpoint Security, which is a dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a set of security rules defined as specifications of the Corporate Security Policies, but with the ability of `learning' from the user's past behaviour and adapt the set of rules, or even inferring new ones, in order to deal with potential future security incidents due to the user's.
-%FERGU: The user's "algo que falta"?
-o eso hace referencia a su culpa?
-Then the system will react, in a non-intrusive way, to the potentially dangerous sequence of actions (events) that he or she is conducting at any time.
+Thus, this work introduces a recently released (in alpha) system named
+MUSES, from Multiplatform Usable Endpoint Security, which is a
+dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
+set of security rules defined as specifications of the Corporate
+Security Policies, but with the ability of `learning' from the user's
+past behaviour and adapt the set of rules, or even inferring new ones,
+in order to deal with potential future security incidents due to the
+user's. %FERGU: The user's "algo que falta"? o eso hace referencia a
+        %su culpa? 
+%"lo del usuario", literalmente. Pero mejorquitarlo - JJ
+Then the system will react, in a non-intrusive way, to the potentially
+dangerous sequence of actions (events) that he or she is conducting at
+any time.
 
-To this end MUSES will analyse the users' behaviour by means of Data Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning (ML) methods \cite{MachineLearning_Bishop06}, extracting a set of patterns which will be later processed by means of Computational Intelligence (CI) algorithms, namely Evolutionary Computation methods \cite{EAs_Back96,GP_Koza92}.
+To this end MUSES analyses the users' behaviour by means of Data
+Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
+(ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
+patterns which will be later processed by means of Computational
+Intelligence (CI) algorithms, namely Evolutionary Computation methods
+\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
+already presented in
+\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
+the implementation was in its early stages when those papers were
+submitted. After the release of the first prototypes and additional
+work on the data mining techniques used \cite{mora14:urls} we have a
+clearer idea of MUSES capabilities and, as such, will be presented in
+this paper.
 
@@
 The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.
+%Antares - Yo podrían en lugar de ``next year'' el año, porque el artículo puede ser leído en cualquier momento y es mejor emplear referencias absolutas, ¿no creeis?
 
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{review_muses} %geneura-latin1
-
-% Antonio - Poner la bibliografía en fichero .bib
-
-%\begin{thebibliography}{00}
-
-%\bibitem{ids13}
-%Sommestad T., Hunstad A.. \emph{Intrusion detection and the role of the system administrator.}, from Swedish Defence Research Agency (FOI), Linköping, Sweden, 2013.
-
-%\bibitem{m2m12}
-%NTT DOCOMO, \emph{DOCOMO to Launch Global M2M Platform}, in M2M Magazine, December 2012.
-%http://www.machinetomachinemagazine.com/2012/12/05/docomo-to-launch-global-m2m-platform/.
-
-%\bibitem{suites12}
-%The Radicati Group Inc., report \emph{Microsoft Office 365 - Analysis and Forecast, 2012-2016}. June 2012.
-
-%\bibitem{Adams_Users05}
-%Adams, A. and Sasse, A.:
-%\newblock {\em Users are not the enemy}.
-%\newblock Security and Usability: Designing Systems That People Can Use.
-%  O\'Reilly Associations, 2005.
-
-%\bibitem{cost_adjustment_07}
-%Alfaro-Cid, E., Sharman, K. and Esparcia-Alcázar, A.I.:
-%\newblock A genetic programming approach for bankruptcy prediction using a
-%  highly unbalanced database.
-%\newblock In M.~Giacobini, editor, {\em Applications of Evolutionary
-%  Computing}, volume 4448 of {\em Lecture Notes in Computer Science}, pages
-%  169--178. Springer Berlin Heidelberg, 2007.
-
-%\bibitem{AzurriMDM}
-%Azurri Communications.
-%\newblock Icon Mobilise.
-%\newblock \url{http://www.azzurricommunications.com/~/media/Resources/Brochures/Media/icon_mobilise_brochure_online.ashx}
-
-%\bibitem{SecPolComp12}
-%Al-Omari, A., El-Gayar, O., Deokar, A., and Walters, J.: \emph{Security Policy Compliance: User Acceptance Perspective}. 45th Hawaii International
-%Conference on System Sciences (pp. 3317-3326). IEEE, 2012.
-
-%\bibitem{BYOD13}
-%Bacik, S.: \emph{Security Implications of Bring Your Own Device, IT Consumerization, and Managing User Choices}, in Information Security Management Handbook, Sixth Edition, Volume 7, pp.
-133-142, 2013.
-
-%\bibitem{EAs_Back96}
-%Back, T.:
-%\newblock {\em Evolutionary algorithms in theory and practice}.
-%\newblock Oxford University Press, 1996.
-
-%\bibitem{MachineLearning_Bishop06}
-%Bishop, C.:
-%\newblock {\em Pattern recognition and Machine Learning}.
-%\newblock Springer, 2006.
-
-%\bibitem{Blackberry_tool}
-%Blackberry.
-%\newblock Blackberry balance.
-%\newblock \url{http://es.blackberry.com/business/software/blackberry-balance.html}
-
-%\bibitem{Blackphone}
-%Blackphone.
-%\newblock \url{https://www.blackphone.ch/}
-
-%\bibitem{SecPolComp10}
-%Bulgurcu, B., Cavusoglu, H., and Benbasat, I.: \emph{Information security policy compliance: an empirical study of rationality-based beliefs and information security awareness}.
-MIS Quarterly, 34(3), 523-548.
-2010.
-
-%\bibitem{botnet_detection_clustering_09}
-%Chang, S. and Daniels, T.E.:
-%\newblock P2P botnet detection using behavior clustering \& statistical tests.
-%\newblock In {\em Proceedings of the 2nd ACM Workshop on Security and
-%  Artificial Intelligence}, AISec '09, pages 23--30, New York, NY, USA, 2009.
-%  ACM.
-
-%\bibitem{SecPol09}
-%Cresson Wood, C. and Lineman, D.: \emph{Information Security Policies Made Easy Version 11}. Information Shield, Inc. 2009.
-
-%\bibitem{inferring_policies_socialnetworks_09}
-%Danezis, G.:
-%\newblock Inferring privacy policies for social networking services.
-%\newblock In {\em Proceedings of the 2Nd ACM Workshop on Security and
-%  Artificial Intelligence}, AISec '09, pages 5--10, New York, NY, USA, 2009.
-%  ACM.
-
-%\bibitem{Good_tool}
-%Good's Technology.
-%\newblock BYOD Solution.
-%\newblock
-%  \url{http://www1.good.com/secure-mobility-solution/bring-your-own-device.html}
-
-%\bibitem{GAs_Goldberg89}
-%Goldberg, D.E.:
-%\newblock {\em Genetic Algorithms in search, optimization and machine
-%  learning}.
-%\newblock Addison Wesley, 1989.
-
-%\bibitem{FeatureSelection_Guyon03}
-%Guyon, I.,  and Elisseeff, A.:
-%\newblock An introduction to variable and feature selection.
-%\newblock {\em J. Mach. Learn. Res.}, 3:1157--1182, 2003.
-
-%\bibitem{PatternMining_Han07}
-%Han, J., Cheng, H., Xin, D., and Yan, X.:
-%\newblock Frequent pattern mining: Current status and future directions.
-%\newblock {\em Data Min. Knowl. Discov.}, 15(1):55--86, 2007.
-
-%\bibitem{SecPolPenalty09}
-%Herath, T., and Rao, H.R.: \emph{Protection motivation and deterrence: a framework for security policy compliance in organisations}.
-European Journal of Information Systems, vol.
-18, pp.
-106-125, 2009.
-
-%\bibitem{IBM_tool}
-%IBM.
-%\newblock Hosted mobile device security management.
-%\newblock
-%\url{http://www-935.ibm.com/services/us/en/it-services/managed-security-services-cloud-computing} \url{ -hosted-mobile-device-security-management.html}
-
-%\bibitem{Clustering_Jain99}
-%Jain, A.K., Murty, M.N., and Flynn, P.~J.:
-%\newblock Data clustering: A review.
-%\newblock {\em ACM Comput. Surv.}, 31(3):264--323, Sept. 1999.
-
-%\bibitem{imbalance_techniques_02}
-%Japkowicz, N. and Stephen, S.:
-%\newblock The class imbalance problem: A systematic study.
-%\newblock {\em Intell. Data Anal.}, 6(5):429--449, Oct. 2002.
-
-%\bibitem{ibm11}
-%Kao, I-L.: \emph{IBM Security Services. Securing mobile devices in the business environment}, IBM, 2011.
-
-%\bibitem{feature_selection_anomalies_08}
-%Kloft, M., Brefeld, U., D\"{u}essel, P., Gehl, C. and Laskov, P.:
-%\newblock Automatic feature selection for anomaly detection.
-%\newblock In {\em Proceedings of the 1st ACM Workshop on Workshop on AISec},
-%  AISec '08, pages 71--76, New York, NY, USA, 2008. ACM.
-
-%\bibitem{GP_Koza92}
-%Koza, J.~R.:
-%\newblock {\em Genetic Programming: On the programming of computers by means of
-%  natural selection}.
-%\newblock MIT Press, Cambridge, MA, 1992.
-
-%\bibitem{EAs_securitycosts-kirta} 
-%Kirta, T., and Kivimaab, J.: Optimizing it security costs by evolutionary algorithms. In C. Czosseck and K. Podins, editors, Conference on Cyber Con ict,pages 145-160, CCD COE Publications, 2010.
-
-%\bibitem{DataMining_Lee01}
-%Lee, S.J. and Siau, K.:
-%\newblock A review of data mining techniques.
-%\newblock {\em Industrial Management \& Data Systems}, 101(1):41--46, 2001.
-
-%\bibitem{user_classification_ml_13}
-%Leontjeva, A., Goldszmidt, M., Xie, Y., Yu, F. and Abadi, M.:
-%\newblock Early security classification of skype users via machine learning.
-%\newblock In {\em Proceedings of the 2013 ACM Workshop on Artificial
-%  Intelligence and Security}, AISec '13, pages 35--44, New York, NY, USA, 2013.
-%  ACM.
-
-%\bibitem{sec_policy_evolution_gp_08}
-%Lim, Y.T., Cheng, P.C., Rohatgi, P. and Clark, J.A.:
-%\newblock Mls security policy evolution with genetic programming.
-%\newblock In {\em Proceedings of the 10th Annual Conference on Genetic and
-%  Evolutionary Computation}, GECCO '08, pages 1571--1578, New York, NY, USA,
-%  2008. ACM.
-
-%\bibitem{MIT05}
-%Lippmann, R.P., Ingols, K.W., Scott, C., Piwowarski, K., Kratkiewicz, K.J., Artz, M., and Cunningham, R.K.: \emph{Evaluating and Strengthening Enterprise
-%Network Security Using Attack Graphs}. Project Report IA-2. Lincoln Laboratory, Massachusetts Institute of Technology, October 2005.
-
-%\bibitem{GP_intrusion-lu} Lu, W.
-and Traore, L.: Detecting new forms of network intrusion using genetic programming.
-In Proceedings of the 2003 Congress on Evolutionary Computation, pages 2165-2172, 2003.
-
-%\bibitem{EventProcessing_Luckham02}
-%Luckham, D.:
-%\newblock {\em The Power of Events: An Introduction to Complex Event Processing
-%  in Distributed Enterprise Systems}.
-%\newblock Addison-Wesley, MA, USA, 2002.
-
-%\bibitem{classification_67}
-%MacQueen, J.:
-%\newblock Some methods for classification and analysis of multivariate
-%  observations.
-%\newblock In {\em Proceedings of the fifth Berkeley symposium on mathematical
-%  statistics and probability}, volume~1, page~14. California, USA, 1967.
-
-%\bibitem{GA_intrusion-majeed} Majeed, P.G.
-and Kumar, S.
-Genetic algorithms in intrusion detection systems: A survey.
-International Journal of Innovation and Applied Studies, 5(3):233-240, March 2014.
-
-%\bibitem{Opp_Security11}
-%Oppliger, R.:
-%\newblock Security and privacy in an online world.
-%\newblock {\em IEEE Computer}, 44(9):21--22, September 2011.
-
-%\bibitem{android11}
-%Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}.
-MobiSec Session on Smartphone Security, Aalborg 2011.
-
-%\bibitem{BigData_11}
-%Ratner, B.:
-%\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
-%  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
-%\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.
-
-%\bibitem{policy_generation_clustering_10}
-%Samak, T. and Al-Shaer, E.:
-%\newblock Synthetic security policy generation via network traffic clustering.
-%\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
-%  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
-%  ACM.
-
-%\bibitem{Samsung_tool}
-%Samsung KNOX.
-%\newblock
-%  \url{https://www.samsungknox.com}
-
-%\bibitem{Schu_SecPatterns05}
-%Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
-%  Sommerlad, P.:
-%\newblock {\em Security Patterns: Integrating Security and Systems
-%  Engineering}.
-%\newblock John Wiley \& sons, 2005.
-
-%\bibitem{RT2AE_SOTICS13}
-%Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
-%\newblock A survey of trust and risk metrics for a BYOD mobile working world.
-%\newblock In {\em Third International Conference on Social Eco-Informatics
-%  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.
-
-%\bibitem{SecPolComp09}
-%Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
-%awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.
-
-%\bibitem{SecPolComp07}
-%Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}.
-In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp.
-133-144, 2007.
-
-%\bibitem{AAI_book_2009}
-%Solanas, A. and Martínez-bal, A.:
-%\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
-%  Security}.
-%\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.
-
-%\bibitem{Sophos_tool}
-%Sophos.
-%\newblock Mobile control.
-%\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}
-%
-%\bibitem{rule_generation_gp_09}
-%Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
-%\newblock Automatic rule generation based on genetic programming for event
-%  correlation.
-%\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
-%  Computational Intelligence in Security for Information Systems}, volume~63 of
-%  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
-%  Berlin Heidelberg, 2009.
-
-%\bibitem{risk_reduction_ga_12}
-%Tamjidyamcholo, A.:
-%\newblock Genetic algorithm approach for risk reduction of information
-%  security.
-%\newblock {\em International Journal of Cyber-Security and Digital Forensics
-%  (IJCSDF)}, 1(1), 2012.
-
-%\bibitem{SurveyEventCorrelation_Tiffany02}
-%Tiffany, M.:
-%\newblock A survey of event correlation techniques and related topics.
-%\newblock Research paper, Georgia Institute of Technology, 2002.
-
-%\bibitem{WorxSDK}
-%Citrix.
-%\newblock Worx App SDK.
-%\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}
-%
-%\bibitem{WSO2_tool}
-%WSO2.
-%\newblock Enterprise Mobility Manager.
-%\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}
-
-%\bibitem{GA_networksecurity-zarza} 
-%Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358.
-World Scientific, 2010.
-%
-%\bibitem{GA_cryptographicprotocols-zarza2} 
-%Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques.
-In M.
-Malek, E.
-Fernández-Medina, and J.
-Hernando, editors, SECRYPT, pages 316-319.
-INSTICC Press, 2006.
-
-%\end{thebibliography}
+\bibliography{review_muses,geneura-latin1}
 

### 2015-04-16 Response to reviewers.tex
Continuing with response to reviewers

@@
 
-***COMPLETAR destacando lo que se haya cambiado para que el revisor perciba que el cambio ha sido gordo***
+We have also compared this solutions with the current features of the
+MUSES prototype, which is already being used in tests, in Section 5.
 
@@
 distant with respect to our previous works. Moreover, we have remarked
-in ***Section X (Page Y) the contributions of the present work with
-respect to the previous ones***
+in the introduction the contributions of the present work with
+respect to the previous ones, and included also references to other
+research whose result has been included in Muses, for instance:
 
-***COMPLETAR UN POCO, JUSTIFICANDO LA IMPORTANCIA DE ESTE TRABAJO***
+[10] A. Mora, P. De las Cuevas, J. Merelo, Going a step beyond the black and
+white lists for url accesses in the enterprise by means of categorical classi-
+fiers, in: A. Rosa, J. J. Merelo, J. Filipe (Eds.), ECTA 2014 - Proceedings
+of the International Conference on Evolutionary Computation Theory and
+Applications, 2014, pp. 125–134.
 
@@
 
->>> The aim of this paper is to present a state of the art... ***COMPLETAR***
+Although in this version of the paper we make reference to the release
+of the first versions of MUSES, the main objective  of this paper is
+to present a state of the art in BYOD and how the issues present in
+this area are addressed using computational intelligence techniques.
 
@@
 
->>> ***RESPONDER***
+Security and privacy are obviously the main concerns of MUSES: data
+security and user privacy. The BYOD philosophy tries to maintain data
+security while keeping the privacy of the user's own data and
+applications, so we think that the current version of the paper are in
+scope of the special issue. The new introduction tries to make this
+clearer.
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Addressing more reviewer comments, but some remain to be done by @amorag and @unintendedbear
Re-writing abstract trying to include the structure problem->solution->did we solve it?

@@
 want to ensure that their Security Policies are complied, but this
-goal turned hard to achieve since employees are able to use, or bring
-their own devices (in what is known as BYOD, bring your own device) at
-work, or at home but for work purposes. As this BYOD philosophy is
-adopted by many companies everyday, a number of solutions have arisen
-in order to adopt it securely. In this paper, a novel system named
-MUSES (Multiplatform Usable Endpoint Security) which should be able 
-to adapt Security Policies to a BYOD environment is introduced. MUSES
-has been designed to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules.
-MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
-This system, which has released its first prototypes this year, is compared with the most relevant
-solutions offered by other companies to deal with the same issues as
-MUSES, remarking the advantages that our system will offer with
-respect to them. % What do we do in this paper? Present the
+goal turned hard to achieve since employees are able to use, or bring,
+their personal devices at work. This has been named as ``Bring Your Own Device'' (BYOD). % <- Problem
+As this BYOD philosophy is being adopted by many companies everyday, a number of solutions have appeared in the market, 
+in order to adapt to it in a secure way. In this paper, a novel and open source system named
+MUSES (Multiplatform Usable Endpoint Security), able 
+to securely manage BYOD environments, is described. % <- Solution
+MUSES has been developed to cope with security issues with regard to enterprise security policies, but as a user-centric tool.
+It considers users' behaviour in order to adapt, improve, or even increase the defined set of security rules.
+To do this, the system applies Machine Learning and Computational Intelligence techniques, being also able to predict future security incidences produced by these users.
+% <- Solution, details.
+MUSES, which has released its first prototype this year, is compared with the most relevant
+solutions offered by other companies to deal with the same issues as, remarking the advantages that our system will offer with
+respect to them. % <- we will explain why is better in the work
+
+% What do we do in this paper? Present the
                  % architecture? The prototypes? - JJ

### 2015-04-16 Response to reviewers.tex

@@
 
-[10] A. Mora, P. De las Cuevas, J. Merelo, Going a step beyond the black and
+[10] A. Mora, P. De las Cuevas, J. J.  Merelo, Going a step beyond the black and
 white lists for url accesses in the enterprise by means of categorical classi-
@@
 of the International Conference on Evolutionary Computation Theory and
-Applications, 2014, pp. 125–134.
+Applications, 2014, pp. 125-134.
 
@@
 - Pages 15-19 are a raw copy of [REF2], nearly word by word.
-- Pages 19-21 are extremely similar to section 4 in [REF1] and section 5 in [REF2], put together.
+- Pages 19-21 are extremely similar to section 4 in [REF1] and section
+5 in [REF2], put together.
 
@@
   Muses architecture and implementation. 
+\end{itemize}
 
@@
 has been compared with the existing tools in a more detailed way and
-the description of the system has been reduced in the same way.  
-***DECIR LAS SECCIONES CAMBIADAS***
+the description of the system has been reduced in the same way. All
+sections have been rewritten and new sub-sections have been added to
+more accurately reflect the state of the art.
 
@@
 
->>> ***DECIR QUE HEMOS OPTADO POR LO PRIMERO AL NO HABER SUFICIENTES RESULTADOS SIN PUBLICAR ACTUALMENTE***
+We have found more interesting to follow the first suggestion, for
+which we are grateful, leaving this for future work.
 
@@
 \end{verbatim}
+
+Option {\em a)} was actually closer to our initial intention when
+submitting this paper, so we opted for it.
 
@@
 
->>> ***REESCRIBIR ESTO CORRECTAMENTE***
+% Not done so far - JJ
 
@@
 
->>> ***EXPLICAR ESTO MEJOR***
+% Not done so far.
 
@@
 
->>> ***PONER EJEMPLOS DE SENSORES Y MONITORIZACIÓN***
+% Not done  so far
 
@@
 
->>> The way user data is anonymised in the system, as long as other legal aspects about the data privacy, have been properly detailed, as well as complemented with a reference.
+ The way user data is anonymised in the system, as long as other legal
+ aspects about the data privacy, have been properly detailed, as well
+ as complemented with a reference.  %where and which one?
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambiados los will del futuro a lo que hace MUSES ahora para el issue #19

@@
 MUSES, which has released its first prototype this year, is compared with the most relevant
-solutions offered by other companies to deal with the same issues as, remarking the advantages that our system will offer with
+solutions offered by other companies to deal with the same issues as, remarking the advantages that our system offers with
 respect to them. % <- we will explain why is better in the work
@@
 past behaviour and adapt the set of rules, or even inferring new ones,
-in order to deal with potential future security incidents due to the
-user's. %FERGU: The user's "algo que falta"? o eso hace referencia a
-        %su culpa? 
-%"lo del usuario", literalmente. Pero mejorquitarlo - JJ
-Then the system will react, in a non-intrusive way, to the potentially
+in order to deal with potential future security incidents. 
+Then the system  reacts, in a non-intrusive way, to the potentially
 dangerous sequence of actions (events) that he or she is conducting at
@@
 (ML) methods \cite{MachineLearning_Bishop06}, extracting a set of
-patterns which will be later processed by means of Computational
+patterns which is later processed by means of Computational
 Intelligence (CI) algorithms, namely Evolutionary Computation methods
@@
 
-MUSES will include some important modules in the loop, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
- such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset.
+MUSES includes some important modules in the loop, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
+ such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} process (along with other trust data and profiles), to select the best subset.
 
-In this paper, the system architecture is presented, in addition to a deep description of the soft computing methods the system will apply.
+In this paper, the system architecture is presented, in addition to a deep description of the soft computing methods the system applies.
 
 But first, this work presents a brief overview of the main existing solutions in this environment.
-Then a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) will bring.
+Then a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) offers.
 
@@
 
-The MUSES system overview is presented in Figure \ref{fig:system_overview}.
-As it can be seen, in this system, the user interacts with the devices, own or corporate, through the MUSES graphical interface inside his or her own context (situation, connection, status).
+The MUSES system overview is presented in Figure
+\ref{fig:system_overview}. As it can be seen, in this system, the user
+interacts with the devices, own or corporate, through the MUSES
+graphical interface inside his or her own context (situation,
+connection, status).
+% This has been criticized by the reviewer and has to be changed - JJ
 
@@
 The designed MUSES architecture is shown in Figure \ref{fig:architecture}.
-It is a \textit{client/server} approach in which the \textit{client} program will be installed in every user's mobile or portable device, independently of the platform (operating system and type of device).
-The \textit{server} side would be installed in the corporate SOC.
+It is a \textit{client/server} approach in which the \textit{client} program can be installed in every user's mobile or portable device, independently of the platform (operating system and type of device).
+The \textit{server} side can be installed in the corporate SOC.
 Both sides are connected through a secure channel (using HTTPS) over the Internet.
@@
 The use of a server is mainly based on the need of a powerful machine, able to work with massive amounts of data (\textit{Big Data}) \cite{BigData_11}, since the algorithms to apply to them require high computational costs \cite{Shirkhorshidi14Review}.
-Moreover, part of the high computational cost methods to apply will be derived to this high-performance server, as the mobile devices do not count with enough computational power.
-These methods will include Data Mining \cite{DataMining_Lee01} and Machine Learning \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
-This server will be also devoted to centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques will be applied.
+Moreover, part of the high computational cost methods to apply needs to be derived to this high-performance server, as the mobile devices do not count with enough computational power.
+These methods include Data Mining \cite{DataMining_Lee01} and Machine Learning \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
+This server is also devoted to centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques can be applied.
 
@@
 On the other hand, in \textit{offline} mode the server cannot be reached by the device (there is not an available connection between them), so all the decisions should be made locally.
-This will be done using an up-to-date copy on the Decision Table inside the Local database, which will contain decisions for any type of detected event, along with the default actions to be performed if no rule is met.
-Anyway, in this mode, the gathered information by the sensors in the device will be stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
-Moreover, when switching from offline to online mode, the device will receive an updated copy of the Decision Rules (the so-called Device Policies), as a kind of antivirus database, in order to work again perfectly in offline mode (if the connection is lost).
+This is done using an up-to-date copy on the Decision Table inside the Local database, which contains decisions for any type of detected event, along with the default actions to be performed if no rule is met.
+Anyway, in this mode, the gathered information by the sensors in the device  is stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
+Moreover, when switching from offline to online mode, the device  receives an updated copy of the Decision Rules (the so-called Device Policies), as a kind of antivirus database, in order to work again perfectly in offline mode (if the connection is lost).
 
-All data in MUSES will be encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
+All data in MUSES  is encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
 % Antonio - Sí, se va a comentar mejor en uno de los Issues. ;)
@@
  	 \item \textit{Local Database}: it is a local security-based storage, which includes the set of security rules to be applied locally (Device Policies), user authentication data, and a cache of gathered events and information.
-The latter will be useful when the device is in offline mode, so these data are stored to be later submitted to the server side.
+The latter is useful when the device is in offline mode, so these data are stored to be later submitted to the server side.
 %It contains the so-called \textit{Decision Table}, a set of rules in which the antecedents are high-level events, and the consequents are the corresponding decisions/actions, namely `allow', `deny' or `request' (the decision must be made in the server side).
@@
 In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring and acting).
-This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API will be defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
+This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
 On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with.
-Usually it will be accessed through the operating system (OS).
-So the type of information to gather from them and also the type of actions to do over them will vary depending on the OS.
+Usually it can be accessed through the operating system (OS).
+So the type of information to gather from them and also the type of actions to do over them vary depending on the OS.
 In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user).
@@
 \begin{itemize}
-	 \item \textit{System Database}: it stores all the information that the system will manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
+	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
 
@@
 
-As previously stated, one of the main features of this system will be the self-adaptation (to the user and context), of the set of Corporate Security Rules (specification of the ISPs), that it will be able to perform.
-To this end, the \textit{MusKRS} module will be run asynchronously in the server (once a day or every X hours) and will be in charge of analysing all the gathered information (events, context, user-related data), and adapting/refining the security rules.
-The refinement (improvement) will have as aim to better deal with these events, optimizing the current set of rules (removing redundant or non-useful rules, for instance), and even trying to predict future threats due to the user's behaviour.
+As previously stated, one of the main features of this system is the self-adaptation (to the user and context), of the set of Corporate Security Rules (specification of the ISPs), that it is be able to perform.
+To this end, the \textit{MusKRS} module is run asynchronously in the server (once a day or every X hours) and it is in charge of analysing all the gathered information (events, context, user-related data), and adapting/refining the security rules.
+The refinement (improvement)  has as aim to better deal with these events, optimizing the current set of rules (removing redundant or non-useful rules, for instance), and even trying to predict future threats due to the user's behaviour.
 
-This procedure will be composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process will be performed (in the \textit{Data Miner} sub-component);  second, a refinement and inference process will be done (in the \textit{Knowledge Compiler} sub-component), considering the data `extracted' in the first step, by means of Computational Intelligence (CI) techniques.
-It should be noticed that part of the refinement (or adaptation) of the security rules will be made using simpler methods, such as generalisation or specialisation of rules, for instance.
-Then, other parts of the process would be conducted using CI.
+This procedure is be composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed (in the \textit{Data Miner} sub-component);  second, a refinement and inference process  is done (in the \textit{Knowledge Compiler} sub-component), considering the data `extracted' in the first step, by means of Computational Intelligence (CI) techniques.
+It should be noticed that part of the refinement (or adaptation) of the security rules is made using simpler methods, such as generalisation or specialisation of rules, for instance.
+Then, other parts of the process can be conducted using CI.
 
-Another important fact is that MUSES will count with a human controller, normally the Chief Security Officer (CSO) of the company, who will supervise the system activity by means of logs or feedback messages.
-Thus, adapted and inferred security rules will not be, in principle, directly added to the current set of rules.
-Instead, they will be proposed as draft rules to this controller, in order that he/she will accept them if they are interesting and correct.
-It is planned that the system will be able to `learn' from this decisions, so after a so-called training or `warm up' period, the rules would be directly accepted (included in the set) or rejected autonomously by the MusKRS.
+Another important fact is that MUSES  counts with a human controller, normally the Chief Security Officer (CSO) of the company, who  supervises the system activity by means of logs or feedback messages.
+Thus, adapted and inferred security rules are not, in principle, directly added to the current set of rules.
+Instead, they  are proposed as draft rules to this controller, in order that he/she can accept them if they are interesting and correct.
+The system  is able to `learn' from this decisions, so after a so-called training or `warm up' period, the rules can be directly accepted (included in the set) or rejected autonomously by the MusKRS.
 
@@
 
-This task will be performed by the \textit{Data Miner} module.
-It will take the `raw' data from the database and will process the information, in order to yield a set of relevant data for the Knowledge Compiler module or for the human controller.
-In the first case, this sub-component will take them as a reference in order to refine or adapt the current set of security rules (for instance, to deal with anomalous situations).
+This task is performed by the \textit{Data Miner} module.
+It  takes the `raw' data from the database and  process the information, in order to yield a set of relevant data for the Knowledge Compiler module or for the human controller.
+In the first case, this sub-component  takes them as a reference in order to refine or adapt the current set of security rules (for instance, to deal with anomalous situations).
 
-The process will be mainly non-supervised. Moreover, eventually, the datasets can be huge (depending on the company's data flows), so Big Data processing methods \cite{BigData_11} will be applied.
+The process is be mainly non-supervised. Moreover, eventually, the datasets can be huge (depending on the company's data flows), so Big Data processing methods \cite{BigData_11} can be applied.
 
-The DM/ML techniques will process the so-called patterns, which in this context correspond to events (and their related information) produced by the users' interactions with the system.
-As stated, these events will be captured from the sensors in the users' devices and transmitted to the server to be processed and stored in the system database.
+The DM/ML techniques process the so-called patterns, which in this context correspond to events (and their related information) produced by the users' interactions with the system.
+As stated, these events  are captured from the sensors in the users' devices and transmitted to the server to be processed and stored in the system database.
 The methods to be applied are:
@@
 \item \textit{Pattern Mining} \cite{PatternMining_Han07}: 
-This process will try to identify frequent or, on the contrary, anomalous patterns, in order to process them lately.
+This process  tries to identify frequent or, on the contrary, anomalous patterns, in order to process them lately.
 The idea is that non-frequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO or to serve as a reference for the rule-refinement process.
@@
 \item \textit{Data Analysis}: 
-This will provide the CSO with mechanisms to visualise interesting facts about the data, such as more frequent events, dangerous or suspicious users (according to their behaviour), more triggered rules, etc.
+This  provides the CSO with mechanisms to visualise interesting facts about the data, such as more frequent events, dangerous or suspicious users (according to their behaviour), more triggered rules, etc.
 
@@
 
-MUSES will use different EC approaches, initially, two in the DM/ML part of the process, and three in the rule-refinement/adaptation phase.
+MUSES  uses different EC approaches, initially, two in the DM/ML part of the process, and three in the rule-refinement/adaptation phase.
 They are based on Genetic Programming (GP) \cite{GP_Koza92}, and Genetic Algorithms (GAs) \cite{GAs_Goldberg89}.
 
-The first evolutionary-based approach will be a \textit{GP-based classification} method.
-This will be useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems in real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features/variables and information gathered from the events take these kind of values.
+The first evolutionary-based approach is a \textit{GP-based classification} method.
+This is useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems in real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features/variables and information gathered from the events take these kind of values.
 
-Thus, this approach will be able to manage unbalanced datasets considering a fitness function in which a cost can be associated with the classifier accuracy at every epoch, having a penalty cost when the classifier makes a false negative (an element from the minority class which is classified as belonging to the majority class) \cite{cost_adjustment_07}.
-Regarding the type of data, since GP algorithms can manage rule- or tree-based models, it will work perfectly with any categorical variable, yielding a good classifier as it has been made in other works (such as the aforementioned \cite{cost_adjustment_07}).
+Thus, this approach is be able to manage unbalanced datasets considering a fitness function in which a cost can be associated with the classifier accuracy at every epoch, having a penalty cost when the classifier makes a false negative (an element from the minority class which is classified as belonging to the majority class) \cite{cost_adjustment_07}.
+Regarding the type of data, since GP algorithms can manage rule- or tree-based models, it  works perfectly with any categorical variable, yielding a good classifier as it has been made in other works (such as the aforementioned \cite{cost_adjustment_07}).
 
-The second approach will be a Feature Selection process, conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features/variables in the classification.
+The second approach is a Feature Selection process, conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features/variables in the classification.
 Thus, the algorithm can optimize the group of features to be considered in the classification task, improving both the computational time of this task and also the obtained accuracy of the method.
@@
 The second set of EC techniques is, as stated, part of the rule-refinement (or adaptation) process, to be performed by the \textit{Knowledge Compiler} module.
-These methods will be used for inference and optimisation, and will consider this data as a part of the process:
+These methods can be used for inference and optimisation, and consider this data as a part of the process:
 
@@
 \item User-related information corresponding to those anomalous or unlabelled patterns (events).
-Thus, the user's ID, location and role, for instance, will be considered in order to select the applicable set of rules for that conditions.
+Thus, the user's ID, location and role, for instance, can be considered in order to select the applicable set of rules for that conditions.
 
@@
 
-Other useful information to consider in the refinement/ adaptation process will be:
+Other useful information to consider in the refinement/ adaptation process are:
 
@@
 ``Is he/she trustworthy?''.
-In case the user is not, more restrictive rules would be created for him, otherwise the corresponding rules could be `relaxed' for that user.
+In case the user is not, more restrictive rules can be created for him, otherwise the corresponding rules could be `relaxed' for that user.
 
@@
 This could result in the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignore warning messages.
-Moreover, important log information regarding the parameters used or the decisions made in the different modules will be used for further tests of new inferred rules, as it is explained below.
+Moreover, important log information regarding the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.
 
@@
 
-Given this, the approaches that will be implemented are:
+Given this, the approaches that can be implemented are:
 
@@
 
-\item \textit{GP rule inference} method, which will generate/create new rules in order to `cover' those situations non contemplated in the current set of rules.
+\item \textit{GP rule inference} method, which generates/creates new rules in order to `cover' those situations non contemplated in the current set of rules.
 Thus, for instance, a new rule could be created in order to deal with the patterns to which the classifier could not assign a class.
-The generation will be done considering the so-called \textit{dictionary}, i.e.
-a set of terms corresponding to all the possible inputs and actions in the system, which will be antecedents (conditions) and consequents in the security rules to be inferred.
-The evaluation of these rules will be done considering the stored log information concerning the parameters along with the actions/decisions made in every component in the system.
-Thus, it will be possible to `simulate' the whole  system behaviour when the new rule is included and get a value of its performance.
+The generation can be done considering the so-called \textit{dictionary}, i.e.
+a set of terms corresponding to all the possible inputs and actions in the system, which are antecedents (conditions) and consequents in the security rules to be inferred.
+The evaluation of these rules can be done considering the stored log information concerning the parameters along with the actions/decisions made in every component in the system.
+Thus, it is possible to `simulate' the whole  system behaviour when the new rule is included and get a value of its performance.
 
-\item \textit{GP rule refinement} approach, which will optimise the current set of rules, adjusting the values in the conditions (antecedents), for instance.
+\item \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions (antecedents), for instance.
 Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
-The evaluation (of the whole set of security rules) will be done considering the number of unlabelled patterns that will be `covered' after the adjustments.
+The evaluation (of the whole set of security rules) is done considering the number of unlabelled patterns that are `covered' after the adjustments.
 
@@
 MUSES is mainly a free, open-source, platform independent solution, so these set of features make it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
-In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also will cover laptops and company PCs too, thus, it is not only for BYOD.
+In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD.
 Moreover the companies which desire work with those systems need a specific operating system and server (such as Windows Server, for instance), being even more strict in some cases, as in Samsung Knox, in which companies must work with a specific (though they can choose from a list) MDM service of being able of deploy Knox in their environments, or in the use of the Blackphone.
-MUSES will be a good solution in these cases, since it will be a multiplatform system.
+MUSES is a good solution in these cases, since it is a multiplatform system.
 
@@
 
-First, as mentioned previously, it will implement a self-adaptive event correlation, including a novel hybrid technique of rule refinement and rule adjustment extracting relevant information from processing huge amounts of data.
+First, as mentioned previously, it  implements a self-adaptive event correlation, including a novel hybrid technique of rule refinement and rule adjustment extracting relevant information from processing huge amounts of data.
 Then, the project defines a new approach to risk management taking into account threats (with their costs) as well as the innovative concept of opportunity, i.e.
@@
 
-About HCI and usability of mobile devices, this will set up a significant advance in the state of the art because of the novelty of the BYOD philosophy, and trying to look for individual differences among the users in susceptibility to persuasive strategies for secure behaviour.
-Regarding device monitoring, MUSES will also take into account the so-called context observation, by which private or professional scenarios will be detected, or predicted, based on advanced machine learning techniques.
-Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it will contribute to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.
+About HCI and usability of mobile devices, this sets up a significant advance in the state of the art because of the novelty of the BYOD philosophy, and trying to look for individual differences among the users in susceptibility to persuasive strategies for secure behaviour.
+Regarding device monitoring, MUSES  also take into account the so-called context observation, by which private or professional scenarios can be detected, or predicted, based on advanced machine learning techniques.
+Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it  contributes to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.
 
@@
 through interaction/events, rather than more general and external threats.
-Moreover, the techniques to be used in MUSES will work with real data (in a real system), as a difference to several research works (they consider simulated or artificial data).
+Moreover, the techniques to be used in MUSES  works with real data (in a real system), as a difference to several research works (they consider simulated or artificial data).
 
@@
 
-This work introduces a self-adaptive user-centric end-to-end system, named MUSES, which is in development (it will be launched next year).
+This work introduces a self-adaptive user-centric end-to-end system, named MUSES.
 The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.
 %Antares - Yo podrían en lugar de ``next year'' el año, porque el artículo puede ser leído en cualquier momento y es mejor emplear referencias absolutas, ¿no creeis?
+FERGU: fuera
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
ALL INTRO written all over again

--- 2015-04-16 MUSES_vs_BYOD_solutions.tex
@@
 
-The way on how data has been stored and accessed in companies has
-completely changed along the last years. The scenario where
-company-owned servers are being accessed by desktop PCs (and maybe
-laptops) from inside the company facilities has been transformed into
-another where data, increasingly a company asset, is distributed
-between a number of machines, maybe not all owned by the company, and
-working on the famous Cloud. Besides, being
-stored in the cloud or not, data is being consulted and modified
-through a wide variety of devices, some of them owned by the company's
-employees, in what is called the Bring Your Own Device (BYOD)
-philosophy. This philosophy has become highly successful due to the impact that
-portable devices (such as smartphones and tablets) are having on the
-market. % There should be a reference for this - JJ
-Data security and privacy are key factors for a company, thus, in
-order to protect them, it is usual to define Organisational Security
-Policies. Their definition is nowadays a very difficult problem, since
-the BYOD tendency means that several factors must be considered
-\cite{Opp_Security11}, most of them previously ignored or non
-considered in security systems. For instance, the current mixture
-between personal and professional information in these devices (the
-user could navigate inside social networks where there could be
-friends and also company partners or clients).
+The way how users have used their devices has changed in the past few years, even the number of different devices per user is increasing because of the so-called Internet of Things \cite{weber2010internet}.
+Thanks to it, users have more flexibility, and also at their works, because now they can use their devices to access company assets and continue working outside of the workplace.
+To allow this way of working is what has been called called the Bring Your Own Device (BYOD) philosophy.
 
-In this scenario several solutions have arisen in order to manage the corporate security.
-Some solutions are focused only on smartphones, while others are thought for laptops; also some are implemented for a certain platform, but others consider multiplatform.
-However, most of them try to be non-intrusive (regarding the users' personal data), friendly and easy to use.
+Data security and privacy are key factors for a company, and thus, in
+order to protect them, it is usual that the Chief Security Officer (CSO) of a company defines a set of Organisational Security
+Policies \cite{Opp_Security11}.
+However, allowing a BYOD environment means to take care of the risks that the use of personal smartphones can bring to the company \cite{gangula2013survey}.
+For instance, the mixture between personal and professional information in these devices would allow the user to navigate inside social networks, where important data could be leaked in the event of a security incident.
 
-Moreover, it has been demonstrated that people are the main hazard regarding the company security \cite{Adams_Users05}, so in this situation, some monitorization and security-aimed applications are arising, aiming to cope with the concept of seamless working experience on different devices.
-This concept is a methodology of work which allows users to start/continue a working session over multiple devices and locations without any significant loss of data.
-This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company's data borders have changed in the last years, so now the users can access significant data from outside the enterprise, and possibly through a non absolutely secure channel.
+In this scenario several solutions have appeared in order to manage corporate security.
+Most of the solutions are focused for both smartphones and desktop PCs, although some are implemented for a certain platform.
+However, almost all of them try to be non-intrusive (regarding the users' personal data), friendly and easy to use.
+
+Moreover, it has been demonstrated that employees who ignore the company security policies are the main hazard for the company security \cite{Adams_Users05}.
+In this situation, the tools that are appearing in the market aim to cope with the concept of seamless working experience on different devices.
+This concept is a methodology of work which allows users to start/continue a working session, over multiple devices and locations, without any significant loss of data.
+This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company data borders have changed in the last years, ans therefore now the users can access important data from outside the enterprise, and possibly through a non absolutely secure channel.
 %Antares - Yo quitaba lo de significant loss of data, ya que significant se repite después.
+%Cambiado
 
-Thus, this work introduces a recently released (in alpha) system named
+This work introduces a recently released system named
 MUSES, from Multiplatform Usable Endpoint Security, which is a
@@
 set of security rules defined as specifications of the Corporate
-Security Policies, but with the ability of `learning' from the user's
+Security Policies. In addition, it has the ability of `learning' from the user's (the employees)
 past behaviour and adapt the set of rules, or even inferring new ones,
-in order to deal with potential future security incidents due to the
-user's. %FERGU: The user's "algo que falta"? o eso hace referencia a
+in order to deal with potential security incidents that they might cause in the future. %FERGU: The user's "algo que falta"? o eso hace referencia a
         %su culpa? 
@@
 Then the system will react, in a non-intrusive way, to the potentially
-dangerous sequence of actions (events) that he or she is conducting at
+dangerous sequence of actions (events) that the employees are conducting at
 any time.
 
-To this end MUSES analyses the users' behaviour by means of Data
+To this end, MUSES analyses the users' behaviour by means of Data
 Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
@@
 the implementation was in its early stages when those papers were
-submitted. After the release of the first prototypes and additional
-work on the data mining techniques used \cite{mora14:urls} we have a
-clearer idea of MUSES capabilities and, as such, will be presented in
+submitted. After the release of the first prototype, an additional
+work on the data mining techniques was conducted in \cite{mora14:urls} so that we have a
+clearer idea of MUSES capabilities and, as such, they will be presented in
 this paper.
 
-MUSES will include some important modules in the loop, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
- such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset.
-
-In this paper, the system architecture is presented, in addition to a deep description of the soft computing methods the system will apply.
+MUSES will include some important modules in it core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
+%cambiado
+ such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset of policies.
 
 But first, this work presents a brief overview of the main existing solutions in this environment.
-Then a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) will bring.
+Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) includes.
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Incluyendo lo de las trials para que quede más guay

@@
 %"lo del usuario", literalmente. Pero mejorquitarlo - JJ
-Then the system will react, in a non-intrusive way, to the potentially
+Then the system reacts, in a non-intrusive way, to the potentially
 dangerous sequence of actions (events) that the employees are conducting at
-any time.
+any time. The MUSES system has been also tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.
 
@@
 
-MUSES will include some important modules in it core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
+MUSES includes some important modules in it core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
 %cambiado
@@
 But first, this work presents a brief overview of the main existing solutions in this environment.
-Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) includes.
+Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) includes .
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex

--- 2015-04-16 MUSES_vs_BYOD_solutions.tex
@@
 set of security rules defined as specifications of the Corporate
-Security Policies, but with the ability of `learning' from the user's
+Security Policies. In addition, it has the ability of `learning' from the user's (the employees)
 past behaviour and adapt the set of rules, or even inferring new ones,
-in order to deal with potential future security incidents. 
+in order to deal with potential security incidents that they might cause in the future. 
 Then the system reacts, in a non-intrusive way, to the potentially
-dangerous sequence of actions (events) that he or she is conducting at
-any time.
+dangerous sequence of actions (events) that the employees are conducting at
+any time. The MUSES system has been also tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.
 
-To this end MUSES analyses the users' behaviour by means of Data
+To this end, MUSES analyses the users' behaviour by means of Data
 Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
@@
 the implementation was in its early stages when those papers were
-submitted. After the release of the first prototypes and additional
-work on the data mining techniques used \cite{mora14:urls} we have a
-clearer idea of MUSES capabilities and, as such, will be presented in
+submitted. After the release of the first prototype, an additional
+work on the data mining techniques was conducted in \cite{mora14:urls} so that we have a
+clearer idea of MUSES capabilities and, as such, they will be presented in
 this paper.
 
-MUSES includes some important modules in the loop, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
- such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them and extracting threads that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} process (along with other trust data and profiles), to select the best subset.
-
-In this paper, the system architecture is presented, in addition to a deep description of the soft computing methods the system applies.
+MUSES includes some important modules in it core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
+%cambiado
+ such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset of policies.
 
 But first, this work presents a brief overview of the main existing solutions in this environment.
-Then a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) offers.
+Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) includes .
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
COntestando a otro comentario de revisor y cambiando el texto para ello

--- 2015-04-16 MUSES_vs_BYOD_solutions.tex
@@
 The MUSES system overview is presented in Figure
-\ref{fig:system_overview}. As it can be seen, in this system, the user
-interacts with the devices, own or corporate, through the MUSES
-graphical interface inside his or her own context (situation,
-connection, status).
+\ref{fig:system_overview}. As it can be seen, in this system the user
+interacts with the devices, being self-owned or corporate-owned.
+MUSES is running as a background process, and monitoring those interactions along with the context of the environment.
+Context was defined by Abowd et
+al. \cite{abowd1999towards} as ``any information that can be used to
+characterize the situation of an entity''. And the entity itself is defined as ``a person, place, or object that is considered relevant to the
+interaction between a user and an application, including the user and applications
+themselves''.
 % This has been criticized by the reviewer and has to be changed - JJ

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambiando los his/her por their o they para referirse a users

@@
 As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}.
-The first one monitors the environment (context) and the user's behaviour, translating his/her actions in a sequence of events.
+The first one monitors the environment (context) and the user's behaviour, translating their actions in a sequence of events.
 These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module.
@@
 In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user).
-This is due to the usual forbiddance or limitation of interactions with other applications that the OSs have.
+This is due to the usual denial or limitation of interactions with other applications that the OSs have.
 %FERGU: forbiddance parece que existe, pero el corrector me dice que no.

### 2015-04-16 Response to reviewers.tex
COntestando a otro comentario de revisor y cambiando el texto para ello
Aclarado lo de la encriptación, closes #14

@@
 
-% Not done so far - JJ
+This observation is very much appreciated since it is true that what was written could lead to a missunderstanding. The description has been changed, and the context properly defined and explained.
 
@@
 
-% Not done so far.
+We strongly agree with this and a detailed description of the encryption methods, that the second prototype of MUSES will implement, has been included.
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Aclarado lo de la encriptación, closes #14

@@
 These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module.
-Then, a decision is taken in the corporate security operations centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context.
-The corresponding feedback is communicated to the user through the \textit{actuator}, which is also in charge of triggering the recommended actions to stop the user's or application's doings, in case it is required.
+Then, a decision is taken in the corporate Security Operations Centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context.
+The corresponding feedback is communicated to the user through the \textit{actuator}, who decides to comply or not with the policy.
+As was mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high.
+In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease.
 
 The designed MUSES architecture is shown in Figure \ref{fig:architecture}.
-It is a \textit{client/server} approach in which the \textit{client} program can be installed in every user's mobile or portable device, independently of the platform (operating system and type of device).
-The \textit{server} side can be installed in the corporate SOC.
+It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform (operating system and type of device).
+The \textit{server} side can be installed in the corporate server.
 Both sides are connected through a secure channel (using HTTPS) over the Internet.
-In that figure just the high-level components in each part are shown, along with the information flows labelled as `Info XX'.
+In that figure just the high-level components in each part are shown, along with the way the information flows in the system.
 %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras
@@
 The system considers two working modes for every device: online and offline.
-In the \textit{online} mode the device can connect with the MUSES server, so it can request the server to make a decision.
-On the other hand, in \textit{offline} mode the server cannot be reached by the device (there is not an available connection between them), so all the decisions should be made locally.
+In the \textit{online} mode the device can connect with the MUSES server, so that it can request the server to make a decision.
+On the other hand, in \textit{offline} mode the server cannot be reached by the device because there is not an available connection between them, so all the decisions are made locally.
 This is done using an up-to-date copy on the Decision Table inside the Local database, which contains decisions for any type of detected event, along with the default actions to be performed if no rule is met.
@@
 
-All data in MUSES  is encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
+All flows of information in MUSES are encrypted with AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations fo the Fact Sheet on Suite B Cryptography \cite{salter2012suite}.
+Also, the MUSES server authenticates to the MUSES client by means of a self-signed certificate.
+The authentication of the users is based on Spring Security, which is a Java/Java EE framework that provides authentication, authorization and other security features for enterprise applications.
+And finally, MUSES makes use of the fact that current operating systems for mobile devices provide encrypted data containers by default, like the feature used in Android Work.
+%FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar?
+Que tecnología se usará, cómo se encriptará y todo eso.
 % Antonio - Sí, se va a comentar mejor en uno de los Issues. ;)

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Cambiando moar cosas y me voy a cenar algo

@@
 
-\item Risk information extracted from the user profile (reputation), e.g.
+\item Risk information extracted from the user profile (user trust value), e.g.
 ``Did the user received a lot of `denies'/`allows' before?'', i.e.
-``Is he/she trustworthy?''.
-In case the user is not, more restrictive rules can be created for him, otherwise the corresponding rules could be `relaxed' for that user.
+``Is the user trustworthy?''.
+In case the user is not, more restrictive rules can be created, otherwise the corresponding rules could be `relaxed' for that user.
 
-\item The information stored in logs along the system, which can, for instance, tell about how the user responds to system messages (either an action or if he gives feedback).
+\item The information stored in logs along the system, which can, for instance, tell about how the user responds to system messages (either an action or if the user gives feedback).
 This could result in the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignore warning messages.
@@
 
-Given this, the approaches that can be implemented are:
+This being said, and because the refinement of rules is considered of the same importance as inferring new ones, the approaches that have been implemented are:
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Re-writing comparison

@@
 
-MUSES is mainly a free, open-source, platform independent solution, so these set of features make it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
+MUSES is mainly a free, open-source, platform independent solution, and that makes it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
 In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD.
-Moreover the companies which desire work with those systems need a specific operating system and server (such as Windows Server, for instance), being even more strict in some cases, as in Samsung Knox, in which companies must work with a specific (though they can choose from a list) MDM service of being able of deploy Knox in their environments, or in the use of the Blackphone.
-MUSES is a good solution in these cases, since it is a multiplatform system.
+Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases.
+This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device.
+MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.
 
-Another comparison concerns that the existing products are mostly policy-based, but MUSES makes its decisions not only considering policies, but also based on the terminals/users context (location, connected networks and so on), to really understand the real danger of a specific action, i.e.
-it adds a Risk Analysis Process (performed in the RT2AE).
+Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals/users context (connection properties, or trust value of the device, for instance), to really understand the real risk thas comes with a specific action.
 
@@
 
-Moreover, another clear advantage over the rest is that MUSES can work in two connection modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.
+Moreover, another clear advantage over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.
 
-Though these are clearly advantages of MUSES over the aforementioned products, they also establish a progress beyond the state of the art with respect to the existing solutions.
-Other issues that MUSES aims to progress on are related to risk and trust data analysis, human-computer interaction (or HCI), device monitoring, and legal compliance.
+These are not only advantages of MUSES over the existing products, but also a progress beyond the state of the art in some fields like risk and trust analyris, event correlation, and human-computer interaction (HCI).
 

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Revised and rewriting conclusions, closes #21, and thank you everyone, good night

@@
 This work introduces a self-adaptive user-centric end-to-end system, named MUSES.
+The first prototype of this system has been recently released, and it has been already tested in an actual company.
 The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.
@@
 In addition, a scientific comparison between the techniques used in the presented system and those in the literature, in the same scope, has been done.
+It has been discussed that MUSES has the advantage of being multiplatform, while most of the reviewed tools are not.
+In addition, MUSES is able to adapt and evolve the security policies that a company has built, and not only apply them, as the other tools do.
+Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the aim of going beyond the state of the art in different fields of research.
 
-We can conclude that MUSES offers several advantages over the existing tools, both the some of its `technical' features, but also in the application of Data Mining, Machine Learning and Computational Intelligence methods to the events gathered by the system (users' behaviour), in order to adapt or refine the set of security rules.
-
-Anyway, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.
+However, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.
+The second prototype of the system will be also released, as well as the conclusions extracted after the analysis of data from the test of the first prototype.
 

### 2015-04-17 Response to reviewers.tex
Version final de la revisión
Enviada a la revista. ;)

Closes #5 #11 #15 #16

--- 2015-04-16 Response to reviewers.tex
@@
 
+\noindent
+Dear Sirs,\\
+
+We really appreciate the opportunity for improving our work. Following the reviewers' requests and suggestions we have deeply changed the contents, and  thus, the quality of the paper.
+
+In the next paragraphs you can find these comments and our responses to every one, along with the changes done.\\
+
+\noindent
+Yours sincerely,\\
+The authors.
+
 \section{Editor's comments}
@@
 
-{\emph The paper has been throughly revised.
+\textit{Following your comments and the reviewers' requests we have deeply revised and updated the paper.
+The changes include the rewriting of several sections, clearer and more complete explanations, a wider and more appropriate description of the state of the art in BYOD-focused and corporate security solutions, a better comparison with MUSES system.}
+
+\textit{This can be noticed in the text, but as an example, more than 15 references have been added or updated, which have been used to clarify, describe more precisely and update the contents.}\\
 
@@
 
-We have also compared this solutions with the current features of the
-MUSES prototype, which is already being used in tests, in Section 5.
+Section 3, for instance has been almost completely rewritten and updated, including the commented clues.
+Section 5 has also been improved, comparing these solutions with the current features of the MUSES prototype, which is already being used in tests.
+This shows a clearer description of the advantages of MUSES with respect to the analyzed tools and applications.
+
+Moreover the abstract and introduction have been also rewritten in order to describe the aim and contents of the paper,and the conclusions have been improved.
 
@@
 respect to the previous ones, and included also references to other
-research whose result has been included in Muses, for instance:
+research whose result has been included in MUSES, for instance:
 
-[10] A. Mora, P. De las Cuevas, J. J.  Merelo, Going a step beyond the black and
-white lists for url accesses in the enterprise by means of categorical classi-
-fiers, in: A. Rosa, J. J. Merelo, J. Filipe (Eds.), ECTA 2014 - Proceedings
-of the International Conference on Evolutionary Computation Theory and
-Applications, 2014, pp. 125-134.
+[12] A. Mora, P. De las Cuevas, J. J.  Merelo, Going a step beyond the black and
+white lists for url accesses in the enterprise by means of categorical classifiers, in: A.
+Rosa, J.
+J.
+Merelo, J.
+Filipe (Eds.), ECTA 2014 - Proceedings of the International Conference on Evolutionary Computation Theory and Applications, 2014, pp.
+125-134.
+
+Now the paper presents a more complete and accurate survey/state-of-the-art on BYOD-focused and corporate security tools and applications, a deeper description of the system, and a better comparison between MUSES and the described tools.
+
+More than 15 new references have been included and commented.
 
@@
 
-Security and privacy are obviously the main concerns of MUSES: data
+Security and privacy are the main concerns of MUSES: data
 security and user privacy. The BYOD philosophy tries to maintain data
@@
 clearer.
+
+The first response to Reviewer \#2 presents an outline of the work done in the revision.
+
+We are very grateful to the reviewer for his/her comments and hope he/she can turn his/her opinion considering all these changes and improvements in the paper.
 
@@
 
-The reviewer is right in part, since some of the contents are the same when a system is being described.
-We have followed his/her request and changed/improved several parts in
-the text, namely  \begin{itemize}
-\item The background has been corrected and expanded.
-\item References to papers mentioned by the reviwers and how they
+The reviewer is right in part, since we consider that some of the contents can be the same when a system is being described.
+However, we have followed his/her requests and changed/improved several parts in
+the text, namely:  
+\begin{itemize}
+\item The abstract and introduction have been rewritten.
+\item The background has been rewritten, corrected and expanded.
+\item References to papers mentioned by the reviewer and how they
   compare with the current paper (and situation in the project) have
@@
 \item Many more papers have been reviewed and referenced. The
-  reference section has grown by half.
-\item BYOD solutions have been compared among themselves, and with
-  MUSES (section 5).
+  bibliography section has grown in more than 15 references. Others have been updated to more recent news and URLs.
+\item BYOD and corporate security solutions have been better described and compared among themselves.
+Section 3 has been rewritten in a big part, changing its structure and including new tools and features.
+\item The description of the system has been completed and better explained in Section 4.
+\item The comparison between these tools and MUSES have been completed and improved in Section 5.
+\item The conclusions have been extended.
 \item The paper reflects the current, so far unpublished, state of
-  Muses architecture and implementation. 
+  Muses architecture and implementation, since first prototype has been released some months ago. 
 \end{itemize}
@@
 
-As suggested by the reviewer, we have transformed the paper into a
-state-of-the-art of systems that offer functionalities that are
-similar to MUSES. The paper has been
-almost completely rewritten to reflect the state of the art including
-changes from the time the first paper was submitted (Samsung dropping
-KNOX, for instance).
+We have focused the paper the paper in the state-of-the-art of systems that offer functionalities that are similar to MUSES.
+As stated, the paper has been almost completely rewritten to reflect the state of the art including changes from the time the first paper was submitted (Samsung dropping KNOX, for instance).
 
@@
 a) extending the state-of-the-art section, and converting the paper in
-a "state of the art" or tools for corporate mobile security. They
+a "state of the art" of tools for corporate mobile security. They
 already provide very detailed descriptions of IBM, Samsung, Sophos and
@@
 into a state-of-the-art in tools for corporate mobile security. MUSES
-has been compared with the existing tools in a more detailed way and
-the description of the system has been reduced in the same way. All
-sections have been rewritten and new sub-sections have been added to
-more accurately reflect the state of the art.
+has been better described and compared with the existing tools in a more detailed way.
+All sections have been rewritten and new sub-sections have been added to more accurately reflect the state of the art.
 
@@
 
-% Not done so far - JJ
+This observation is very much appreciated since it is true that what was written could lead to a misunderstanding.
+The description has been changed (now in page 11), and the context properly defined and explained.
 
@@
 
-The reviewer is right. We have rewritten the paragraph justifying the
-use of a server machine due to its computational power, needed for
+The reviewer is right. We have rewritten the paragraph (in page 12) justifying the use of a server machine due to its computational power, needed for
 applying Data Mining and Machine Learning techniques over Big
@@
 
-% Not done so far.
+We strongly agree with this and a detailed description of the encryption methods, that the second prototype of MUSES will implement, has been included by the end of the introduction of section 4 (page 13).
 
@@
 
-% Not done  so far
+We have included a text describing what are sensors and actuators and giving some examples of a few of the sensors that MUSES includes.
+It is described by the end of page 13 and in the following paragraphs (when the MUSES Aware Apps are commented).
 
@@
 
-The description of the performance of the CRTEP has been extended
-and improved, with references to two Project Reports which better fit
-to the contents.
+Following your comment, the description of the performance of the CRTEP has been extended and improved (in section 4.2, page 15), with references to two Project Reports which better fit to the contents.
 
@@
 
- The way user data is anonymised in the system, as long as other legal
- aspects about the data privacy, have been properly detailed, as well
- as complemented with a reference.  %where and which one?
+The reviewer is right, the way user data is anonymised in the system, as long as other legal aspects about the data privacy, have been properly detailed, as well
+as complemented with a reference. It is written in the last paragraph of page 15.  %where and which one?
+
+We really appreciate the reviewer's comments and hope that he/she will be satisfied with the revised work.
 

### 2015-04-17 MUSES_vs_BYOD_solutions.tex
Versión final de la revisión
Le he dado sin querer a un checkbox y no se ha subido esto. :D

@@
 
-MUSES includes some important modules in it core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
+MUSES includes some important modules in its core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
 %cambiado
@@
 As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}.
-The first one monitors the environment (context) and the user's behaviour, translating their actions in a sequence of events.
+The first one monitors the environment (context) and the users' behaviour, translating their actions in a sequence of events.
 These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module.
@@
 And finally, MUSES makes use of the fact that current operating systems for mobile devices provide encrypted data containers by default, like the feature used in Android Work.
-%FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar?
-Que tecnología se usará, cómo se encriptará y todo eso.
-% Antonio - Sí, se va a comentar mejor en uno de los Issues. ;)
 
@@
 
-The rest of the components are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides.
-In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring and acting).
+As a clarification, there are several sensors implemented in the system.
+A \textit{sensor} is an application which monitorizes one type of interaction between the users and their devices.
+For instance MUSES includes a \textit{CONNECTIVITY SENSOR}, able to detect if the device has the WiFi or the Bluetooth enabled, if it is connected, if so, the BSSID of the network to which it is connected, the type of encryption, if the airplane mode is on, or the device's IP.
+
+There are also \textit{actuators} in the system, which are applications in charge of doing something on the monitorized user's actions, normally showing a message according to the decision made by the system, but which could sometimes act over some specific features of the device.
+For instance, in the previous example there is also a related actuator, which could restrict the connection to some networks, or activate the airplane mode, if required.
+
+Some other examples of sensors are: DEVICE PROTECTION SENSOR (checks if the device is rooted, if it is protected by a password, or if there is an antivirus running), LOCATION SENSOR (detects if the device is within a secure zone), or a MAIL SENSOR (able to recognize the contents of an e-mail: from, to, cc, subject, attachment), among others.
+
+The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides.
+In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring with the sensors and acting as a consequence of the decisions made by the system).
 This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
+Some of the commented sensors require the interaction with MUSES Aware Apps, in order to request for information.
+For instance, the MAIL SENSOR could not detect or recognize the contents of an e-mail unless the mail application provides them (so this must be MUSES Aware).
+
 On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with.
@@
 
-Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals/users context (connection properties, or trust value of the device, for instance), to really understand the real risk thas comes with a specific action.
+Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals/users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.
 
@@
 
-These are not only advantages of MUSES over the existing products, but also a progress beyond the state of the art in some fields like risk and trust analyris, event correlation, and human-computer interaction (HCI).
+These are not only advantages of MUSES over the existing products, but also a progress beyond the state of the art in some fields like risk and trust analysis, event correlation, and human-computer interaction (HCI).
 
@@
 
+%\begin{table}
+%{\tiny
+%\begin{tabular}{cllllll}
+%\hline
+%\multicolumn{1}{|c|}{\textbf{Feature}} & 
+%\multicolumn{1}{c|}{\textbf{Muses}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}IBM\\ Mobile\\ Security\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Sophos\\ Mobile\\ Control\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Samsung Knox\\ and\\ Blackberry Balance\end{tabular}}} &
+%\multicolumn{1}{c|}{\textbf{Blackphone}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[|c]{@{}c@{}}Android\\ for\\ Work\end{tabular}}}\\
+%\hline
+%License                                                           & Open Source                         & Proprietary                                                                                    & Proprietary                                                                                      & Proprietary                                                                                                    & Proprietary                                                           & Proprietary\\
+%\begin{tabular}[|c]{@{}c@{}}Devices\\ \&\\ Platforms\end{tabular} &                                     &                                                                                               & \begin{tabular}[|c]{@{}l@{}}IOS, Android\\ and Windows Phone 8\end{tabular}                      & \begin{tabular}[|c]{@{}l@{}}Android Samsung devices\\ and IOS\end{tabular}                                     & Own device                                                           & \begin{tabular}[|c]{@{}l@{}}Android and\\ Devices with \\ Chrome Browser\end{tabular}\\
+%Price                                                             & Free*                               &                                                                                               & By request                                                                                      & 12\$ per year/device                                                                                          & \begin{tabular}[|c]{@{}l@{}}120\$ per \\ year **\end{tabular}         & \begin{tabular}[|c]{@{}l@{}}\$50 per user per month\\ \$12 per user per month\\ with unlimited storage\end{tabular} \\
+%Strengths                                                         &                                     &                                                                                               & \begin{tabular}[|c]{@{}l@{}}Can manage countless\\ devices with one solution\end{tabular}        &                                                                                                               &                                                                      & \begin{tabular}[|c]{@{}l@{}}Cloud based\\ Integrated in Google for Work\end{tabular}                              \\
+%Handicap                                                          &                                     &                                                                                               &                                                                                                 &                                                                                                               & \begin{tabular}[|c]{@{}l@{}}Only to their\\ own devices.\end{tabular} &                                                                                                                  \\
+%\hline
+%\multicolumn{7}{l}{\begin{tabular}[c]{@{}l@{}}\textit{* Requires own hardware}\\ \\ \textit{** By purchasing the terminal tree one-year subscriptions are archived}\end{tabular}}
+%\end{tabular}
+%}
+%\end{table}
+
 %----------------------------------------------------------------------------
@@
 This work introduces a self-adaptive user-centric end-to-end system, named MUSES.
-The first prototype of this system has been recently released, and it has been already tested in an actual company.
+The first prototype of this system has been recently released, and it has been already tested in an actual company, with excellent results and very positive feedback.
 The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Sentence not clear, stated by reviewer 4, may be related to #29
Re-writing to avoid parentheses, related to #39

@@
 Thanks to it, users have more flexibility, and also at their works, because now they can use their devices to access company assets and continue working outside of the workplace.
-To allow this way of working is what has been called called the Bring Your Own Device (BYOD) philosophy.
+To allow this way of working, companies started to adopt what has been called the Bring Your Own Device (BYOD) philosophy.
 
@@
 Most of the solutions are focused for both smartphones and desktop PCs, although some are implemented for a certain platform.
-However, almost all of them try to be non-intrusive (regarding the users' personal data), friendly and easy to use.
+However, almost all of them try to be non-intrusive -with regard to users' personal data-, friendly, and easy to use.
 

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Re-writing another paragraph to avoid forward slashes, and to improve it in general. Related to #38

@@
 
-Moreover, it has been demonstrated that employees who ignore the company security policies are the main hazard for the company security \cite{Adams_Users05}.
+Moreover, it has been demonstrated that employees who ignore company security policies are the main hazard for company security \cite{Adams_Users05}.
 In this situation, the tools that are appearing in the market aim to cope with the concept of seamless working experience on different devices.
-This concept is a methodology of work which allows users to start/continue a working session, over multiple devices and locations, without any significant loss of data.
-This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company data borders have changed in the last years, ans therefore now the users can access important data from outside the enterprise, and possibly through a non absolutely secure channel.
+This concept is a methodology of work which allows users to start, or continue a working session, over multiple devices and locations, without any significant loss of data.
+This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since company data borders have changed in the last years.
+Therefore, now the users can access important data from outside the enterprise, and possibly through a non completely secure channel.
 %Antares - Yo quitaba lo de significant loss of data, ya que significant se repite después.

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Related to #22. Highlighted the differences with the previous works, plus re-writing because what was already written was simply not true. Please @JJ @fergunet @pacastillo review before closing

@@
 set of security rules defined as specifications of the Corporate
-Security Policies. In addition, it has the ability of `learning' from the user's (the employees)
-past behaviour and adapt the set of rules, or even inferring new ones,
+Security Policies. In addition, it has the ability of `learning' from the user's past behaviour and adapt the set of existing rules, or even inferring new ones,
 in order to deal with potential security incidents that they might cause in the future. 
 Then the system reacts, in a non-intrusive way, to the potentially
-dangerous sequence of actions (events) that the employees are conducting at
+dangerous sequence of actions \footnote{Which are treated as `events' inside the system.} that the employees are conducting at
 any time. The MUSES system has been also tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.
@@
 the implementation was in its early stages when those papers were
-submitted. After the release of the first prototype, an additional
-work on the data mining techniques was conducted in \cite{mora14:urls} so that we have a
-clearer idea of MUSES capabilities and, as such, they will be presented in
-this paper.
+submitted.
+Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype.
+As there was no available test data, a set of URL connection logs were provided by a Spanish company, as well as both black and white lists.
+These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees.
+By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, could be presented at \cite{mora14:urls}.
+Now, after the release of the first prototype, along with the first conducted tests, we have a clearer idea of MUSES capabilities and, as such, they will be presented in this paper.
 

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
un detalle de ortografía
un par de comentarios

@@
 dangerous sequence of actions \footnote{Which are treated as `events' inside the system.} that the employees are conducting at
-any time. The MUSES system has been also tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.
+any time. The MUSES system has also been tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.
 
@@
 Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype.
-As there was no available test data, a set of URL connection logs were provided by a Spanish company, as well as both black and white lists.
-These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees.
+As there was no available test data, a set of URL connection logs were provided by a Spanish company, % [Pedro] quizás decir que es una empresa de seguridad o algo así
+as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
 By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, could be presented at \cite{mora14:urls}. 
 Now, after the release of the first prototype, along with the first conducted tests, we have a clearer idea of MUSES capabilities and, as such, they will be presented in this paper.
+% [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...
 

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
un par de comentarios

@@
 By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, could be presented at \cite{mora14:urls}.
+% [Pedro] ¿ese "could be" se refiere a verbo en pasado?
+en ese caso, quizás usar "...
+was presented at..."
 Now, after the release of the first prototype, along with the first conducted tests, we have a clearer idea of MUSES capabilities and, as such, they will be presented in this paper.
@@
 
+% [Pedro] en este punto se puede comentar lo que se va a presentar en el trabajo introduciendo directamente con "This work presents..." o "This paper presents..." (yo quitaría el "But first,"
 But first, this work presents a brief overview of the main existing solutions in this environment.
-Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) includes .
+Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
+ includes.
 

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Adding details about multiplatform in p.12. Related to #32. Please @JJ @fergunet @pacastillo review before closing

--- 2015-06-16 MUSES_vs_BYOD_solutions.tex
@@
 Then, a decision is taken in the corporate Security Operations Centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context.
-The corresponding feedback is communicated to the user through the \textit{actuator}, who decides to comply or not with the policy.
+The corresponding feedback is communicated to the user through the \textit{actuator}, and then the user decides to comply or not with the policy.
 As was mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high.
@@
 The designed MUSES architecture is shown in Figure \ref{fig:architecture}.
-It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform (operating system and type of device).
+It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform.
+On the one hand, MUSES client has been developed for Android, to be used in Android smartphones and tablets, as well as for Windows, so it can be used in Windows devices and laptops, and finally, iOS client will be also developed.
+On the other hand, MUSES server has been developed in Java, and works with an Apache Tomcat server.
 The \textit{server} side can be installed in the corporate server.

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
un comentario
Accepting advice and comments by @pacastillo

@@
 Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype.
-As there was no available test data, a set of URL connection logs were provided by a Spanish company, % [Pedro] quizás decir que es una empresa de seguridad o algo así
+As there was no available test data, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
 as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
-By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, could be presented at \cite{mora14:urls}.
+By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented at \cite{mora14:urls}.
 % [Pedro] ¿ese "could be" se refiere a verbo en pasado?
 en ese caso, quizás usar "...
-was presented at..."
-Now, after the release of the first prototype, along with the first conducted tests, we have a clearer idea of MUSES capabilities and, as such, they will be presented in this paper.
+was presented at..." % Gracias again
+In this paper, once the first MUSES prototype has been released, and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them.
 % [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
un comentario
Removed all slashes in the text (changed by 'ors' and 'ands'). Closes #38

@@
 First, some background situation about enterprise security is presented in Section \ref{sec:preliminaryconcepts}, explaining how BYOD philosophy affects it.
-Then, the main tools/solutions are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
+Then, the main solutions or tools are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
 Then, in Section \ref{sec:muses}, the Multiplatform Usable Endpoint Security System is presented (architecture + soft computing techniques).
@@
 A needed security policy, or in this case, an ISP should deal with the way of protecting a certain organization's information against a security breach.
-Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community/organisation that they are built for.
+Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community or organisation that they are built for.
 In this sense, MUSES stands up for a self-adaptation of the security policies of a company.
@@
 The other issue to cope with is the elaboration of a good ISP, understandable for every user of the company, and more importantly, non-intrusive for him.
-A lot of researchers have studied the natural tendency of employees to comply with the ISP \cite{SecPolComp10,SecPolComp12,SecPolComp14}, reaching conclusions such as the employees compliance with the security policies increases educating/training them in information security awareness  \cite{SecPolComp09}, and decreases applying too much sanctions when a misuse or abuse occurs \cite{SecPolPenalty09}.
+A lot of researchers have studied the natural tendency of employees to comply with the ISP \cite{SecPolComp10,SecPolComp12,SecPolComp14}, reaching conclusions such as the employees compliance with the security policies increases educating or training them in information security awareness  \cite{SecPolComp09}, and decreases applying too much sanctions when a misuse or abuse occurs \cite{SecPolPenalty09}.
 Thus, in this paper, for each tool in Section \ref{sec:toolsreview} it is specified if the developers have taken into account the construction of ISPs, or even if they give some guidelines for building them.
@@
 Several enterprise-security aimed applications will be offered in the market, so the IT would decide which ones will be installed (even as a bundle) in the employees' devices, and also, they can manage the updates of these apps, in order to ensure that all the employees are up to date.
-For instance, one app could manage the creation of personal/work profiles, so the user just could access corporate assets after login in into the app.
+For instance, one app could manage the creation of personal and work profiles, so the user just could access corporate assets after login in into the app.
 Moreover, the enterprise IT department could define specific security policies on these apps, in addition to the inherent protection that the container provides.
@@
 \item It does it by enforcing passwords and providing mechanisms for remote lock.
-\item It offers the ability to wipe/selective wipe corporate data email/contacts on the device if lost or stolen.
+\item It offers the ability to wipe (even selectively) corporate data email and contacts on the device if lost or stolen.
 \end{itemize}
@@
 
-The designed MUSES architecture is shown in Figure \ref{fig:architecture}.
+The designed MUSES architecture is shown in Figure \ref{fig:architecture}. % [Pedro] creo que la frase "suena mejor" sin "The designed" (pero es una apreciación subjetiva mía).
 It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform.
 On the one hand, MUSES client has been developed for Android, to be used in Android smartphones and tablets, as well as for Windows, so it can be used in Windows devices and laptops, and finally, iOS client will be also developed.
+% [Pedro] ¿qué tal decir: "MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development."
 On the other hand, MUSES server has been developed in Java, and works with an Apache Tomcat server.
 The \textit{server} side can be installed in the corporate server.
+% [Pedro] y respecto al servidor: "As far as the server is concerned, it has been developed using Java to be used with an Apache Tomcat in the corporate server."
 Both sides are connected through a secure channel (using HTTPS) over the Internet.
@@
 Also, the MUSES server authenticates to the MUSES client by means of a self-signed certificate.
-The authentication of the users is based on Spring Security, which is a Java/Java EE framework that provides authentication, authorization and other security features for enterprise applications.
+The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications.
 And finally, MUSES makes use of the fact that current operating systems for mobile devices provide encrypted data containers by default, like the feature used in Android Work.
@@
 So the type of information to gather from them and also the type of actions to do over them vary depending on the OS.
-In most of the cases MUSES could just detect/recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user).
+In most of the cases MUSES could just detect or recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user).
 This is due to the usual denial or limitation of interactions with other applications that the OSs have.
@@
 As previously stated, one of the main features of this system is the self-adaptation (to the user and context), of the set of Corporate Security Rules (specification of the ISPs), that it is be able to perform.
-To this end, the \textit{MusKRS} module is run asynchronously in the server (once a day or every X hours) and it is in charge of analysing all the gathered information (events, context, user-related data), and adapting/refining the security rules.
+To this end, the \textit{MusKRS} module is run asynchronously in the server (once a day or every X hours) and it is in charge of analysing all the gathered information (events, context, user-related data), and adapting or refining the security rules.
 The refinement (improvement)  has as aim to better deal with these events, optimizing the current set of rules (removing redundant or non-useful rules, for instance), and even trying to predict future threats due to the user's behaviour.
@@
 
-The following sections describe these processes: first focusing on DM techniques to be used both automatically by the MusKRS, and as a kind of decision-aid/monitoring tool for the CSO; second, the CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches, since these methods perform very well, and have been widely used in security-based environments for solving security issues, such as the intrusion detection \cite{GA_intrusion-majeed}, the design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.
+The following sections describe these processes: first focusing on DM techniques to be used both automatically by the MusKRS, and as a kind of decision-aid and monitoring tool for the CSO; second, the CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches, since these methods perform very well, and have been widely used in security-based environments for solving security issues, such as the intrusion detection \cite{GA_intrusion-majeed}, the design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.
 
@@
 The aim of this method is grouping the patterns considering some similarity criteria, in order to manage them as a set.
-This could be used for providing data visualisation mechanisms, in order to make it easier to interpret the data interaction and the distribution in clusters with respect to the different properties/features of the patterns.
+This could be used for providing data visualisation mechanisms, in order to make it easier to interpret the data interaction and the distribution in clusters with respect to the different properties (features) of the patterns.
 
 \item \textit{Feature Selection} \cite{FeatureSelection_Guyon03}: 
-It consists on extract the most important features/variables from the data.
+It consists on extract the most important features (variables) from the data.
 This could be useful if we want to discard non-key features, which could be interesting in order to reduce the database weight, for improving the performance of other techniques (such as classification or clustering), and even to improve the performance of the whole system, since less information would be gathered and transmitted.
@@
 
-MUSES  uses different EC approaches, initially, two in the DM/ML part of the process, and three in the rule-refinement/adaptation phase.
+MUSES  uses different EC approaches, initially, two in the DM/ML part of the process, and three in the rule-refinement and adaptation phase.
 They are based on Genetic Programming (GP) \cite{GP_Koza92}, and Genetic Algorithms (GAs) \cite{GAs_Goldberg89}.
@@
 The first evolutionary-based approach is a \textit{GP-based classification} method.
-This is useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems in real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features/variables and information gathered from the events take these kind of values.
+This is useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems in real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features (variables) and information gathered from the events take these kind of values.
 
@@
 
-The second approach is a Feature Selection process, conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features/variables in the classification.
+The second approach is a Feature Selection process, conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features (variables) in the classification.
 Thus, the algorithm can optimize the group of features to be considered in the classification task, improving both the computational time of this task and also the obtained accuracy of the method.
@@
 
-Other useful information to consider in the refinement/ adaptation process are:
+Other useful information to consider in the refinement and adaptation process are:
 
@@
 \item Risk information extracted from the user profile (user trust value), e.g.
-``Did the user received a lot of `denies'/`allows' before?'', i.e.
+``Did the user received a lot of `denies' or `allows' before?'', i.e.
 ``Is the user trustworthy?''.
@@
 
-\item \textit{GP rule inference} method, which generates/creates new rules in order to `cover' those situations non contemplated in the current set of rules.
+\item \textit{GP rule inference} method, which generates new rules in order to `cover' those situations non contemplated in the current set of rules.
 Thus, for instance, a new rule could be created in order to deal with the patterns to which the classifier could not assign a class.
@@
 a set of terms corresponding to all the possible inputs and actions in the system, which are antecedents (conditions) and consequents in the security rules to be inferred.
-The evaluation of these rules can be done considering the stored log information concerning the parameters along with the actions/decisions made in every component in the system.
+The evaluation of these rules can be done considering the stored log information concerning the parameters along with the actions and decisions made in every component in the system.
 Thus, it is possible to `simulate' the whole  system behaviour when the new rule is included and get a value of its performance.
@@
 
-Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals/users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.
+Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.
 
@@
 With regard to the scientific contribution of the system, one of the main differences with respect to previous works is the consideration of security threats `brought' by the user's behaviour inside the system, i.e.
-through interaction/events, rather than more general and external threats.
+through interaction or events, rather than more general and external threats.
 Moreover, the techniques to be used in MUSES  works with real data (in a real system), as a difference to several research works (they consider simulated or artificial data).
@@
 
-MUSES has been compared with other existing solutions/tools with a similar aim: to ensure the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
+MUSES has been compared with other existing solutions with a similar aim: to ensure the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
 The main advantages of MUSES with respect to the other solutions have been discussed, also remarking its advances beyond the state of the art that define these tools.

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
Accepting more comments by @pacastillo

@@
 This work introduces a recently released system named
-MUSES, from Multiplatform Usable Endpoint Security, which is a
+MUSES, from Multiplatform Usable Endpoint Security, which is being developed within an European Project\footnote{\url{http://musesproject.eu/}} of the same name. MUSES is a
 dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
@@
 % [Pedro] en este punto se puede comentar lo que se va a presentar en el trabajo introduciendo directamente con "This work presents..." o "This paper presents..." (yo quitaría el "But first,"
-But first, this work presents a brief overview of the main existing solutions in this environment.
-Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
+% Totalmente de acuerdo, cambiado.
+This work presents a brief overview of the main existing solutions in this environment.
+Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
+% Perfecto, cambiado.
  includes.

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
Accepting more comments by @pacastillo

@@
 
-The designed MUSES architecture is shown in Figure \ref{fig:architecture}. % [Pedro] creo que la frase "suena mejor" sin "The designed" (pero es una apreciación subjetiva mía).
+MUSES architecture is shown in Figure \ref{fig:architecture}. % [Pedro] creo que la frase "suena mejor" sin "The designed" (pero es una apreciación subjetiva mía). % Agree
 It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform.
-On the one hand, MUSES client has been developed for Android, to be used in Android smartphones and tablets, as well as for Windows, so it can be used in Windows devices and laptops, and finally, iOS client will be also developed.
+MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development.
 % [Pedro] ¿qué tal decir: "MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development."
-On the other hand, MUSES server has been developed in Java, and works with an Apache Tomcat server.
-The \textit{server} side can be installed in the corporate server.
-% [Pedro] y respecto al servidor: "As far as the server is concerned, it has been developed using Java to be used with an Apache Tomcat in the corporate server."
+% La verdad es que sí, la he releído y estaba muy mal redactada, qué vergüenza :(
+As far as the server is concerned, it has been developed using Java to be installed with an Apache Tomcat in the corporate server, independently of its operating system.
+% [Pedro] y respecto al servidor: "As far as the server is concerned, it has been developed using Java to be used with an Apache Tomcat in the corporate server." % Ok, cambiado y añadido lo del final.
 Both sides are connected through a secure channel (using HTTPS) over the Internet.

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
My eyes. And preparing for changing all of this
Re-writing a lot. Related to #23. Please review before closing

@@
 As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}.
-The first one monitors the environment (context) and the users' behaviour, translating their actions in a sequence of events.
-These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module.
+The former consists of a number of implemented \textit{sensors} in the device, which monitor the environment and the users' behaviour \footnote{Which has been introduced as the `context' of an event.}.
+Then, the user's actions, as well as device configuration, or connection properties, are translated into a sequence of events.
+These events, along with the stored patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module.
 Then, a decision is taken in the corporate Security Operations Centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context.
@@
  	 \item \textit{Local Database}: it is a local security-based storage, which includes the set of security rules to be applied locally (Device Policies), user authentication data, and a cache of gathered events and information.
-The latter is useful when the device is in offline mode, so these data are stored to be later submitted to the server side.
+The latter is useful when the device is in offline mode, so these events can be later submitted to the server side, when the device returns to online mode.
 %It contains the so-called \textit{Decision Table}, a set of rules in which the antecedents are high-level events, and the consequents are the corresponding decisions/actions, namely `allow', `deny' or `request' (the decision must be made in the server side).
- 	 \item \textit{Device Monitor (MusDM)}: module which gathers the events and information produced by the user.
-It also acts following the decisions made by the system, in order to allow or deny the controlled application (or the user) for doing something.
-It is composed by a monitoring and an actuator submodules.
+ 	 \item \textit{Device Monitor (MusDM)}: module which contains the two main described modules, controller and actuator.
+When a user performs an action, an event is automatically created and either sent to the server (online) or locally stored (offline).
+In addition, there are several sensors implemented in the system which periodically scan different aspects of the device configuration, and the environment.
+This way, the system acts equally over specific actions, as well as when it detects something from the sensors that is against the security policies.
  	 \item \textit{Access Control System (MusACS)}: module in charge of making the decisions considering the gathered data.
@@
 
-As a clarification, there are several sensors implemented in the system.
-A \textit{sensor} is an application which monitorizes one type of interaction between the users and their devices.
-For instance MUSES includes a \textit{CONNECTIVITY SENSOR}, able to detect if the device has the WiFi or the Bluetooth enabled, if it is connected, if so, the BSSID of the network to which it is connected, the type of encryption, if the airplane mode is on, or the device's IP.
+The client is an important part of the a-priori risk treatment, because it both monitors the whole context and finally acts or warns the user in event of a security violation.
+Security violations are mainly identified by security rules, which is why MUSES uses DM and CI techniques to evolve them and enhance the coverage.
+That is to say, the more sensors are implemented, the more enforced the security in the device is.
+%Esta última frase revisádmela por favor, e insultadme si es necesario.
+ For this reason, MUSES implements the following sensors:
 
-There are also \textit{actuators} in the system, which are applications in charge of doing something on the monitorized user's actions, normally showing a message according to the decision made by the system, but which could sometimes act over some specific features of the device.
-For instance, in the previous example there is also a related actuator, which could restrict the connection to some networks, or activate the airplane mode, if required.
+\begin{description}
+  \item[CONNECTIVITY SENSOR] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
+This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
+  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen tunrs off, or if the device has the screen protected with a password.
+This sensor adds the possibility of detecting security violations event if the user is not doing a specific action.
+  \item[LOCATION SENSOR] User location can be obtained from the device GPS.
+Although, and to preserve user privacy, a number of `zones' can be defined by the company, so MUSES only checks if the user is inside them and acts in consequence.
+  \item[MAIL SENSOR] If the user is going to send an email, MUSES client sensors check also the email attributes.
+This way, they can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
+  \item[FILE SENSOR] The type of file, also called \textit{asset}, is also very important for the application of security rules.
+Thus, this sensor aims to detect is some files might need more strict security policies, also depending on the rest of sensors.
+  \item[APP SENSOR] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
+Additionally, this sensor gathers information abaut the applicationes which the user tries to install or uninstall.
+\end{description}
 
-Some other examples of sensors are: DEVICE PROTECTION SENSOR (checks if the device is rooted, if it is protected by a password, or if there is an antivirus running), LOCATION SENSOR (detects if the device is within a secure zone), or a MAIL SENSOR (able to recognize the contents of an e-mail: from, to, cc, subject, attachment), among others.
-
-The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between client and server sides.
+The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between MUSES client and MUSES server.
 In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring with the sensors and acting as a consequence of the decisions made by the system).
@@
 So the type of information to gather from them and also the type of actions to do over them vary depending on the OS.
-In most of the cases MUSES could just detect or recognize very specific events, and also do very limited actions to prevent or block them (maybe showing a screen on the top until something is accomplished by the user).
-This is due to the usual denial or limitation of interactions with other applications that the OSs have.
-%FERGU: forbiddance parece que existe, pero el corrector me dice que no.
-Prohibition mejor?
-% Yo diría que es forbidding...
+As was already mentioned, in cases MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user.
+This message informs about why the action is considered as risky and what the user can do to avoid it.
 

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
Adding paragraph to solve issue #25 but if @gstvrmrlpz @pacastillo or @jlmacal could review please... (crying eyes)

@@
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen tunrs off, or if the device has the screen protected with a password.
+  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen tunrs off, if the device has the screen protected with a password, or even if the device is rooted \cite{hildenbrand2014}.
 This sensor adds the possibility of detecting security violations event if the user is not doing a specific action.
@@
 \end{description}
+
+It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not.
+It might happen then that the user ignores this advice and the device becomes compromised.
+As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, soted, and processed on the server.
+In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will be noticed by the server, which will immediately warn the user, and decrease the devide trust value.
 

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
Couple of errors and forgot to add changed .bib

@@
 It might happen then that the user ignores this advice and the device becomes compromised.
-As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, soted, and processed on the server.
+As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, stored, and processed on the server.
 In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will be noticed by the server, which will immediately warn the user, and decrease the devide trust value.
@@
 
-There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company's CSO to define and manage Security Policies and Rules in a friendly way.
+There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company CSO to define and manage Security Policies and Rules in a friendly way.
 It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values.
@@
 First, the data that the user provides to the system (such as name, or email) is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks.
-Then, the location of the device is never sent and stored in the database, but instead, there are a number of defined `zones'.
+Then, the location of the device is never sent and stored in the database, but as was stated in the previous section, there are a number of defined `zones'.
 What is checked is that the user is inside one of those zones of interest.

### 2015-06-17 table_License_Devices_price.tex
Add minitable with License, Devices and price

\documentclass{article}
\usepackage{array,booktabs,graphicx}% http://ctan.org/pkg/{array,booktabs}

\begin{document}

\begin{table}[ht]

  \centering
  \caption{License, Devices and plataform and prices}
  \renewcommand{\arraystretch}{1.5}% Spread rows out...
  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
    \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
    \midrule
    MUSES & OpenSource &  & Free*  \\
    IBM Mobile Security & Propietary &  &  \\
    Sophos Mobile Control & Propietary & IOS, Android, Windows Phone  &  By Request\\
    Samsung Knox and Blackbery Balance & Propietary & Android Samsung Devices and IOS & 12\$ per year/device \\
    Blackphone & Propietary & Own device & 120\$ per year \\
    Android for Work & Propietary & Android and devices with Chrome Browser &  12\$ per month/user\\
    \bottomrule
  \end{tabular}
  }
\end{table}

\end{document}

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
una falta...

@@
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen tunrs off, if the device has the screen protected with a password, or even if the device is rooted \cite{hildenbrand2014}.
+  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or even if the device is rooted \cite{hildenbrand2014}.
 This sensor adds the possibility of detecting security violations event if the user is not doing a specific action.

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
una sugerencia
una sugerencia y una pregunta

@@
   \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or even if the device is rooted \cite{hildenbrand2014}.
-This sensor adds the possibility of detecting security violations event if the user is not doing a specific action.
+This sensor %¿cambiarlo por "This security mechanism" ?
+   adds the possibility of detecting security violations event if the user is not doing a specific action.
   \item[LOCATION SENSOR] User location can be obtained from the device GPS.
@@
 
-It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not.
+It is important to note that MUSES does not work as an antivirus itself, but has a sensor which % quizás quitar "has a sensor which" y sólo poner "it"
+checks if the device has already an antivirus, and raises a security violation alert if not.
 It might happen then that the user ignores this advice and the device becomes compromised.
@@
 In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will be noticed by the server, which will immediately warn the user, and decrease the devide trust value.
+% [Pedro] aquí pueden preguntar sobre cómo se lleva a cabo esa detección del cambio en los sensores...
 

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
Accepting @pacastillo comments and re-writing paragraph added in commit #e34fdc4

@@
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or even if the device is rooted \cite{hildenbrand2014}.
-This sensor %¿cambiarlo por "This security mechanism" ?
-   adds the possibility of detecting security violations event if the user is not doing a specific action.
+  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
+This security mechanism %¿cambiarlo por "This security mechanism" ?
+% Ok, cambiado, creo que está mejor así.
+   adds the possibility of detecting security violations even if the user is not doing a specific action.
   \item[LOCATION SENSOR] User location can be obtained from the device GPS.
@@
 It is important to note that MUSES does not work as an antivirus itself, but has a sensor which % quizás quitar "has a sensor which" y sólo poner "it"
+% Esto ya no sé porque entonces se me repite mucho la palabra "it", serían 2 veces en esta frase y la siguiente que también empieza por "it"...
 checks if the device has already an antivirus, and raises a security violation alert if not.
@@
 As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, stored, and processed on the server.
-In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will be noticed by the server, which will immediately warn the user, and decrease the devide trust value.
+In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will mean a significant change in the patterns.
+Then, this change in the patterns will be noticed by the server, which will immediately warn the user, and decrease the device trust value.
 % [Pedro] aquí pueden preguntar sobre cómo se lleva a cabo esa detección del cambio en los sensores...

### 2015-06-19 MUSES_vs_BYOD_solutions.tex
Abstract improved
And also related to the title, which is not "Talk about Muses", but BYOD solutions.

Refs #29

@@
 want to ensure that their Security Policies are complied, but this
-goal turned hard to achieve since employees are able to use, or bring,
-their personal devices at work. This has been named as ``Bring Your Own Device'' (BYOD). % <- Problem
-As this BYOD philosophy is being adopted by many companies everyday, a number of solutions have appeared in the market, 
-in order to adapt to it in a secure way. In this paper, a novel and open source system named
+becomes a difficult goal to achieve at the point employees are able to use, or bring,
+their personal devices at work, in a practice that has been named ``Bring Your
+Own Device'' (BYOD). % <- Problem
+Since this BYOD philosophy is being adopted by many companies
+everyday, a number of solutions have appeared in the market so that it
+can implemented in a secure way and comply with the Security Policies
+mentioned above. In this paper we present an overview of BYOD security
+solutions along a novel and open source system named
 MUSES (Multiplatform Usable Endpoint Security), able 
-to securely manage BYOD environments, is described. % <- Solution
-MUSES has been developed to cope with security issues with regard to enterprise security policies, but as a user-centric tool.
-It considers users' behaviour in order to adapt, improve, or even increase the defined set of security rules.
-To do this, the system applies Machine Learning and Computational Intelligence techniques, being also able to predict future security incidences produced by these users.
-% <- Solution, details.
-MUSES, which has released its first prototype this year, is compared with the most relevant
+to securely manage BYOD environments. % <- Solution
+MUSES has been developed to cope with security issues with regard to
+enterprise security policies, but as a user-centric tool. It considers
+users' behaviour in order to adapt, improve, or even increase the
+defined set of security rules. To do this, the system applies Machine
+Learning and Computational Intelligence techniques, being also able to
+predict future security incidences produced by these users. % <-
+                                % Solution, details. 
+MUSES, which has released its first prototype in early 2015, is
+compared with the most relevant 
 solutions offered by other companies to deal with the same issues as, remarking the advantages that our system offers with

### 2015-06-19 Response to reviewers - r2.tex
Starting response to reviewer
Refs #42. We will use this paper for inserting answers as soon as they are ready.

\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System: Response to Reviewers\' comments}

\noindent
Dear Sirs,\\

We really appreciate the opportunity for improving our work. Following the reviewers' requests and suggestions we have improved the paper, incorporating all suggestions.

In the next paragraphs you can find these comments and how they have been addressed, along with the changes done.\\

\noindent
Yours sincerely,\\
The authors.

\section{Editor's comments}
Dear Dr. Mora,

Reviewers' comments on your work have now been received. After analyzing the reviewers' reports and the manuscript, the Guest Editors are recommending that you perform a further MAJOR revision of your manuscript to address the reviewers' comments.

While revising the manuscript please carefully revise the analysis of the state of the art to include all recent and relevant works in the field.
An updated analysis of the state of the art is mandatory for a publication in Computer Communications.

If you decide to revise the work, please submit a list of changes or a rebuttal against each point which is being raised when you submit the revised manuscript.

\textit{Include an overview of all changes made in the paper.}

\section{Comments by Reviewer \#1}

\end{document}

### 2015-06-19 Response to reviewers - r2.tex
Added reviewer's comments as verbatim blocks

@@
 
-\section{Comments by Reviewer \#1}
+\section{Comments by Reviewer \#2}
+
+\begin{verbatim}
+After reviewing the new version of the document, I admit the authors have  substantially changed section 3 (state of the art) and they have improved and extended the introduction and sections 4 (description of the system) and section 5 (comparison with other systems) I acknowledge the ideas are really interesting and exciting, but I'm still not sure if the authors are providing new results not published in their previous works or just rephrasing their text.
+
+Since there is an obvious over-the-top quality in their work and some good ideas, I'll let the editors decide if the contents are novel enough (compared to other previous works by the same authors) to be published in the journal.
+
+\end{verbatim}
+
+\section{Comments by Reviewer \#3}
+
+\begin{verbatim}
+This paper describes MUSES, an adaptable framework for enforcing security policies on mobile devices.
+This tool relies on Machine Learning and CI techniques to predict policy violations and is self-adaptive on user behaviors.
+The idea seems interesting although several technical concerns arise from the reading of this work:
+1.
+The tools aims at enforcing security policies, however the security response occurs only AFTER a particular pattern is recognized to be potentially malicious.
+From my understandings, there is no a-priori enforcement except for the prediction based on event logs.
+This could mean that e security violation could in principle happen and only later recognized.
+This is not so suitable for a corporate environment with strict security requirements.
+This statement should be discussed and preferably discredited with experimental results.
+2.
+A strong limitation is that an effective enforcement is only possible with MUSES Aware Apps.
+It is unclear the effectiveness of the approach with commercial applications.
+In page 14 "MUSES could just detect very specific events and also do very limited actions".
+With those assumptions, it seems unlikely that a company would adopt MUSES since it is not able to offer an adequate level of security.
+I think that this is very far from being acceptable for a BYOD solution.
+Also in this respect, experimental results are needed.
+3.
+MUSES Sensors are essentially user-space applications that collects logs on specific activities.
+This aspect really concerns me since a compromised device or compromised sensor apps could vanish all MUSES effort.
+Authors should deeply discuss this aspect.
+4.
+Paper structure is really confusing.
+Many essential concepts are introduced and explained too late in the paper forcing the reader to go back and forth to understand the architecture (e.g.
+MUSES aware apps and Data Mining techniques).
+I suggest authors to deeply revise the presentation of their work.
+5.      A discussion on research activities on BYOD is completely missing. This is unacceptable for a solution that aims at solving BYOD security issues. Just to cite a few:
+a.      Gessner, Dennis, et al. "Towards a User-Friendly Security-Enhancing BYOD Solution." NEC Technical Journal 7.3 (2013): 113.
+b.      Samaras, Vasileios. A BYOD Enterprise Security Architecture for accessing SaaS cloud services. Diss. TU Delft, Delft University of Technology, 2013.
+c.      Armando, Alessandro, et al. "Enabling BYOD through secure meta-market." Proceedings of the 2014 ACM conference on Security and privacy in wireless & mobile networks. ACM, 2014.
+6.
+The experimental section is completely missing.
+Is MUSES able to identify security violations?
+Which are the computational cost for both the company (server) and users (mobile devices)?
+Are there any limitations?
+Under such considerations I recommend authors for a *STRONG* major revision to cover the aforementioned points.
+
+\end{verbatim}
+
+\section{Comments by Reviewer \#4}
+
+\begin{verbatim}
+In this work authors present state-of-the art in BYOD solutions, and introduce a new solution, MUSES, a result of an EU FP7 project.
+
+General and specific comments:
+
+The abstract of the paper should be improved. Sentence on page 1, lines 23-25 is unclear. It suggests that the BYOD solutions appeared in the market with the purpose to adapt to it in a secure way.
+
+The description of IBM products, in section 3.1, does not provide clear distinction between various service types provided by IBM.
+It furthermore lacks focused coverage of services relevant for this work.
+
+In analysis of IBM offer, authors refer to general web site for mobile security products and consumer guide/whitepaper that explores the general problem of BYOD.
+They consider services that are not purely related to BYOD and MUSES.
+For instance, it is not clear how "Enterprise Wireless Networks" (page 6, lines 21-26) fit into comparison, and how establishment of secure connections can be related to MUSES's adaptability.
+On the other hand, the products such as MobileFirst and MaaS360 are omitted.
+The suggestion in this regard is to consider rewriting this part, including updated references and current tools in comparison.
+
+In section 3.3 (p.7, sentence in l.18-19) there is provided a statement about success of two solutions, however without referencing relevant sources or providing details.
+It is furthermore questionable whether this statement is relevant for the scope of this work at all.
+
+Section 3.6.1 covers WSO2, an open source tool that should be freely available for evaluation and comparison.
+However, in review, this tool has been only roughly mentioned.
+The context and relevance to the work are omitted, as well as features and comparison with MUSES.
+It is not clear therefore how this tool and MUSES differ.
+
+Section 3.6.4 (p10, 44) states "are Worx-enable are capable". The meaning of this part is not clear, nor to which concept Worx refers.
+
+Basically, in section 3 the following possibilities for improvement are identified:
+ 1) Explain why particular solutions are chosen for inclusion in review and what is their relevance? Did authors consider other (possible) solutions relying on DM and CI?
+ 2) Considering variety of BYOD tools and their different features, authors might consider to introduce or reuse a taxonomy or classification of those approaches, and state the place of MUSES there (or define a new subcategory, if deemed necessary)
+ 3) Some presented solutions miss their relationship to MUSES (coverage, features, comparison).
+This point also refers to inconsistent coverage amongst solutions and weak arguments favouring MUSES.
+Either coverage should be more consisent by focusing on common (present or missing) aspects, or it should be elaborated why such coverage is missing.
+Also see the comment for dicussion part bellow.
+
+On p.12, l.9-12 authors state that MUSES can be installed in every mobile or portable device, independently of the operating system and device type.
+This is also derived from the title "Multiplatform Usable Endpoint Security System".
+The authors however do not provide additional details on how is this achieved in the practice and are there any limitations in regards to that.
+How they managed to provide the same sistem for Androd, Windows, iOS, PCs, without limitations?
+How MUSES manage the variety of OS versions and underlying platform features provided to the app?
+This feature is important differentiator against some other solutions and in opinion of this reviewer should be elaborated in more detail.
+
+When stating (p.13, l.15-24) that MUSES relies on AES based symmetric encryption, does it mean that information flows in MUSES client internally, as well as client-server communication, are encrypted with the same key?
+Does MUSES uses client specific and/or temporal keys?
+What measures are taken to protect this key from malicious applications both on client and server side?
+How and where is this key generated?
+What is lifetime of the key?
+In my opinion this part should be reworked, providing more detailed description of security aspects of their approach.
+Also please see security related comment bellow.
+
+On p.14, l.16-28 authors introduce the concepts of MUSES Aware App and MUSES API.
+In my opinion they should provide more details on integration options and necessary effort to make an application MUSES Aware.
+This is a crucial aspect of their approach as this requirement and related complexity might hinder the adoption of the solution.
+
+On p.17, l.7-9 authors state that the data sets can be huge, leading to necessity to apply Big Data processing methods.
+They however do not provide at least an indication of the data amount/complexity that is gathered and processed by the system, and at what rate it grows.
+Is it really necessary to employ Big Data processing?
+
+On p.18, for two bullets announced under l.46-47 there is not clear if they are included in the refinement process or not.
+In the later case, it is suggested to explain why they are not present in the processing.
+Maybe these bullets could be moved into part relating to further work.
+
+>From the presented concepts behind MUSES and its flows, it is not completely clear how it approaches "newly discovered vulnerabilities or threats" (p.20 l.27-28).
+It is hence suggested to clarify this statement and provide explanation to which extent is rule refinement and adaptation used to discover and address new vulnerabilities and threats in the software and systems.
+
+Similar applies to human-computer interaction (p.20 l.34).
+Although some details are provided in l.43-45 on the same page, in opinion of this reviewer, the statement about progress beyond the state of the art should be backed with more (stronger) details and data.
+
+This reviewer would also suggest to provide more details on security aspect of the system.
+Some hints are provided in previous comments.
+Additionally, as the client/server interaction is concerned, what measures and aspects have been applied in order to identify and prevent malicious parties to manipulate or inject malicious rules in the system?
+By injecting such rules, the complete sub-network of clients of the company can be affected.
+Furthermore, author assumes that the clients are non-rooted devices.
+What happens, and at which extent can some rooted device affect local application of the system, and also central server and other clients?
+
+For the section 5 and discussion, this reviewer would suggest to consider providing overview in the form of table(s) or figure, comparing different aspects of MUSES and other tools and providing hints/references to further details in this or other works.
+As there are many features of MUSES and other tools, employed approaches and techniques, different coverages and limitations, such overview could countribute to clarity and position of the proposed solution.
+
+Overall, this reviewer perceives this work as a good contribution in presenting and advancing the state-of-the art.
+It is however suggested to consider revising this work and take into account provided suggestions.
+
+Specific comments regarding organization and presentation:
+
+1) This work overuses forward slashes in linking words similar in concept or meaning.
+Although they are necessary in some situations, forward slashes very often link redundant words and reduce flow and readability of the text.
+They also contribute to the vagueness.
+I would suggest authors to review the text in this concern.
+
+2) Authors overuse parentheses to explain details.
+This hinders readability and text flow.
+The level of details provided and their relevance in the context are only partially consistent.
+On p.14 users introduce footnotes for additional details.
+Maybe they should consider applying such approach in other parts of the document as well.
+
+3) The structure and flow of the work can be improved.
+\end{verbatim}
 

### 2015-06-19 Response to reviewers - r2.tex
Included a first response to reviewer
This is intended as an example. Edit lines to make then fit in the
page, close the verbatim before the response and open it again after.

Closes #42 and refers #29 to be closed by @unintendedbear if needed.

@@
 
-The abstract of the paper should be improved. Sentence on page 1, lines 23-25 is unclear. It suggests that the BYOD solutions appeared in the market with the purpose to adapt to it in a secure way.
+The abstract of the paper should be improved. Sentence on page 1,
+lines 23-25 is unclear. It suggests that the BYOD solutions appeared
+in the market with the purpose to adapt to it in a secure way. 
+\end{verbatim}
 
+The abstract has been changed and that confusing sentence has been
+eliminated. Now it is clear, as intended, the intention and focus of
+the paper.
+
+\begin{verbatim}
 The description of IBM products, in section 3.1, does not provide clear distinction between various service types provided by IBM.

### 2015-06-22 MUSES_vs_BYOD_solutions.tex

@@
 
-The way how users have used their devices has changed in the past few years, even the number of different devices per user is increasing because of the so-called Internet of Things \cite{weber2010internet}.
-Thanks to it, users have more flexibility, and also at their works, because now they can use their devices to access company assets and continue working outside of the workplace.
-To allow this way of working, companies started to adopt what has been called the Bring Your Own Device (BYOD) philosophy.
+The way how users employ their devices has changed in the past few
+years, even the number of different devices per user is increasing
+because of the so-called Internet of Things
+\cite{weber2010internet}. Thanks to it, users have more flexibility,
+and also at their works, because now they can use their devices to
+access company assets and continue working outside of the
+workplace. To allow this way of working, companies started to adopt
+what has been called the Bring Your Own Device (BYOD) philosophy.
 

### 2015-06-25 MUSES_vs_BYOD_solutions.tex
Changing introduction of 4.3 section

@@
 
-As previously stated, one of the main features of this system is the self-adaptation (to the user and context), of the set of Corporate Security Rules (specification of the ISPs), that it is be able to perform.
-To this end, the \textit{MusKRS} module is run asynchronously in the server (once a day or every X hours) and it is in charge of analysing all the gathered information (events, context, user-related data), and adapting or refining the security rules.
-The refinement (improvement)  has as aim to better deal with these events, optimizing the current set of rules (removing redundant or non-useful rules, for instance), and even trying to predict future threats due to the user's behaviour.
+The self-adaptation, to the user and context, of the set of Corporate Security Rules is one of the main features of this MUSES system.
+To this end, the \textit{MusKRS} module is in charge of analysing all the gathered events, context, and user-related data.
+Then it processes the data and adapts or refines the security rules.
+This refinement is meant as an improvement of the existing security rules, and it aim is to deal with new, possibly insecure, events.
+As a result, a set of optimisations and additions to the set of security rules are proposed to the Chief Security Officer (CSO) of the company.
 
-This procedure is be composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed (in the \textit{Data Miner} sub-component);  second, a refinement and inference process  is done (in the \textit{Knowledge Compiler} sub-component), considering the data `extracted' in the first step, by means of Computational Intelligence (CI) techniques.
-It should be noticed that part of the refinement (or adaptation) of the security rules is made using simpler methods, such as generalisation or specialisation of rules, for instance.
-Then, other parts of the process can be conducted using CI.
+This procedure is composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of Computational Intelligence (CI) techniques.
+The refinement, or adaptation, of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms.
 
-Another important fact is that MUSES  counts with a human controller, normally the Chief Security Officer (CSO) of the company, who  supervises the system activity by means of logs or feedback messages.
-Thus, adapted and inferred security rules are not, in principle, directly added to the current set of rules.
-Instead, they  are proposed as draft rules to this controller, in order that he/she can accept them if they are interesting and correct.
-The system  is able to `learn' from this decisions, so after a so-called training or `warm up' period, the rules can be directly accepted (included in the set) or rejected autonomously by the MusKRS.
+Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface the CSO can interact with.
+Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order that they can be accepted if they are interesting and useful.
+The system also uses the acceptance or rejection of new rules as `feedback`, learning from this decisions, and refining the rules according to this.
 
-The following sections describe these processes: first focusing on DM techniques to be used both automatically by the MusKRS, and as a kind of decision-aid and monitoring tool for the CSO; second, the CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches, since these methods perform very well, and have been widely used in security-based environments for solving security issues, such as the intrusion detection \cite{GA_intrusion-majeed}, the design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.
+The following sections describe these processes: first, focusing on DM techniques to be used both automatically by the MusKRS, and by the mentioned graphic interface for showing useful information to the CSO; second, used CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches.
+EC methods have demonstrated to have a good performance, and have been widely used in security-based environments for solving security issues, such as intrusion detection \cite{GA_intrusion-majeed}, design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or for the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.
 

### 2015-06-25 MUSES_vs_BYOD_solutions.tex
Re-writing more and more... this 4.3 section is a mess

@@
 This task is performed by the \textit{Data Miner} module.
-It  takes the `raw' data from the database and  process the information, in order to yield a set of relevant data for the Knowledge Compiler module or for the human controller.
-In the first case, this sub-component  takes them as a reference in order to refine or adapt the current set of security rules (for instance, to deal with anomalous situations).
+It  takes the `raw' data from the database and processes the information, in order to yield a set of relevant data for the Knowledge Compiler module and for the human controller.
+In the first case, this Data Miner component takes the set of data as a reference for refining or adapting the current set of security rules, to deal with anomalous situations, for instance.
 
-The process is be mainly non-supervised. Moreover, eventually, the datasets can be huge (depending on the company's data flows), so Big Data processing methods \cite{BigData_11} can be applied.
+The set of data are composed by the so-called patterns, which consist of an event and all the related information to that event.
+This means that the context in which the event was is translated into a number of \textit{attributes} of the pattern.
+This process is mainly non-supervised.
+Moreover, as the datasets are huge, because a lot of attributes are extracted from the events so the more complete information is obtained, MUSES applies Big Data processing methods \cite{BigData_11}.
+%JUSTIFY (Paloma will do it)
 
-The DM/ML techniques process the so-called patterns, which in this context correspond to events (and their related information) produced by the users' interactions with the system.
-As stated, these events  are captured from the sensors in the users' devices and transmitted to the server to be processed and stored in the system database.
-The methods to be applied are:
+The methods that MUSES applies over the data are:
 

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Borrando comentarios de la revisión al párrafo para cerrar un issue. Closes #25

@@
 
-It is important to note that MUSES does not work as an antivirus itself, but has a sensor which % quizás quitar "has a sensor which" y sólo poner "it"
-% Esto ya no sé porque entonces se me repite mucho la palabra "it", serían 2 veces en esta frase y la siguiente que también empieza por "it"...
-checks if the device has already an antivirus, and raises a security violation alert if not.
+It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not.
 It might happen then that the user ignores this advice and the device becomes compromised.
@@
 Then, this change in the patterns will be noticed by the server, which will immediately warn the user, and decrease the device trust value.
-% [Pedro] aquí pueden preguntar sobre cómo se lleva a cabo esa detección del cambio en los sensores...
 

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Descrito el a priori enforcement. Closes #23

@@
 That is to say, the more sensors are implemented, the more enforced the security in the device is.
-%Esta última frase revisádmela por favor, e insultadme si es necesario.
+To implement a sensor means to include a programmed method which makes MUSES to start `listening' some parts of a device.
 For this reason, MUSES implements the following sensors:
@@
   \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
-This security mechanism %¿cambiarlo por "This security mechanism" ?
-% Ok, cambiado, creo que está mejor así.
-   adds the possibility of detecting security violations even if the user is not doing a specific action.
+This security mechanism adds the possibility of detecting security violations even if the user is not doing a specific action.
   \item[LOCATION SENSOR] User location can be obtained from the device GPS.

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Improving section 4.3.1

@@
 \item \textit{Pattern Mining} \cite{PatternMining_Han07}: 
-This process  tries to identify frequent or, on the contrary, anomalous patterns, in order to process them lately.
-The idea is that non-frequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO or to serve as a reference for the rule-refinement process.
+By this process, the patterns are obtained from the `raw' data, as has been explained.
+These form what is called a dataset, and from it, the most frequent or anomalous patterns, can be extracted.
+The idea is that non-frequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO, or to serve as a reference for the rule-refinement process.
 
@@
 This technique tries to train a model (classifier) able to associate every pattern in the dataset to a class, so that the model could be used for assigning a class for further incoming patterns with an unknown category.
-For instance, it could look for events (patterns) that had been previously  marked as `allowed' or `denied' (according to the ISPs).
-When a new event arises, if it has not an assigned decision, the classifier should provide one based on the similarity with previous (and already labelled) patterns.
+Then, the model learns from events that, according to the ISPs, had been previously marked as `allowed' or `denied'.
+When a new event arrives to the server, if it has not an assigned decision, the classifier should provide one based on the similarity with previous, and already labelled, patterns.
 
@@
 The aim of this method is grouping the patterns considering some similarity criteria, in order to manage them as a set.
-This could be used for providing data visualisation mechanisms, in order to make it easier to interpret the data interaction and the distribution in clusters with respect to the different properties (features) of the patterns.
+This is used for providing data visualisation mechanisms through a graphical interface.
+This would make easier to interpret data interaction and the distribution in clusters with respect to the different attributes, or features, of the patterns.
 
 \item \textit{Feature Selection} \cite{FeatureSelection_Guyon03}: 
-It consists on extract the most important features (variables) from the data.
-This could be useful if we want to discard non-key features, which could be interesting in order to reduce the database weight, for improving the performance of other techniques (such as classification or clustering), and even to improve the performance of the whole system, since less information would be gathered and transmitted.
+It consists of extracting the most important featuresvariables from the data.
+Feature selection techniques have been proven \cite{liu1998feature} to preserve the performance of a dataset in terms of classification accuracies, while significantly increasing the processing time.
 
 \item \textit{Data Analysis}: 
-This  provides the CSO with mechanisms to visualise interesting facts about the data, such as more frequent events, dangerous or suspicious users (according to their behaviour), more triggered rules, etc.
+This provides the CSO with mechanisms to visualise interesting facts about the data, such as most frequent events, dangerous or suspicious users according to their behaviour, most triggered rules, etc.
+All this information is shown to the CSO via the mentioned graphical interface, implemented in the server.
 

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Re-writing part of section 4.3.2

@@
 
-The first evolutionary-based approach is a \textit{GP-based classification} method.
-This is useful for two main reasons: first, in order to deal with the data class imbalance \cite{imbalance_techniques_02}, very common in classification problems in real systems (with real data); and second, to better manage categorical (non-numeric) data, since most of the features (variables) and information gathered from the events take these kind of values.
+The Data Miner module adopts, then, two evolutionary-based approaches.
+In the first place, a \textit{GP-based classification} method.
+This is useful for two main reasons: to deal with the data class imbalance \cite{imbalance_techniques_02}, which is very common in classification problems with real systems, gathering real data; and to better manage categorical data, since most of the features and information gathered from the events take these kind of values, and being non-numeric does not allow to measure the distance between them.
 
-Thus, this approach is be able to manage unbalanced datasets considering a fitness function in which a cost can be associated with the classifier accuracy at every epoch, having a penalty cost when the classifier makes a false negative (an element from the minority class which is classified as belonging to the majority class) \cite{cost_adjustment_07}.
-Regarding the type of data, since GP algorithms can manage rule- or tree-based models, it  works perfectly with any categorical variable, yielding a good classifier as it has been made in other works (such as the aforementioned \cite{cost_adjustment_07}).
+Thus, this kind of classification method is able to manage unbalanced datasets, by considering a fitness function in which a cost is associated with the classifier accuracy at every iteration, having a penalty cost when the classifier makes a false negative.
+A false negative is an element from the minority class which is classified like as belonging to the majority class \cite{cost_adjustment_07}.
+With regard to the type of data, since GP algorithms can manage rule or tree based models, it works perfectly with any categorical feature, yielding a good classifier as it has been demonstrated in \cite{cost_adjustment_07}.
 
-The second approach is a Feature Selection process, conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features (variables) in the classification.
-Thus, the algorithm can optimize the group of features to be considered in the classification task, improving both the computational time of this task and also the obtained accuracy of the method.
+The second approach taken in the Data Miner is the Feature Selection process that was mentioned in the previous section.
+This process is conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features in the classification.
+Thus, the GA algorithm can optimise the group of features to be considered in the classification task, improving both the computational time of this task and also the obtained accuracy of the method \cite{liu1998feature}.
 
-The second set of EC techniques is, as stated, part of the rule-refinement (or adaptation) process, to be performed by the \textit{Knowledge Compiler} module.
-These methods can be used for inference and optimisation, and consider this data as a part of the process:
+On the other hand, the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods.
+These methods can be used for inference and optimisation, while considering feedback about the final use of the new rules as a part of the process:
 

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Re-writing another part of section 4.3.2. Vamos @unintendedbear que ya queda menos.

@@
 On the other hand, the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods.
-These methods can be used for inference and optimisation, while considering feedback about the final use of the new rules as a part of the process:
+These methods can be used for inference and optimisation, and they use different data as part of the process, such as:
 
@@
 \item The information extracted from the Data Miner sub-component, mainly concerning the anomalous, unclassified or misclassified patterns.
-These are those patterns which did not match with any of the existing classes (they are quite different from the patterns belonging to those classes), so they cannot be included in any of the classes and thus they should be taken into account for a potential inference or update in the set of security rules, in order to `cover' them.
+These are those patterns which did not match with any of the existing classes, as they are quite different from the patterns belonging to those classes.
+This way, they cannot be included in any of the classes and thus they should be taken into account for a potential inference or update in the set of security rules, in order to `cover' them.
 
-\item User-related information corresponding to those anomalous or unlabelled patterns (events).
-Thus, the user's ID, location and role, for instance, can be considered in order to select the applicable set of rules for that conditions.
+\item User-related information, and context information in general, corresponding to those anomalous or unlabelled events.
+Thus, the user's location zone, role, or device settings, for instance, can be considered in order to select the applicable set of rules for that conditions.
 
-\item Context information for the same patterns, in order to also restrict the applicable set of rules considering this information.
+\item Risk information extracted from the user profile, e.g.
+``Did the user received a lot of `denies' or `allows' before?'', in other words, ``Is the user trustworthy?''.
+In case the user is not, meaning that the user trust value is low, more restrictive rules can be created, otherwise the corresponding rules could be `softer' for that user.
 
-\end{itemize}
-
-Other useful information to consider in the refinement and adaptation process are:
-
-\begin{itemize}
-
-\item Risk information extracted from the user profile (user trust value), e.g.
-``Did the user received a lot of `denies' or `allows' before?'', i.e.
-``Is the user trustworthy?''.
-In case the user is not, more restrictive rules can be created, otherwise the corresponding rules could be `relaxed' for that user.
-
-\item The information stored in logs along the system, which can, for instance, tell about how the user responds to system messages (either an action or if the user gives feedback).
-This could result in the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignore warning messages.
-Moreover, important log information regarding the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.
+\item The information about the user behaviour with respect to system messages, wether the users acts in consequence or against MUSES advice, as well as user feedback.
+The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can be also measured by pop-up messages, ``has this information been useful?''-type.
+All this information contribute to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
+Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.
 

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Reviewed, rewritten, re-everything section 4. References #34 before closing because I need re-review @JJ @pacastillo @fergunet

@@
 
-\item \textit{GP rule inference} method, which generates new rules in order to `cover' those situations non contemplated in the current set of rules.
-Thus, for instance, a new rule could be created in order to deal with the patterns to which the classifier could not assign a class.
+\item A \textit{GP rule inference} method, which generates new rules in order to `cover' those situations that have been not contemplated in the current set of rules.
+Thus, a new rule would be created for dealing with the patterns to which the classifier could not assign a class.
 The generation can be done considering the so-called \textit{dictionary}, i.e.
-a set of terms corresponding to all the possible inputs and actions in the system, which are antecedents (conditions) and consequents in the security rules to be inferred.
-The evaluation of these rules can be done considering the stored log information concerning the parameters along with the actions and decisions made in every component in the system.
+a set of terms corresponding to all the possible inputs and actions in the system, which are antecedents and consequents \footnote{The antecedents are the conditions of a rule that have to be met to apply the consequents.} in the security rules to be inferred.
+The evaluation of these rules is done by considering the stored log information concerning the parameters along with the actions and decisions made in every component in the system.
 Thus, it is possible to `simulate' the whole system behaviour when the new rule is included and get a value of its performance.
 
-\item \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions (antecedents), for instance.
+\item A \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions.
 Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
-The evaluation (of the whole set of security rules) is done considering the number of unlabelled patterns that are `covered' after the adjustments.
+The evaluation of the whole set of security rules is done by considering the number of unlabelled patterns that are `covered' after the adjustments.
 
-\item \textit{GA optimisation} algorithm for setting up and adapting the assets' values.
+\item A \textit{GA optimisation} algorithm for setting up and adapting the assets' values.
 These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
-If it is possible to evaluate the partial solutions proposed by the GA, this approach could be very useful for the CSO (who is in charge of assigning and adjusting these values over time).
-The adaptation or adjustment concerns the change in value that an asset could have due to a loss of importance, once an event has passed (a project presentation, for instance).
+By evaluating the partial solutions proposed by the GA, this approach provides the CSO, who is in charge of assigning and adjusting these values over time, with information about the most dangerous situations for certain assets.
+The adaptation or adjustment concerns the change in value that an asset could have due to a loss of importance, for instance, for being and out-to-date document.
 

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
a proposal
another proposal
a doubt about the 3 EC methods
Added taxonomy in Section 3 for issue #41 . Please @unintendedbear @amorag and @JJ check if I am not saying something weird

@@
 The present section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.
+
+As these tools have several different access levels and different detection methods. Therefore, we propose the next taxonomy in order to classify the BYOD methods described in this paper.
+
+\begin{itemize}
+\item {\em Online or offline threat detection method}.
+Tools can identify security threats during runtime (online) or before their implantation (offline).
+For example, using some kind of Data Mining technique, such as classification methods, or merely the system administrator experience, can be used to generate rules before the deployment of the tool (offline) to detect threats in runtime.
+However, new rules can not be added.
+On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system follows an online scheme.
+\item {\em Updatable of fixed information database}.
+This classification is related with the previous one.
+The new information gathered by the system during runtime can be stored in a database to generate new rules.
+If this database is not changed during runtime, as in the offline example explained above, the database is {\em fixed}.
+An example could be the hand-coded rules of a firewall, such as {\em iptables}, obtained from an offline method.
+On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable source for dynamic adaptation mechanisms.
+However, it is not mandatory for an online threat detection method to use a updatable database, as all the current data may be analysed and deleted once a new rule are created.
+\item {\em Invasive or non-invasive data access}.
+A system can be considered {\em invasive} if a user needs to use the tool to perform his job.
+For example, open a specific browser provided by the tool, instead the original device browser, such as Chrome of Safari.
+A {\em non-invasive} data access is transparent to the user.
+An example is a log analyser daemon that updates other programs configuration or send information to the company server.
+\item {\em Superuser or non-superuser system control}.
+Using a tool in superuser mode would add more information and control than a non-superuser execution, as it can access to elements of the device usually forbidden for regular applications, such as network, logs or other devices.
+However using superuser control may lead to a lack of privacy for the user.
+\end{itemize}
 
@@
 These methods can be used for inference and optimisation, and they use different data as part of the process, such as:
+% [Pedro] maybe we should specify how the following data is used in each one of the 3 EC methods...
 
@@
 This being said, and because the refinement of rules is considered of the same importance as inferring new ones, the approaches that have been implemented are:
+% [Pedro] I'd change this to: "As the rule refinement process is considered of the same importance as inferring new ones, the following three approaches have been implemented:"
+% or even to:
+% "Due to the importance of the refinement process (it is considered of the same importance as inferring new ones) the following three approaches have been implemented:"
 
@@
 Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
+% [Pedro] change "could mean a better" to "could lead to a better"
 The evaluation of the whole set of security rules is done by considering the number of unlabelled patterns that are `covered' after the adjustments.
@@
 \end{itemize}
+
+% [Pedro] it is not clear for me whether those 3 methods can be used (are used) independiently or one after the other(s).
 

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Whops, fixing the first sentence for issue #41, that was incomplete

@@
 
-As these tools have several different access levels and different detection methods. Therefore, we propose the next taxonomy in order to classify the BYOD methods described in this paper.
+As these tools have several access levels, different detection methods or data control, there exist a number of aspects that the end-user needs to take into account to validate if a product fits his needs.
+Therefore, we propose the next taxonomy in order to classify the BYOD tools described in this paper.
 

### 2015-06-27 MUSES_vs_BYOD_solutions.tex
accepting @pacastillo suggestion. I've chosen the first one because it does not contain parentheses

@@
 
-This being said, and because the refinement of rules is considered of the same importance as inferring new ones, the approaches that have been implemented are:
+As the rule refinement process is considered of the same importance as inferring new ones, the following three approaches have been implemented:
 % [Pedro] I'd change this to: "As the rule refinement process is considered of the same importance as inferring new ones, the following three approaches have been implemented:"

### 2015-06-27 MUSES_vs_BYOD_solutions.tex
accepting @pacastillo grammar change

@@
 \item A \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions.
-Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
+Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could lead to a better performance.
 % [Pedro] change "could mean a better" to "could lead to a better"

### 2015-06-27 MUSES_vs_BYOD_solutions.tex
Adding more details about how the EC methods are dependant or not on the others

@@
 Thus, a new rule would be created for dealing with the patterns to which the classifier could not assign a class.
-The generation can be done considering the so-called \textit{dictionary}, i.e.
+The generation of new rules is done by considering the so-called \textit{dictionary}, i.e.
 a set of terms corresponding to all the possible inputs and actions in the system, which are antecedents and consequents \footnote{The antecedents are the conditions of a rule that have to be met to apply the consequents.} in the security rules to be inferred.
@@
 Thus, it is possible to `simulate' the whole system behaviour when the new rule is included and get a value of its performance.
+Finally, the inferred rules are proposed to the CSO as ``new, but not yet refined'', along with their evaluated performance.
 
 \item A \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions.
+The set of rules that could be refined is composed by the new rules from the GP-based inference, but also by the original set of rules which was already completed by the Data Miner.
 Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could lead to a better performance.
@@
 The evaluation of the whole set of security rules is done by considering the number of unlabelled patterns that are `covered' after the adjustments.
+Again, the rules at the end of this step are presented to the CSO as ``refined''.
+The CSO is the one who decides, according to the preformance simulation results, if an inferred rule, or the refined one, is the rule which is finally included in the system.
 
-\item A \textit{GA optimisation} algorithm for setting up and adapting the assets' values.
+\item A \textit{GA optimisation} algorithm for adapting the assets' values.
 These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
 By evaluating the partial solutions proposed by the GA, this approach provides the CSO, who is in charge of assigning and adjusting these values over time, with information about the most dangerous situations for certain assets.
-The adaptation or adjustment concerns the change in value that an asset could have due to a loss of importance, for instance, for being and out-to-date document.
+The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being and out-to-date document.
 
@@
 % [Pedro] it is not clear for me whether those 3 methods can be used (are used) independiently or one after the other(s).
+
+As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting assets' values.
+Both the inferred rules and the refined rules are presented to the CSO, who includes them or not in the system, and this acceptance or rejection acts itself as a feedback for future rule inference.
 

### 2015-06-27 MUSES_vs_BYOD_solutions.tex
Including more information about how te different kinds of data are used in the EC methods

@@
 The generation of new rules is done by considering the so-called \textit{dictionary}, i.e.
-a set of terms corresponding to all the possible inputs and actions in the system, which are antecedents and consequents \footnote{The antecedents are the conditions of a rule that have to be met to apply the consequents.} in the security rules to be inferred.
-The evaluation of these rules is done by considering the stored log information concerning the parameters along with the actions and decisions made in every component in the system.
-Thus, it is possible to `simulate' the whole system behaviour when the new rule is included and get a value of its performance.
+a set of terms corresponding to all the possible context situations and user actions in the system, which are the antecedents and consequents \footnote{The antecedents are the conditions of a rule that have to be met to apply the consequents.} of the security rules to be inferred.
+The evaluation of these rules is done by considering the information that has been described.
+Thus, it is possible to `simulate' the whole system behaviour when the new rule is included.
+Therefore, the system gets a value of its performance in terms of, for instance, how many of the events that were not classified or misclassified, are covered now.
+As was also mentioned, the user or device trust values have influence in the creation of the rules.
 Finally, the inferred rules are proposed to the CSO as ``new, but not yet refined'', along with their evaluated performance.
@@
 By evaluating the partial solutions proposed by the GA, this approach provides the CSO, who is in charge of assigning and adjusting these values over time, with information about the most dangerous situations for certain assets.
+The context information that is gathered by the system is very important, then, in this process.
 The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being and out-to-date document.

### 2015-06-27 MUSES_vs_BYOD_solutions.tex
Reviewing and accepting @fergunet 's taxonomy description

@@
 
-As these tools have several access levels, different detection methods or data control, there exist a number of aspects that the end-user needs to take into account to validate if a product fits his needs.
+As these tools have several access levels, different detection methods, or diverse data control, there exist a number of aspects that the end-users need to take into account to validate if a product fits their needs.
 Therefore, we propose the next taxonomy in order to classify the BYOD tools described in this paper.
@@
 However, new rules can not be added.
-On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system follows an online scheme.
+On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system, follows an online scheme.
 \item {\em Updatable of fixed information database}.
-This classification is related with the previous one.
+This classification is related to the previous one.
 The new information gathered by the system during runtime can be stored in a database to generate new rules.
@@
 An example could be the hand-coded rules of a firewall, such as {\em iptables}, obtained from an offline method.
-On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable source for dynamic adaptation mechanisms.
-However, it is not mandatory for an online threat detection method to use a updatable database, as all the current data may be analysed and deleted once a new rule are created.
+On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable data source for dynamic adaptation mechanisms.
+However, it is not mandatory for an online threat detection method to use a updatable database, as all the current data may be analysed and deleted once a new rule is created.
 \item {\em Invasive or non-invasive data access}.
-A system can be considered {\em invasive} if a user needs to use the tool to perform his job.
-For example, open a specific browser provided by the tool, instead the original device browser, such as Chrome of Safari.
-A {\em non-invasive} data access is transparent to the user.
-An example is a log analyser daemon that updates other programs configuration or send information to the company server.
+A system can be considered {\em invasive} if a user needs to use the tool to perform their job.
+For example, opening a specific browser provided by the tool, instead of the original device browser, such as Chrome of Safari.
+Instead, a {\em non-invasive} data access is transparent to the user.
+An example is a log analyser daemon that updates other programs configuration or sends information to the company server.
 \item {\em Superuser or non-superuser system control}.

### 2015-06-28 MUSES_vs_BYOD_solutions.tex
Cambios y sugerencias en varios apartados
Comentarios con la etiqueta 'Antonio'

@@
 The client is an important part of the a-priori risk treatment, because it both monitors the whole context and finally acts or warns the user in event of a security violation.
-Security violations are mainly identified by security rules, which is why MUSES uses DM and CI techniques to evolve them and enhance the coverage.
+Security violations are mainly identified by security rules,
+% Antonio - yo pienso que en este sistema cualquier violación de seguridad que se detecte se hará por medio de las reglas de seguridad.
+Eso sería lo ideal, pero para ello el CSO debe definir un conjunto que asegure la seguridad del sistema en la mayoría de casos.
+Luego el KRS podrá proponer nuevas reglas a través de 'predicciones' (inferencias) o refinamiento, pero estas últimas se construirán como reglas optimizadas para tratar con incidentes de seguridad ya detectados.
+No se pueden crear de la nada reglas para tratar con nuevos incidentes (desconocidos).
+which is why MUSES uses DM and CI techniques to improve or optimize them and enhance the coverage. 
 That is to say, the more sensors are implemented, the more enforced the security in the device is. 
+% Antonio - esto no lo veo correcto. El meter más sensores no implica que se vayan a mejorar en mayor medida las reglas. Sino que se pueden controlar más formas de actuación de los usuarios.
+% Yo o escribría como algo separado, por ejemplo "A way to enforce the security in these devices is the inclusion of more sensors, which would be able to detect more potentially dangerous behaviours by the users (and thus, security violations)"
 To implement a sensor means to include a programmed method which makes MUSES to start `listening' some parts of a device. 
-For this reason, MUSES implements the following sensors:
+MUSES implements the following sensors:
+% Antonio - yo quitaría el 'for this reason'
 
@@
 
-The self-adaptation, to the user and context, of the set of Corporate Security Rules is one of the main features of this MUSES system.
+The self-adaptation, to the user and context, of the set of Corporate Security Rules is one of the main features of the MUSES system.
 To this end, the \textit{MusKRS} module is in charge of analysing all the gathered events, context, and user-related data.
 Then it processes the data and adapts or refines the security rules.
-This refinement is meant as an improvement of the existing security rules, and it aim is to deal with new, possibly insecure, events.
+This refinement is meant as an improvement of the existing security rules, and its aim is to deal with new, possibly insecure, events.
 As a result, a set of optimisations and additions to the set of security rules are proposed to the Chief Security Officer (CSO) of the company.
@@
 This procedure is composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of Computational Intelligence (CI) techniques.
-The refinement, or adaptation, of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms.
+The refinement, or adaptation, of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms \cite{EAs_Back96}.
 
@@
 
-The set of data are composed by the so-called patterns, which consist of an event and all the related information to that event.
-This means that the context in which the event was is translated into a number of \textit{attributes} of the pattern.
-This process is mainly non-supervised.
-Moreover, as the datasets are huge, because a lot of attributes are extracted from the events so the more complete information is obtained, MUSES applies Big Data processing methods \cite{BigData_11}.
-%JUSTIFY (Paloma will do it)
+The dataset is composed by the so-called patterns, which consist of the features of an event 
+% Antonio - quedaba raro decir que estaba formado por 'un evento' como tal
+and all the related information to that event. This means that the context in which the event was, is translated into a number of \textit{attributes} of the pattern. 
+%This process is mainly non-supervised. 
+% Antonio - Lo que es no supervisado es la clasificación, pero si se está explicando de otra forma ya no tiene sentido decirlo.
+Moreover, as the datasets are huge, because a lot of attributes are extracted from the events so the 
+% Antonio - este 'the' no sé si sobra
+more complete information is obtained, MUSES applies Big Data processing methods \cite{BigData_11}. %JUSTIFY (Paloma will do it)
 
-The methods that MUSES applies over the data are:
+The DM/ML methods that MUSES applies over the data are:
 
@@
 \item \textit{Pattern Mining} \cite{PatternMining_Han07}: 
-By this process, the patterns are obtained from the `raw' data, as has been explained.
-These form what is called a dataset, and from it, the most frequent or anomalous patterns, can be extracted.
+By this process, the patterns are obtained from the `raw' data, as has been explained. These form what is called a dataset, and from it, 
+% Antonio - estaba más correcto como estaba antes (aunque estuviese peor redactado).
+La primera parte no es pattern mining, es la creación de un dataset, que se ha explicado antes.
+Por otra parte, 'dataset' es un término conocido en este entorno.
+the most frequent or anomalous patterns, can be extracted.
 The idea is that non-frequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO, or to serve as a reference for the rule-refinement process.
@@
 \item \textit{Feature Selection} \cite{FeatureSelection_Guyon03}: 
-It consists of extracting the most important featuresvariables from the data.
-Feature selection techniques have been proven \cite{liu1998feature} to preserve the performance of a dataset in terms of classification accuracies, while significantly increasing the processing time.
+It consists of extracting the most important variables from the data. Feature selection techniques have been proven \cite{liu1998feature} to preserve the performance of a dataset 
+% Antonio - yo pondría 'quality' en lugar de 'performance'. Un dataset no tiene rendimiento, bajo mi punto de vista
+in terms of classification accuracies, while significantly improve the processing time.
 
@@
 In the first place, a \textit{GP-based classification} method.
-This is useful for two main reasons: to deal with the data class imbalance \cite{imbalance_techniques_02}, which is very common in classification problems with real systems, gathering real data; and to better manage categorical data, since most of the features and information gathered from the events take these kind of values, and being non-numeric does not allow to measure the distance between them.
+This is useful for two main reasons: to deal with the data class imbalance \cite{imbalance_techniques_02}, which is very common in classification problems with real systems, gathering real data; and to better manage categorical data, since most of the features and information gathered from the events take these kind of values.
+%, and being non-numeric does not allow to measure the distance between them.
+% Antonio - claro que se puede medir la distancia entre valores no numéricos, lo que pasa es que normalmente, ésta no es representativa.
+Mejor omitir esto o poner de forma genérica que 'los valores categóricos dificultan el proceso de machine learning'.
 
-Thus, this kind of classification method is able to manage unbalanced datasets, by considering a fitness function in which a cost is associated with the classifier accuracy at every iteration, having a penalty cost when the classifier makes a false negative.
-A false negative is an element from the minority class which is classified like as belonging to the majority class \cite{cost_adjustment_07}.
+Thus, this kind of classification method is able to manage unbalanced datasets, for instance, by considering a fitness function in which a cost is associated with the classifier accuracy at every iteration, having a penalty cost when the classifier makes a false negative (i.e.
+an element from the minority class which is classified like as belonging to the majority class \cite{cost_adjustment_07}).
 With regard to the type of data, since GP algorithms can manage rule or tree based models, it works perfectly with any categorical feature, yielding a good classifier as it has been demonstrated in \cite{cost_adjustment_07}.
 
-The second approach taken in the Data Miner is the Feature Selection process that was mentioned in the previous section.
+The second evolutionary approach taken in the Data Miner is the Feature Selection process that was mentioned in the previous section.
 This process is conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features in the classification.
@@
 
-On the other hand, the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods.
+On the other hand, 
+% Antonio - creo que no se debe poner 'on the other hand' sin tener un 'on the one hand', pero no sé si es una regla estricta.
+the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods.
 These methods can be used for inference and optimisation, and they use different data as part of the process, such as:

### 2015-06-28 MUSES_vs_BYOD_solutions.tex
Adding @pacastillo to the author list
Improving a-priori enforcement paragraph

@@
 
-\author{P. de las Cuevas, A.M. Mora, J.J. Merelo,\\ P. García-Sánchez, A. Fernández-Ares}
-\ead{\{paloma, amorag, jmerelo, pgarcia, antares\}@geneura.ugr.es}
+\author{P. de las Cuevas, J.J. Merelo, A.M. Mora\\P. A. Castillo, P. García-Sánchez, A. Fernández-Ares}
+\ead{\{paloma, jmerelo, amorag, pacv, pgarcia, antares\}@geneura.ugr.es}
 \address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
@@
 
-The client is an important part of the a-priori risk treatment, because it both monitors the whole context and finally acts or warns the user in event of a security violation.
-Security violations are mainly identified by security rules,
+The client is an important part of the a-priori risk treatment, because it both monitors the whole context, and finally acts or warns the user in event of a security violation. 
 % Antonio - yo pienso que en este sistema cualquier violación de seguridad que se detecte se hará por medio de las reglas de seguridad.
@@
 No se pueden crear de la nada reglas para tratar con nuevos incidentes (desconocidos).
-which is why MUSES uses DM and CI techniques to improve or optimize them and enhance the coverage. 
-That is to say, the more sensors are implemented, the more enforced the security in the device is. 
+But security violations are mainly identified by security rules, which is why MUSES needs at least an initial set of rules, defined by the CSO.
+Then, it makes use of DM and CI techniques to improve or optimise them, enhancing the coverage.
+That is to say, the more sensors are implemented, the more information related to event context can be extracted.
+To implement a sensor means to include a programmed method which triggers MUSES to start `listening' to some parts of a device.
+Then, the initial security rules establish which situations might cause a security violation, and the sensors provide with information which helps the MUSES server to identify events that are alike to the ones that are already known as dangerous.
 % Antonio - esto no lo veo correcto. El meter más sensores no implica que se vayan a mejorar en mayor medida las reglas. Sino que se pueden controlar más formas de actuación de los usuarios.
 % Yo o escribría como algo separado, por ejemplo "A way to enforce the security in these devices is the inclusion of more sensors, which would be able to detect more potentially dangerous behaviours by the users (and thus, security violations)"
-To implement a sensor means to include a programmed method which makes MUSES to start `listening' some parts of a device. 
-MUSES implements the following sensors:
+For these reasons, MUSES implements the following sensors:
 % Antonio - yo quitaría el 'for this reason'

### 2015-06-28 MUSES_vs_BYOD_solutions.tex
... Please is a reviewer states that we should not put parentheses every 2 words, and I spend DAYS erasing them... don't put them all over again

@@
 
-The dataset is composed by the so-called patterns, which consist of the features of an event 
+The set of data is composed by the so-called patterns, which consist of an occurred event 
 % Antonio - quedaba raro decir que estaba formado por 'un evento' como tal
@@
 % Antonio - Lo que es no supervisado es la clasificación, pero si se está explicando de otra forma ya no tiene sentido decirlo.
-Moreover, as the datasets are huge, because a lot of attributes are extracted from the events so the 
-% Antonio - este 'the' no sé si sobra
-more complete information is obtained, MUSES applies Big Data processing methods \cite{BigData_11}. %JUSTIFY (Paloma will do it)
+Moreover, a lot of attributes are extracted from the events, for obtaining the mor information as possible.
+This results in huge datasets, which is why MUSES applies Big Data processing methods \cite{BigData_11}.
+%JUSTIFY (Paloma will do it)
 
@@
 \item \textit{Pattern Mining} \cite{PatternMining_Han07}: 
-By this process, the patterns are obtained from the `raw' data, as has been explained. These form what is called a dataset, and from it, 
-% Antonio - estaba más correcto como estaba antes (aunque estuviese peor redactado).
-La primera parte no es pattern mining, es la creación de un dataset, que se ha explicado antes.
-Por otra parte, 'dataset' es un término conocido en este entorno.
-the most frequent or anomalous patterns, can be extracted.
-The idea is that non-frequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO, or to serve as a reference for the rule-refinement process.
+From the whole set of patterns which form the built dataset, the most frequent ones, as well as the uncommon, are obtained.
+The idea is that infrequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO, or to serve as a reference for the rule-refinement process.
 
@@
 \item \textit{Feature Selection} \cite{FeatureSelection_Guyon03}: 
-It consists of extracting the most important variables from the data. Feature selection techniques have been proven \cite{liu1998feature} to preserve the performance of a dataset 
+It consists of extracting the most important variables from the data. Feature selection techniques have been proven \cite{liu1998feature} to preserve the performance of the original feature set 
 % Antonio - yo pondría 'quality' en lugar de 'performance'. Un dataset no tiene rendimiento, bajo mi punto de vista
@@
 
-Thus, this kind of classification method is able to manage unbalanced datasets, for instance, by considering a fitness function in which a cost is associated with the classifier accuracy at every iteration, having a penalty cost when the classifier makes a false negative (i.e.
-an element from the minority class which is classified like as belonging to the majority class \cite{cost_adjustment_07}).
+Thus, this kind of classification method is able to manage unbalanced datasets, for instance, by considering a fitness function in which a cost is associated with the classifier accuracy at every iteration, having a penalty cost when the classifier makes a false negative.
+A false negative is an element from the minority class which is classified like as belonging to the majority class \cite{cost_adjustment_07}.
 With regard to the type of data, since GP algorithms can manage rule or tree based models, it works perfectly with any categorical feature, yielding a good classifier as it has been demonstrated in \cite{cost_adjustment_07}.

### 2015-06-28 MUSES_vs_BYOD_solutions.tex
No @amorag, is not mandatory to put 'on the one hand' before 'on the other hand'
my apologies to @amorag for overreacting

@@
 
-\author{P. de las Cuevas, J.J. Merelo, A.M. Mora\\P. A. Castillo, P. García-Sánchez, A. Fernández-Ares}
-\ead{\{paloma, jmerelo, amorag, pacv, pgarcia, antares\}@geneura.ugr.es}
+\author{P. de las Cuevas, A.M. Mora, J.J. Merelo,\\P. A. Castillo, P. García-Sánchez, A. Fernández-Ares}
+\ead{\{paloma, amorag, jmerelo, pacv, pgarcia, antares\}@geneura.ugr.es}
 \address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
@@
 
-On the other hand, 
-% Antonio - creo que no se debe poner 'on the other hand' sin tener un 'on the one hand', pero no sé si es una regla estricta.
-the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods.
+On the other hand, the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods.
 These methods can be used for inference and optimisation, and they use different data as part of the process, such as:

### 2015-06-28 Response to reviewers.tex

@@
 
-Moreover the abstract and introduction have been also rewritten in order to describe the aim and contents of the paper,and the conclusions have been improved.
+Moreover the abstract and introduction have been also rewritten in order to describe the aim and contents of the paper, and the conclusions have been improved.
+% [Pedro] I propose rewrite this sentence as follows: "Moreover, both the abstract and introduction sections have been rewritten ....
+and the conclusions have also been improved."
 
@@
 this area are addressed using computational intelligence techniques.
+% [Pedro] add: "in the MUSES project."
 

### 2015-06-28 MUSES_vs_BYOD_solutions.tex
I don't think this can be improved any more.
Revised and added response. Closes #29.

@@
 \begin{abstract} 
-Enterprises, and particularly their Chief Security Officers (CSOs),
-want to ensure that their Security Policies are complied, but this
+Companies and particularly their Chief Security Officers (CSOs)
+want to ensure that their Security Policies are followed, but this
 becomes a difficult goal to achieve at the point employees are able to use, or bring,
@@
 everyday, a number of solutions have appeared in the market so that it
-can implemented in a secure way and comply with the Security Policies
+can be implemented in a secure way and comply with the Security Policies
 mentioned above. In this paper we present an overview of BYOD security
-solutions along a novel and open source system named
+solutions along a novel, adaptive and open source system named
 MUSES (Multiplatform Usable Endpoint Security), able 
@@
                                 % Solution, details. 
-MUSES, which has released its first prototype in early 2015, is
+The MUSES framweork, which has released its first prototype in early 2015, is
 compared with the most relevant 
@@
 respect to them. % <- we will explain why is better in the work
-
-% What do we do in this paper? Present the
-                 % architecture? The prototypes? - JJ
 \end{abstract}

### 2015-06-28 MUSES_vs_BYOD_solutions.tex
Reviewed subsection for issue #34 for @unintendedbear

@@
 
-The Data Miner module adopts, then, two evolutionary-based approaches.
+The Data Miner module adopts two evolutionary-based approaches.
 In the first place, a \textit{GP-based classification} method.
@@
 \item User-related information, and context information in general, corresponding to those anomalous or unlabelled events.
-Thus, the user's location zone, role, or device settings, for instance, can be considered in order to select the applicable set of rules for that conditions.
+Thus, the user's location zone, role, or device settings, for instance, can be considered in order to select the applicable set of rules for those conditions.
 
@@
 
-\item The information about the user behaviour with respect to system messages, wether the users acts in consequence or against MUSES advice, as well as user feedback.
+\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
 The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can be also measured by pop-up messages, ``has this information been useful?''-type.
-All this information contribute to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
+All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
 Moreover, important log information with regard to the parameters used or the decisions made in the different modules can be used for further tests of new inferred rules, as it is explained below.
@@
 Again, the rules at the end of this step are presented to the CSO as ``refined''.
-The CSO is the one who decides, according to the preformance simulation results, if an inferred rule, or the refined one, is the rule which is finally included in the system.
+The CSO is the one who decides, according to the performance simulation results, if an inferred rule, or the refined one, is the rule which is finally included in the system.
 
 \item A \textit{GA optimisation} algorithm for adapting the assets' values.
+%FERGU: "values of the assets" mejor?
+Los valores no son "poseidos" por los assets, no?
+xD (tampoco tengo mucha idea del genitivo sajón, ojo)
 These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
@@
 The context information that is gathered by the system is very important, then, in this process.
-The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being and out-to-date document.
+%FERGU: pondría el "in this process" al principio de la frase.
+The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being an out-to-date document.
 

### 2015-06-29 MUSES_vs_BYOD_solutions.tex
Addressing comments by @fergunet

@@
 
-\item A \textit{GA optimisation} algorithm for adapting the assets' values.
+\item A \textit{GA optimisation} algorithm for adapting the values of the assets.
 %FERGU: "values of the assets" mejor?
@@
 xD (tampoco tengo mucha idea del genitivo sajón, ojo)
+% Toda la razón :D Se ma colao, shame on me!
 These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
 By evaluating the partial solutions proposed by the GA, this approach provides the CSO, who is in charge of assigning and adjusting these values over time, with information about the most dangerous situations for certain assets.
-The context information that is gathered by the system is very important, then, in this process.
+In this process, then, the context information that is gathered by the system is very important.
 %FERGU: pondría el "in this process" al principio de la frase.
+% Ok, cambiado
 The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being an out-to-date document.

### 2015-06-30 MUSES_vs_BYOD_solutions.tex
@pacastillo 's comments, abstract and section 1

@@
 \author{P. de las Cuevas, A.M. Mora, J.J. Merelo,\\P. A. Castillo, P. García-Sánchez, A. Fernández-Ares}
-\ead{\{paloma, amorag, jmerelo, pacv, pgarcia, antares\}@geneura.ugr.es}
+\ead{\{paloma, amorag, jmerelo, pedro, pgarcia, antares\}@geneura.ugr.es}
 \address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
@@
                                 % Solution, details. 
-The MUSES framweork, which has released its first prototype in early 2015, is
+The MUSES framework, which has released its first prototype in early 2015, is
 compared with the most relevant 
-solutions offered by other companies to deal with the same issues as, remarking the advantages that our system offers with
+solutions offered by other companies to deal with the same issues, remarking the advantages that our system offers with
 respect to them. % <- we will explain why is better in the work
@@
 The way how users employ their devices has changed in the past few
-years, even the number of different devices per user is increasing
+years; even the number of different devices per user is increasing
 because of the so-called Internet of Things
@@
 Policies \cite{Opp_Security11}.
-However, allowing a BYOD environment means to take care of the risks that the use of personal smartphones can bring to the company \cite{gangula2013survey}.
+However, allowing a BYOD environment means to take care of the risks that the use of personal devices can bring to the company \cite{gangula2013survey}.
 For instance, the mixture between personal and professional information in these devices would allow the user to navigate inside social networks, where important data could be leaked in the event of a security incident.
@@
 MUSES, from Multiplatform Usable Endpoint Security, which is being developed within an European Project\footnote{\url{http://musesproject.eu/}} of the same name. MUSES is a
-dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
+dev\-ice\--in\-de\-pen\-dent end-to-end user-centric tool, based on a
 set of security rules defined as specifications of the Corporate
 Security Policies. In addition, it has the ability of `learning' from the user's past behaviour and adapt the set of existing rules, or even inferring new ones,
-in order to deal with potential security incidents that they might cause in the future. 
+in order to deal with potential security incidents that users might cause in the future. 
 Then the system reacts, in a non-intrusive way, to the potentially
@@
 was presented at..." % Gracias again
-In this paper, once the first MUSES prototype has been released, and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them.
+In this paper, once the first MUSES prototype has been released and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them with other existing tools in the market.
 % [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...
@@
 %cambiado
- such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset of policies.
+ such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best policies subset.
 
@@
 % Totalmente de acuerdo, cambiado.
-This work presents a brief overview of the main existing solutions in this environment.
+This work presents a brief overview of the main existing solutions in the BYOD environment.
 Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
@@
 First, some background situation about enterprise security is presented in Section \ref{sec:preliminaryconcepts}, explaining how BYOD philosophy affects it.
-Then, the main solutions or tools are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
-Then, in Section \ref{sec:muses}, the Multiplatform Usable Endpoint Security System is presented (architecture + soft computing techniques).
-Its advantages and benefits in comparison with the other solutions are commented in Section \ref{sec:comparison}.
-Finally, the reached conclusions are discussed in Section \ref{sec:conclusions}.
+The main solutions or tools are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
+Section \ref{sec:muses} presents the Multiplatform Usable Endpoint Security System, with its architecture and the soft computing techniques it makes uses of.
+Advantages and benefits of the proposed system are compared to other solutions found in bibliography in Section \ref{sec:comparison}.
+Finally, the reached conclusions are discussed in Section \ref{sec:conclusions}, followed by future work.
 
@@
 
-One of the tasks of a Chief Security Officer (CSO) is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}.
+One of the tasks of a CSO is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}.
 This means that, until the appearance of BYOD, enterprises used to follow static security policies devoted to control an environment where the company assets and the devices were purchased and maintained by the company.
-Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk because the devices that the employees use are not always company-owned.
+Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk as employees' devices are not always company-owned.
 This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying to avoid monitoring the users in a way that is against privacy.

### 2015-06-30 MUSES_vs_BYOD_solutions.tex
Question for @pacastillo

@@
 Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk as employees' devices are not always company-owned.
-This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying to avoid monitoring the users in a way that is against privacy.
+This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying not to intrude into users' privacy.
+%Pedro, me señalaste esto como para modificarlo por algo en plan "tratar de evitar intromisiones en la privacidad".
+¿Te parece bien esto?
 A needed security policy, or in this case, an ISP should deal with the way of protecting a certain organization's information against a security breach.

### 2015-06-30 MUSES_vs_BYOD_solutions.tex
@pacastillo 's comments, abstract and section 2

@@
 Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community or organisation that they are built for.
-In this sense, MUSES stands up for a self-adaptation of the security policies of a company.
+In this sense, MUSES stands up for a self-adaptation of company security policies.
 
 On the other hand, employee-owned devices like smartphones, can be both used for personal matters at work, and for continuing working outside of the workplace.
-As the name says, smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life.
-For this reason, the risk of uncontrolled devices accessing to corporate assets in unsafe conditions, due to the number of new risks which are linked to smartphones \cite{gangula2013survey}, is bigger.
+Smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life.
+For this reason, the risk of uncontrolled devices accessing to corporate assets in unsafe conditions, due to the number of new risks which are linked to smartphones \cite{gangula2013survey}, is increasing.
 
-Normally, the enterprise network architecture was being adapted to cope with external attackers \cite{MIT05}.
-With the incorporation of BYOD, the threat is about corporate assets being compromised due to employees' devices with vulnerabilities \cite{android11}, or leaked because they are being accessed from a device connected through an insecure (public) network.
+Usually, the enterprise network architecture is being adapted to cope with external attackers \cite{MIT05}.
+However, with the incorporation of BYOD, the threat is about corporate assets being compromised due to employees' devices with vulnerabilities \cite{android11}, or leaked because they are being accessed from a device connected through an insecure (public) network.
 
 Thus now, more risky situations should be considered when designing a company's network architecture.
-In Figure \ref{fig:proposed_diagram} there is a proposal which can be used for the beginning of the study of solutions that may secure such a dynamic environment.
+Figure \ref{fig:proposed_diagram} shows the proposal that can be used to start the study of solutions that may secure such a dynamic environment.
 It includes the possibility of having employee-owned mobile (smartphones and tablets) and portable (laptops) devices, and also the opportunity that the employees have of connecting these devices either from inside or outside the company premises.

### 2015-06-30 MUSES_vs_BYOD_solutions.tex
Reviewed some papers proposed by Referee 3 for issue #27. Also, a reference for taxonomy of issue #41

--- 2015-06-30 MUSES_vs_BYOD_solutions.tex
@@
 \author{P. de las Cuevas, A.M. Mora, J.J. Merelo,\\P. A. Castillo, P. García-Sánchez, A. Fernández-Ares}
-\ead{\{paloma, amorag, jmerelo, pedro, pgarcia, antares\}@geneura.ugr.es}
+\ead{\{paloma, amorag, jmerelo, pacv, pgarcia, antares\}@geneura.ugr.es}
 \address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
@@
                                 % Solution, details. 
-The MUSES framework, which has released its first prototype in early 2015, is
+The MUSES framweork, which has released its first prototype in early 2015, is
 compared with the most relevant 
-solutions offered by other companies to deal with the same issues, remarking the advantages that our system offers with
+solutions offered by other companies to deal with the same issues as, remarking the advantages that our system offers with
 respect to them. % <- we will explain why is better in the work
@@
 The way how users employ their devices has changed in the past few
-years; even the number of different devices per user is increasing
+years, even the number of different devices per user is increasing
 because of the so-called Internet of Things
@@
 Policies \cite{Opp_Security11}.
-However, allowing a BYOD environment means to take care of the risks that the use of personal devices can bring to the company \cite{gangula2013survey}.
+However, allowing a BYOD environment means to take care of the risks that the use of personal smartphones can bring to the company \cite{gangula2013survey}.
 For instance, the mixture between personal and professional information in these devices would allow the user to navigate inside social networks, where important data could be leaked in the event of a security incident.
@@
 MUSES, from Multiplatform Usable Endpoint Security, which is being developed within an European Project\footnote{\url{http://musesproject.eu/}} of the same name. MUSES is a
-dev\-ice\--in\-de\-pen\-dent end-to-end user-centric tool, based on a
+dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
 set of security rules defined as specifications of the Corporate
 Security Policies. In addition, it has the ability of `learning' from the user's past behaviour and adapt the set of existing rules, or even inferring new ones,
-in order to deal with potential security incidents that users might cause in the future. 
+in order to deal with potential security incidents that they might cause in the future. 
 Then the system reacts, in a non-intrusive way, to the potentially
@@
 was presented at..." % Gracias again
-In this paper, once the first MUSES prototype has been released and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them with other existing tools in the market.
+In this paper, once the first MUSES prototype has been released, and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them.
 % [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...
@@
 %cambiado
- such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best policies subset.
+ such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset of policies.
 
@@
 % Totalmente de acuerdo, cambiado.
-This work presents a brief overview of the main existing solutions in the BYOD environment.
+This work presents a brief overview of the main existing solutions in this environment.
 Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
@@
 First, some background situation about enterprise security is presented in Section \ref{sec:preliminaryconcepts}, explaining how BYOD philosophy affects it.
-The main solutions or tools are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
-Section \ref{sec:muses} presents the Multiplatform Usable Endpoint Security System, with its architecture and the soft computing techniques it makes uses of.
-Advantages and benefits of the proposed system are compared to other solutions found in bibliography in Section \ref{sec:comparison}.
-Finally, the reached conclusions are discussed in Section \ref{sec:conclusions}, followed by future work.
+Then, the main solutions or tools are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
+Then, in Section \ref{sec:muses}, the Multiplatform Usable Endpoint Security System is presented (architecture + soft computing techniques).
+Its advantages and benefits in comparison with the other solutions are commented in Section \ref{sec:comparison}.
+Finally, the reached conclusions are discussed in Section \ref{sec:conclusions}.
 
@@
 
-One of the tasks of a CSO is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}.
+One of the tasks of a Chief Security Officer (CSO) is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}.
 This means that, until the appearance of BYOD, enterprises used to follow static security policies devoted to control an environment where the company assets and the devices were purchased and maintained by the company.
-Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk as employees' devices are not always company-owned.
+Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk because the devices that the employees use are not always company-owned.
 This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying to avoid monitoring the users in a way that is against privacy.
@@
 For this reason, the risk of uncontrolled devices accessing to corporate assets in unsafe conditions, due to the number of new risks which are linked to smartphones \cite{gangula2013survey}, is bigger.
+
+%%%%FERGU-SOA
+%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
+There is an emerging research area in the field of BYOD as it is becoming a growing trend \cite{Garba15organisational}.
+The work \cite{Scarfo12survey} presents a survey about the emerging methods in BYOD security.
+This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices.
+The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.
+
+An example of hands-off method is presented in the work by Gessner et al.
+\cite{Gessner13userfriendly}.
+This work mentions the importance of avoid the modification of the underlying operating system.
+Therefore, they propose the use of a ``container'' application installed in the mobile device.
+This container is able to execute inside it the enterprise applications, acting as a barrier with the rest of the applications, and allowing direct communication with the enterprise VPN.
+The combination of this method, along cryptographic protocols and time-based sessions offers a tradeoff between security and usability.
+Also, this method avoids the modification of the underlying kernel of the device.
+%FERGU: citad este trabajo cuando digáis que es bueno no modificar el OS
+
+Other works propose the analysis of the applications before being installed.
+For example, in \cite{Armando14metamarket} a meta-market application is used to supervise the installation of new applications, using static analysis and code instrumentation techniques, taking into account the organizational security policies.
+A prototype meta-market is tested with Google Play market using a real world BYOD security policy (the US Government BYOD security guidelines).
+
+It is interesting to mention that previous works are mainly focused in separating into hands-off vs hand-on devices, or static analysis techniques.
+Adaptive methods have not been...
+%FERGU: enlazadlo con lo guay de este paper y el dinamismo TERMINAR
+%%%%/FERGU-SOA
 
@@
 Using a tool in superuser mode would add more information and control than a non-superuser execution, as it can access to elements of the device usually forbidden for regular applications, such as network, logs or other devices.
-However using superuser control may lead to a lack of privacy for the user.
+However using superuser control may lead to a lack of privacy for the user (as explained in \cite{Gessner13userfriendly}).
 \end{itemize}

### 2015-07-01 MUSES_vs_BYOD_solutions.tex

--- 2015-06-30 MUSES_vs_BYOD_solutions.tex
@@
 
+%%%%FERGU-SOA
+%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
+There is an emerging research area in the field of BYOD as it is becoming a growing trend \cite{Garba15organisational}.
+The work \cite{Scarfo12survey} presents a survey about the emerging methods in BYOD security.
+This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices.
+The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.
+
+An example of hands-off method is presented in the work by Gessner et al.
+\cite{Gessner13userfriendly}.
+This work mentions the importance of avoid the modification of the underlying operating system.
+Therefore, they propose the use of a ``container'' application installed in the mobile device.
+This container is able to execute inside it the enterprise applications, acting as a barrier with the rest of the applications, and allowing direct communication with the enterprise VPN.
+The combination of this method, along cryptographic protocols and time-based sessions offers a tradeoff between security and usability.
+Also, this method avoids the modification of the underlying kernel of the device.
+%FERGU: citad este trabajo cuando digáis que es bueno no modificar el OS
+
+Other works propose the analysis of the applications before being installed.
+For example, in \cite{Armando14metamarket} a meta-market application is used to supervise the installation of new applications, using static analysis and code instrumentation techniques, taking into account the organizational security policies.
+A prototype meta-market is tested with Google Play market using a real world BYOD security policy (the US Government BYOD security guidelines).
+
+It is interesting to mention that previous works are mainly focused in separating into hands-off vs hand-on devices, or static analysis techniques.
+Adaptive methods have not been...
+%FERGU: enlazadlo con lo guay de este paper y el dinamismo TERMINAR
+%%%%/FERG U-SOA
+
 Thus now, more risky situations should be considered when designing a company's network architecture.

### 2015-07-01 MUSES_vs_BYOD_solutions.tex
Little change to avoid parentheses
Trying to finish @fergunet paragraph with the SotA

@@
 
-%%%%FERGU-SOA
-%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
-There is an emerging research area in the field of BYOD as it is becoming a growing trend \cite{Garba15organisational}.
-The work \cite{Scarfo12survey} presents a survey about the emerging methods in BYOD security.
-This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices.
-The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.
-
-An example of hands-off method is presented in the work by Gessner et al.
-\cite{Gessner13userfriendly}.
-This work mentions the importance of avoid the modification of the underlying operating system.
-Therefore, they propose the use of a ``container'' application installed in the mobile device.
-This container is able to execute inside it the enterprise applications, acting as a barrier with the rest of the applications, and allowing direct communication with the enterprise VPN.
-The combination of this method, along cryptographic protocols and time-based sessions offers a tradeoff between security and usability.
-Also, this method avoids the modification of the underlying kernel of the device.
-%FERGU: citad este trabajo cuando digáis que es bueno no modificar el OS
-
-Other works propose the analysis of the applications before being installed.
-For example, in \cite{Armando14metamarket} a meta-market application is used to supervise the installation of new applications, using static analysis and code instrumentation techniques, taking into account the organizational security policies.
-A prototype meta-market is tested with Google Play market using a real world BYOD security policy (the US Government BYOD security guidelines).
-
-It is interesting to mention that previous works are mainly focused in separating into hands-off vs hand-on devices, or static analysis techniques.
-Adaptive methods have not been...
-%FERGU: enlazadlo con lo guay de este paper y el dinamismo TERMINAR
-%%%%/FERG U-SOA
-
 Thus now, more risky situations should be considered when designing a company's network architecture.
@@
 
+%%%%FERGU-SOA
+%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
+Besides, there is an emerging research area in the field of BYOD.
+This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}.
+The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security.
+This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices.
+The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.
+
+An example of hands-off method is presented in the work by Gessner et al.
+\cite{Gessner13userfriendly}.
+This work mentions the importance of avoiding the modification of the underlying operating system.
+Therefore, they propose the use of a ``container'' application, installed in the mobile device.
+This container is able to execute inside it the enterprise applications, acting as a barrier with the rest of the applications, and allowing direct communication with the enterprise VPN.
+The combination of this method, along cryptographic protocols and time-based sessions, offers a tradeoff between security and usability.
+Also, this method avoids the modification of the underlying kernel of the device.
+%FERGU: citad este trabajo cuando digáis que es bueno no modificar el OS
+
+Other works propose the analysis of the applications before being installed.
+For example, in \cite{Armando14metamarket} a meta-market application is used to supervise the installation of new applications, using static analysis and code instrumentation techniques, taking into account the organisational security policies.
+A meta-market prototype is tested with Google Play market using a real world BYOD security policy \footnote{The US Government BYOD security guidelines}.
+
+It is interesting to mention that previous works are mainly focused in separating into hands-off vs hand-on devices, or static analysis techniques.
+However, neither of the papers found in bibliography stablishes a taxonomy.
+In addition, the tools described in the reviewed works, do not implement any security policies adaptation methods, as the system that we present in this paper.
+%FERGU: enlazadlo con lo guay de este paper y el dinamismo TERMINAR
+%%%%/FERG U-SOA
+
 %------------------------------------------------------------------------------
@@
 
-Many tools for companies, as well as for devices, which have adopted the BYOD have been released in the past four years. This way, and
+Many tools for companies, as well as for devices, have adopted the BYOD have been released in the past four years. This way, and
 more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter into the system, for instance, and also to protect the employees' data by means of data encryption and data protection by requiring the use of strong and secure passwords.
-Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs.
+Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs, like Good's BYOD solution (see Section \ref{subsec:othertools}).
 On the other hand, many solutions have been presented which are more focused on the device side, although they implement also the server side.
+This is the case, for instance, of Android for Work (see Section \ref{subsec:androidwork}).
 Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art.
-The present section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.
+This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.
 
@@
 \item {\em Online or offline threat detection method}.
-Tools can identify security threats during runtime (online) or before their implantation (offline).
-For example, using some kind of Data Mining technique, such as classification methods, or merely the system administrator experience, can be used to generate rules before the deployment of the tool (offline) to detect threats in runtime.
+This kind of tools can identify security threats during runtime (online) or before their implantation (offline).
+For example, using some kind of DM technique, such as classification methods, or merely the system administrator experience, can be used to generate rules before the deployment of the tool (offline) to detect threats in runtime.
 However, new rules can not be added.
 On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system, follows an online scheme.
-\item {\em Updatable of fixed information database}.
+\item {\em Updatable or fixed information database}.
 This classification is related to the previous one.
-The new information gathered by the system during runtime can be stored in a database to generate new rules.
+New information gathered by the system during runtime can be stored in a database to generate new rules.
 If this database is not changed during runtime, as in the offline example explained above, the database is {\em fixed}.
@@
 On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable data source for dynamic adaptation mechanisms.
-However, it is not mandatory for an online threat detection method to use a updatable database, as all the current data may be analysed and deleted once a new rule is created.
+However, it is not mandatory for an online threat detection method to use an updatable database, as current data may be analysed and deleted once a new rule is created.
 \item {\em Invasive or non-invasive data access}.
@@
 Instead, a {\em non-invasive} data access is transparent to the user.
-An example is a log analyser daemon that updates other programs configuration or sends information to the company server.
+An example is a log analyser daemon that updates other program configurations or sends information to the company server.
 \item {\em Superuser or non-superuser system control}.
-Using a tool in superuser mode would add more information and control than a non-superuser execution, as it can access to elements of the device usually forbidden for regular applications, such as network, logs or other devices.
-However using superuser control may lead to a lack of privacy for the user (as explained in \cite{Gessner13userfriendly}).
+Using a tool in superuser mode would add more information and control than a non-superuser running mode, as it can access to elements of the device usually forbidden for regular applications, such as network, logs or other devices.
+However using superuser control may lead to a lack of user privacy, as explained in \cite{Gessner13userfriendly}.
 \end{itemize}

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
Added a new paper to SOA for issue #27
Adding @pacastillo 's review of IBM section

@@
 One of the first companies who supported the BYOD model was IBM \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace \cite{ibm11}.
-IBM has different solutions divided into ``technology solutions'', and ``services'', and almost all are are mainly focused on the management of the devices in the system.
-Then, it might seem clear that the first disadvantage is not including all features in one system, but to make the companies to choose between one or another, or invest even more resources instead.
+IBM provides different solutions divided into ``technology solutions'', and ``services'', and almost all are are mainly focused on the management of the devices in the system.
+Then, it might seem clear that the first disadvantage is not including all features in one system, but to make the companies choosing between one or another, or invest even more resources instead.
 
-Having a look into what IBM offers as ``services'', three services can be found:
+Main services offered by IBM can be divided into three categories:
 
@@
 The last one is specially interesting for the scope of this paper, given the fact that it seems to implement one of the most important advantages of the MUSES system, the self-adaptation.
-IBM, by performing deeper scans over the security incidents data, either if they were successful (computer forensics analysis) or not (the device was enough secure), they claim to be able to recognise new vulnerabilities - or threats - with enough accuracy.
-The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately, and configuring the different parts.
-Also, the fact that IBM software is not open source as MUSES system is, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
-	\item \textit{Hosted Mobile Device Security Management}: A particular service of the Mobile Enterprise Services.
+IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure.
+They claim in their website that they are able to recognise new vulnerabilities - or threats - with enough accuracy.
+The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts.
+Another difference is the fact that IBM software is not open source as MUSES system is.
+Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
+	\item \textit{Hosted Mobile Device Security Management}: This is a particular service of the Mobile Enterprise Services.
 It includes itself a number of subservices, going from tools to make easy to develop secure mobile apps, to an interface for managing the devices in the system, checking their configuration security level.
-Again, what is offered by IBM as `services', are included as default features in the MUSES system.
+As in the previous case, they are offered by IBM as `services', but these are included as default features in the MUSES system.
 	\item \textit{Enterprise Wireless Networks}: Devoted to provide secure channels for communications.

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
Adding @pacastillo 's review of Sophos and Blackberry+KNOX sections

@@
 %Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
-Besides, there is an emerging research area in the field of BYOD.
-This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}.
+Besides, there is an emerging research area in the field of BYOD. This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}. 
+Although some works present studies on its impact in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm.
 The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security.
@@
 This console monitors the devices since the initial set up and registration, until they log off.
-Other features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.
+Remainder features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.
 
@@
 
-Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation.
-They are not being successful in spite of their features.
+Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they are not being successful in spite of their features.
 On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.
-On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available on its last Galaxy smartphone generation.
-Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still semained delayed until it was apparently found insecure \cite{Samsung_insecure}.
+On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available for its last Galaxy smartphone generation.
+Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still remained delayed until it was apparently found insecure \cite{Samsung_insecure}.
 Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android} (see Section \ref{subsec:androidwork}).
@@
 The main feature of KNOX is the use of different containers, or environments, for business and personal sides.
-Each one even includes its own graphical configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
-A password is required in order to enter into the business side and, once \textit{logged in} in this container, no more passwords are needed for the business applications.
-The applications approved by the company IT department must meet Samsung security standards and, though it has been said that KNOX is a device-focused solution, it offered an API.
+Each one includes its own graphical configuration, suche as wallpapers, or colour themes, in order to be more easily recognised and distinguished by the user.
+A password is required in order to enter into the business side and, once \textit{logged in} to this container, no more passwords are needed for the business applications.
+The applications approved by the company IT department must meet Samsung security standards and, though it has been said that KNOX is a device-focused solution, the company offered an API.
 This API would allow the company to access to over almost 205 predefined IT policies.

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
More comments from Pedro, added to Android for Work section

@@
 
-On the device side, one of the most powerful solutions found in the BYOD state of the art seems to be to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone}.
+On the device side, one of the most powerful solutions found in the BYOD state of the art is, apparently, to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone}.
 It has its own Android-based operating system, called \textit{PrivatOS}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}.
-This BlackPhone also allows a remote wiping of the data if the device is lost or stolen.
+BlackPhone also allows a remote wiping of the data if the device is lost or stolen.
 The main disadvantage of this solution is either the enterprise having to make
@@
 
-Android work has only one advantage over MUSES, and roughly over all solutions, which is the ability to act over the Android kernel.
-All the other tools only have permission for monitoring the running processes in the devices, while Android work has, for instance, the ability to provide a `work' version of its native apps.
-MUSES, instead, depends on if the developers adapt their applications through a MUSES API, transforming them to MUSES Aware apps (see Section \ref{subsec:client}).
-In any other case, and most of all with the ``self-adaptation'' feature of MUSES, it can be said that MUSES has more advantages than the Google solution.
+Android Work presents only one advantage over MUSES, and roughly over all solutions, which is the ability to act over the Android kernel.
+The rest of tools only have permission for monitoring the running processes in the devices, while Android Work has, for instance, the ability to provide a `work' version of its native apps.
+MUSES, instead, depends on the developers to adapt their applications through a MUSES API, transforming them to MUSES Aware apps (see Section \ref{subsec:client}).
+In any other case, and most of all with the ``self-adaptation'' feature of MUSES, it can be said that MUSES presents more advantages than the Google solution.
 

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
Sensor names changed to lower case

@@
 \begin{description}
-  \item[CONNECTIVITY SENSOR] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
+  \item[Connectivity sensor] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
+  \item[Device protection sensor] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
 This security mechanism adds the possibility of detecting security violations even if the user is not doing a specific action.
-  \item[LOCATION SENSOR] User location can be obtained from the device GPS.
+  \item[Location sensor] User location can be obtained from the device GPS.
 Although, and to preserve user privacy, a number of `zones' can be defined by the company, so MUSES only checks if the user is inside them and acts in consequence.
-  \item[MAIL SENSOR] If the user is going to send an email, MUSES client sensors check also the email attributes.
+  \item[Mail sensor] If the user is going to send an email, MUSES client sensors check also the email attributes.
 This way, they can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
-  \item[FILE SENSOR] The type of file, also called \textit{asset}, is also very important for the application of security rules.
+  \item[File sensor] The type of file, also called \textit{asset}, is also very important for the application of security rules.
 Thus, this sensor aims to detect is some files might need more strict security policies, also depending on the rest of sensors.
-  \item[APP SENSOR] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
+  \item[App sensor] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
 Additionally, this sensor gathers information abaut the applicationes which the user tries to install or uninstall.

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
All comments by Pedro to section 3 have been now addressed

@@
 \cite{Gessner13userfriendly}.
-This work mentions the importance of avoiding the modification of the underlying operating system.
+This work mentions the importance of avoiding the modification of the underlying operating system (OS).
 Therefore, they propose the use of a ``container'' application, installed in the mobile device.
@@
 On the device side, one of the most powerful solutions found in the BYOD state of the art is, apparently, to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone}.
-It has its own Android-based operating system, called \textit{PrivatOS}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}.
+It has its own Android-based operating system, called \textit{PrivatOS} \cite{Blackphone}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}.
 BlackPhone also allows a remote wiping of the data if the device is lost or stolen.
@@
 \begin{description}
-  \item[Mobile Device Management] that is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
-It should be noted that this tool allows the tracking of every enrolled device, as well as obtaining reports and analytics of their use.
-  \item[Mobile Application Management] With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
-  \item[Enterprise App Store] This store provides users with both enterprise and public applications approved by the company.
-  \item[Mobile Data Security] WSO2 also allows the user's data to be encrypted via password.
+  \item[Mobile Device Management,] which is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
+It should be noted that this tool allows tracking every enrolled device, as well as obtaining reports and analytics of their use.
+  \item[Mobile Application Management:] With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
+  \item[Enterprise App Store:] This store provides users with both enterprise and public applications approved by the company.
+  \item[Mobile Data Security:] WSO2 also allows the user's data to be encrypted via password.
 \end{description}
@@
 
-The philosophy followed by Good is similar to Samsung KNOX one: to create a secure container that places an unreachable partition between personal and business data in order to protect company assets.
+The philosophy followed by Good \cite{Good_tool} is similar to Samsung KNOX one: to create a secure container that places an unreachable partition between personal and business data in order to protect company assets.
 The solutions that they offer \cite{Good_tool} are similar than in the already described solutions.
-Their solution has been developed for the main Operating Systems (OSs) (iOS, Android, and Windows phone), and also desktop computers with Windows.
+Their solution has been developed for the main OSs: iOS, Android, Windows phone, and also desktop computers with Windows.
 A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, documents, calendar), the intranet, and both in-house or third-party mobile applications.
@@
 
-It is a cloud-based service to manage enterprise devices from the BYOD point of view (protecting sensitive corporate data and also letting the users enjoy them privately), by outsourcing the management of those devices to Azzurri.
+It is a cloud-based service \cite{Azzurri_tool} to manage enterprise devices from the BYOD point of view, protecting sensitive corporate data and also letting the users enjoy them privately, by outsourcing the management of those devices to Azzurri.
 
@@
 
-Once the main tools and systems in this area have been introduced, in the following section our own system (still in development) is presented, giving an overview on its general architecture.
-Moreover, we devote a subsection to describe its main features: the use of Data Mining + Machine Learning techniques, and also its self-adaptation ability using Computational Intelligence methods, which compose the real difference with all these tools.
+Once the main tools and systems in this area have been introduced, in the following section our own system is presented, giving an overview on its general architecture.
+Moreover, we devote a subsection to describe its main features: the use of DM + ML techniques, and also its self-adaptation ability using CI methods, which compose the real difference with all the reviewed tools.
 
@@
 % La verdad es que sí, la he releído y estaba muy mal redactada, qué vergüenza :(
-As far as the server is concerned, it has been developed using Java to be installed with an Apache Tomcat in the corporate server, independently of its operating system.
+As far as the server is concerned, it has been developed using Java to be installed with an Apache Tomcat in the corporate server, independently of its OS.
 % [Pedro] y respecto al servidor: "As far as the server is concerned, it has been developed using Java to be used with an Apache Tomcat in the corporate server." % Ok, cambiado y añadido lo del final.
@@
 The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications.
-And finally, MUSES makes use of the fact that current operating systems for mobile devices provide encrypted data containers by default, like the feature used in Android Work.
+And finally, MUSES makes use of the fact that current OS for mobile devices provide encrypted data containers by default, like the feature used in Android Work.
 
@@
 On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with.
-Usually it can be accessed through the operating system (OS).
+Usually it can be accessed through the OS.
 So the type of information to gather from them and also the type of actions to do over them vary depending on the OS.

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
Added thesis required by referee for issue #27

@@
 %Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
-Besides, there is an emerging research area in the field of BYOD. This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}. 
-Although some works present studies on its impact in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm.
+Besides, there is an emerging research area in the field of BYOD.
+This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}.
+There exist several methodological works on this subject.
+Samaras \cite{Samaras13SaaS} proposes a methodology design of a security architecture taking into account their logical design, logical architecture, security mechanisms and physical architecture.
+First, the business processes are studied and legal and security requirements are analysed.
+After applying several controls the architecture is validated using different criteria: Correctness, Completeness, Usability and Flexibility.
+
+Although some works present studies on the impact of BYOD in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm.
 The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security.

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
Cambios a la Intro para darle más coherencia
Creo que ahora está mejor enlazado todo.

@@
 mentioned above. In this paper we present an overview of BYOD security
-solutions along a novel, adaptive and open source system named
+solutions along with a novel, adaptive and open source system named
 MUSES (Multiplatform Usable Endpoint Security), able 
@@
 enterprise security policies, but as a user-centric tool. It considers
-users' behaviour in order to adapt, improve, or even increase the
+users' behaviour in order to adapt, improve, and even increase the
 defined set of security rules. To do this, the system applies Machine
@@
 %FERGU: seguro que ya lo habéis discutido, pero presentar MUSES como algo a hacer en el futuro es un poco... yasabesh xD
+% Antonio - bueno, ya existe. :)
 
@@
 dangerous sequence of actions \footnote{Which are treated as `events' inside the system.} that the employees are conducting at
-any time. The MUSES system has also been tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.
+any time.
 
@@
 patterns which is later processed by means of Computational
-Intelligence (CI) algorithms, namely Evolutionary Computation methods
-\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
-already presented in
-\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
-the implementation was in its early stages when those papers were
-submitted.
-Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype.
-As there was no available test data, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
-as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
-By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented at \cite{mora14:urls}.
-% [Pedro] ¿ese "could be" se refiere a verbo en pasado?
-en ese caso, quizás usar "...
-was presented at..." % Gracias again
-In this paper, once the first MUSES prototype has been released and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them with other existing tools in the market.
-% [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...
+Intelligence (CI) algorithms, mainly Evolutionary Computation methods
+\cite{EAs_Back96,GP_Koza92}.
 
@@
 
-% [Pedro] en este punto se puede comentar lo que se va a presentar en el trabajo introduciendo directamente con "This work presents..." o "This paper presents..." (yo quitaría el "But first,"
-% Totalmente de acuerdo, cambiado.
-This work presents a brief overview of the main existing solutions in the BYOD environment.
-Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
+The general ideas behind MUSES were already presented in
+\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
+the implementation was in its early stages when those papers were
+published.
+Also, an additional work on applying data mining and machine learning techniques was conducted in \cite{mora14:urls}.
+It presented a study over a dataset similar to those that MUSES will manage, but not the same, since the prototype of MUSES had not still been released.
+Thus, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
+as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
+By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented in that work.
+% [Pedro] ¿ese "could be" se refiere a verbo en pasado?
+en ese caso, quizás usar "...
+was presented at..." % Gracias again
+
+% Antonio- muevo esta frase a un sitio más adecuado
+The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results, so we have now a clearer idea of its capabilities. 
+Thus, in this paper we present an overview of the main existing solutions in the BYOD environment.
+Then, a comparison between these tools and MUSES is conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
 % Perfecto, cambiado.
@@
 
+% Antonio - Yo separaría esta sección en dos: Preliminary concepts y SOA.
+Así se suele hacer y así podemos destacar en la respuestas lo de la nueva sección con el SOA.
+Eso sí, en ese caso debería ser mayor y mejor.
+¿Qué opináis?
 \section{Preliminary concepts and background about enterprise security}
@@
 
-However, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.
+As stated, MUSES has been recently tested in an actual company with satisfactory results according to the users' and to the evaluators of the trials.
+% Antonio - lo del trabajo futuro mejor decirlo al final.
+En la intro no se suele poner a no ser que quieras aclarar que este trabajo no va de esto.
+Pero eso suele verse como algo negativo.
+Los revisores te pueden decir que por qué no has hecho ese análisis si ya tienes los datos...
+However, the analysis of all data from these tests, and conclusions, will be addressed in future works.
+
+There is also room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.
 The second prototype of the system will be also released, as well as the conclusions extracted after the analysis of data from the test of the first prototype.

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
Adding @pacastillo 's comments to introduction of section 4. I consider as 'reviewed' some text I added for issue #32, so closes #32

@@
 MUSES is running as a background process, and monitoring those interactions along with the context of the environment.
-Context was defined by Abowd et
+\textit{Context} was defined by Abowd et
 al. \cite{abowd1999towards} as ``any information that can be used to
-characterize the situation of an entity''. And the entity itself is defined as ``a person, place, or object that is considered relevant to the
+characterize the situation of an entity''. And the \textit{entity} itself is defined as ``a person, place, or object that is considered relevant to the
 interaction between a user and an application, including the user and applications
@@
 The corresponding feedback is communicated to the user through the \textit{actuator}, and then the user decides to comply or not with the policy.
-As was mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high.
-In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease.
+As mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high.
+In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease and the CSO will be notified.
 
@@
 Both sides are connected through a secure channel (using HTTPS) over the Internet.
-In that figure just the high-level components in each part are shown, along with the way the information flows in the system.
+Figure \ref{fig:architecture} only shows the high-level components in each part, along with the way the information flows in the system.
 %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras
@@
 Moreover, part of the high computational cost methods to apply needs to be derived to this high-performance server, as the mobile devices do not count with enough computational power.
-These methods include Data Mining \cite{DataMining_Lee01} and Machine Learning \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
+These methods include DM \cite{DataMining_Lee01} and ML \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
 This server is also devoted to centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques can be applied.
@@
 
-All flows of information in MUSES are encrypted with AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations fo the Fact Sheet on Suite B Cryptography \cite{salter2012suite}.
+All flows of information in MUSES are encrypted using AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations of the Fact Sheet on Suite B Cryptography \cite{salter2012suite}.
 Also, the MUSES server authenticates to the MUSES client by means of a self-signed certificate.

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
Question for @pacastillo

@@
 When a user performs an action, an event is automatically created and either sent to the server (online) or locally stored (offline).
-In addition, there are several sensors implemented in the system which periodically scan different aspects of the device configuration, and the environment.
+In addition, there are several sensors implemented in the system which periodically scan different aspects of the device configuration and the environment.
 This way, the system acts equally over specific actions, as well as when it detects something from the sensors that is against the security policies.
@@
 That is to say, the more sensors are implemented, the more information related to event context can be extracted.
-To implement a sensor means to include a programmed method which triggers MUSES to start `listening' to some parts of a device.
+Implementing a sensor means to include a programmed method which triggers MUSES to start `listening' to some parts of a device.
 Then, the initial security rules establish which situations might cause a security violation, and the sensors provide with information which helps the MUSES server to identify events that are alike to the ones that are already known as dangerous.
@@
 For these reasons, MUSES implements the following sensors:
+% Para Pedro -> El caso es que "sensors" es su nombre dentro del sistema. ¿Estaría mejor su pusiésemos "monitoring sensors"?
 % Antonio - yo quitaría el 'for this reason'

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
Comment for @pacastillo and all

@@
 \begin{description}
-  \item[Connectivity sensor] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
+  \item[Connectivity sensor:] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item[Device protection sensor] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
+  \item[Device protection sensor:] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
 This security mechanism adds the possibility of detecting security violations even if the user is not doing a specific action.
-  \item[Location sensor] User location can be obtained from the device GPS.
-Although, and to preserve user privacy, a number of `zones' can be defined by the company, so MUSES only checks if the user is inside them and acts in consequence.
-  \item[Mail sensor] If the user is going to send an email, MUSES client sensors check also the email attributes.
-This way, they can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
-  \item[File sensor] The type of file, also called \textit{asset}, is also very important for the application of security rules.
-Thus, this sensor aims to detect is some files might need more strict security policies, also depending on the rest of sensors.
-  \item[App sensor] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
+  \item[Location sensor:] User location can be obtained using the device GPS.
+Although, this might be taken against the preservation of user privacy.
+This is why MUSES allows the definition of a number of `zones', and therefore it only checks if the user is inside them or not, acting in consequence.
+  \item[Mail sensor:] If the user is writing an email, MUSES client sensor can also check the email attributes.
+Thus, it can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
+  % (Paloma) Pedro, aquí he cambiado el "is going to send" a "is writing" en vez de "is sending" porque en realidad lo que queremos es que se le avise antes de mandarlo, no cuando lo está mandando o lo ha mandado.
+Se explica después.
+¿Cómo lo veis?
+  \item[File sensor:] The type of file, also called \textit{asset}, is also very important for the application of security rules.
+Thus, this sensor aims to detect if some files might need more strict security policies, also depending on the rest of sensors.
+  \item[App sensor:] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
 Additionally, this sensor gathers information abaut the applicationes which the user tries to install or uninstall.

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
MUSES API and MUSES Aware apps are now better explained. Related to #33. Please review before closing

@@
 
-The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between MUSES client and MUSES server.
-In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring with the sensors and acting as a consequence of the decisions made by the system).
-This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
-Some of the commented sensors require the interaction with MUSES Aware Apps, in order to request for information.
-For instance, the MAIL SENSOR could not detect or recognize the contents of an e-mail unless the mail application provides them (so this must be MUSES Aware).
+The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager}, which controls the communications between MUSES client and MUSES server.
+In addition, there are two types of applications considered in this system.
+On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interacts with it.
+This application must be implemented using the MUSES API (Application Program Interface).
+It should be noted that MUSES is an application that is running in the background, and third party apps can communicate with MUSES and ask for a response.
+Then, the MUSES API is not a normal API for building the third party application, but a collection of methods to allow this communication\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
+The main advantage of having MUSES Aware applications, is because actuator is able to actually forbid the users for doing something, if it implies a big risk for the company.
 

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
Adding Pedro's comments on section 4.2

@@
 
-On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with.
-Usually it can be accessed through the OS.
-So the type of information to gather from them and also the type of actions to do over them vary depending on the OS.
-As was already mentioned, in cases MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user.
+On the other hand, the \textit{Non MUSES Aware Apps} are those which MUSES cannot directly interact with.
+Usually, they can be accessed through the OS.
+But the type of information to gather from them and also the type of actions to do over them strongly vary depending on the OS.
+As was already mentioned, when MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user.
 This message informs about why the action is considered as risky and what the user can do to avoid it.
@@
 
-As in the client, there are three main components:
+As in the client, we describe the three main components:
 \begin{itemize}
@@
 It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{deliverable21, deliverable52}.
-This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analyse them to look for an existing security rule that could be applied to the situation.
+This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analysing them to look for an existing security rule that could be applied to the situation.
 The engine discovers that by analysing the context events which are sent with the user action event, so that a complete model of the risks can be built.
@@
 These are later processed for tuning up the existing set of rules, or for inferring new ones.
-The KRS component, along with the CRTEP, are what represent the extension of the state of the art in security solutions for a BYOD environment.
+The MusKRS component, along with the MusCRTEP, are what represent the extension of the state of the art in security solutions for a BYOD environment.
 
@@
 
-There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company CSO to define and manage Security Policies and Rules in a friendly way.
+There are some other components, which add extra functionalities to the system, namely:
+
+\begin{itemize}
+  \item A \textit{Security Policies/Risk Management} tool, that lets the company CSO to define and manage Security Policies and Rules in a friendly way.
 It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values.
-The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
+  \item  The \textit{Privacy Enhancing System}, which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
 There are three important points with relation to this matter \cite{deliverable72}.
 First, the data that the user provides to the system (such as name, or email) is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks.
-Then, the location of the device is never sent and stored in the database, but as was stated in the previous section, there are a number of defined `zones'.
+Then, the location of the device is never sent and stored in the database, but as stated in the previous section, there are a number of defined `zones'.
 What is checked is that the user is inside one of those zones of interest.
@@
 In addition, the hard limit is provided by the law, in case that the employee leaves the company, or if there is a national law specifying a maximum data retention period.
-
-Then, the \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
-Finally, there is another \textit{Connection Manager} which controls the communication with the device side.
+  \item \textit{User, Context, Event Data Receiver}, which is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
+Finally, there is another \textit{Connection Manager} which controls the communications with the device side.
 %FERGU: no usar etc en artículos, mejor poner: (events, user-related LOQUESEA, among others)
 % Cambiado
+\end{itemize}
 

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
As section 4 is reviewed and fixed, this closes #34

@@
 This refinement is meant as an improvement of the existing security rules, and its aim is to deal with new, possibly insecure, events.
-As a result, a set of optimisations and additions to the set of security rules are proposed to the Chief Security Officer (CSO) of the company.
+As a result, a set of optimisations and additions to the set of security rules are proposed to the CSO of the company.
 
-This procedure is composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of Computational Intelligence (CI) techniques.
-The refinement, or adaptation, of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms \cite{EAs_Back96}.
+This procedure is composed by two main steps: first, a DM \cite{DataMining_Lee01} + ML \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of CI techniques.
+The refinement or adaptation of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms \cite{EAs_Back96}.
 
 Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface the CSO can interact with.
-Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order that they can be accepted if they are interesting and useful.
-The system also uses the acceptance or rejection of new rules as `feedback`, learning from this decisions, and refining the rules according to this.
+Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
+The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.
 
@@
 % Antonio - Lo que es no supervisado es la clasificación, pero si se está explicando de otra forma ya no tiene sentido decirlo.
-Moreover, a lot of attributes are extracted from the events, for obtaining the mor information as possible.
-This results in huge datasets, which is why MUSES applies Big Data processing methods \cite{BigData_11}.
-%JUSTIFY (Paloma will do it)
-
-The DM/ML methods that MUSES applies over the data are:
+Moreover, a lot of attributes are extracted from the events, for obtaining the more information as possible. 
+% During the first trials, a ratio of _ events per day was observed.
+As this results in huge datasets, MUSES makes use of several Big Data processing methods \cite{BigData_11}, such as: %JUSTIFY (Paloma will do it)
 
@@
 \item \textit{Pattern Mining} \cite{PatternMining_Han07}: 
-From the whole set of patterns which form the built dataset, the most frequent ones, as well as the uncommon, are obtained.
+From the whole set of patterns which form the built dataset, the most frequent, as well as the uncommon, are obtained.
 The idea is that infrequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO, or to serve as a reference for the rule-refinement process.
@@
 Thus, this kind of classification method is able to manage unbalanced datasets, for instance, by considering a fitness function in which a cost is associated with the classifier accuracy at every iteration, having a penalty cost when the classifier makes a false negative.
-A false negative is an element from the minority class which is classified like as belonging to the majority class \cite{cost_adjustment_07}.
+A false negative is an element from the minority class which is classified as belonging to the majority class \cite{cost_adjustment_07}.
 With regard to the type of data, since GP algorithms can manage rule or tree based models, it works perfectly with any categorical feature, yielding a good classifier as it has been demonstrated in \cite{cost_adjustment_07}.
@@
 \item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
-The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can be also measured by pop-up messages, ``has this information been useful?''-type.
+The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, ``has this information been useful?''-type.
 All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
@@
 Therefore, the system gets a value of its performance in terms of, for instance, how many of the events that were not classified or misclassified, are covered now.
-As was also mentioned, the user or device trust values have influence in the creation of the rules.
+As was also mentioned, the user or device trust values influence the creation of the rules.
 Finally, the inferred rules are proposed to the CSO as ``new, but not yet refined'', along with their evaluated performance.

### 2015-07-06 Response to reviewers - r2.tex
Revises response refs #29
Added two more references and response to reviewer for issue #27. Also, a new item for the taxonomy, based on these new references

@@
 I suggest authors to deeply revise the presentation of their work.
+\end{verbatim}
+
+\begin{verbatim}
 5.      A discussion on research activities on BYOD is completely missing. This is unacceptable for a solution that aims at solving BYOD security issues. Just to cite a few:
@@
 c.      Armando, Alessandro, et al. "Enabling BYOD through secure meta-market." Proceedings of the 2014 ACM conference on Security and privacy in wireless & mobile networks. ACM, 2014.
+\end{verbatim}
+
+Reviewer is right.
+Although several works have been cited in other sections of the work, a proper discussion on research on BYOD was necessary.
+Therefore, we have analysed the 3 papers suggested by the reviewer, together with several new relevant ones.
+These new references also have been used along other sections of the work to justify MUSES features (for example, the set of best practices used) and to propose the new taxonomy, taking into account the works described in the new section.
+The new references added \cite{Garba15organisational,Scarfo12survey,Gessner13userfriendly,Armando14metamarket,Haejung12Door,Samaras13SaaS,Miller12Privacy,Romer14BestPractices} can be found at the end of this document.
+
+\begin{verbatim}
 6.
@@
 Under such considerations I recommend authors for a *STRONG* major revision to cover the aforementioned points.
+\end{verbatim}
 
@@
 The abstract has been changed and that confusing sentence has been
-eliminated. Now it is clear, as intended, the intention and focus of
+eliminated. Now we think it is clear, as intended, the intention,
+context and focus of
 the paper.
@@
 
+%FERGU: Añado las nuevas referencias a partir del fichero bibtex, poned las vuestras!
+\bibliography{review_muses}
 \end{document}

### 2015-07-06 MUSES_vs_BYOD_solutions.tex
Added two more references and response to reviewer for issue #27. Also, a new item for the taxonomy, based on these new references

--- 2015-07-06 MUSES_vs_BYOD_solutions.tex
@@
 After applying several controls the architecture is validated using different criteria: Correctness, Completeness, Usability and Flexibility.
+Romer \cite{Romer14BestPractices} proposes a set of best practices for BYOD security: centralize control and monitoring, protect confidential devices, increase trust with private clouds, connect to important services (such as Dropbox), block risky services and choose proven solutions.
+%FERGU: quizás enlazarlo con lo que presentamos en el paper?
 
-Although some works present studies on the impact of BYOD in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm.
+Although some works present studies on the impact of BYOD in privacy \cite{Miller12Privacy} or relationship between workers productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm.
 The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security.
@@
 It is interesting to mention that previous works are mainly focused in separating into hands-off vs hand-on devices, or static analysis techniques.
-However, neither of the papers found in bibliography stablishes a taxonomy.
+However, neither of the papers found in bibliography establishes a taxonomy.
 In addition, the tools described in the reviewed works, do not implement any security policies adaptation methods, as the system that we present in this paper.
@@
 However, it is not mandatory for an online threat detection method to use an updatable database, as current data may be analysed and deleted once a new rule is created.
+\item {\em Based in an external service or standalone}: A standalone tool do not require a external service to be used.
+For example, a basic firewall.
+However, as mentioned by \cite{Romer14BestPractices} in previous section, a service for threat monitoring, or a private cloud usage are good practices to apply in BYOD.
 \item {\em Invasive or non-invasive data access}.
@@
 For example, opening a specific browser provided by the tool, instead of the original device browser, such as Chrome of Safari.
+An example of an invasive marketplace is the one proposed by \cite{Armando14metamarket} and discussed in previous section.
 Instead, a {\em non-invasive} data access is transparent to the user.

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Empezando con las respuestas a los revisores
Y un par de correcciones chorras

@@
 In addition, there are two types of applications considered in this system.
-On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interacts with it.
+On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interact with it.
 This application must be implemented using the MUSES API (Application Program Interface).
@@
 \begin{itemize}
-	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
+	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, assets' values, 
+% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "assets' values" o "values of the assets". Yo me inclino por la segunda.
+user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
 
@@
 The output of this module is an `access request' which is sent to the \textit{RT2AE}.
-It considers the information included in the access request, as well as other information such as trust data and profiles, assets' values, user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}.
+It considers the information included in the access request, as well as other information such as trust data and profiles, assets' values,
+% Antonio - "values of the assets"
+user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}.
 Finally, the RT2AE extracts the set of potential rules to consider in the analysed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.
@@
 It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values.
+% Antonio - "values of the assets"
   \item  The \textit{Privacy Enhancing System}, which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
@@
 As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting assets' values.
+% Antonio - "values of the assets"
  Both the inferred rules and the refined rules are presented to the CSO, who includes them or not in the system, and this acceptance or rejection acts itself as a feedback for future rule inference.

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Fixing genitive issue

@@
 \begin{itemize}
-	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, assets' values, 
-% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "assets' values" o "values of the assets". Yo me inclino por la segunda.
+	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, values of the assets, 
+% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "values of the assets" o "values of the assets". Yo me inclino por la segunda.
 user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
@@
 The output of this module is an `access request' which is sent to the \textit{RT2AE}.
-It considers the information included in the access request, as well as other information such as trust data and profiles, assets' values,
+It considers the information included in the access request, as well as other information such as trust data and profiles, values of the assetss, s
 % Antonio - "values of the assets"
@@
   \item A \textit{Security Policies/Risk Management} tool, that lets the company CSO to define and manage Security Policies and Rules in a friendly way.
-It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values.
+It also lets the management of risk-related information, useful for the RT2AE process, such as the values of the assets.
 % Antonio - "values of the assets"
@@
 
-As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting assets' values.
+As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting values of the assets.
 % Antonio - "values of the assets"

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Adding clarification about MUSES advantages with respect to self-adaptation

@@
 	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, values of the assets, 
-% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "values of the assets" o "values of the assets". Yo me inclino por la segunda.
+% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "assets' values" o "values of the assets". Yo me inclino por la segunda.
 user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
@@
 The output of this module is an `access request' which is sent to the \textit{RT2AE}.
-It considers the information included in the access request, as well as other information such as trust data and profiles, values of the assetss, s
+It considers the information included in the access request, as well as other information such as trust data and profiles, values of the assets,
 % Antonio - "values of the assets"
@@
 
-MUSES is mainly a free, open-source, platform independent solution, and that makes it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
-In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD.
+MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
+ These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
+In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD.
 Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases.
@@
 
-Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.
+Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context.
+Thus it uses connection properties, or the device trust value, for instance, to really understand the real risk that comes with a specific action.
 
-Also related to this issue, a very big plus of the MUSES system (not present in the other solutions) is its self-adaptivity power.
-Thus, MUSES is able to adapt to changes, either regarding corporate security policies, newly discovered vulnerabilities or threats, different environments of use, or user profiles.
+Also related to this issue, a very big advantage of the MUSES system that is not present in the other solutions is its self-adaptivity power.
+The proposed system uses different methods to create new security rules, being their aim to cover new vulnerabilities or threats.
+Thus, MUSES is able to adapt to changes by applying classification techniques to create new rules, and then refining the whole set of existing policies.
+Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis, plus a classifier trained with all the occurred events in the system.
 
-Moreover, another clear advantage over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.
+Moreover, another clear improvement over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.
 

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Adding clarification about MUSES advantages with respect to self-adaptation. Related to #35

--- 2015-07-07 MUSES_vs_BYOD_solutions.tex
@@
 
-Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context.
-Thus it uses connection properties, or the device trust value, for instance, to really understand the real risk that comes with a specific action.
+Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.
 

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Clarifications about HCI, also related to #35

@@
 Thus, MUSES is able to adapt to changes by applying classification techniques to create new rules, and then refining the whole set of existing policies.
-Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis, plus a classifier trained with all the occurred events in the system.
+Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis plus a classifier trained with all the occurred events in the system.
 
-Moreover, another clear improvement over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.
+Moreover, another clear improvement over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours the real-time decision making process.
 
@@
 First, as mentioned previously, it  implements a self-adaptive event correlation, including a novel hybrid technique of rule refinement and rule adjustment extracting relevant information from processing huge amounts of data.
-Then, the project defines a new approach to risk management taking into account threats (with their costs) as well as the innovative concept of opportunity, i.e.
-the following beneficial outcome from a situation on which, for instance, a user is able to work while waiting at the airport if the risk is low enough.
+Then, the project defines a new approach to risk management taking into account threats, with their costs, as well as the innovative concept of opportunity \footnote{The following beneficial outcome from a situation on which, for instance, a user is able to work while waiting at the airport if the risk is low enough.}.
 
-About HCI and usability of mobile devices, this sets up a significant advance in the state of the art because of the novelty of the BYOD philosophy, and trying to look for individual differences among the users in susceptibility to persuasive strategies for secure behaviour.
-Regarding device monitoring, MUSES  also take into account the so-called context observation, by which private or professional scenarios can be detected, or predicted, based on advanced machine learning techniques.
+About HCI, in Section \ref{sec:preliminaryconcepts} we talked about how it has been demonstrated by Shaw et al.
+\cite{SecPolComp09} and Herath et al.
+\cite{SecPolPenalty09} that the compliance of the employees of a company, with respect to the security policies, increases by educating them and decreases by punishing them.
+Therefore, the fact that MUSES is focused in avoiding security incidents due to users' unawareness of the CSPs, it sets up a significant advance in the state of the art.
+This is because not only the incident is avoided, but the user is educated, which at the same time avoids future risky situations.
+With regard to device monitoring, MUSES  also take into account the so-called context observation, by which private or professional scenarios can be detected, or predicted, based on advanced machine learning techniques.
 Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it  contributes to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Adding Pedro's comments to section 5

@@
 
-About HCI, in Section \ref{sec:preliminaryconcepts} we talked about how it has been demonstrated by Shaw et al.
+As far as the HCI is concerned, in Section \ref{sec:preliminaryconcepts} we talked about how it has been demonstrated by Shaw et al.
 \cite{SecPolComp09} and Herath et al.
 \cite{SecPolPenalty09} that the compliance of the employees of a company, with respect to the security policies, increases by educating them and decreases by punishing them.
-Therefore, the fact that MUSES is focused in avoiding security incidents due to users' unawareness of the CSPs, it sets up a significant advance in the state of the art.
+Therefore, the fact that MUSES is focused in avoiding security incidents due to users' unawareness of the ISPs, it sets up a significant advance in the state of the art.
 This is because not only the incident is avoided, but the user is educated, which at the same time avoids future risky situations.
@@
 through interaction or events, rather than more general and external threats.
-Moreover, the techniques to be used in MUSES  works with real data (in a real system), as a difference to several research works (they consider simulated or artificial data).
+Moreover, the techniques to be used in MUSES  works with real data, as a difference to several research works which consider simulated data.
 
-Data Mining techniques have been used by the authors in some works, but usually aiming for a specific general objective, for instance the detection of threats (botnet) \cite{botnet_detection_clustering_09}, or the recognition of anomalies \cite{feature_selection_anomalies_08}, but they are not linked with a following process to improve the system (the refinement phase in MUSES).
+Authors have used DM techniques in previous works, but usually aiming for a specific general objective, for instance the detection of threats such as botnet \cite{botnet_detection_clustering_09}, or the recognition of anomalies \cite{feature_selection_anomalies_08}.
+However, these works do not contemplate any process to improve the system as the refinement phase in MUSES.
 
@@
 
-Genetic Programming has been previously used by several authors \cite{rule_generation_gp_09,sec_policy_evolution_gp_08}, even for creating new policies or rules in a security-aimed sense, but they do not affect the ISPs and moreover, our proposed evaluation functions (completely integrated in the system) for the refinement and inference approaches are novel.
+GP has been previously proposed in bibliography \cite{rule_generation_gp_09,sec_policy_evolution_gp_08}, even for creating new policies or rules in a security-aimed sense.
+In any case they do not affect the ISPs and moreover, our proposed evaluation functions (completely integrated in the system) for the refinement and inference approaches are novel.
 
-With respect to Genetic Algorithms, they have been extensively used in this scope in the literature, mainly for the detection of anomalies and intrusions rather than for optimisation, as in our case.
+With respect to GA, they have been extensively used in this scope in the literature, mainly for the detection of anomalies and intrusions rather than for optimisation, as it is used in the proposed system.
 However, there are some examples that could be used as model for our approach, such as \cite{EAs_securitycosts-kirta,risk_reduction_ga_12}.

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Finishing the addition of @pacastillo 's comments. Thank you Pedro :D

@@
 The first prototype of this system has been recently released, and it has been already tested in an actual company, with excellent results and very positive feedback.
-The architecture and main features of the system are described, paying special attention to the application of Soft Computing methods in tasks of data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.
+The architecture and main features of the system have been described, paying special attention to the application of Soft Computing methods in tasks related to data analysis, machine learning, and also in the use of evolutionary algorithms to improve the existing set of corporate security rules which leads the system.
 %Antares - Yo podrían en lugar de ``next year'' el año, porque el artículo puede ser leído en cualquier momento y es mejor emplear referencias absolutas, ¿no creeis?
@@
 
-MUSES has been compared with other existing solutions with a similar aim: to ensure the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
-The main advantages of MUSES with respect to the other solutions have been discussed, also remarking its advances beyond the state of the art that define these tools.
+MUSES has been compared to other existing solutions with a similar aim: enduring the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
+Main advantages of MUSES with respect to the other solutions have been discussed, remarking its advances beyond the state of the art that define these tools.
 
-In addition, a scientific comparison between the techniques used in the presented system and those in the literature, in the same scope, has been done.
+In addition, a scientific comparison between the techniques used in the proposed system and those in the literature, in the same scope, has been done.
 It has been discussed that MUSES has the advantage of being multiplatform, while most of the reviewed tools are not.
 In addition, MUSES is able to adapt and evolve the security policies that a company has built, and not only apply them, as the other tools do.
-Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the aim of going beyond the state of the art in different fields of research.
+Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the effort of going beyond the state of the art in different fields of research.
 
@@
 
-There is also room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.
-The second prototype of the system will be also released, as well as the conclusions extracted after the analysis of data from the test of the first prototype.
+There is also room for considering some future improvements to MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}.
+The second prototype of the system will be released in the next months, as well as the conclusions extracted after the analysis of data from the test of the first prototype.
 

### 2015-07-07 Response to reviewers - r2.tex
Added IBM products to section 3.1 for issue #30

--- 2015-06-19 Response to reviewers - r2.tex
@@
 The suggestion in this regard is to consider rewriting this part, including updated references and current tools in comparison.
+\end{verbatim}
 
+This section has been rewrited, and the references mentioned by the referee (including new products) have been added. %FERGU: PONED ESTO MÁS BONICO!
+
+\begin{verbatim}
 In section 3.3 (p.7, sentence in l.18-19) there is provided a statement about success of two solutions, however without referencing relevant sources or providing details.

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Added IBM products to section 3.1 for issue #30

--- 2015-07-07 MUSES_vs_BYOD_solutions.tex
@@
 mentioned above. In this paper we present an overview of BYOD security
-solutions along with a novel, adaptive and open source system named
+solutions along a novel, adaptive and open source system named
 MUSES (Multiplatform Usable Endpoint Security), able 
@@
 enterprise security policies, but as a user-centric tool. It considers
-users' behaviour in order to adapt, improve, and even increase the
+users' behaviour in order to adapt, improve, or even increase the
 defined set of security rules. To do this, the system applies Machine
@@
 %FERGU: seguro que ya lo habéis discutido, pero presentar MUSES como algo a hacer en el futuro es un poco... yasabesh xD
-% Antonio - bueno, ya existe. :)
 
@@
 dangerous sequence of actions \footnote{Which are treated as `events' inside the system.} that the employees are conducting at
-any time.
+any time. The MUSES system has also been tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.
 
@@
 patterns which is later processed by means of Computational
-Intelligence (CI) algorithms, mainly Evolutionary Computation methods
-\cite{EAs_Back96,GP_Koza92}.
+Intelligence (CI) algorithms, namely Evolutionary Computation methods
+\cite{EAs_Back96,GP_Koza92}. The general ideas behind MUSES were
+already presented in
+\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
+the implementation was in its early stages when those papers were
+submitted.
+Also, an additional work on the data mining techniques was conducted in \cite{mora14:urls}, over a set of data previous to the release and test of the first MUSES prototype.
+As there was no available test data, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
+as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
+By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented at \cite{mora14:urls}.
+% [Pedro] ¿ese "could be" se refiere a verbo en pasado?
+en ese caso, quizás usar "...
+was presented at..." % Gracias again
+In this paper, once the first MUSES prototype has been released and the first tests have been conducted, we have a clearer idea of its capabilities, so that we present and compare them with other existing tools in the market.
+% [Pedro] Quizás comenzar la frase con: In this paper, once the first prototipe has been released and the first tests have been conducted, we ...
 
@@
 
-The general ideas behind MUSES were already presented in
-\cite{DBLP:conf/sac/MoraCGZJEBAH14,DBLP:conf/gecco/MoraCGZE14}. However,
-the implementation was in its early stages when those papers were
-published.
-Also, an additional work on applying data mining and machine learning techniques was conducted in \cite{mora14:urls}.
-It presented a study over a dataset similar to those that MUSES will manage, but not the same, since the prototype of MUSES had not still been released.
-Thus, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
-as well as both black and white lists. These lists contained the URLs that were forbidden, or allowed, to be accessed by the employees. 
-By taking the lists as `rules', and the HTTP connections as `events', a previous simulation of the rule generation through classification, and its results, were presented in that work.
-% [Pedro] ¿ese "could be" se refiere a verbo en pasado?
-en ese caso, quizás usar "...
-was presented at..." % Gracias again
-
-% Antonio- muevo esta frase a un sitio más adecuado
-The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results, so we have now a clearer idea of its capabilities. 
-Thus, in this paper we present an overview of the main existing solutions in the BYOD environment.
-Then, a comparison between these tools and MUSES is conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
+% [Pedro] en este punto se puede comentar lo que se va a presentar en el trabajo introduciendo directamente con "This work presents..." o "This paper presents..." (yo quitaría el "But first,"
+% Totalmente de acuerdo, cambiado.
+This work presents a brief overview of the main existing solutions in the BYOD environment.
+Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
 % Perfecto, cambiado.
@@
 
-% Antonio - Yo separaría esta sección en dos: Preliminary concepts y SOA.
-Así se suele hacer y así podemos destacar en la respuestas lo de la nueva sección con el SOA.
-Eso sí, en ese caso debería ser mayor y mejor.
-¿Qué opináis?
 \section{Preliminary concepts and background about enterprise security}
@@
 After applying several controls the architecture is validated using different criteria: Correctness, Completeness, Usability and Flexibility.
-Romer \cite{Romer14BestPractices} proposes a set of best practices for BYOD security: centralize control and monitoring, protect confidential devices, increase trust with private clouds, connect to important services (such as Dropbox), block risky services and choose proven solutions.
-%FERGU: quizás enlazarlo con lo que presentamos en el paper?
 
-Although some works present studies on the impact of BYOD in privacy \cite{Miller12Privacy} or relationship between workers productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm.
+Although some works present studies on the impact of BYOD in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm.
 The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security.
@@
 It is interesting to mention that previous works are mainly focused in separating into hands-off vs hand-on devices, or static analysis techniques.
-However, neither of the papers found in bibliography establishes a taxonomy.
+However, neither of the papers found in bibliography stablishes a taxonomy.
 In addition, the tools described in the reviewed works, do not implement any security policies adaptation methods, as the system that we present in this paper.
@@
 However, it is not mandatory for an online threat detection method to use an updatable database, as current data may be analysed and deleted once a new rule is created.
-\item {\em Based in an external service or standalone}: A standalone tool do not require a external service to be used.
-For example, a basic firewall.
-However, as mentioned by \cite{Romer14BestPractices} in previous section, a service for threat monitoring, or a private cloud usage are good practices to apply in BYOD.
 \item {\em Invasive or non-invasive data access}.
@@
 For example, opening a specific browser provided by the tool, instead of the original device browser, such as Chrome of Safari.
-An example of an invasive marketplace is the one proposed by \cite{Armando14metamarket} and discussed in previous section.
 Instead, a {\em non-invasive} data access is transparent to the user.
@@
 
+%FERGU: HABLANDO DE LOS PRODUCTOS
+{\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing.
+It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport).
+%FERGU: sí, es rApport, no rEpport, no lo cambiéis :P
+ However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}.
+This product, formerly known as {\em MaaS360}) \footonote{\url{http://www.maas360.com/}}, is a MDM (Mobile Device Management) software to securize, monitor and manage mobile devices.
+It uses a web portal in order to centralize the security and control policies.
+This allows the deployment of applications or backups, among other possibilities.
 %----------------------------------------------------------------------------
@@
 MUSES is running as a background process, and monitoring those interactions along with the context of the environment.
-\textit{Context} was defined by Abowd et
+Context was defined by Abowd et
 al. \cite{abowd1999towards} as ``any information that can be used to
-characterize the situation of an entity''. And the \textit{entity} itself is defined as ``a person, place, or object that is considered relevant to the
+characterize the situation of an entity''. And the entity itself is defined as ``a person, place, or object that is considered relevant to the
 interaction between a user and an application, including the user and applications
@@
 The corresponding feedback is communicated to the user through the \textit{actuator}, and then the user decides to comply or not with the policy.
-As mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high.
-In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease and the CSO will be notified.
+As was mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high.
+In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease.
 
@@
 Both sides are connected through a secure channel (using HTTPS) over the Internet.
-Figure \ref{fig:architecture} only shows the high-level components in each part, along with the way the information flows in the system.
+In that figure just the high-level components in each part are shown, along with the way the information flows in the system.
 %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras
@@
 Moreover, part of the high computational cost methods to apply needs to be derived to this high-performance server, as the mobile devices do not count with enough computational power.
-These methods include DM \cite{DataMining_Lee01} and ML \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
+These methods include Data Mining \cite{DataMining_Lee01} and Machine Learning \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
 This server is also devoted to centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques can be applied.
@@
 
-All flows of information in MUSES are encrypted using AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations of the Fact Sheet on Suite B Cryptography \cite{salter2012suite}.
+All flows of information in MUSES are encrypted with AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations fo the Fact Sheet on Suite B Cryptography \cite{salter2012suite}.
 Also, the MUSES server authenticates to the MUSES client by means of a self-signed certificate.
@@
 When a user performs an action, an event is automatically created and either sent to the server (online) or locally stored (offline).
-In addition, there are several sensors implemented in the system which periodically scan different aspects of the device configuration and the environment.
+In addition, there are several sensors implemented in the system which periodically scan different aspects of the device configuration, and the environment.
 This way, the system acts equally over specific actions, as well as when it detects something from the sensors that is against the security policies.
@@
 That is to say, the more sensors are implemented, the more information related to event context can be extracted.
-Implementing a sensor means to include a programmed method which triggers MUSES to start `listening' to some parts of a device.
+To implement a sensor means to include a programmed method which triggers MUSES to start `listening' to some parts of a device.
 Then, the initial security rules establish which situations might cause a security violation, and the sensors provide with information which helps the MUSES server to identify events that are alike to the ones that are already known as dangerous.
@@
 For these reasons, MUSES implements the following sensors:
-% Para Pedro -> El caso es que "sensors" es su nombre dentro del sistema. ¿Estaría mejor su pusiésemos "monitoring sensors"?
 % Antonio - yo quitaría el 'for this reason'
@@
 \begin{description}
-  \item[Connectivity sensor:] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
+  \item[Connectivity sensor] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item[Device protection sensor:] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
+  \item[Device protection sensor] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
 This security mechanism adds the possibility of detecting security violations even if the user is not doing a specific action.
-  \item[Location sensor:] User location can be obtained using the device GPS.
-Although, this might be taken against the preservation of user privacy.
-This is why MUSES allows the definition of a number of `zones', and therefore it only checks if the user is inside them or not, acting in consequence.
-  \item[Mail sensor:] If the user is writing an email, MUSES client sensor can also check the email attributes.
-Thus, it can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
-  % (Paloma) Pedro, aquí he cambiado el "is going to send" a "is writing" en vez de "is sending" porque en realidad lo que queremos es que se le avise antes de mandarlo, no cuando lo está mandando o lo ha mandado.
-Se explica después.
-¿Cómo lo veis?
-  \item[File sensor:] The type of file, also called \textit{asset}, is also very important for the application of security rules.
-Thus, this sensor aims to detect if some files might need more strict security policies, also depending on the rest of sensors.
-  \item[App sensor:] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
+  \item[Location sensor] User location can be obtained from the device GPS.
+Although, and to preserve user privacy, a number of `zones' can be defined by the company, so MUSES only checks if the user is inside them and acts in consequence.
+  \item[Mail sensor] If the user is going to send an email, MUSES client sensors check also the email attributes.
+This way, they can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
+  \item[File sensor] The type of file, also called \textit{asset}, is also very important for the application of security rules.
+Thus, this sensor aims to detect is some files might need more strict security policies, also depending on the rest of sensors.
+  \item[App sensor] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
 Additionally, this sensor gathers information abaut the applicationes which the user tries to install or uninstall.
@@
 
-The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager}, which controls the communications between MUSES client and MUSES server.
-In addition, there are two types of applications considered in this system.
-On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interact with it.
-This application must be implemented using the MUSES API (Application Program Interface).
-It should be noted that MUSES is an application that is running in the background, and third party apps can communicate with MUSES and ask for a response.
-Then, the MUSES API is not a normal API for building the third party application, but a collection of methods to allow this communication\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
-The main advantage of having MUSES Aware applications, is because actuator is able to actually forbid the users for doing something, if it implies a big risk for the company.
+The rest of the components shown in the figure are: the \textit{MUSES User Interface (UI)}, the application through which the user interacts with the system; and the \textit{Connection Manager} which controls the communications between MUSES client and MUSES server.
+In addition, there are two types of applications considered in this system: on the one hand the \textit{MUSES Aware App}, which is an application adapted to MUSES, so the system can directly interact with it (monitoring with the sensors and acting as a consequence of the decisions made by the system).
+This application must be implemented using the MUSES API (Application Program Interface)\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
+Some of the commented sensors require the interaction with MUSES Aware Apps, in order to request for information.
+For instance, the MAIL SENSOR could not detect or recognize the contents of an e-mail unless the mail application provides them (so this must be MUSES Aware).
 
-On the other hand, the \textit{Non MUSES Aware Apps} are those which MUSES cannot directly interact with.
-Usually, they can be accessed through the OS.
-But the type of information to gather from them and also the type of actions to do over them strongly vary depending on the OS.
-As was already mentioned, when MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user.
+On the other hand the \textit{Non MUSES Aware App} is that which MUSES cannot directly interact with.
+Usually it can be accessed through the OS.
+So the type of information to gather from them and also the type of actions to do over them vary depending on the OS.
+As was already mentioned, in cases MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user.
 This message informs about why the action is considered as risky and what the user can do to avoid it.
@@
 
-As in the client, we describe the three main components:
+As in the client, there are three main components:
 \begin{itemize}
-	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, values of the assets, 
-% Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "assets' values" o "values of the assets". Yo me inclino por la segunda.
-user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
+	 \item \textit{System Database}: it stores all the information that the system can manage, including authentication data, enterprise security policies, assets' values, user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
 
@@
 It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{deliverable21, deliverable52}.
-This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analysing them to look for an existing security rule that could be applied to the situation.
+This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analyse them to look for an existing security rule that could be applied to the situation.
 The engine discovers that by analysing the context events which are sent with the user action event, so that a complete model of the risks can be built.
 The output of this module is an `access request' which is sent to the \textit{RT2AE}.
-It considers the information included in the access request, as well as other information such as trust data and profiles, values of the assets,
-% Antonio - "values of the assets"
-user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}.
+It considers the information included in the access request, as well as other information such as trust data and profiles, assets' values, user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}.
 Finally, the RT2AE extracts the set of potential rules to consider in the analysed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.
@@
 These are later processed for tuning up the existing set of rules, or for inferring new ones.
-The MusKRS component, along with the MusCRTEP, are what represent the extension of the state of the art in security solutions for a BYOD environment.
+The KRS component, along with the CRTEP, are what represent the extension of the state of the art in security solutions for a BYOD environment.
 
@@
 
-There are some other components, which add extra functionalities to the system, namely:
-
-\begin{itemize}
-  \item A \textit{Security Policies/Risk Management} tool, that lets the company CSO to define and manage Security Policies and Rules in a friendly way.
-It also lets the management of risk-related information, useful for the RT2AE process, such as the values of the assets.
-% Antonio - "values of the assets"
-  \item  The \textit{Privacy Enhancing System}, which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
+There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company CSO to define and manage Security Policies and Rules in a friendly way.
+It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values.
+The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
 There are three important points with relation to this matter \cite{deliverable72}.
 First, the data that the user provides to the system (such as name, or email) is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks.
-Then, the location of the device is never sent and stored in the database, but as stated in the previous section, there are a number of defined `zones'.
+Then, the location of the device is never sent and stored in the database, but as was stated in the previous section, there are a number of defined `zones'.
 What is checked is that the user is inside one of those zones of interest.
@@
 In addition, the hard limit is provided by the law, in case that the employee leaves the company, or if there is a national law specifying a maximum data retention period.
-  \item \textit{User, Context, Event Data Receiver}, which is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
-Finally, there is another \textit{Connection Manager} which controls the communications with the device side.
+
+Then, the \textit{User, Context, Event Data Receiver} is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
+Finally, there is another \textit{Connection Manager} which controls the communication with the device side.
 %FERGU: no usar etc en artículos, mejor poner: (events, user-related LOQUESEA, among others)
 % Cambiado
-\end{itemize}
 
@@
 This refinement is meant as an improvement of the existing security rules, and its aim is to deal with new, possibly insecure, events.
-As a result, a set of optimisations and additions to the set of security rules are proposed to the CSO of the company.
+As a result, a set of optimisations and additions to the set of security rules are proposed to the Chief Security Officer (CSO) of the company.
 
-This procedure is composed by two main steps: first, a DM \cite{DataMining_Lee01} + ML \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of CI techniques.
-The refinement or adaptation of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms \cite{EAs_Back96}.
+This procedure is composed by two main steps: first, a Data Mining (DM) \cite{DataMining_Lee01} + Machine Learning (ML) \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of Computational Intelligence (CI) techniques.
+The refinement, or adaptation, of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms \cite{EAs_Back96}.
 
 Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface the CSO can interact with.
-Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
-The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.
+Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order that they can be accepted if they are interesting and useful.
+The system also uses the acceptance or rejection of new rules as `feedback`, learning from this decisions, and refining the rules according to this.
 
@@
 % Antonio - Lo que es no supervisado es la clasificación, pero si se está explicando de otra forma ya no tiene sentido decirlo.
-Moreover, a lot of attributes are extracted from the events, for obtaining the more information as possible. 
-% During the first trials, a ratio of _ events per day was observed.
-As this results in huge datasets, MUSES makes use of several Big Data processing methods \cite{BigData_11}, such as: %JUSTIFY (Paloma will do it)
+Moreover, a lot of attributes are extracted from the events, for obtaining the mor information as possible.
+This results in huge datasets, which is why MUSES applies Big Data processing methods \cite{BigData_11}.
+%JUSTIFY (Paloma will do it)
+
+The DM/ML methods that MUSES applies over the data are:
 
@@
 \item \textit{Pattern Mining} \cite{PatternMining_Han07}: 
-From the whole set of patterns which form the built dataset, the most frequent, as well as the uncommon, are obtained.
+From the whole set of patterns which form the built dataset, the most frequent ones, as well as the uncommon, are obtained.
 The idea is that infrequent patterns are potentially suspicious, and thus, could be of interest to be checked by the CSO, or to serve as a reference for the rule-refinement process.
@@
 Thus, this kind of classification method is able to manage unbalanced datasets, for instance, by considering a fitness function in which a cost is associated with the classifier accuracy at every iteration, having a penalty cost when the classifier makes a false negative.
-A false negative is an element from the minority class which is classified as belonging to the majority class \cite{cost_adjustment_07}.
+A false negative is an element from the minority class which is classified like as belonging to the majority class \cite{cost_adjustment_07}.
 With regard to the type of data, since GP algorithms can manage rule or tree based models, it works perfectly with any categorical feature, yielding a good classifier as it has been demonstrated in \cite{cost_adjustment_07}.
@@
 \item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
-The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, ``has this information been useful?''-type.
+The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can be also measured by pop-up messages, ``has this information been useful?''-type.
 All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
@@
 Therefore, the system gets a value of its performance in terms of, for instance, how many of the events that were not classified or misclassified, are covered now.
-As was also mentioned, the user or device trust values influence the creation of the rules.
+As was also mentioned, the user or device trust values have influence in the creation of the rules.
 Finally, the inferred rules are proposed to the CSO as ``new, but not yet refined'', along with their evaluated performance.
@@
 
-As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting values of the assets.
-% Antonio - "values of the assets"
+As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting assets' values.
 Both the inferred rules and the refined rules are presented to the CSO, who includes them or not in the system, and this acceptance or rejection acts itself as a feedback for future rule inference.
@@
 
-MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
- These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
-In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD.
+MUSES is mainly a free, open-source, platform independent solution, and that makes it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2).
+In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD.
 Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases.
@@
 
-Also related to this issue, a very big advantage of the MUSES system that is not present in the other solutions is its self-adaptivity power.
-The proposed system uses different methods to create new security rules, being their aim to cover new vulnerabilities or threats.
-Thus, MUSES is able to adapt to changes by applying classification techniques to create new rules, and then refining the whole set of existing policies.
-Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis plus a classifier trained with all the occurred events in the system.
+Also related to this issue, a very big plus of the MUSES system (not present in the other solutions) is its self-adaptivity power.
+Thus, MUSES is able to adapt to changes, either regarding corporate security policies, newly discovered vulnerabilities or threats, different environments of use, or user profiles.
 
-Moreover, another clear improvement over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours the real-time decision making process.
+Moreover, another clear advantage over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours a real-time decision making process.
 
@@
 First, as mentioned previously, it  implements a self-adaptive event correlation, including a novel hybrid technique of rule refinement and rule adjustment extracting relevant information from processing huge amounts of data.
-Then, the project defines a new approach to risk management taking into account threats, with their costs, as well as the innovative concept of opportunity \footnote{The following beneficial outcome from a situation on which, for instance, a user is able to work while waiting at the airport if the risk is low enough.}.
+Then, the project defines a new approach to risk management taking into account threats (with their costs) as well as the innovative concept of opportunity, i.e.
+the following beneficial outcome from a situation on which, for instance, a user is able to work while waiting at the airport if the risk is low enough.
 
-About HCI, in Section \ref{sec:preliminaryconcepts} we talked about how it has been demonstrated by Shaw et al.
-\cite{SecPolComp09} and Herath et al.
-\cite{SecPolPenalty09} that the compliance of the employees of a company, with respect to the security policies, increases by educating them and decreases by punishing them.
-Therefore, the fact that MUSES is focused in avoiding security incidents due to users' unawareness of the CSPs, it sets up a significant advance in the state of the art.
-This is because not only the incident is avoided, but the user is educated, which at the same time avoids future risky situations.
-With regard to device monitoring, MUSES  also take into account the so-called context observation, by which private or professional scenarios can be detected, or predicted, based on advanced machine learning techniques.
+About HCI and usability of mobile devices, this sets up a significant advance in the state of the art because of the novelty of the BYOD philosophy, and trying to look for individual differences among the users in susceptibility to persuasive strategies for secure behaviour.
+Regarding device monitoring, MUSES  also take into account the so-called context observation, by which private or professional scenarios can be detected, or predicted, based on advanced machine learning techniques.
 Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it  contributes to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.
@@
 
-As stated, MUSES has been recently tested in an actual company with satisfactory results according to the users' and to the evaluators of the trials.
-% Antonio - lo del trabajo futuro mejor decirlo al final.
-En la intro no se suele poner a no ser que quieras aclarar que este trabajo no va de esto.
-Pero eso suele verse como algo negativo.
-Los revisores te pueden decir que por qué no has hecho ese análisis si ya tienes los datos...
-However, the analysis of all data from these tests, and conclusions, will be addressed in future works.
-
-There is also room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.
+However, there is room for considering some of the existing researches that could be added as future features for MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}, which is another feature also considered in MUSES.
 The second prototype of the system will be also released, as well as the conclusions extracted after the analysis of data from the test of the first prototype.

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Correcciones, sugerencias y peticiones
@deantares @fergunet Echadle un ojo a los comentarios con la etiqueta
'Antonio', porfa

@@
 %\usepackage{textcomp}
-\usepackage{graphicx}
+\usepackage{array,booktabs,graphicx}
 \usepackage{color}
@@
  However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}.
-This product, formerly known as {\em MaaS360}) \footonote{\url{http://www.maas360.com/}}, is a MDM (Mobile Device Management) software to securize, monitor and manage mobile devices.
+This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is a MDM (Mobile Device Management) software to securize, monitor and manage mobile devices.
 It uses a web portal in order to centralize the security and control policies.
@@
 WSO2 Enterprise Mobility Manager (WSO2 EMM) \cite{WSO2_tool} is an open source platform that also works with the BYOD program. Some of this WSO2 EMM key features are:
-
-\begin{description}
-  \item[Mobile Device Management,] which is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
+% Antonio - cambio esto porque las negritas no se suelen usar apenas y para mantener la concordancia en formato con el resto de listas
+\begin{itemize}
+  \item \textit{Mobile Device Management}: Which is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
 It should be noted that this tool allows tracking every enrolled device, as well as obtaining reports and analytics of their use.
-  \item[Mobile Application Management:] With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
-  \item[Enterprise App Store:] This store provides users with both enterprise and public applications approved by the company.
-  \item[Mobile Data Security:] WSO2 also allows the user's data to be encrypted via password.
-\end{description}
+  \item \textit{Mobile Application Management}: With regard to the software, this platform is able to allow or deny the use of applications on enrolled devices based on the role of the user or policies, thus restricting the use of some apps to certain users.
+  \item \textit{Enterprise App Store}: This store provides users with both enterprise and public applications approved by the company.
+  \item \textit{Mobile Data Security}: WSO2 also allows the user's data to be encrypted via password.
+\end{itemize}
 
@@
 
-Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface the CSO can interact with.
+Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface he/she can interact with.
 Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
@@
 \item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
-The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, ``has this information been useful?''-type.
+The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''.
+% Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
 All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.
@@
 MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.
+Table \ref{tab:comparison} summarizes the features of the main analyzed tools, regarding these facts.
+% Antonio - Antares, ¿podrías incluir en la comparativa las otras herramientas que se han analizado? Las de Citrix, WSO2, Azzurri, Good...
+
+\begin{table}[ht]
+
+  \centering
+  \renewcommand{\arraystretch}{1.5}% Spread rows out...
+%  \resizebox{8cm}{!}{
+  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
+    \toprule
+      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
+    \midrule
+    MUSES & Open Source & IOS, Android, Windows Phone & Free  \\
+    IBM Mobile Security & Proprietary &  &  \\
+    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
+    Samsung Knox and Blackbery Balance & Proprietary & IOS, Android, Samsung Devices & 12\$ per year/device \\
+    Blackphone & Proprietary & Own device & 120\$ per year \\
+    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
+    \bottomrule
+  \end{tabular}
+%  }
+  \caption{Features of the analyzed products considering licenses, type of devices and price. \label{tab:comparison}}
+\end{table}
+% Antonio - Antares, ¿no había más tablas?
+% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
+% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?
 
@@
 
-In addition, a scientific comparison between the techniques used in the proposed system and those in the literature, in the same scope, has been done.
-It has been discussed that MUSES has the advantage of being multiplatform, while most of the reviewed tools are not.
-In addition, MUSES is able to adapt and evolve the security policies that a company has built, and not only apply them, as the other tools do.
-Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the effort of going beyond the state of the art in different fields of research.
+In addition, a comparison between the techniques used in the proposed system and those in the literature, in the same scope, has been done.
+It has been concluded that the biggest advantage of MUSES with respect to the rest is its ability to adapt and evolve the security policies (security rules) that a company has built, and not only apply them, as the other tools do.
+% Antonio - pongo primero la adaptabilidad del sistema porque es la característica más relevante y más 'científica'
+Moreover it has the advantage of being multiplatform, while most of the reviewed tools are not.
+Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the effort of going beyond the state of the art in different fields of research in corporate security, such as risk and trust analysis or event correlation.
 
@@
 (FP7-318508), along with Spanish National projects
-TIN2011-28627-C04-02
-(ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), and GENIL PYR-2014-17,
-awarded by the CEI-BioTIC UGR.
+TIN2011-28627-C04-02 (ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), along with GENIL PYR-2014-17, awarded by the CEI-BioTIC UGR.
 

### 2015-07-08 table_License_Devices_price.tex
Correcciones, sugerencias y peticiones
@deantares @fergunet Echadle un ojo a los comentarios con la etiqueta
'Antonio', porfa

@@
   \centering
-  \caption{License, Devices and plataform and prices}
   \renewcommand{\arraystretch}{1.5}% Spread rows out...
-  \resizebox{8cm}{!}{
+%  \resizebox{8cm}{!}{
   \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
@@
     MUSES & OpenSource &  & Free*  \\
-    IBM Mobile Security & Propietary &  &  \\
-    Sophos Mobile Control & Propietary & IOS, Android, Windows Phone  &  By Request\\
-    Samsung Knox and Blackbery Balance & Propietary & Android Samsung Devices and IOS & 12\$ per year/device \\
-    Blackphone & Propietary & Own device & 120\$ per year \\
-    Android for Work & Propietary & Android and devices with Chrome Browser &  12\$ per month/user\\
+    IBM Mobile Security & Proprietary &  &  \\
+    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
+    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
+    Blackphone & Proprietary & Own device & 120\$ per year \\
+    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
     \bottomrule
   \end{tabular}
-  }
+%  }
+  \caption{Features of the analyzed products considering licenses, type of devices and price.}
 \end{table}

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Please, use of 'they' is always preferable than 'he/she'

@@
 \begin{itemize}
-  \item \textit{Mobile Device Management}: Which is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
+  \item \textit{Mobile Device Management}: It is used to manage both user and corporate owned devices, providing support for Android and iOS at the moment.
 It should be noted that this tool allows tracking every enrolled device, as well as obtaining reports and analytics of their use.
@@
 
-Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface he/she can interact with.
+Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with.
 Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
@@
 \item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
-The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''.
+The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''-type.
 % Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
+% Paloma -  "forward slash" no significa guión. Un forward slash es un / que sí había muchos en el texto.
 All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
'-type' issue
Ok, 'they' instead of 'he/she'
But I think that here is not correct
Accepting @amorag changes and explaining about sigular they

@@
 Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with. 
+% Antonio - Si estamos hablando en tercera persona del singular se suele poner 'she' para referirnos a una persona de cualquier sexo, pero me gusta más poner 'he/she' para no discriminar.
+En todo caso intentaré poner 'they' en lugar de 'he/she', pero aquí, tal y como está redactado 'they' no queda bien por el verbo.
+% Antonio - No lo cambio porque no sé tu opinión, no es por dar trabajo extra.
+% A ver, este fenómeno gramático se llama "singular they", y se considera más correcto utilizarlo que poner "he/she". No es que me lo haya inventado yo :\
 Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
@@
 \item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
-The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''-type.
+The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''.
 % Antonio - quito el guión porque un revisor dice que se usan demasiados y que hacen el texto menos fluído y legible.
 % Paloma -  "forward slash" no significa guión. Un forward slash es un / que sí había muchos en el texto.
+% Antonio- Ok. En todo caso lo dejaría sin el '-type', pero como veas. Si lo quieres poner como estaba, el ', such as' lo añadí yo y lo mismo no queda bien así. 
+% Ok pues con el such as.
 All this information contributes to the inference of new rules or in adaptation, in order to deal with, for instance, users that repeatedly ignored warning messages.

### 2015-07-08 Response to reviewers - r2.tex
Sigo con las respuestas a los revisores
Mirad los comentarios, porfa.
Todos tenemos que ir metiendo cosas aquí porque cada uno sabe mejor que
nadie lo que ha escrito y la justificación.

--- 2015-07-06 Response to reviewers - r2.tex
@@
 
+% -----------------------------------------------------------------------------
+
 \section{Comments by Reviewer \#2}
 
-\begin{verbatim}
+% Antonio - Voy a sustituir el Verbatim por un cambio de color en las respuestas porque al compilarlo no hace los saltos de lÌnea si no se los especificas y el texto se sale del margen.
+
+%\begin{quotation}
 After reviewing the new version of the document, I admit the authors have  substantially changed section 3 (state of the art) and they have improved and extended the introduction and sections 4 (description of the system) and section 5 (comparison with other systems) I acknowledge the ideas are really interesting and exciting, but I'm still not sure if the authors are providing new results not published in their previous works or just rephrasing their text.
 
-Since there is an obvious over-the-top quality in their work and some good ideas, I'll let the editors decide if the contents are novel enough (compared to other previous works by the same authors) to be published in the journal.
+Since there is an obvious over-the-top quality in their work and some good ideas, I'll let the editors decide if the contents are novel enough (compared to other previous works by the same authors) to be published in the journal.\\
+%\end{quotation}
 
-\end{verbatim}
+\textcolor{blue}{We would like to thank the reviewer for his/her opinion and would lead him/her to have another look at the new version, since it has been highly improved. 
+As a summary:}
+%
+\textcolor{blue}{
+\begin{itemize}
+\item We have described in a more detailed way our previously published papers in this scope, clarifying the differences and contributions of this work with respect to them.
+\item Section 2 has been deeply improved adding a much more complete State of the Art in the scope of this work... 
+% Antonio - TODO: Fergu, completa esto t˙ que tienes la idea global de lo nuevo en el SotA, por favor.
+The reviewer can see the set of new references added by the end of this response letter.
+\item The description of MUSES system is now much better.
+Several points have been clarified and better explained in Section 4.
+Moreover, a prototype of the system has been tested in an actual company with success, according to the obtained results.
+This is also commented by the end of that section.
+% Antonio - TODO: Revisar que esto se haya dicho/hecho en el paper
+\item Section 3 has been rewritten in a big part, including a new taxonomy for the analyzed systems, along with a better comparison with MUSES in Section 5.
+% Antonio - TODO: extender esto de la secciÛn 3 y 5 un poco m·s.
+\item A complete proof-editing process has been done, revising the English grammar and rewriting several paragraphs for a better comprehension.
+\end{itemize}}
+% Antonio - TODO: AÒadir m·s cosas (medianamente relevantes) que se hayan hecho
+%
+\textcolor{blue}{These changes are better described in the responses to the others reviewers, so we encourage this reviewer to read them to have a better idea of their impact in the new version of the manuscript.}
+
+% -----------------------------------------------------------------------------
 
@@
 
-\begin{verbatim}
 This paper describes MUSES, an adaptable framework for enforcing security policies on mobile devices.
@@
 From my understandings, there is no a-priori enforcement except for the prediction based on event logs.
-This could mean that e security violation could in principle happen and only later recognized.
+This could mean that a security violation could in principle happen and only later recognized.
 This is not so suitable for a corporate environment with strict security requirements.
 This statement should be discussed and preferably discredited with experimental results.
+
+\textcolor{blue}{MUSES starts from a defined set of security rules that the CSO must define.
+Ideally, these rules should deal, in principle, all the potential security incidents that the company aims to detect.
+MUSES would be able to define new rules (by means of refinement) which could be labelled (i.e.
+assigned a decision) after the corresponding events have happened.
+However, it can also infer or create new rules, which the CSO must approve, using computational intelligence techniques.
+These rules could deal with expected situations (not previously happened).
+Anyway, the idea is to define a set of `restrictive' rules at the very beginning, able to ensure the system safety in a big amount of situations.
+Then, MUSES will refine or improve this set, making more specific and optimal rules.}
+
+\textcolor{blue}{Moreover, MUSES offers visual analysis tools to the CSOs, which can aid (or guide) they to detect suspicious or anomalous patterns, and to study how to avoid these patterns become malicious to the company.}
+
+\textcolor{blue}{In order to clarify this we have rewritten and completed the second paragraph in section 4.1 (page XX). It is now:}
+
+% Antonio - yo pienso que en este sistema cualquier violaciÛn de seguridad que se detecte se har· por medio de las reglas de seguridad.
+Eso serÌa lo ideal, pero para ello el CSO debe definir un conjunto que asegure la seguridad del sistema en la mayorÌa de casos.
+Luego el KRS podr· proponer nuevas reglas a travÈs de 'predicciones' (inferencias) o refinamiento, pero estas ˙ltimas se construir·n como reglas optimizadas para tratar con incidentes de seguridad ya detectados.
+No se pueden crear de la nada reglas para tratar con nuevos incidentes (desconocidos).
+
+\textcolor{blue}{\textit{The client is an important part of the a-priori risk treatment, because it both monitors the whole context, and finally acts or warns the user in event of a security violation.
+But security violations are mainly identified by security rules, which is why MUSES needs at least an initial set of rules, defined by the CSO.
+Then, it makes use of DM and CI techniques to improve or optimise them, enhancing the coverage.
+That is to say, the more sensors are implemented, the more information related to event context can be extracted.
+Implementing a sensor means to include a programmed method which triggers MUSES to start `listening' to some parts of a device.
+Then, the initial security rules establish which situations might cause a security violation, and the sensors provide with information which helps the MUSES server to identify events that are alike to the ones that are already known as dangerous.}}
+
+% Antonio - TODO: aclarar lo otro que comento en la respuesta (la idea de empezar con reglas restrictivas e irlas refinando) en el texto.
+
 2.
@@
 Also in this respect, experimental results are needed.
+
 3.
@@
 Authors should deeply discuss this aspect.
+
 4.
@@
 I suggest authors to deeply revise the presentation of their work.
-\end{verbatim}
 
@@
 
-\end{verbatim}
+% -----------------------------------------------------------------------------
 
@@
 The suggestion in this regard is to consider rewriting this part, including updated references and current tools in comparison.
+\end{verbatim}
 
+This section has been rewrited, and the references mentioned by the referee (including new products) have been added. %FERGU: PONED ESTO M√ÅS BONICO!
+
+\begin{verbatim}
 In section 3.3 (p.7, sentence in l.18-19) there is provided a statement about success of two solutions, however without referencing relevant sources or providing details.
@@
 Section 3.6.4 (p10, 44) states "are Worx-enable are capable". The meaning of this part is not clear, nor to which concept Worx refers.
+\end{verbatim}
 
@@
  1) Explain why particular solutions are chosen for inclusion in review and what is their relevance? Did authors consider other (possible) solutions relying on DM and CI?
+
  2) Considering variety of BYOD tools and their different features, authors might consider to introduce or reuse a taxonomy or classification of those approaches, and state the place of MUSES there (or define a new subcategory, if deemed necessary)
+
+\textcolor{blue}{Following the reviewer's suggestion we have introduced a taxonomy for the analyzed systems, according to the works that we have revised in the state of the art section.
+This taxonomy is described at the beginning of Section 3 (second paragraph, Page XX).}
+% Antonio - completar con el n˙mero de p·gina final
+% Antonio - TODO: decir si MUSES y el resto de sistemas se han encuadrado dentro de esa taxonomÌa
+
  3) Some presented solutions miss their relationship to MUSES (coverage, features, comparison).
 This point also refers to inconsistent coverage amongst solutions and weak arguments favouring MUSES.
-Either coverage should be more consisent by focusing on common (present or missing) aspects, or it should be elaborated why such coverage is missing.
-Also see the comment for dicussion part bellow.
+Either coverage should be more consistent by focusing on common (present or missing) aspects, or it should be elaborated why such coverage is missing.
+Also see the comment for discussion part bellow.
 
@@
 The authors however do not provide additional details on how is this achieved in the practice and are there any limitations in regards to that.
-How they managed to provide the same sistem for Androd, Windows, iOS, PCs, without limitations?
+How they managed to provide the same system for Android, Windows, iOS, PCs, without limitations?
 How MUSES manage the variety of OS versions and underlying platform features provided to the app?
@@
 
+% Antonio - TODO
+
 On p.17, l.7-9 authors state that the data sets can be huge, leading to necessity to apply Big Data processing methods.
@@
 Is it really necessary to employ Big Data processing?
+
+% Antonio - TODO: Incluir justificaciÛn de Big Data Processing considerando el n˙mero de eventos generados en las Trials y extrapol·ndolo a muchos meses (al menos los 6 del hard limit).
 
@@
 
->From the presented concepts behind MUSES and its flows, it is not completely clear how it approaches "newly discovered vulnerabilities or threats" (p.20 l.27-28).
+% Antonio - no sÈ a quÈ 'bullets' se refiere
+
+From the presented concepts behind MUSES and its flows, it is not completely clear how it approaches "newly discovered vulnerabilities or threats" (p.20 l.27-28).
 It is hence suggested to clarify this statement and provide explanation to which extent is rule refinement and adaptation used to discover and address new vulnerabilities and threats in the software and systems.
@@
 For the section 5 and discussion, this reviewer would suggest to consider providing overview in the form of table(s) or figure, comparing different aspects of MUSES and other tools and providing hints/references to further details in this or other works.
-As there are many features of MUSES and other tools, employed approaches and techniques, different coverages and limitations, such overview could countribute to clarity and position of the proposed solution.
+As there are many features of MUSES and other tools, employed approaches and techniques, different coverages and limitations, such overview could contribute to clarity and position of the proposed solution.
+
+\textcolor{blue}{We agree with the reviewer.
+A comparative table has been included in the section 5 (Table 1 - Page XX), summarizing some of the features of the presented systems and those of MUSES system.}
+
+% Antonio - TODO: M·s Tablas comparativas. øAntares, puedes hacerlas?
+% Antonio - øquiz· una tabla con lo de la taxonomÌa y en quÈ categorÌa entra cada sistema?
 
@@
 It is however suggested to consider revising this work and take into account provided suggestions.
+
+\textcolor{blue}{We have addressed all the suggestions by the reviewer so we hope the work has been improved enough.}
 
@@
 
+\textcolor{blue}{The reviewer is right. We have fixed this in the text omitting their use in those cases.}
+
 2) Authors overuse parentheses to explain details.
@@
 
+\textcolor{blue}{Following reviewer's suggestion we have rewritten the majority of the phrases where parentheses were used, avoiding them for the sake of a better text flow and reading.}
+
 3) The structure and flow of the work can be improved.
-\end{verbatim}
 
-%FERGU: Añado las nuevas referencias a partir del fichero bibtex, poned las vuestras!
+\textcolor{blue}{We have rewritten several parts of the paper and included new sections, subsections, tables and lists in order to improve the structure, contents and fluency of the text.}
+% Antonio - Por favor, completad esta justificaciÛn mejor.
+
+\textcolor{blue}{We think that the work has been highly improved following the reviewer's suggestions, and would like to thank you for your careful revision and useful comments.}
+
+%FERGU: A√±ado las nuevas referencias a partir del fichero bibtex, poned las vuestras!
+\bibliographystyle{elsarticle-num}
 \bibliography{review_muses}

### 2015-07-08 Response to reviewers - r2.tex
Más respuestas a los revisores
Y un par de párrafos en el artículo para las respuestas

@@
 However, it can also infer or create new rules, which the CSO must approve, using computational intelligence techniques.
-These rules could deal with expected situations (not previously happened).
+These rules could deal with unexpected situations (not previously happened).
 Anyway, the idea is to define a set of `restrictive' rules at the very beginning, able to ensure the system safety in a big amount of situations.
@@
 \textcolor{blue}{In order to clarify this we have rewritten and completed the second paragraph in section 4.1 (page XX). It is now:}
-
-% Antonio - yo pienso que en este sistema cualquier violaciÛn de seguridad que se detecte se har· por medio de las reglas de seguridad.
-Eso serÌa lo ideal, pero para ello el CSO debe definir un conjunto que asegure la seguridad del sistema en la mayorÌa de casos.
-Luego el KRS podr· proponer nuevas reglas a travÈs de 'predicciones' (inferencias) o refinamiento, pero estas ˙ltimas se construir·n como reglas optimizadas para tratar con incidentes de seguridad ya detectados.
-No se pueden crear de la nada reglas para tratar con nuevos incidentes (desconocidos).
 
@@
 
-% Antonio - TODO: aclarar lo otro que comento en la respuesta (la idea de empezar con reglas restrictivas e irlas refinando) en el texto.
+We have also improved this clarification in section 5 (page XX), adding the text:
+
+\textcolor{blue}{\textit{However, MUSES presents a limitation regarding the enhance of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
+The philosophy is that the initial set of rules, defined by the CSO, should be very restrictive regarding possible unexpected users' behaviours or events, in order to avoid as much security incidents as possible.
+As the system works, MUSES would be able to define new rules (through refinement) which could get an associated decision after the corresponding events have happened.
+Thus, this will lead to get eventually an optimal set of security rules.}}
+
+\textcolor{blue}{\textit{In addition, MUSES can also infer or create new rules using computational intelligence techniques.
+These rules could deal with unexpected situations (not previously happened), but must be previously approved by the CSO.
+Of course, everything is constrained by the available set of sensors which, in turn, define the possible information that MUSES will analyze and use in the refinement and inference processes.}}
 
@@
 
+\textcolor{blue}{TODO}
+
 3.
@@
 Authors should deeply discuss this aspect.
+
+\textcolor{blue}{TODO}
 
@@
 
-\begin{verbatim}
+\textcolor{blue}{TODO}
+
 5.      A discussion on research activities on BYOD is completely missing. This is unacceptable for a solution that aims at solving BYOD security issues. Just to cite a few:
@@
 c.      Armando, Alessandro, et al. "Enabling BYOD through secure meta-market." Proceedings of the 2014 ACM conference on Security and privacy in wireless & mobile networks. ACM, 2014.
-\end{verbatim}
 
-Reviewer is right.
+\textcolor{blue}{The reviewer is right.
 Although several works have been cited in other sections of the work, a proper discussion on research on BYOD was necessary.
-Therefore, we have analysed the 3 papers suggested by the reviewer, together with several new relevant ones.
-These new references also have been used along other sections of the work to justify MUSES features (for example, the set of best practices used) and to propose the new taxonomy, taking into account the works described in the new section.
-The new references added \cite{Garba15organisational,Scarfo12survey,Gessner13userfriendly,Armando14metamarket,Haejung12Door,Samaras13SaaS,Miller12Privacy,Romer14BestPractices} can be found at the end of this document.
+Therefore, we have analysed the papers suggested by the reviewer, along with several new relevant ones.
+These new references also have been also cited in other sections of the work to justify MUSES features; for example, the set of best practices for BYOD security proposed by H.
+Romer.
+These works have been also considered to propose the new taxonomy included in the paper (Section X, Page XX).
+These references are \cite{Garba15organisational,Scarfo12survey,Gessner13userfriendly,Armando14metamarket,Haejung12Door,Samaras13SaaS,Miller12Privacy,Romer14BestPractices}, and can be found at the end of this document.}
 
-\begin{verbatim}
 6.
@@
 Are there any limitations?
+
+\textcolor{blue}{TODO}
+
 Under such considerations I recommend authors for a *STRONG* major revision to cover the aforementioned points.
-\end{verbatim}
+
+\textcolor{blue}{The authors think that the work has been highly improved following the reviewer's suggestions. We would like to thank he/she for his/her careful revision and interesting comments.}
 
@@
 
-\begin{verbatim}
 In this work authors present state-of-the art in BYOD solutions, and introduce a new solution, MUSES, a result of an EU FP7 project.
@@
 in the market with the purpose to adapt to it in a secure way.
-\end{verbatim}
 
-The abstract has been changed and that confusing sentence has been
-eliminated. Now we think it is clear, as intended, the intention,
-context and focus of
-the paper.
+\textcolor{blue}{The abstract has been changed and that confusing sentence has been eliminated. Now we think it is clear, as intended, the motivation, context and focus of the paper.}
 
-\begin{verbatim}
 The description of IBM products, in section 3.1, does not provide clear distinction between various service types provided by IBM.
@@
 The suggestion in this regard is to consider rewriting this part, including updated references and current tools in comparison.
-\end{verbatim}
 
-This section has been rewrited, and the references mentioned by the referee (including new products) have been added. %FERGU: PONED ESTO M√ÅS BONICO!
+\textcolor{blue}{Following reviewer's suggestions, this section has been rewritten, and the references mentioned by the referee (including new products) have been considered in the study.
+The tools have been described (by the end of Section 3.1, in page XX), and compared with MUSES in Section 5.}
+%FERGU: PONED ESTO M√ÅS BONICO!
+% Antonio - ahora est· un poco mejor, pero no sÈ si m·s bonico.
+Fergu debes justificar el por quÈ se han puesto los tres servicios de IBM, ya que el revisor dice que algunos no est·n relacionados con el tema del trabajo...
+t˙ que sabes de esto de IBM.
+;D
+% Fergu, tambiÈn falta la comparativa con MUSES de esas herramientas (SecciÛn 5)...
 
-\begin{verbatim}
 In section 3.3 (p.7, sentence in l.18-19) there is provided a statement about success of two solutions, however without referencing relevant sources or providing details.
 It is furthermore questionable whether this statement is relevant for the scope of this work at all.
+
+\textcolor{blue}{TODO}
 
@@
 
+\textcolor{blue}{TODO}
+
 Section 3.6.4 (p10, 44) states "are Worx-enable are capable". The meaning of this part is not clear, nor to which concept Worx refers.
-\end{verbatim}
+
+\textcolor{blue}{TODO}
 
 Basically, in section 3 the following possibilities for improvement are identified:
+
  1) Explain why particular solutions are chosen for inclusion in review and what is their relevance? Did authors consider other (possible) solutions relying on DM and CI?
+
+\textcolor{blue}{TODO}
 
@@
 \textcolor{blue}{Following the reviewer's suggestion we have introduced a taxonomy for the analyzed systems, according to the works that we have revised in the state of the art section.
-This taxonomy is described at the beginning of Section 3 (second paragraph, Page XX).}
+This taxonomy is described at the beginning of Section 3 (second paragraph, page XX).}
 % Antonio - completar con el n˙mero de p·gina final
@@
 
+\textcolor{blue}{TODO - justificar que todos los sistemas no tienen las mismas propiedades, pero sÌ la misma filosofÌa}
+
 On p.12, l.9-12 authors state that MUSES can be installed in every mobile or portable device, independently of the operating system and device type.
@@
 This feature is important differentiator against some other solutions and in opinion of this reviewer should be elaborated in more detail.
+
+\textcolor{blue}{TODO - describir las limitaciones de MUSES en cada sistema}
 
@@
 
+\textcolor{blue}{TODO}
+
 On p.14, l.16-28 authors introduce the concepts of MUSES Aware App and MUSES API.
@@
 
-% Antonio - TODO
+\textcolor{blue}{TODO}
 
@@
 
-% Antonio - TODO: Incluir justificaciÛn de Big Data Processing considerando el n˙mero de eventos generados en las Trials y extrapol·ndolo a muchos meses (al menos los 6 del hard limit).
+\textcolor{blue}{TODO - Incluir justificaciÛn de Big Data Processing considerando el n˙mero de eventos generados en las Trials y extrapol·ndolo a muchos meses (al menos los 6 del hard limit)}.
 
@@
 
-% Antonio - no sÈ a quÈ 'bullets' se refiere
+\textcolor{blue}{TODO - no sÈ a quÈ 'bullets' se refiere}
 
@@
 
+\textcolor{blue}{TODO}
+
 Similar applies to human-computer interaction (p.20 l.34).
 Although some details are provided in l.43-45 on the same page, in opinion of this reviewer, the statement about progress beyond the state of the art should be backed with more (stronger) details and data.
+
+\textcolor{blue}{TODO}
 
@@
 What happens, and at which extent can some rooted device affect local application of the system, and also central server and other clients?
+
+\textcolor{blue}{TODO}
 
@@
 
-\textcolor{blue}{We think that the work has been highly improved following the reviewer's suggestions, and would like to thank you for your careful revision and useful comments.}
+\textcolor{blue}{We are very grateful to the reviewer for his/her useful comments and hope he/she will be satisfied with the revised work.}
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Sigo con las respuestas a los revisores
Mirad los comentarios, porfa.
Todos tenemos que ir metiendo cosas aquí porque cada uno sabe mejor que
nadie lo que ha escrito y la justificación.
Comment for @fergunet
Más respuestas a los revisores
Y un par de párrafos en el artículo para las respuestas

@@
 \address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
-%\author{A. M. Mora}
-%\ead{amorag@geneura.ugr.es}
-%\address{Departamento de Arquitectura y Tecnología de Computadores. Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación. CITIC. University of Granada, Spain}
 
@@
 For example, using some kind of DM technique, such as classification methods, or merely the system administrator experience, can be used to generate rules before the deployment of the tool (offline) to detect threats in runtime.
-However, new rules can not be added.
+However, new rules cannot be added.
 On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system, follows an online scheme.
@@
 A system can be considered {\em invasive} if a user needs to use the tool to perform their job.
+% (Paloma) Fergu, te parece bien cambiar esta frase a "A system can be considered {\em invasive} if a user must use a certain tool to perform their job." ?
+Porque con el "the tool" no me queda muy claro.
 For example, opening a specific browser provided by the tool, instead of the original device browser, such as Chrome of Safari.
@@
 %FERGU: HABLANDO DE LOS PRODUCTOS
+% Antonio - Fergu, introduce esto, no lo pongas así a pelo. ;D
 {\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing.
@@
 This allows the deployment of applications or backups, among other possibilities.
+
 %----------------------------------------------------------------------------
@@
 The main feature of KNOX is the use of different containers, or environments, for business and personal sides.
-Each one includes its own graphical configuration, suche as wallpapers, or colour themes, in order to be more easily recognised and distinguished by the user.
+Each one includes its own graphical configuration, such as wallpapers, or colour themes, in order to be more easily recognised and distinguished by the user.
 A password is required in order to enter into the business side and, once \textit{logged in} to this container, no more passwords are needed for the business applications.
@@
 % A ver, este fenómeno gramático se llama "singular they", y se considera más correcto utilizarlo que poner "he/she". No es que me lo haya inventado yo :\
+% Antonio - Ok, entendido. Es que nunca lo habia visto.
 Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
@@
 
+However, MUSES presents a limitation regarding the enhance of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
+The philosophy is that the initial set of rules, defined by the CSO, should be very restrictive regarding possible unexpected users' behaviours or events, in order to avoid as much security incidents as possible.
+As the system works, MUSES would be able to define new rules (through refinement) which could get an associated decision after the corresponding events have happened.
+Thus, this will lead to get eventually an optimal set of security rules.
+
+In addition, MUSES can also infer or create new rules using computational intelligence techniques.
+These rules could deal with unexpected situations (not previously happened), but must be previously approved by the CSO.
+Of course, everything is constrained by the available set of sensors which, in turn, define the possible information that MUSES will analyze and use in the refinement and inference processes.
+
 Moreover, another clear improvement over the rest is that MUSES can work in both online and offline modes, depending on the client being able to connect with the server or not, which favours the real-time decision making process.
@@
 However, there are some examples that could be used as model for our approach, such as \cite{EAs_securitycosts-kirta,risk_reduction_ga_12}.
+
+% Antonio - Fergu, falta por comparar las soluciones de IBM con MUSES (Mobile First y Maas360). Lo pide el revisor... :_(
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Fixing IBM section. References #30. References #31. Please @fergunet review and close corresponding issue

--- 2015-07-08 MUSES_vs_BYOD_solutions.tex
@@
 
-Main services offered by IBM can be divided into three categories:
-
-\begin{itemize} 
-	\item \textit{Mobile Enterprise Services}: Is offered as an integrated solution for smartphones, and tablets as well, but then it is divided in different subservices that the company has to acquire separately.
-Some of them are related to cloud computing, such as events and log management as a cloud security service, cloud backup, or the so-called `hosted vulnerability management'.
-The last one is specially interesting for the scope of this paper, given the fact that it seems to implement one of the most important advantages of the MUSES system, the self-adaptation.
+Main services offered by IBM can be divided into three categories: Mobile Enterprise Services, Hosted Mobile Device Security Management, and Enterprise Wireless Networks.
+However, here we only discuss the former, because it is the only one related to BYOD.
+Mobile Enterprise Services is offered as an integrated solution for smartphones and tablets as well, but then it is divided in different subservices that the company has to acquire separately.
+Some of them are related, to cloud computing.
+Among them, there is one which is interesting for the scope of this paper, the so-called `hosted vulnerability management'.
+This subservice seems to implement one of the most important advantages of the MUSES system, the self-adaptation.
 IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure.
-They claim in their website that they are able to recognise new vulnerabilities - or threats - with enough accuracy.
+They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognise new vulnerabilities - or threats - with enough accuracy.
 The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts.
@@
 Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
-	\item \textit{Hosted Mobile Device Security Management}: This is a particular service of the Mobile Enterprise Services.
-It includes itself a number of subservices, going from tools to make easy to develop secure mobile apps, to an interface for managing the devices in the system, checking their configuration security level.
-As in the previous case, they are offered by IBM as `services', but these are included as default features in the MUSES system.
-	\item \textit{Enterprise Wireless Networks}: Devoted to provide secure channels for communications.
-This is related to ensuring employees that any connection they might perform to access company assets, is properly secured, at the time it delivers the expected performance.
-Thus, this service is, in some sense, adaptive to the situation, yet only in terms of a secure connection and not evolving the security policies, like MUSES.
-\end{itemize}
 
 %FERGU: HABLANDO DE LOS PRODUCTOS
+IBM also offers some products related to BYOD security.
 {\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing.
@@
  However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}.
-This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is a MDM (Mobile Device Management) software to securize, monitor and manage mobile devices.
-It uses a web portal in order to centralize the security and control policies.
+This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is an MDM (Mobile Device Management) software to secure, monitor, and manage mobile devices.
+It uses a web portal in order to centralise the security and control policies.
 This allows the deployment of applications or backups, among other possibilities.
+However, MobileFirst Protect seems a typical MDM tool, which just applies the existing set of security policies.
+No further risk and trust analysis is performed, neither is included a refinement of the rules derived from the policies.
 %----------------------------------------------------------------------------
@@
 
-Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they are not being successful in spite of their features.
+Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they found problems in the market in spite of their features.
 On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.

### 2015-07-08 MUSES_vs_BYOD_solutions.tex

@@
 No further risk and trust analysis is performed, neither is included a refinement of the rules derived from the policies.
+
 %----------------------------------------------------------------------------

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Pasado comprobador ortográfico
Corregido spelling británico (s) a americano (z) y añadido guión en multi-platform (que se menciona muchas veces). No he llegado a hacer ningún otro tipo de revisión. refs #7

@@
 solutions along with a novel, adaptive and open source system named
-MUSES (Multiplatform Usable Endpoint Security), able 
+MUSES (Multi-platform Usable Endpoint Security), able 
 to securely manage BYOD environments. % <- Solution
@@
 \begin{keyword}
-Corporate mobile security \sep End-to-end security solutions \sep User-centric systems \sep Self-adaptation \sep Multiplatform \sep Security Policies \sep Data security and data privacy \sep BYOD
+Corporate mobile security \sep End-to-end security solutions \sep User-centric systems \sep Self-adaptation \sep Multi-platform \sep Security Policies \sep Data security and data privacy \sep BYOD
 \end{keyword}
@@
 Data security and privacy are key factors for a company, and thus, in
-order to protect them, it is usual that the Chief Security Officer (CSO) of a company defines a set of Organisational Security
+order to protect them, it is usual that the Chief Security Officer (CSO) of a company defines a set of Organizational Security
 Policies \cite{Opp_Security11}.
@@
 This work introduces a recently released system named
-MUSES, from Multiplatform Usable Endpoint Security, which is being developed within an European Project\footnote{\url{http://musesproject.eu/}} of the same name. MUSES is a
+MUSES, from Multi-platform Usable Endpoint Security, which is being developed within an European Project\footnote{\url{http://musesproject.eu/}} of the same name. MUSES is a
 dev\-ice\--in\-de\-pen\-dent end-to-end user-centric tool, based on a
@@
 The main solutions or tools are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
-Section \ref{sec:muses} presents the Multiplatform Usable Endpoint Security System, with its architecture and the soft computing techniques it makes uses of.
+Section \ref{sec:muses} presents the Multi-platform Usable Endpoint Security System, with its architecture and the soft computing techniques it makes uses of.
 Advantages and benefits of the proposed system are compared to other solutions found in bibliography in Section \ref{sec:comparison}.
@@
 A needed security policy, or in this case, an ISP should deal with the way of protecting a certain organization's information against a security breach.
-Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community or organisation that they are built for.
+Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community or organization that they are built for.
 In this sense, MUSES stands up for a self-adaptation of company security policies.
@@
 
-This situation leads to a need of protecting the organisation's side, but also the users' side, making non-interfering easy-to-follow ISPs, and leaving them to use their devices for personal purposes while working, without putting organisation's information assets under risk.
+This situation leads to a need of protecting the organization's side, but also the users' side, making non-interfering easy-to-follow ISPs, and leaving them to use their devices for personal purposes while working, without putting organization's information assets under risk.
 The compliance of these requirements would compose an End-to-End Security Solution (protecting both enterprise and employee), which is the motivation of the commented tools and, as presented in Section \ref{sec:muses}, is the aim of the MUSES project.
@@
 Samaras \cite{Samaras13SaaS} proposes a methodology design of a security architecture taking into account their logical design, logical architecture, security mechanisms and physical architecture.
-First, the business processes are studied and legal and security requirements are analysed.
+First, the business processes are studied and legal and security requirements are analyzed.
 After applying several controls the architecture is validated using different criteria: Correctness, Completeness, Usability and Flexibility.
@@
 This container is able to execute inside it the enterprise applications, acting as a barrier with the rest of the applications, and allowing direct communication with the enterprise VPN.
-The combination of this method, along cryptographic protocols and time-based sessions, offers a tradeoff between security and usability.
+The combination of this method, along cryptographic protocols and time-based sessions, offers a trade-off between security and usability.
 Also, this method avoids the modification of the underlying kernel of the device.
@@
 Other works propose the analysis of the applications before being installed.
-For example, in \cite{Armando14metamarket} a meta-market application is used to supervise the installation of new applications, using static analysis and code instrumentation techniques, taking into account the organisational security policies.
+For example, in \cite{Armando14metamarket} a meta-market application is used to supervise the installation of new applications, using static analysis and code instrumentation techniques, taking into account the organizational security policies.
 A meta-market prototype is tested with Google Play market using a real world BYOD security policy \footnote{The US Government BYOD security guidelines}.
@@
 On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable data source for dynamic adaptation mechanisms.
-However, it is not mandatory for an online threat detection method to use an updatable database, as current data may be analysed and deleted once a new rule is created.
+However, it is not mandatory for an online threat detection method to use an updatable database, as current data may be analyzed and deleted once a new rule is created.
 \item {\em Based in an external service or standalone}: A standalone tool do not require a external service to be used.
@@
 Instead, a {\em non-invasive} data access is transparent to the user.
-An example is a log analyser daemon that updates other program configurations or sends information to the company server.
+An example is a log analyzer daemon that updates other program configurations or sends information to the company server.
 \item {\em Superuser or non-superuser system control}.
@@
 However, here we only discuss the former, because it is the only one related to BYOD.
-Mobile Enterprise Services is offered as an integrated solution for smartphones and tablets as well, but then it is divided in different subservices that the company has to acquire separately.
+Mobile Enterprise Services is offered as an integrated solution for smartphones and tablets as well, but then it is divided in different sub-services that the company has to acquire separately.
 Some of them are related, to cloud computing.
 Among them, there is one which is interesting for the scope of this paper, the so-called `hosted vulnerability management'.
-This subservice seems to implement one of the most important advantages of the MUSES system, the self-adaptation.
+This sub-service seems to implement one of the most important advantages of the MUSES system, the self-adaptation.
 IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure.
-They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognise new vulnerabilities - or threats - with enough accuracy.
+They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognize new vulnerabilities - or threats - with enough accuracy.
 The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts.
@@
 This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is an MDM (Mobile Device Management) software to secure, monitor, and manage mobile devices.
-It uses a web portal in order to centralise the security and control policies.
+It uses a web portal in order to centralize the security and control policies.
 This allows the deployment of applications or backups, among other possibilities.
@@
 The main feature of KNOX is the use of different containers, or environments, for business and personal sides.
-Each one includes its own graphical configuration, such as wallpapers, or colour themes, in order to be more easily recognised and distinguished by the user.
+Each one includes its own graphical configuration, such as wallpapers, or colour themes, in order to be more easily recognized and distinguished by the user.
 A password is required in order to enter into the business side and, once \textit{logged in} to this container, no more passwords are needed for the business applications.
@@
 
-Even though it does not analyse the system information for security rules evolution purposes, it offers policy management.
+Even though it does not analyze the system information for security rules evolution purposes, it offers policy management.
 Thus, the system will provide a framework for IT staff to manage business devices, but also, and more importantly, personal devices being used in a BYOD context (The CSO would give the employee an activation code in order to `connect' the smartphone to the enterprise and use this Android Work).
@@
 Their solution has been developed for the main OSs: iOS, Android, Windows phone, and also desktop computers with Windows.
-A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, documents, calendar), the intranet, and both in-house or third-party mobile applications.
+A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorized devices, or for providing access to secure collaboration solutions (email, documents, calendar), the intranet, and both in-house or third-party mobile applications.
 Finally, Good offers best practise recommendations to help the company developing BYOD policies.
@@
 
-\section{Multiplatform Usable Endpoint Security System}
+\section{Multi-platform Usable Endpoint Security System}
 \label{sec:muses}
@@
 These methods include DM \cite{DataMining_Lee01} and ML \cite{MachineLearning_Bishop06} techniques, which have been proved to be computationally expensive \cite{Cios07DataMining}.
-This server is also devoted to centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques can be applied.
+This server is also devoted to centralize the data gathering from all the devices in the company, composing a big database to which the commented techniques can be applied.
 
@@
 But security violations are mainly identified by security rules, which is why MUSES needs at least an initial set of rules, defined by the CSO.
-Then, it makes use of DM and CI techniques to improve or optimise them, enhancing the coverage.
+Then, it makes use of DM and CI techniques to improve or optimize them, enhancing the coverage.
 That is to say, the more sensors are implemented, the more information related to event context can be extracted.
@@
   \item[App sensor:] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
-Additionally, this sensor gathers information abaut the applicationes which the user tries to install or uninstall.
+Additionally, this sensor gathers information about the applications which the user tries to install or uninstall.
 \end{description}
@@
 It includes an \textit{Event Processor}, the module in charge of performing the event correlation process \cite{deliverable21, deliverable52}.
-This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analysing them to look for an existing security rule that could be applied to the situation.
-The engine discovers that by analysing the context events which are sent with the user action event, so that a complete model of the risks can be built.
+This is done by a so-called `Event correlation engine', which is in charge of taking the user action events that are sent from the device client, and analyzing them to look for an existing security rule that could be applied to the situation.
+The engine discovers that by analyzing the context events which are sent with the user action event, so that a complete model of the risks can be built.
 The output of this module is an `access request' which is sent to the \textit{RT2AE}.
@@
 user reputation, or opportunity, to perform a risk and trust analysis task \cite{RT2AE_SOTICS13}.
-Finally, the RT2AE extracts the set of potential rules to consider in the analysed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.
+Finally, the RT2AE extracts the set of potential rules to consider in the analyzed situation, and these rules are therefore transformed into decisions (or Device Policies) and submitted to those devices to which they apply.
 
-	 \item \textit{Knowledge Refinement System (MusKRS)}: this module is in charge of analysing the information stored in the system database by means of Data Mining techniques, identifying relevant data, such as important patterns, key features, or security incidents.
+	 \item \textit{Knowledge Refinement System (MusKRS)}: this module is in charge of analyzing the information stored in the system database by means of Data Mining techniques, identifying relevant data, such as important patterns, key features, or security incidents.
 These are later processed for tuning up the existing set of rules, or for inferring new ones.
@@
 The self-adaptation, to the user and context, of the set of Corporate Security Rules is one of the main features of the MUSES system.
-To this end, the \textit{MusKRS} module is in charge of analysing all the gathered events, context, and user-related data.
+To this end, the \textit{MusKRS} module is in charge of analyzing all the gathered events, context, and user-related data.
 Then it processes the data and adapts or refines the security rules.
 This refinement is meant as an improvement of the existing security rules, and its aim is to deal with new, possibly insecure, events.
-As a result, a set of optimisations and additions to the set of security rules are proposed to the CSO of the company.
+As a result, a set of optimizations and additions to the set of security rules are proposed to the CSO of the company.
 
 This procedure is composed by two main steps: first, a DM \cite{DataMining_Lee01} + ML \cite{MachineLearning_Bishop06} process is performed in the \textit{Data Miner} sub-component; second, a refinement and inference process is done in the \textit{Knowledge Compiler} sub-component, using the data that was extracted in the first step, and by means of CI techniques.
-The refinement or adaptation of the security rules can be made through techniques as simpler as generalisation or specialisation of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms \cite{EAs_Back96}.
+The refinement or adaptation of the security rules can be made through techniques as simpler as generalization or specialization of rules, for instance, or by more complex CI methods such as Evolutionary Algorithms \cite{EAs_Back96}.
 
@@
 The following sections describe these processes: first, focusing on DM techniques to be used both automatically by the MusKRS, and by the mentioned graphic interface for showing useful information to the CSO; second, used CI techniques are explained, mainly focusing in Evolutionary Computation (EC) \cite{EAs_Back96} approaches.
-EC methods have demonstrated to have a good performance, and have been widely used in security-based environments for solving security issues, such as intrusion detection \cite{GA_intrusion-majeed}, design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or for the optimisation of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.
+EC methods have demonstrated to have a good performance, and have been widely used in security-based environments for solving security issues, such as intrusion detection \cite{GA_intrusion-majeed}, design and evaluation of security protocols \cite{GP_intrusion-lu,GA_networksecurity-zarza}, or for the optimization of different aspects related with security: IT security costs \cite{EAs_securitycosts-kirta}, and cryptographic protocols \cite{GA_cryptographicprotocols-zarza2}, among others.
 
@@
 The aim of this method is grouping the patterns considering some similarity criteria, in order to manage them as a set.
-This is used for providing data visualisation mechanisms through a graphical interface.
+This is used for providing data visualization mechanisms through a graphical interface.
 This would make easier to interpret data interaction and the distribution in clusters with respect to the different attributes, or features, of the patterns.
@@
 \item \textit{Data Analysis}: 
-This provides the CSO with mechanisms to visualise interesting facts about the data, such as most frequent events, dangerous or suspicious users according to their behaviour, most triggered rules, etc.
+This provides the CSO with mechanisms to visualize interesting facts about the data, such as most frequent events, dangerous or suspicious users according to their behaviour, most triggered rules, etc.
 All this information is shown to the CSO via the mentioned graphical interface, implemented in the server.
@@
 This process is conducted using a GA as a meta-algorithm to test all the possible combinations of pattern features in the classification.
-Thus, the GA algorithm can optimise the group of features to be considered in the classification task, improving both the computational time of this task and also the obtained accuracy of the method \cite{liu1998feature}.
+Thus, the GA algorithm can optimize the group of features to be considered in the classification task, improving both the computational time of this task and also the obtained accuracy of the method \cite{liu1998feature}.
 
 On the other hand, the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods.
-These methods can be used for inference and optimisation, and they use different data as part of the process, such as:
+These methods can be used for inference and optimization, and they use different data as part of the process, such as:
 % [Pedro] maybe we should specify how the following data is used in each one of the 3 EC methods...
@@
 
-\item A \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions.
+\item A \textit{GP rule refinement} approach, which optimizes the current set of rules, adjusting the values in the conditions.
 The set of rules that could be refined is composed by the new rules from the GP-based inference, but also by the original set of rules which was already completed by the Data Miner.
-Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could lead to a better performance.
+Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specializations or generalizations of existing rules which could lead to a better performance.
 % [Pedro] change "could mean a better" to "could lead to a better"
@@
 
-\item A \textit{GA optimisation} algorithm for adapting the values of the assets.
+\item A \textit{GA optimization} algorithm for adapting the values of the assets.
 %FERGU: "values of the assets" mejor?
@@
 This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device.
-MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.
+MUSES is a good solution towards these cases, since it is a multi-platform system in both the client and the server.
 Table \ref{tab:comparison} summarizes the features of the main analyzed tools, regarding these facts.
@@
     Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
-    Samsung Knox and Blackbery Balance & Proprietary & IOS, Android, Samsung Devices & 12\$ per year/device \\
+    Samsung Knox and Blackberry Balance & Proprietary & IOS, Android, Samsung Devices & 12\$ per year/device \\
     Blackphone & Proprietary & Own device & 120\$ per year \\
@@
 
-With respect to GA, they have been extensively used in this scope in the literature, mainly for the detection of anomalies and intrusions rather than for optimisation, as it is used in the proposed system.
+With respect to GA, they have been extensively used in this scope in the literature, mainly for the detection of anomalies and intrusions rather than for optimization, as it is used in the proposed system.
 However, there are some examples that could be used as model for our approach, such as \cite{EAs_securitycosts-kirta,risk_reduction_ga_12}.
@@
 % Antonio - pongo primero la adaptabilidad del sistema porque es la característica más relevante y más 'científica'
-Moreover it has the advantage of being multiplatform, while most of the reviewed tools are not.
+Moreover it has the advantage of being multi-platform, while most of the reviewed tools are not.
 Also, it is remarkable that this MUSES tool is not a solution offered by a company, but the result of the effort of going beyond the state of the art in different fields of research in corporate security, such as risk and trust analysis or event correlation.
@@
 
-There is also room for considering some future improvements to MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimisation of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}.
+There is also room for considering some future improvements to MUSES, such as the analysis of users via social networks \cite{inferring_policies_socialnetworks_09,user_classification_ml_13}, the optimization of security protocols \cite{GA_networksecurity-zarza}, the implementation of intrusion detection mechanisms \cite{GA_intrusion-majeed}, or the application of novel privacy-related techniques \cite{AAI_book_2009}.
 The second prototype of the system will be released in the next months, as well as the conclusions extracted after the analysis of data from the test of the first prototype.

### 2015-07-08 Response to reviewers - r2.tex
Revisada la primera respuesta al revisor
Por favor @amorag haz el resto como esta. En un editor no tienes más que configurarlo para que te ponga el tamaño de línea que quieras. Y si no lo puedes hacer a mano. No pongas colores azules ni cosas de esas que no tienen por qué entenderse (y es mucho más trabajo poner a mano todo)

También corrige el error del & que daba error en LaTeX

@@
 
-%\begin{quotation}
-After reviewing the new version of the document, I admit the authors have  substantially changed section 3 (state of the art) and they have improved and extended the introduction and sections 4 (description of the system) and section 5 (comparison with other systems) I acknowledge the ideas are really interesting and exciting, but I'm still not sure if the authors are providing new results not published in their previous works or just rephrasing their text.
+\begin{quotation}
+After reviewing the new version of the document, I admit the authors
+have  substantially changed section 3 (state of the art) and they have
+improved and extended the introduction and sections 4 (description of
+the system) and section 5 (comparison with other systems) I
+acknowledge the ideas are really interesting and exciting, but I'm
+still not sure if the authors are providing new results not published
+in their previous works or just rephrasing their text.
 
-Since there is an obvious over-the-top quality in their work and some good ideas, I'll let the editors decide if the contents are novel enough (compared to other previous works by the same authors) to be published in the journal.\\
-%\end{quotation}
+Since there is an obvious over-the-top quality in their work and some
+good ideas, I'll let the editors decide if the contents are novel
+enough (compared to other previous works by the same authors) to be
+published in the journal.\\ 
+\end{quotation}
 
-\textcolor{blue}{We would like to thank the reviewer for his/her opinion and would lead him/her to have another look at the new version, since it has been highly improved. 
-As a summary:}
+We would like to thank the reviewer for his/her
+  opinion and would lead him/her to have another look at the new
+  version, since it has been highly improved.  
+As a summary:
 %
-\textcolor{blue}{
 \begin{itemize}
@@
 \item A complete proof-editing process has been done, revising the English grammar and rewriting several paragraphs for a better comprehension.
-\end{itemize}}
+\end{itemize}
 % Antonio - TODO: AÒadir m·s cosas (medianamente relevantes) que se hayan hecho
 %
-\textcolor{blue}{These changes are better described in the responses to the others reviewers, so we encourage this reviewer to read them to have a better idea of their impact in the new version of the manuscript.}
+These changes are better described in the responses to the others reviewers, so we encourage this reviewer to read them to have a better idea of their impact in the new version of the manuscript.
 
@@
 b.      Samaras, Vasileios. A BYOD Enterprise Security Architecture for accessing SaaS cloud services. Diss. TU Delft, Delft University of Technology, 2013.
-c.      Armando, Alessandro, et al. "Enabling BYOD through secure meta-market." Proceedings of the 2014 ACM conference on Security and privacy in wireless & mobile networks. ACM, 2014.
+c.      Armando, Alessandro, et al. "Enabling BYOD through secure meta-market." Proceedings of the 2014 ACM conference on Security and privacy in wireless and mobile networks. ACM, 2014.
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Checking references to things that have been done.
Closes #19

@@
 Also, an additional work on applying data mining and machine learning techniques was conducted in \cite{mora14:urls}.
-It presented a study over a dataset similar to those that MUSES will manage, but not the same, since the prototype of MUSES had not still been released.
+It presented a study over a dataset similar to those that MUSES manages, but not the same, since the prototype of MUSES had not still been released.
 Thus, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
@@
 
-Thus, given the fact that this tool is more focused on the company than in the user, it is worth to compare it to the MUSES system, as the latter tries to focus on the users, being user-centric.
-This means that is preferred to let the user know about a risky situation, rather than making them feel ``watched''.
+Thus, given the fact that this tool is more focused on the company
+than in the user, it is worth to compare it to the MUSES system, as
+the latter tries to focus on the users, being user-centric. This means
+that is preferred to let the user know about a risky situation, rather
+than making them feel ``watched''.
 
@@
 
-However, MUSES presents a limitation regarding the enhance of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
-The philosophy is that the initial set of rules, defined by the CSO, should be very restrictive regarding possible unexpected users' behaviours or events, in order to avoid as much security incidents as possible.
-As the system works, MUSES would be able to define new rules (through refinement) which could get an associated decision after the corresponding events have happened.
-Thus, this will lead to get eventually an optimal set of security rules.
+However, MUSES presents a limitation regarding the enhance of rules,
+since, in principle, it cannot predict (generate rules for dealing
+with) unexpected or unknown events which could lead to a security
+incident. The philosophy is that the initial set of rules, defined by
+the CSO, should be very restrictive regarding possible unexpected
+users' behaviours or events, in order to avoid as much security
+incidents as possible. As the system works, MUSES would be able to
+define new rules (through refinement) which could get an associated
+decision after the corresponding events have happened. Thus, this will
+lead to obtaining an optimal set of security rules.
 

### 2015-07-08 Response to reviewers - r2.tex
Reformatting and fixing responses

@@
 
-In this work authors present state-of-the art in BYOD solutions, and introduce a new solution, MUSES, a result of an EU FP7 project.
+\begin{quotation}
+In this work authors present state-of-the art in BYOD solutions, and
+introduce a new solution, MUSES, a result of an EU FP7 project.
 
@@
 in the market with the purpose to adapt to it in a secure way. 
+\end{quotation}
 
-\textcolor{blue}{The abstract has been changed and that confusing sentence has been eliminated. Now we think it is clear, as intended, the motivation, context and focus of the paper.}
+The abstract has been changed and that confusing sentence has been
+eliminated. Now we think it is clear, as intended, the motivation,
+context and focus of the paper.
 
-The description of IBM products, in section 3.1, does not provide clear distinction between various service types provided by IBM.
-It furthermore lacks focused coverage of services relevant for this work.
+\begin{quotation}
+The description of IBM products, in section 3.1, does not provide
+clear distinction between various service types provided by IBM. It
+furthermore lacks focused coverage of services relevant for this
+work.
 
-In analysis of IBM offer, authors refer to general web site for mobile security products and consumer guide/whitepaper that explores the general problem of BYOD.
-They consider services that are not purely related to BYOD and MUSES.
-For instance, it is not clear how "Enterprise Wireless Networks" (page 6, lines 21-26) fit into comparison, and how establishment of secure connections can be related to MUSES's adaptability.
-On the other hand, the products such as MobileFirst and MaaS360 are omitted.
-The suggestion in this regard is to consider rewriting this part, including updated references and current tools in comparison.
+In analysis of IBM offer, authors refer to general web site for mobile
+security products and consumer guide/whitepaper that explores the
+general problem of BYOD. They consider services that are not purely
+related to BYOD and MUSES. For instance, it is not clear how
+"Enterprise Wireless Networks" (page 6, lines 21-26) fit into
+comparison, and how establishment of secure connections can be related
+to MUSES's adaptability. On the other hand, the products such as
+MobileFirst and MaaS360 are omitted. The suggestion in this regard is
+to consider rewriting this part, including updated references and
+current tools in comparison. 
+\end{quotation}
 
-\textcolor{blue}{Following reviewer's suggestions, this section has been rewritten, and the references mentioned by the referee (including new products) have been considered in the study.
-The tools have been described (by the end of Section 3.1, in page XX), and compared with MUSES in Section 5.}
+Following reviewer's suggestions, this section has been rewritten, and
+the references mentioned by the referee (including new products) have
+been considered in the study. The tools have been described (by the
+end of Section 3.1, in page XX), and compared with MUSES in Section
+5.
 %FERGU: PONED ESTO M√ÅS BONICO!
@@
 
-In section 3.3 (p.7, sentence in l.18-19) there is provided a statement about success of two solutions, however without referencing relevant sources or providing details.
-It is furthermore questionable whether this statement is relevant for the scope of this work at all.
+\begin{quotation}
+In section 3.3 (p.7, sentence in l.18-19) there is provided a
+statement about success of two solutions, however without referencing
+relevant sources or providing details. It is furthermore questionable
+whether this statement is relevant for the scope of this work at all.
+\end{quotation}
 
@@
 
-Section 3.6.1 covers WSO2, an open source tool that should be freely available for evaluation and comparison.
-However, in review, this tool has been only roughly mentioned.
-The context and relevance to the work are omitted, as well as features and comparison with MUSES.
-It is not clear therefore how this tool and MUSES differ.
+\begin{quotation}
+Section 3.6.1 covers WSO2, an open source tool that should be freely
+available for evaluation and comparison. However, in review, this tool
+has been only roughly mentioned. The context and relevance to the work
+are omitted, as well as features and comparison with MUSES. It is not
+clear therefore how this tool and MUSES differ. 
+\end{quotation}
 

### 2015-07-08 Response to reviewers - r2.tex
Revised answer to reviewer
Closes #20 closes #37

@@
 
-For the section 5 and discussion, this reviewer would suggest to consider providing overview in the form of table(s) or figure, comparing different aspects of MUSES and other tools and providing hints/references to further details in this or other works.
-As there are many features of MUSES and other tools, employed approaches and techniques, different coverages and limitations, such overview could contribute to clarity and position of the proposed solution.
+\begin{quotation}
+For the section 5 and discussion, this reviewer would suggest to
+consider providing overview in the form of table(s) or figure,
+comparing different aspects of MUSES and other tools and providing
+hints/references to further details in this or other works. As there
+are many features of MUSES and other tools, employed approaches and
+techniques, different coverages and limitations, such overview could
+contribute to clarity and position of the proposed solution. 
+\end{quotation}
 
-\textcolor{blue}{We agree with the reviewer.
-A comparative table has been included in the section 5 (Table 1 - Page XX), summarizing some of the features of the presented systems and those of MUSES system.}
+We agree with the reviewer. A comparative table has been included in
+the section 5 (Table 1), summarizing some of the features of
+the presented systems and those of MUSES system. As it can be seen,
+all other systems are proprietary and have a cost, which makes MUSES
+unique in the sense that, being free software, can be adapted and
+extended by corporate security departments to the corporate special
+needs.
 
@@
 
-Overall, this reviewer perceives this work as a good contribution in presenting and advancing the state-of-the art.
-It is however suggested to consider revising this work and take into account provided suggestions.
+\begin{quotation}
+Overall, this reviewer perceives this work as a good contribution in
+presenting and advancing the state-of-the art. It is however suggested
+to consider revising this work and take into account provided
+suggestions.
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
open source -> free software (in some places)

@@
 mentioned above. In this paper we present an overview of BYOD security
-solutions along with a novel, adaptive and open source system named
+solutions along with a novel, adaptive and free software system named
 MUSES (Multi-platform Usable Endpoint Security), able 
@@
     \midrule
-    MUSES & Open Source & IOS, Android, Windows Phone & Free  \\
+    MUSES & Free software & IOS, Android, Windows Phone & Free  \\
     IBM Mobile Security & Proprietary &  &  \\

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Rewrite a part of Section 3.1. Closes #30

@@
 They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognize new vulnerabilities - or threats - with enough accuracy.
-The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts.
-Another difference is the fact that IBM software is not open source as MUSES system is.
-Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
 
 %FERGU: HABLANDO DE LOS PRODUCTOS
-IBM also offers some products related to BYOD security.
-{\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing.
+The specific IBM products related to BYOD security are included in their {\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} suite.
+MobileFirst is a set of mobile applications and services, based in big data analytics and cloud computing.
 It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport).
@@
 No further risk and trust analysis is performed, neither is included a refinement of the rules derived from the policies.
+
+ The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts.
+Another difference is the fact that IBM software is not open source as MUSES system is.
+Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Fixing KNOX and blackberry. References #31
Changing a sentence because Fergu gave me the ocs

@@
 \item {\em Invasive or non-invasive data access}.
-A system can be considered {\em invasive} if a user needs to use the tool to perform their job.
-% (Paloma) Fergu, te parece bien cambiar esta frase a "A system can be considered {\em invasive} if a user must use a certain tool to perform their job." ?
-Porque con el "the tool" no me queda muy claro.
+A system can be considered {\em invasive} if a user must use a certain tool to perform their job.
 For example, opening a specific browser provided by the tool, instead of the original device browser, such as Chrome of Safari.
@@
 This also means that they are not device-independent, as KNOX is only for Samsung devices and Balance is integrated in BlackBerry 10 \cite{Blackberry_tool}.
+Looking at their situation and problems, it could be thought that making a BYOD solution platform-dependent is counteractive, which is why MUSES is independent of the device platform.
 

### 2015-07-08 table_taxonomy.tex
Ladies and gentlemen, the best tables in the nation for personal enjoyment :neckbeard:

\documentclass{article}
\usepackage{array,booktabs,graphicx,colortbl, pifont}% http://ctan.org/pkg/{array,booktabs}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\begin{document}

\begin{table}[ht]

  \centering
%  \renewcommand{\arraystretch}{1.2}% Spread rows out...
  \resizebox{14cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
    \toprule
      & \textbf{Online threat detection method} & \textbf{Updatable database information} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \xmark & & &  \\
     \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & & & & &  \\
     \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & & & & &\\
     \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & & & & &\\
     \arrayrulecolor[gray]{0.8}\hline
    Blackphone & & & & &\\
     \arrayrulecolor[gray]{0.8}\hline
    Android for Work & & & & &\\
    \bottomrule
  \end{tabular}
  }
  \caption{Features of the analyzed products considering licenses, type of devices and price.}
\end{table}

\end{document}

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Minor changes to Sophos. References #31

@@
 
- The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts.
+The main difference with MUSES in this case, is that MUSES includes the threat recognition feature feature in the system, without the need of purchasing the service separately and configuring the different parts.
 Another difference is the fact that IBM software is not open source as MUSES system is.
 Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
+In addition, this product also offers the possibility to work offline, though an initial online authentication is needed \footnote{\url{https://developer.ibm.com/mobilefirstplatform/documentation/getting-started-6-3/authentication-security/offline-authentication/}}.
 
@@
 Remainder features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.
+Also, version 4.0 adds a new version of what has been called `Sophos Antivirus Engine', with offline detection capabilities.
 
@@
 Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of the breach.
-For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe may be the chosen option.
+For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe might be the chosen option.
 Finally, compliance check, by constantly performing scans to detect malware and putting the devices in quarantine when they are found infected.

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Minor changes with regard to parentheses to Sophos. References #31

@@
 With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users.
-But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad (even not on purpose) users' behaviour.
+But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even if it was not on purpose.
 Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs.

### 2015-07-08 table_License_Devices_price.tex

@@
 \documentclass{article}
-\usepackage{array,booktabs,graphicx}% http://ctan.org/pkg/{array,booktabs}
+\usepackage{array,booktabs,graphicx,colortbl}% http://ctan.org/pkg/{array,booktabs}
 
@@
     MUSES & OpenSource &  & Free*  \\
+       \arrayrulecolor[gray]{0.8}\hline
     IBM Mobile Security & Proprietary &  &  \\
+        \arrayrulecolor[gray]{0.8}\hline
     Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
+        \arrayrulecolor[gray]{0.8}\hline
     Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
+        \arrayrulecolor[gray]{0.8}\hline
     Blackphone & Proprietary & Own device & 120\$ per year \\
+        \arrayrulecolor[gray]{0.8}\hline
     Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Removed all literary parentheses. Closes #39

--- 2015-07-08 MUSES_vs_BYOD_solutions.tex
@@
 With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users.
-But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad (even not on purpose) users' behaviour.
+But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even not on purpose.
 Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs.
@@
 Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still remained delayed until it was apparently found insecure \cite{Samsung_insecure}.
-Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android} (see Section \ref{subsec:androidwork}).
+Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android}, as mentioned in Section \ref{subsec:androidwork}.
 
@@
 On the device side, one of the most powerful solutions found in the BYOD state of the art is, apparently, to directly use a phone which has been developed with data security in mind such as the BlackPhone \cite{Blackphone}.
-It has its own Android-based operating system, called \textit{PrivatOS} \cite{Blackphone}, which includes a privacy-focused application store (called \textit{Silent Store}) that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}.
+It has its own Android-based operating system, called \textit{PrivatOS} \cite{Blackphone}, which includes a privacy-focused application store, called \textit{Silent Store}, that takes care of the problem of applications which ask for certain permissions that can lead, for instance, to personal data leakage \cite{gangula2013survey}.
 BlackPhone also allows a remote wiping of the data if the device is lost or stolen.
 The main disadvantage of this solution is either the enterprise having to make
-an investment and buy these smartphones to the employees (which, in fact, is against the BYOD philosophy), or to make employees buy them,
-so they cannot use the device they already have. On the contrary, the MUSES system proposed in this work is designed as device-independent.
+an investment and buy these smartphones to the employees or to make employees buy them,
+so they cannot use the device they already have. Both options are against the BYOD philosophy. On the contrary, the MUSES system proposed in this work is designed as device-independent.
 
@@
 Thus, Android Work will provide the CSOs with a tool to define which apps would be allowed for being installed by the users and considered as corporate-related applications.
-Several enterprise-security aimed applications will be offered in the market, so the IT would decide which ones will be installed (even as a bundle) in the employees' devices, and also, they can manage the updates of these apps, in order to ensure that all the employees are up to date.
+Several enterprise-security aimed applications will be offered in the market, so the IT would decide which ones will be installed in the employees' devices.
+Also, they can manage the updates of these apps, in order to ensure that all the employees are up to date.
 For instance, one app could manage the creation of personal and work profiles, so the user just could access corporate assets after login in into the app.
@@
 Even though it does not analyze the system information for security rules evolution purposes, it offers policy management.
-Thus, the system will provide a framework for IT staff to manage business devices, but also, and more importantly, personal devices being used in a BYOD context (The CSO would give the employee an activation code in order to `connect' the smartphone to the enterprise and use this Android Work).
-Therefore, IT admins will be able to specify which Google Play apps will be available for users to install through this work profile, including being able to provision apps to specific individuals or groups (inside the company).
+Thus, the system will provide a framework for IT staff to manage business devices, but also, and more importantly, personal devices being used in a BYOD context.
+The CSO would give the employee an activation code in order to `connect' the smartphone to the enterprise and use this Android Work.
+Therefore, IT admins will be able to specify which Google Play apps will be available for users to install through this work profile, including being able to provision apps to specific individuals or groups inside the company.
 
@@
 The rest of tools only have permission for monitoring the running processes in the devices, while Android Work has, for instance, the ability to provide a `work' version of its native apps.
-MUSES, instead, depends on the developers to adapt their applications through a MUSES API, transforming them to MUSES Aware apps (see Section \ref{subsec:client}).
+MUSES, instead, depends on the developers to adapt their applications through a MUSES API, transforming them to MUSES Aware apps, as will be explained in Section \ref{subsec:client}.
 In any other case, and most of all with the ``self-adaptation'' feature of MUSES, it can be said that MUSES presents more advantages than the Google solution.
@@
 \item It does it by enforcing passwords and providing mechanisms for remote lock.
-\item It offers the ability to wipe (even selectively) corporate data email and contacts on the device if lost or stolen.
+\item It offers the ability to wipe, even selectively, corporate data email and contacts on the device if lost or stolen.
 \end{itemize}
@@
 
-XenMobile with Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions (like using the mobile phone's camera, GPS or microphone) \cite{WorxSDK}.
+XenMobile with Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions \cite{WorxSDK}.
+For example using the mobile phone's camera, GPS or microphone.
 These policies can be turned on or off using its own GUI.
-Citrix is framework-enabled, and it is aware of some (or all) apps installed on the device.
+Citrix is framework-enabled, and it is aware of the apps installed on the device.
 All the apps that are Worx-enable are capable of interacting, and thus offering the user a better experience.
@@
 % [Pedro] y respecto al servidor: "As far as the server is concerned, it has been developed using Java to be used with an Apache Tomcat in the corporate server." % Ok, cambiado y añadido lo del final.
-Both sides are connected through a secure channel (using HTTPS) over the Internet.
+Both sides are connected through a secure channel using HTTPS over the Internet.
 Figure \ref{fig:architecture} only shows the high-level components in each part, along with the way the information flows in the system.
@@
 Anyway, in this mode, the gathered information by the sensors in the device is stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
-Moreover, when switching from offline to online mode, the device  receives an updated copy of the Decision Rules (the so-called Device Policies), as a kind of antivirus database, in order to work again perfectly in offline mode (if the connection is lost).
+Moreover, when switching from offline to online mode, the device  receives an updated copy of the Decision Rules, the so-called Device Policies, as a kind of antivirus database, in order to work again perfectly in offline mode if the connection is lost.
 
@@
  	 \item \textit{Access Control System (MusACS)}: module in charge of making the decisions considering the gathered data.
-These decisions can be made locally (if possible), or can be requested to the server (if there is no rule which matches with the occurred events).
+These decisions can be made locally if possible, or can be requested to the server if there is no rule which matches with the occurred events.
 
@@
 % Antonio - no sé qué expresión será más correcta, pero deberíamos poner siempre "assets' values" o "values of the assets". Yo me inclino por la segunda.
-user-related information (trust, context), events data, and, of course, security rules to apply (with regard to the security policies).
+user-related information (trust, context), events data, and, of course, security rules to apply with regard to the security policies.
 
@@
 There are three important points with relation to this matter \cite{deliverable72}.
-First, the data that the user provides to the system (such as name, or email) is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks.
+First, the data that the user provides to the system, such as name, or email, is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks.
 Then, the location of the device is never sent and stored in the database, but as stated in the previous section, there are a number of defined `zones'.
@@
 In addition, the hard limit is provided by the law, in case that the employee leaves the company, or if there is a national law specifying a maximum data retention period.
-  \item \textit{User, Context, Event Data Receiver}, which is devoted to receive data from the device side (events, or user-related data, among others) and to distribute them among the components (storing in the database, and requesting the Event Processor to start the correlation task).
+  \item \textit{User, Context, Event Data Receiver}, which is devoted to receive data from the device side, such as events, or user-related data, and to distribute them among the components, storing in the database, and requesting the Event Processor to start the correlation task.
 Finally, there is another \textit{Connection Manager} which controls the communications with the device side.
@@
 In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD.
-Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases.
+Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server, being even more restrictive in some cases.
 This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device.
@@
 
-Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context (connection properties, or trust value of the device, for instance), to really understand the real risk that comes with a specific action.
+Another comparison would be that the existing products are mostly policy-based, while MUSES makes its decisions not only considering policies, but also based on the terminals and users context, such as connection properties, or trust value of the device, to really understand the real risk that comes with a specific action.
 
@@
 However, MUSES presents a limitation regarding the enhance of rules,
-since, in principle, it cannot predict (generate rules for dealing
-with) unexpected or unknown events which could lead to a security
+since, in principle, it cannot predict or generate rules for dealing
+with unexpected or unknown events, which could lead to a security
 incident. The philosophy is that the initial set of rules, defined by
@@
 incidents as possible. As the system works, MUSES would be able to
-define new rules (through refinement) which could get an associated
+define new rules through refinement which could get an associated
 decision after the corresponding events have happened. Thus, this will
@@
 In addition, MUSES can also infer or create new rules using computational intelligence techniques.
-These rules could deal with unexpected situations (not previously happened), but must be previously approved by the CSO.
+These rules could deal with unexpected situations not previously happened, but must be previously approved by the CSO.
 Of course, everything is constrained by the available set of sensors which, in turn, define the possible information that MUSES will analyze and use in the refinement and inference processes.
@@
 GP has been previously proposed in bibliography \cite{rule_generation_gp_09,sec_policy_evolution_gp_08}, even for creating new policies or rules in a security-aimed sense.
-In any case they do not affect the ISPs and moreover, our proposed evaluation functions (completely integrated in the system) for the refinement and inference approaches are novel.
+In any case they do not affect the ISPs and moreover, our proposed evaluation functions, completely integrated in the system, for the refinement and inference approaches are novel.
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
conflict?

--- 2015-07-08 MUSES_vs_BYOD_solutions.tex
@@
 
-On the other side, employees are able to access information and applications related to their personal lives, while staying connected to important work information when they need to perform.
-Finally, another known feature is also offered by Blackberry, so if the device gets lost or is stolen, or if the employee leaves the organization, there will be an option to wipe just work information which can be done remotely.
+On the other side, while KNOX allows to \textit{push} policies from the server to the devices, so they are available offline, Blackberry Balance only allows to read documents in this mode.
+Finally, another known feature is also offered by Blackberry, so if the device gets lost, it is stolen, or if the employee leaves the organization, there is an option to wipe just work information which can be done remotely.
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex

--- 2015-07-08 MUSES_vs_BYOD_solutions.tex
@@
 Remainder features are similar to IBM's product, adding some new such as the incorporation of a service called Malware and Web protection, so that there is no need for having a previously installed antivirus in the devices.
+Also, version 4.0 adds a new version of what has been called `Sophos Antivirus Engine', with offline detection capabilities.
 
 With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users.
-But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even not on purpose.
+But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even if it was not on purpose.
 Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs.
@@
 Secondly, by a risk mitigation in which the actions to perform can be set according to the severity of the breach.
-For minor cases, the company may want to simply inform to the user, but if sensitive data is at risk, a remote wipe may be the chosen option.
+For minor cases, the company might want to simply inform to the user, but if sensitive data is at risk, a remote wipe might be the chosen option.
 Finally, compliance check, by constantly performing scans to detect malware and putting the devices in quarantine when they are found infected.

### 2015-07-08 table_taxonomy.tex

@@
 \newcommand{\xmark}{\ding{55}}%
+\newcommand{\nmark}{\scalebox{1.25}{\textbf{-}} }
 
@@
   \centering
-%  \renewcommand{\arraystretch}{1.2}% Spread rows out...
-  \resizebox{14cm}{!}{
-  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
+  \renewcommand{\arraystretch}{1.8}% Spread rows out...
+%  \resizebox{14cm}{!}{
+  \begin{tabular}{>{\centering\bfseries}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering\arraybackslash}m{0.8in}}
     \toprule
-      & \textbf{Online threat detection method} & \textbf{Updatable database information} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
+      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
     \midrule
-    MUSES & \cmark & \xmark & & &  \\
+    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
      \arrayrulecolor[gray]{0.8}\hline
-    IBM Mobile Security & & & & &  \\
+    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
      \arrayrulecolor[gray]{0.8}\hline
-    Sophos Mobile Control & & & & &\\
+    Sophos Mobile Control & \xmark & \xmark & \cmark & \nmark & \nmark \\
      \arrayrulecolor[gray]{0.8}\hline
-    Samsung Knox and Blackbery Balance & & & & &\\
+    Samsung Knox and Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \nmark\\
      \arrayrulecolor[gray]{0.8}\hline
-    Blackphone & & & & &\\
+    Blackphone & \nmark & \nmark & \cmark & \nmark & \nmark\\
      \arrayrulecolor[gray]{0.8}\hline
-    Android for Work & & & & &\\
+    Android for Work & \nmark & \nmark & \cmark & \nmark & \nmark\\
     \bottomrule
   \end{tabular}
-  }
-  \caption{Features of the analyzed products considering licenses, type of devices and price.}
+%  }
+  \caption{Proposed taxonomy to classify the BYOD tools described in this paper.}
 \end{table}

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Added @deantares tables to the paper for issue #37. @unintendedbear or @amorag just three cells to fill, please finish the table and close the issue :)

@@
 \usepackage[english]{babel}
+\usepackage{colortbl, pifont}% http://ctan.org/pkg/{array,booktabs}
+
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
+\newcommand{\nmark}{\scalebox{1.25}{\textbf{-}} }
 
@@
 MUSES is a good solution towards these cases, since it is a multi-platform system in both the client and the server.
-Table \ref{tab:comparison} summarizes the features of the main analyzed tools, regarding these facts.
+Table \ref{tab:taxonomy} summarizes the features of the main analyzed tools, regarding the proposed taxonomy of Section \ref{sec:toolsreview}.
+Also, Table \ref{tab:features} shows the features of the analyzed products considering licenses, type of devices and price.
 % Antonio - Antares, ¿podrías incluir en la comparativa las otras herramientas que se han analizado? Las de Citrix, WSO2, Azzurri, Good...
@@
   \centering
-  \renewcommand{\arraystretch}{1.5}% Spread rows out...
+  \renewcommand{\arraystretch}{1.8}% Spread rows out...
+  \resizebox{12cm}{!}{
+  \begin{tabular}{>{\centering\bfseries}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering\arraybackslash}m{0.8in}}
+    \toprule
+      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
+    \midrule
+    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
+     \arrayrulecolor[gray]{0.8}\hline
+    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
+     \arrayrulecolor[gray]{0.8}\hline
+    Sophos Mobile Control & \cmark & \xmark & \cmark & \xmark & \xmark \\
+     \arrayrulecolor[gray]{0.8}\hline
+    Samsung Knox & \cmark & \nmark & \cmark & \nmark & \cmark\\
+     \arrayrulecolor[gray]{0.8}\hline
+     Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \cmark\\
+     \arrayrulecolor[gray]{0.8}\hline
+    Blackphone & \nmark & \nmark & \cmark & \cmark & \nmark\\
+     \arrayrulecolor[gray]{0.8}\hline
+    Android for Work & \xmark & \xmark & \cmark & \xmark & \cmark\\
+    \bottomrule
+  \end{tabular}
+  }
+  \caption{Proposed taxonomy to classify the BYOD tools described in this paper.}
+  \label{tab:taxonomy}
+\end{table}
+
+\begin{table}[ht]
+
+  \centering
+  \renewcommand{\arraystretch}{1.8}% Spread rows out...
 %  \resizebox{8cm}{!}{
@@
        \midrule
-    MUSES & Free software & IOS, Android, Windows Phone & Free  \\
+    MUSES & OpenSource &  & Free*  \\
+       \arrayrulecolor[gray]{0.8}\hline
     IBM Mobile Security & Proprietary &  &  \\
+        \arrayrulecolor[gray]{0.8}\hline
     Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
-    Samsung Knox and Blackberry Balance & Proprietary & IOS, Android, Samsung Devices & 12\$ per year/device \\
+        \arrayrulecolor[gray]{0.8}\hline
+    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
+        \arrayrulecolor[gray]{0.8}\hline
     Blackphone & Proprietary & Own device & 120\$ per year \\
+        \arrayrulecolor[gray]{0.8}\hline
     Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
@@
 %  }
-  \caption{Features of the analyzed products considering licenses, type of devices and price. \label{tab:comparison}}
+  \caption{Features of the analyzed products considering licenses, type of devices and price.}
+  \label{tab:features}
 \end{table}

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Fixing all section 3, asigning categories to tools. Closes #31. Closes #44. Closes #41.

--- 2015-07-08 MUSES_vs_BYOD_solutions.tex
@@
 BlackPhone also allows a remote wiping of the data if the device is lost or stolen.
-The main disadvantage of this solution is either the enterprise having to make
-an investment and buy these smartphones to the employees or to make employees buy them,
-so they cannot use the device they already have. Both options are against the BYOD philosophy. On the contrary, the MUSES system proposed in this work is designed as device-independent.
+The main disadvantage of this solution is either the enterprise having to make an investment and buy these smartphones to the employees or to make employees buy them, so they cannot use the device they already have.
+Both options are against the BYOD philosophy.
+On the contrary, the MUSES system proposed in this work is designed as device-independent.
+Furthermore, the lack of information about this system makes difficult to determine its real qualities.
 
@@
 
-This system will be strongly related to the Google Play market, as the applications will be `categorized'.
-Thus, Android Work will provide the CSOs with a tool to define which apps would be allowed for being installed by the users and considered as corporate-related applications.
-Several enterprise-security aimed applications will be offered in the market, so the IT would decide which ones will be installed in the employees' devices.
+This system is be strongly related to the Google Play market, as the applications will be `categorized'.
+Thus, Android Work provides the CSOs with a tool to define which apps would be allowed for being installed by the users and considered as corporate-related applications.
+Several enterprise-security aimed applications will be offered in the market, so the IT can decide which ones will be installed in the employees' devices.
 Also, they can manage the updates of these apps, in order to ensure that all the employees are up to date.
@@
 
+Althoug this tool also includes features such as device location, remote wipe, or encrypt storage, its main disadvantage is that it does not work in offline mode.
+In the documentation \footnote{\url{https://docs.wso2.com/display/EMM200/Working+with+Policies}}, it is clearly stated that the policy compliance can be monitored while the devices are connected to the WSO2 EMM server.
+
 \subsubsection{Good's Bring Your Own Device solution}
@@
 XenMobile with Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions \cite{WorxSDK}.
-For example using the mobile phone's camera, GPS or microphone.
+For example using the mobile phone camera, GPS, or microphone.
 These policies can be turned on or off using its own GUI.
 Citrix is framework-enabled, and it is aware of the apps installed on the device.
-All the apps that are Worx-enable are capable of interacting, and thus offering the user a better experience.
+All the apps that are Worx-enabled are capable of interacting, and thus offering the user a better experience.
+This concept is similar to the `MUSES Aware' one, which was mentioned earlier in this section, and consists of adapting the applications to allow communications with the BYOD tools.
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Adding justification for Big data with data from the current trials

@@
 Moreover, a lot of attributes are extracted from the events, for obtaining the more information as possible. 
-% During the first trials, a ratio of _ events per day was observed.
-As this results in huge datasets, MUSES makes use of several Big Data processing methods \cite{BigData_11}, such as: %JUSTIFY (Paloma will do it)
+During the first trials, a mean of 201 events per day and user was observed.
+By considering just a medium size company, of 250 employees, that would make an average of 50300 events per day, of which a high number of features are extracted.
+For even bigger companies, this results in huge datasets, so that MUSES makes use of several Big Data processing methods \cite{BigData_11}, such as:
 

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Adding results of first trials saying that MUSES is effective because the number of security violations became 0 in verbose mode. References #28.

@@
 % Antonio- muevo esta frase a un sitio más adecuado
-The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results, so we have now a clearer idea of its capabilities. 
+The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results, so we now have a clearer idea of its capabilities.
+Actually, the first trials of the system were performed with an Android prototype, and in two phases: \textit{silent} and \textit{verbose}, 1 month duration each.
+During the \textit{silent} phase, MUSES was able to gather data, but without warning the users when a security incident was happening.
+A total of 23358 security violations were detected.
+In the \textit{verbose}, MUSES started to show warning pop-ups to the users, every time a security incident happened.
+Not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 before the trials period finished.
+This has proven MUSES to be an effective tool.
 Thus, in this paper we present an overview of the main existing solutions in the BYOD environment.
@@
 This is done using an up-to-date copy on the Decision Table inside the Local database, which contains decisions for any type of detected event, along with the default actions to be performed if no rule is met.
-Anyway, in this mode, the gathered information by the sensors in the device is stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
+In this mode, the gathered information by the sensors in the device is stored for later submission to the server side when a connection is available, in order to be processed in the knowledge refinement process.
 Moreover, when switching from offline to online mode, the device receives an updated copy of the Decision Rules, the so-called Device Policies, as a kind of antivirus database, in order to work again perfectly in offline mode if the connection is lost.
@@
 MUSES is a good solution towards these cases, since it is a multi-platform system in both the client and the server.
-Table \ref{tab:taxonomy} summarizes the features of the main analyzed tools, regarding the proposed taxonomy of Section \ref{sec:toolsreview}.
-Also, Table \ref{tab:features} shows the features of the analyzed products considering licenses, type of devices and price.
+Table \ref{tab:taxonomy} summarizes the features of the main analyzed tools, with respect to the proposed taxonomy in Section \ref{sec:toolsreview}.
+Also, Table \ref{tab:features} shows the features of the analyzed products considering licenses, type of supported devices, and price.
 % Antonio - Antares, ¿podrías incluir en la comparativa las otras herramientas que se han analizado? Las de Citrix, WSO2, Azzurri, Good...
@@
        \arrayrulecolor[gray]{0.8}\hline
-    IBM Mobile Security & Proprietary &  &  \\
+    IBM Mobile Security & Proprietary & IOS, Android, Windows Phone, Blackberry  &  By Request\\\\
         \arrayrulecolor[gray]{0.8}\hline

### 2015-07-08 Response to reviewers - r2.tex
@amorag be careful with English false friends.
rewriting some sentences

@@
 % Antonio - TODO: Fergu, completa esto t˙ que tienes la idea global de lo nuevo en el SotA, por favor.
-The reviewer can see the set of new references added by the end of this response letter.
-\item The description of MUSES system is now much better.
+%The reviewer can see the set of new references added by the end of this response letter.
+New references added after the review can be found at the end of this document
+\item The description of MUSES system has been improved.
 Several points have been clarified and better explained in Section 4.
@@
 
-\textcolor{blue}{The authors think that the work has been highly improved following the reviewer's suggestions. We would like to thank he/she for his/her careful revision and interesting comments.}
+\textcolor{blue}{The work has been deeply improved following the reviewer's suggestions. We would like to thank he/she for his/her careful revision and interesting comments.}
 

### 2015-07-08 Response to reviewers - r2.tex
rewriting some sentences

@@
 Following reviewer's suggestions, this section has been rewritten, and
-the references mentioned by the referee (including new products) have
-been considered in the study. The tools have been described (by the
-end of Section 3.1, in page XX), and compared with MUSES in Section
-5.
+the references mentioned by the referee, including new products, have
+been considered in the study. Tools have been described 
+(end of Section 3.1, in page XX), and compared to MUSES in Section 5.
 %FERGU: PONED ESTO M√ÅS BONICO!

### 2015-07-08 Response to reviewers - r2.tex
rewriting some sentences
Adding some responses for reviewers... tired :(

--- 2015-07-08 Response to reviewers - r2.tex
@@
 % Antonio - TODO: extender esto de la secciÛn 3 y 5 un poco m·s.
-\item A complete proof-editing process has been done, revising the English grammar and rewriting several paragraphs for a better comprehension.
+\item A complete proof-editing process has been done, reviewing the English grammar and rewriting several paragraphs for a better comprehension.
 \end{itemize}
@@
 
-\textcolor{blue}{Moreover, MUSES offers visual analysis tools to the CSOs, which can aid (or guide) they to detect suspicious or anomalous patterns, and to study how to avoid these patterns become malicious to the company.}
+\textcolor{blue}{Moreover, MUSES offers visual analysis tools to the CSOs, which can aid (or guide) they to detect suspicious or anomalous patterns, and to study how to avoid these patterns becoming malicious to the company.}
 
@@
 
-\textcolor{blue}{\textit{However, MUSES presents a limitation regarding the enhance of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
+\textcolor{blue}{\textit{However, MUSES presents a limitation regarding the enhancement of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
 The philosophy is that the initial set of rules, defined by the CSO, should be very restrictive regarding possible unexpected users' behaviours or events, in order to avoid as much security incidents as possible.
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{A more detailed definition and description of the sensors has been included.
+In addition, a discussion on how the case the reviewer mentions could affect the system has been added, as:}
+
+\textcolor{blue}{It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not.
+It might happen then that the user ignores this advice and the device becomes compromised.
+As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, stored, and processed on the server.
+In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will mean a significant change in the patterns.
+Then, this change in the patterns will be noticed by the server, which will immediately warn the user, and decrease the device trust value.}
 
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We agree with what the reviwer remarks, and so we have included, at the end of the Introductiono section, the ratio of security violations detected by the system in a prototype trials period.
+Also, a little description of the conditions of the trials has been included, for we consider that a deep description of these trials is not in the scope of the paper.}
 

### 2015-07-08 Response to reviewers - r2.tex

@@
 % Fergu, tambiÈn falta la comparativa con MUSES de esas herramientas (SecciÛn 5)...
+% [Pedro] he cambiado un poco la redacciÛn   ;)
 

### 2015-07-08 Response to reviewers - r2.tex
Nuevas respuestas
Y cambio de formato a Verbatim

@@
 
-\title{Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System: Response to Reviewers\' comments}
+\title{Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System: Response to Reviewers' comments}
+
+\maketitle
 
@@
 
-We really appreciate the opportunity for improving our work. Following the reviewers' requests and suggestions we have improved the paper, incorporating all suggestions.
+We really appreciate the opportunity for improving our work. Following the reviewers' requests and advices we have improved the paper, incorporating all suggestions.
 
@@
 \section{Editor's comments}
+
+\begin{verbatim}
 Dear Dr. Mora,
 
-Reviewers' comments on your work have now been received.
-After analyzing the reviewers' reports and the manuscript, the Guest Editors are recommending that you perform a further MAJOR revision of your manuscript to address the reviewers' comments.
+Reviewers' comments on your work have now been received. After
+analyzing the reviewers' reports and the manuscript, the Guest 
+Editors are recommending that you perform a further MAJOR revision 
+of your manuscript to address the reviewers' comments.
 
-While revising the manuscript please carefully revise the analysis of the state of the art to include all recent and relevant works in the field.
-An updated analysis of the state of the art is mandatory for a publication in Computer Communications.
+While revising the manuscript please carefully revise the analysis 
+of the state of the art to include all recent and relevant works 
+in the field.
+An updated analysis of the state of the art is mandatory for a 
+publication in Computer Communications.
 
-If you decide to revise the work, please submit a list of changes or a rebuttal against each point which is being raised when you submit the revised manuscript.
+If you decide to revise the work, please submit a list of changes 
+or a rebuttal against each point which is being raised when you 
+submit the revised manuscript.
 
-\textit{Include an overview of all changes made in the paper.}
+Include an overview of all changes made in the paper.
+\end{verbatim}
+
+We are very grateful for the opportunity of improving the paper in this revised version.
+
+Following the Editor's and some of the reviewers' requests, we have updated the state of the art, revising and commenting in the text (Section 2) several works with common topics with this manuscript.
+The new references can be consulted b the end of this letter.
 
@@
 
-\begin{quotation}
+\begin{verbatim}
 After reviewing the new version of the document, I admit the authors
@@
 enough (compared to other previous works by the same authors) to be
-published in the journal.\\ 
-\end{quotation}
+published in the journal.
+\end{verbatim}
 
-We would like to thank the reviewer for his/her
-  opinion and would lead him/her to have another look at the new
-  version, since it has been highly improved.  
+We would like to thank the reviewer for his/her opinion and would lead him/her to have another look at the new version, since it has been highly improved.  
 As a summary:
@@
 
-This paper describes MUSES, an adaptable framework for enforcing security policies on mobile devices.
-This tool relies on Machine Learning and CI techniques to predict policy violations and is self-adaptive on user behaviors.
-The idea seems interesting although several technical concerns arise from the reading of this work:
-1.
-The tools aims at enforcing security policies, however the security response occurs only AFTER a particular pattern is recognized to be potentially malicious.
-From my understandings, there is no a-priori enforcement except for the prediction based on event logs.
-This could mean that a security violation could in principle happen and only later recognized.
-This is not so suitable for a corporate environment with strict security requirements.
-This statement should be discussed and preferably discredited with experimental results.
+\begin{verbatim}
+This paper describes MUSES, an adaptable framework for enforcing 
+security policies on mobile devices. This tool relies on Machine 
+Learning and CI techniques to predict policy violations and is 
+self-adaptive on user behaviors.
+The idea seems interesting although several technical concerns 
+arise from the reading of this work:
+1.      The tools aims at enforcing security policies, however 
+the security response occurs only AFTER a particular pattern is 
+recognized to be potentially malicious. From my understandings, 
+there is no a-priori enforcement except for the prediction based 
+on event logs. This could mean that a security violation could 
+in principle happen and only later recognized. This is not so 
+suitable for a corporate environment with strict security 
+requirements. This statement should be discussed and preferably 
+discredited with experimental results.
+\end{verbatim}
 
-\textcolor{blue}{MUSES starts from a defined set of security rules that the CSO must define.
+MUSES starts from a defined set of security rules that the CSO must define.
 Ideally, these rules should deal, in principle, all the potential security incidents that the company aims to detect.
@@
 These rules could deal with unexpected situations (not previously happened).
+
 Anyway, the idea is to define a set of `restrictive' rules at the very beginning, able to ensure the system safety in a big amount of situations.
-Then, MUSES will refine or improve this set, making more specific and optimal rules.}
+Then, MUSES will refine or improve this set, making more specific and optimal rules.
 
-\textcolor{blue}{Moreover, MUSES offers visual analysis tools to the CSOs, which can aid (or guide) they to detect suspicious or anomalous patterns, and to study how to avoid these patterns becoming malicious to the company.}
+Moreover, MUSES offers visual analysis tools to the CSOs, which can aid (or guide) they to detect suspicious or anomalous patterns, and to study how to avoid these patterns becoming malicious to the company.
 
-\textcolor{blue}{In order to clarify this we have rewritten and completed the second paragraph in section 4.1 (page XX). It is now:}
+In order to clarify this we have rewritten and completed the second paragraph in section 4.1 (page XX). It is now:
 
-\textcolor{blue}{\textit{The client is an important part of the a-priori risk treatment, because it both monitors the whole context, and finally acts or warns the user in event of a security violation.
+\textit{The client is an important part of the a-priori risk treatment, because it both monitors the whole context, and finally acts or warns the user in event of a security violation. 
 But security violations are mainly identified by security rules, which is why MUSES needs at least an initial set of rules, defined by the CSO.
@@
 Implementing a sensor means to include a programmed method which triggers MUSES to start `listening' to some parts of a device.
-Then, the initial security rules establish which situations might cause a security violation, and the sensors provide with information which helps the MUSES server to identify events that are alike to the ones that are already known as dangerous.}}
+Then, the initial security rules establish which situations might cause a security violation, and the sensors provide with information which helps the MUSES server to identify events that are alike to the ones that are already known as dangerous.}
 
@@
 
-\textcolor{blue}{\textit{However, MUSES presents a limitation regarding the enhancement of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
+\textit{However, MUSES presents a limitation regarding the enhancement of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
 The philosophy is that the initial set of rules, defined by the CSO, should be very restrictive regarding possible unexpected users' behaviours or events, in order to avoid as much security incidents as possible.
 As the system works, MUSES would be able to define new rules (through refinement) which could get an associated decision after the corresponding events have happened.
-Thus, this will lead to get eventually an optimal set of security rules.}}
+Thus, this will lead to get eventually an optimal set of security rules.}
 
-\textcolor{blue}{\textit{In addition, MUSES can also infer or create new rules using computational intelligence techniques.
+\textit{In addition, MUSES can also infer or create new rules using computational intelligence techniques.
 These rules could deal with unexpected situations (not previously happened), but must be previously approved by the CSO.
-Of course, everything is constrained by the available set of sensors which, in turn, define the possible information that MUSES will analyze and use in the refinement and inference processes.}}
+Of course, everything is constrained by the available set of sensors which, in turn, define the possible information that MUSES will analyze and use in the refinement and inference processes.}
 
-2.
-A strong limitation is that an effective enforcement is only possible with MUSES Aware Apps.
-It is unclear the effectiveness of the approach with commercial applications.
-In page 14 "MUSES could just detect very specific events and also do very limited actions".
-With those assumptions, it seems unlikely that a company would adopt MUSES since it is not able to offer an adequate level of security.
-I think that this is very far from being acceptable for a BYOD solution.
-Also in this respect, experimental results are needed.
+\begin{verbatim}
+2.      A strong limitation is that an effective enforcement is 
+only possible with MUSES Aware Apps. It is unclear the effectiveness 
+of the approach with commercial applications. In page 14 "MUSES 
+could just detect very specific events and also do very limited 
+actions". With those assumptions, it seems unlikely that a company 
+would adopt MUSES since it is not able to offer an adequate level of 
+security. I think that this is very far from being acceptable for a 
+BYOD solution. Also in this respect, experimental results are needed.
+\end{verbatim}
 
@@
 
-3.
-MUSES Sensors are essentially user-space applications that collects logs on specific activities.
-This aspect really concerns me since a compromised device or compromised sensor apps could vanish all MUSES effort.
-Authors should deeply discuss this aspect.
+\begin{verbatim}
+3.      MUSES Sensors are essentially user-space applications that 
+collects logs on specific activities. This aspect really concerns 
+me since a compromised device or compromised sensor apps could vanish 
+all MUSES effort. Authors should deeply discuss this aspect.
+\end{verbatim}
 
-\textcolor{blue}{A more detailed definition and description of the sensors has been included.
-In addition, a discussion on how the case the reviewer mentions could affect the system has been added, as:}
+A more detailed definition and description of the sensors has been included. In addition, a discussion on how the case the reviewer mentions could affect the system has been added, as:
 
-\textcolor{blue}{It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not.
+\textit{It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not.
 It might happen then that the user ignores this advice and the device becomes compromised.
@@
 
-4.
-Paper structure is really confusing.
-Many essential concepts are introduced and explained too late in the paper forcing the reader to go back and forth to understand the architecture (e.g.
-MUSES aware apps and Data Mining techniques).
-I suggest authors to deeply revise the presentation of their work.
+\begin{verbatim}
+4.      Paper structure is really confusing. Many essential concepts 
+are introduced and explained too late in the paper forcing the reader 
+to go back and forth to understand the architecture (e.g. MUSES aware 
+apps and Data Mining techniques). I suggest authors to deeply revise 
+the presentation of their work.
+\end{verbatim}
 
@@
 
-5.      A discussion on research activities on BYOD is completely missing. This is unacceptable for a solution that aims at solving BYOD security issues. Just to cite a few:
-a.      Gessner, Dennis, et al. "Towards a User-Friendly Security-Enhancing BYOD Solution." NEC Technical Journal 7.3 (2013): 113.
-b.      Samaras, Vasileios. A BYOD Enterprise Security Architecture for accessing SaaS cloud services. Diss. TU Delft, Delft University of Technology, 2013.
-c.      Armando, Alessandro, et al. "Enabling BYOD through secure meta-market." Proceedings of the 2014 ACM conference on Security and privacy in wireless and mobile networks. ACM, 2014.
+\begin{verbatim}
+5.      A discussion on research activities on BYOD is completely 
+missing. This is unacceptable for a solution that aims at solving 
+BYOD security issues. Just to cite a few:
+a.      Gessner, Dennis, et al. "Towards a User-Friendly 
+Security-Enhancing BYOD Solution." NEC Technical Journal 
+7.3 (2013): 113.
+b.      Samaras, Vasileios. A BYOD Enterprise Security Architecture 
+for accessing SaaS cloud services. Diss. TU Delft, Delft 
+University of Technology, 2013.
+c.      Armando, Alessandro, et al. "Enabling BYOD through secure 
+meta-market." Proceedings of the 2014 ACM conference on Security 
+and privacy in wireless and mobile networks. ACM, 2014.
+\end{verbatim}
 
-\textcolor{blue}{The reviewer is right.
+The reviewer is right.
 Although several works have been cited in other sections of the work, a proper discussion on research on BYOD was necessary.
@@
 These works have been also considered to propose the new taxonomy included in the paper (Section X, Page XX).
-These references are \cite{Garba15organisational,Scarfo12survey,Gessner13userfriendly,Armando14metamarket,Haejung12Door,Samaras13SaaS,Miller12Privacy,Romer14BestPractices}, and can be found at the end of this document.}
+These references are \cite{Garba15organisational,Scarfo12survey,Gessner13userfriendly,Armando14metamarket,Haejung12Door,Samaras13SaaS,Miller12Privacy,Romer14BestPractices}, and can be found at the end of this document.
 
-6.
-The experimental section is completely missing.
-Is MUSES able to identify security violations?
-Which are the computational cost for both the company (server) and users (mobile devices)?
-Are there any limitations?
+\begin{verbatim}
+6.      The experimental section is completely missing. Is MUSES 
+able to identify security violations? Which are the computational 
+cost for both the company (server) and users (mobile devices)? Are 
+there any limitations?
+\end{verbatim}
 
-\textcolor{blue}{We agree with what the reviwer remarks, and so we have included, at the end of the Introductiono section, the ratio of security violations detected by the system in a prototype trials period.
-Also, a little description of the conditions of the trials has been included, for we consider that a deep description of these trials is not in the scope of the paper.}
+We agree with what the reviewer remarks, and so we have included, at the end of the Introduction section, the ratio of security violations detected by the system in a prototype trials period.
+Also, a little description of the conditions of the trials has been included, for we consider that a deep description of these trials is not in the scope of the paper.
 
-Under such considerations I recommend authors for a *STRONG* major revision to cover the aforementioned points.
+\begin{verbatim}
+Under such considerations I recommend authors for a *STRONG* major 
+revision to cover the aforementioned points.
+\end{verbatim}
 
-\textcolor{blue}{The work has been deeply improved following the reviewer's suggestions. We would like to thank he/she for his/her careful revision and interesting comments.}
+The work has been deeply improved addressing all the reviewer's suggestions. We would like to thank he/she for his/her careful revision and interesting comments.
 
@@
 
-\begin{quotation}
-In this work authors present state-of-the art in BYOD solutions, and
-introduce a new solution, MUSES, a result of an EU FP7 project.
+\begin{verbatim}
+In this work authors present state-of-the art in BYOD solutions, 
+and introduce a new solution, MUSES, a result of an EU FP7 project.
 
@@
 in the market with the purpose to adapt to it in a secure way. 
-\end{quotation}
+\end{verbatim}
 
@@
 
-\begin{quotation}
+\begin{verbatim}
 The description of IBM products, in section 3.1, does not provide
@@
 \end{quotation}
+\end{verbatim}
 
@@
 
-\begin{quotation}
+\begin{verbatim}
 In section 3.3 (p.7, sentence in l.18-19) there is provided a
@@
 whether this statement is relevant for the scope of this work at all.
-\end{quotation}
+\end{verbatim}
 
@@
 
-\begin{quotation}
+\begin{verbatim}
 Section 3.6.1 covers WSO2, an open source tool that should be freely
@@
 clear therefore how this tool and MUSES differ. 
-\end{quotation}
+\end{verbatim}
 
@@
 
-Section 3.6.4 (p10, 44) states "are Worx-enable are capable". The meaning of this part is not clear, nor to which concept Worx refers.
+\begin{verbatim}
+Section 3.6.4 (p10, 44) states "are Worx-enable are capable". The 
+meaning of this part is not clear, nor to which concept Worx refers.
+\end{verbatim}
 
@@
 
-Basically, in section 3 the following possibilities for improvement are identified:
+\begin{verbatim}
+Basically, in section 3 the following possibilities for improvement 
+are identified:
 
- 1) Explain why particular solutions are chosen for inclusion in review and what is their relevance? Did authors consider other (possible) solutions relying on DM and CI?
+1) Explain why particular solutions are chosen for inclusion in review 
+and what is their relevance? Did authors consider other (possible) 
+solutions relying on DM and CI?
+\end{verbatim}
 
@@
 
- 2) Considering variety of BYOD tools and their different features, authors might consider to introduce or reuse a taxonomy or classification of those approaches, and state the place of MUSES there (or define a new subcategory, if deemed necessary)
+\begin{verbatim}
+ 2) Considering variety of BYOD tools and their different features, 
+authors might consider to introduce or reuse a taxonomy or 
+classification of those approaches, and state the place of MUSES 
+there (or define a new subcategory, if deemed necessary)
+\end{verbatim}
 
-\textcolor{blue}{Following the reviewer's suggestion we have introduced a taxonomy for the analyzed systems, according to the works that we have revised in the state of the art section.
-This taxonomy is described at the beginning of Section 3 (second paragraph, page XX).}
+Following the reviewer's suggestion we have introduced a taxonomy for the analyzed systems, according to the works that we have revised in the state of the art section.
+This taxonomy is described at the beginning of Section 3 (second paragraph, page XX).
 % Antonio - completar con el n˙mero de p·gina final
@@
 
- 3) Some presented solutions miss their relationship to MUSES (coverage, features, comparison).
-This point also refers to inconsistent coverage amongst solutions and weak arguments favouring MUSES.
-Either coverage should be more consistent by focusing on common (present or missing) aspects, or it should be elaborated why such coverage is missing.
-Also see the comment for discussion part bellow.
+\begin{verbatim}
+ 3) Some presented solutions miss their relationship to MUSES 
+(coverage, features, comparison). This point also refers to 
+inconsistent coverage amongst solutions and weak arguments 
+favouring MUSES. Either coverage should be more consistent by 
+focusing on common (present or missing) aspects, or it should 
+be elaborated why such coverage is missing. Also see the comment 
+for discussion part bellow.
+\end{verbatim}
 
@@
 
-On p.12, l.9-12 authors state that MUSES can be installed in every mobile or portable device, independently of the operating system and device type.
-This is also derived from the title "Multiplatform Usable Endpoint Security System".
-The authors however do not provide additional details on how is this achieved in the practice and are there any limitations in regards to that.
-How they managed to provide the same system for Android, Windows, iOS, PCs, without limitations?
-How MUSES manage the variety of OS versions and underlying platform features provided to the app?
-This feature is important differentiator against some other solutions and in opinion of this reviewer should be elaborated in more detail.
+\begin{verbatim}
+On p.12, l.9-12 authors state that MUSES can be installed in every 
+mobile or portable device, independently of the operating system 
+and device type. This is also derived from the title "Multiplatform 
+Usable Endpoint Security System".
+The authors however do not provide additional details on how is this 
+achieved in the practice and are there any limitations in regards to 
+that. How they managed to provide the same system for Android, Windows, 
+iOS, PCs, without limitations? How MUSES manage the variety of OS 
+versions and underlying platform features provided to the app? This 
+feature is important differentiator against some other solutions and 
+in opinion of this reviewer should be elaborated in more detail.
+\end{verbatim}
 
@@
 
-When stating (p.13, l.15-24) that MUSES relies on AES based symmetric encryption, does it mean that information flows in MUSES client internally, as well as client-server communication, are encrypted with the same key?
-Does MUSES uses client specific and/or temporal keys?
-What measures are taken to protect this key from malicious applications both on client and server side?
-How and where is this key generated?
-What is lifetime of the key?
-In my opinion this part should be reworked, providing more detailed description of security aspects of their approach.
-Also please see security related comment bellow.
+\begin{verbatim}
+When stating (p.13, l.15-24) that MUSES relies on AES based 
+symmetric encryption, does it mean that information flows in 
+MUSES client internally, as well as client-server communication, 
+are encrypted with the same key? Does MUSES uses client specific 
+and/or temporal keys? What measures are taken to protect this key 
+from malicious applications both on client and server side? How 
+and where is this key generated? What is lifetime of the key? In 
+my opinion this part should be reworked, providing more detailed 
+description of security aspects of their approach. Also please 
+see security related comment bellow.
+\end{verbatim}
 
@@
 
-On p.14, l.16-28 authors introduce the concepts of MUSES Aware App and MUSES API.
-In my opinion they should provide more details on integration options and necessary effort to make an application MUSES Aware.
-This is a crucial aspect of their approach as this requirement and related complexity might hinder the adoption of the solution.
+\begin{verbatim}
+On p.14, l.16-28 authors introduce the concepts of MUSES Aware 
+App and MUSES API. In my opinion they should provide more details 
+on integration options and necessary effort to make an application 
+MUSES Aware. This is a crucial aspect of their approach as this 
+requirement and related complexity might hinder the adoption of 
+the solution.
+\end{verbatim}
 
@@
 
-On p.17, l.7-9 authors state that the data sets can be huge, leading to necessity to apply Big Data processing methods.
-They however do not provide at least an indication of the data amount/complexity that is gathered and processed by the system, and at what rate it grows.
-Is it really necessary to employ Big Data processing?
+\begin{verbatim}
+On p.17, l.7-9 authors state that the data sets can be huge, 
+leading to necessity to apply Big Data processing methods. They 
+however do not provide at least an indication of the data 
+amount/complexity that is gathered and processed by the system, 
+and at what rate it grows. Is it really necessary to employ 
+Big Data processing?
+\end{verbatim}
 
@@
 
-On p.18, for two bullets announced under l.46-47 there is not clear if they are included in the refinement process or not.
-In the later case, it is suggested to explain why they are not present in the processing.
-Maybe these bullets could be moved into part relating to further work.
+\begin{verbatim}
+On p.18, for two bullets announced under l.46-47 there is not 
+clear if they are included in the refinement process or not. 
+In the later case, it is suggested to explain why they are not 
+present in the processing. Maybe these bullets could be moved 
+into part relating to further work.
+\end{verbatim}
 
@@
 
-From the presented concepts behind MUSES and its flows, it is not completely clear how it approaches "newly discovered vulnerabilities or threats" (p.20 l.27-28).
-It is hence suggested to clarify this statement and provide explanation to which extent is rule refinement and adaptation used to discover and address new vulnerabilities and threats in the software and systems.
+\begin{verbatim}
+From the presented concepts behind MUSES and its flows, it
+is not completely clear how it approaches "newly discovered 
+vulnerabilities or threats" (p.20 l.27-28). It is hence 
+suggested to clarify this statement and provide explanation 
+to which extent is rule refinement and adaptation used to 
+discover and address new vulnerabilities and threats in the 
+software and systems.
+\end{verbatim}
 
@@
 
+\begin{verbatim}
 Similar applies to human-computer interaction (p.20 l.34). 
-Although some details are provided in l.43-45 on the same page, in opinion of this reviewer, the statement about progress beyond the state of the art should be backed with more (stronger) details and data.
+Although some details are provided in l.43-45 on the same page, 
+in opinion of this reviewer, the statement about progress beyond 
+the state of the art should be backed with more (stronger) details 
+and data.
+\end{verbatim}
 
@@
 
-This reviewer would also suggest to provide more details on security aspect of the system.
-Some hints are provided in previous comments.
-Additionally, as the client/server interaction is concerned, what measures and aspects have been applied in order to identify and prevent malicious parties to manipulate or inject malicious rules in the system?
-By injecting such rules, the complete sub-network of clients of the company can be affected.
-Furthermore, author assumes that the clients are non-rooted devices.
-What happens, and at which extent can some rooted device affect local application of the system, and also central server and other clients?
+\begin{verbatim}
+This reviewer would also suggest to provide more details on 
+security aspect of the system. Some hints are provided in 
+previous comments. Additionally, as the client/server 
+interaction is concerned, what measures and aspects have 
+been applied in order to identify and prevent malicious 
+parties to manipulate or inject malicious rules in the system? 
+By injecting such rules, the complete sub-network of clients 
+of the company can be affected. Furthermore, author assumes 
+that the clients are non-rooted devices. What happens, and at 
+which extent can some rooted device affect local application 
+of the system, and also central server and other clients?
+\end{verbatim}
 
@@
 
-\begin{quotation}
+\begin{verbatim}
 For the section 5 and discussion, this reviewer would suggest to
@@
 contribute to clarity and position of the proposed solution. 
-\end{quotation}
+\end{verbatim}
 
@@
 needs. 
-
 % Antonio - TODO: M·s Tablas comparativas. øAntares, puedes hacerlas?
@@
 
-\begin{quotation}
+\begin{verbatim}
 Overall, this reviewer perceives this work as a good contribution in
@@
 suggestions. 
+\end{verbatim}
 
-\textcolor{blue}{We have addressed all the suggestions by the reviewer so we hope the work has been improved enough.}
+We have addressed all the suggestions by the reviewer so we hope the work has been improved enough.
 
+\begin{verbatim}
 Specific comments regarding organization and presentation:
 
-1) This work overuses forward slashes in linking words similar in concept or meaning.
-Although they are necessary in some situations, forward slashes very often link redundant words and reduce flow and readability of the text.
-They also contribute to the vagueness.
-I would suggest authors to review the text in this concern.
+1) This work overuses forward slashes in linking words similar in 
+concept or meaning. Although they are necessary in some situations, 
+forward slashes very often link redundant words and reduce flow and 
+readability of the text. They also contribute to the vagueness. I 
+would suggest authors to review the text in this concern.
+\end{verbatim}
 
-\textcolor{blue}{The reviewer is right. We have fixed this in the text omitting their use in those cases.}
+The reviewer is right. We have fixed this in the text omitting their use in those cases.
 
-2) Authors overuse parentheses to explain details.
-This hinders readability and text flow.
-The level of details provided and their relevance in the context are only partially consistent.
-On p.14 users introduce footnotes for additional details.
-Maybe they should consider applying such approach in other parts of the document as well.
+\begin{verbatim}
+2) Authors overuse parentheses to explain details. This hinders 
+readability and text flow. The level of details provided and their 
+relevance in the context are only partially consistent. On p.14 
+users introduce footnotes for additional details. Maybe they 
+should consider applying such approach in other parts of the 
+document as well.
+\end{verbatim}
 
-\textcolor{blue}{Following reviewer's suggestion we have rewritten the majority of the phrases where parentheses were used, avoiding them for the sake of a better text flow and reading.}
+Following reviewer's suggestion we have rewritten the majority 
+of the phrases where parentheses were used, avoiding them for 
+the sake of a better text flow and reading.
 
+\begin{verbatim}
 3) The structure and flow of the work can be improved.
+\end{verbatim}
 
-\textcolor{blue}{We have rewritten several parts of the paper and included new sections, subsections, tables and lists in order to improve the structure, contents and fluency of the text.}
+We have rewritten several parts of the paper and included new sections, subsections, tables and lists in order to improve the structure, contents and fluency of the text.
 % Antonio - Por favor, completad esta justificaciÛn mejor.
 
-\textcolor{blue}{We are very grateful to the reviewer for his/her useful comments and hope he/she will be satisfied with the revised work.}
+We are very grateful to the reviewer for his/her useful comments and hope he/she will be satisfied with the revised work.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Sección con los experimentos (Trials)
Para destacarlos más

@@
 % Antonio- muevo esta frase a un sitio más adecuado
-The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results, so we now have a clearer idea of its capabilities.
-Actually, the first trials of the system were performed with an Android prototype, and in two phases: \textit{silent} and \textit{verbose}, 1 month duration each.
-During the \textit{silent} phase, MUSES was able to gather data, but without warning the users when a security incident was happening.
-A total of 23358 security violations were detected.
-In the \textit{verbose}, MUSES started to show warning pop-ups to the users, every time a security incident happened.
-Not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 before the trials period finished.
-This has proven MUSES to be an effective tool.
+% Antonio - pongo aquí una frase resumida y el grueso de los experimentos (trials) en una sección aparte.
+The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results: the security incidents have been reduced exponentially from 23000 to 0 in just one month.
+So we now have a clear idea of its capabilities.
 Thus, in this paper we present an overview of the main existing solutions in the BYOD environment.
@@
  Both the inferred rules and the refined rules are presented to the CSO, who includes them or not in the system, and this acceptance or rejection acts itself as a feedback for future rule inference.
+
+% Antonio - pongo esto en una sección nueva para que destaque más. Es muy importante para los revisores. Por favor Paloma, revisa si lo que he puesto es correcto (número de usuarios y demás).
+\subsubsection{Trials and tests of MUSES}
+
+A MUSES first prototype, implemented on Android devices, has been tested recently.
+These trials have been conducted in an actual Spanish company (a partner in the European Project where the system is being developed), with 50 employees using the system on their own devices.
+The trials were divided in two phases: \textit{silent} and \textit{verbose}, 1 month duration each.
+During the \textit{silent} phase, MUSES was able to gather data, but without warning the users when a security incident was happening.
+A total of 23358 security violations were detected.
+In the \textit{verbose} stage, MUSES started to show warning pop-ups to the users, every time a security incident happened.
+
+As a results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 before the trials period finished.
+Thus, we can assume that MUSES is an effective tool.
 

### 2015-07-09 Response to reviewers - r2.tex
Cambios en las tablas y en las respuestas

@@
 
-We agree with the reviewer. A comparative table has been included in
-the section 5 (Table 1), summarizing some of the features of
-the presented systems and those of MUSES system. As it can be seen,
-all other systems are proprietary and have a cost, which makes MUSES
-unique in the sense that, being free software, can be adapted and
-extended by corporate security departments to the corporate special
-needs. 
-% Antonio - TODO: M·s Tablas comparativas. øAntares, puedes hacerlas?
-% Antonio - øquiz· una tabla con lo de la taxonomÌa y en quÈ categorÌa entra cada sistema?
+We agree with the reviewer. Two comparative tables have been included in
+section 5 (Table 1 and Table 2). They summarize some of the features of
+the presented tools and MUSES regarding the taxonomy we have described in the paper (Section 3); and also their features with respect to licenses, devices and prices.
+As it can be seen, MUSES is the most complete considering Table 1.
+Moreover, having a look at Table 2, all the other systems are proprietary and have a cost, which makes MUSES unique in the sense that, being free software, can be adapted and extended by corporate security departments to the corporate special needs.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Cambios en las tablas y en las respuestas

@@
 
+% ---------------------------------------------------
+
 % Antonio - pongo esto en una sección nueva para que destaque más. Es muy importante para los revisores. Por favor Paloma, revisa si lo que he puesto es correcto (número de usuarios y demás).
-\subsubsection{Trials and tests of MUSES}
+\subsection{Trials and tests of MUSES}
+\label{subsec:trials}
 
@@
 \begin{table}[ht]
-
+\begin{footnotesize}
   \centering
-  \renewcommand{\arraystretch}{1.8}% Spread rows out...
-  \resizebox{12cm}{!}{
-  \begin{tabular}{>{\centering\bfseries}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering}m{0.8in} >{\centering\arraybackslash}m{0.8in}}
+  \renewcommand{\arraystretch}{2.0}% Spread rows out...
+%  \resizebox{12cm}{!}{
+  \begin{tabular}{>{\centering\bfseries}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering\arraybackslash}m{0.6in}}
     \toprule
@@
     MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
-     \arrayrulecolor[gray]{0.8}\hline
+     \arrayrulecolor[gray]{0.6}\hline
     IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
-     \arrayrulecolor[gray]{0.8}\hline
+     \arrayrulecolor[gray]{0.6}\hline
     Sophos Mobile Control & \cmark & \xmark & \cmark & \xmark & \xmark \\
-     \arrayrulecolor[gray]{0.8}\hline
+     \arrayrulecolor[gray]{0.6}\hline
     Samsung Knox & \cmark & \nmark & \cmark & \nmark & \cmark\\
-     \arrayrulecolor[gray]{0.8}\hline
+     \arrayrulecolor[gray]{0.6}\hline
      Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \cmark\\
-     \arrayrulecolor[gray]{0.8}\hline
+     \arrayrulecolor[gray]{0.6}\hline
     Blackphone & \nmark & \nmark & \cmark & \cmark & \nmark\\
-     \arrayrulecolor[gray]{0.8}\hline
+     \arrayrulecolor[gray]{0.6}\hline
     Android for Work & \xmark & \xmark & \cmark & \xmark & \cmark\\
@@
   \end{tabular}
-  }
-  \caption{Proposed taxonomy to classify the BYOD tools described in this paper.}
+%  }
+\end{footnotesize}
+  \caption{Features of the analyzed tools regarding the proposed taxonomy to classify BYOD systems (see Section \ref{sec:toolsreview}).}
   \label{tab:taxonomy}
@@
 \begin{table}[ht]
-
+\begin{footnotesize}
   \centering
@@
        \midrule
-    MUSES & OpenSource &  & Free*  \\
+    MUSES & OpenSource &  & Free  \\
        \arrayrulecolor[gray]{0.8}\hline
@@
 %  }
+\end{footnotesize}
   \caption{Features of the analyzed products considering licenses, type of devices and price.}

### 2015-07-09 Response to reviewers - r2.tex
Eliminated parentheses from answers
And made some corrections. Closes #46

@@
 
-% Antonio - Voy a sustituir el Verbatim por un cambio de color en las respuestas porque al compilarlo no hace los saltos de lÌnea si no se los especificas y el texto se sale del margen.
+% Antonio - Voy a sustituir el Verbatim por un cambio de color en las
+% respuestas porque al compilarlo no hace los saltos de lÌnea si no se
+% los especificas y el texto se sale del margen. 
+% Es quotation, no verbatim, øno?
 
@@
 
-MUSES starts from a defined set of security rules that the CSO must define.
-Ideally, these rules should deal, in principle, all the potential security incidents that the company aims to detect.
-MUSES would be able to define new rules (by means of refinement) which could be labelled (i.e.
-assigned a decision) after the corresponding events have happened.
-However, it can also infer or create new rules, which the CSO must approve, using computational intelligence techniques.
-These rules could deal with unexpected situations (not previously happened).
+MUSES starts from a defined set of security rules that the CSO must
+define. Ideally, these rules should deal, in principle, with all the
+potential security incidents that the company aims to detect. MUSES
+would be able to define new rules by means of refinement which could
+be labelled, i.e. assigned a decision, after the corresponding events
+have happened. However, it can also infer or create new rules, which
+the CSO must approve, using computational intelligence
+techniques. These rules could deal with unexpected situations, which
+have not happened previously .
 
@@
 
-Moreover, MUSES offers visual analysis tools to the CSOs, which can aid (or guide) they to detect suspicious or anomalous patterns, and to study how to avoid these patterns becoming malicious to the company.
+Moreover, MUSES offers visual analysis tools to the CSOs, which can
+aid or guide them to detect suspicious or anomalous patterns, and to
+study how to avoid these patterns becoming malicious to the company.
 
-In order to clarify this we have rewritten and completed the second paragraph in section 4.1 (page XX). It is now:
+In order to clarify this we have rewritten and completed the second
+paragraph in section 4.1 (page XX). It is now:
 
@@
 current tools in comparison. 
-\end{quotation}
 \end{verbatim}

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Revised intro refs #7

@@
 because of the so-called Internet of Things
-\cite{weber2010internet}. Thanks to it, users have more flexibility,
-and also at their works, because now they can use their devices to
+\cite{weber2010internet}. Thanks to it, users have more flexibility
+since they can now use their devices to
 access company assets and continue working outside of the
-workplace. To allow this way of working, companies started to adopt
+workplace. To allow this way of working, companies have started to adopt
 what has been called the Bring Your Own Device (BYOD) philosophy.
 
-Data security and privacy are key factors for a company, and thus, in
+But data security and privacy are key factors for a company, and thus, in
 order to protect them, it is usual that the Chief Security Officer (CSO) of a company defines a set of Organizational Security
-Policies \cite{Opp_Security11}.
-However, allowing a BYOD environment means to take care of the risks that the use of personal devices can bring to the company \cite{gangula2013survey}.
-For instance, the mixture between personal and professional information in these devices would allow the user to navigate inside social networks, where important data could be leaked in the event of a security incident.
-
-In this scenario several solutions have appeared in order to manage corporate security.
-Most of the solutions are focused for both smartphones and desktop PCs, although some are implemented for a certain platform.
-However, almost all of them try to be non-intrusive -with regard to users' personal data-, friendly, and easy to use.
-
-Moreover, it has been demonstrated that employees who ignore company security policies are the main hazard for company security \cite{Adams_Users05}.
-In this situation, the tools that are appearing in the market aim to cope with the concept of seamless working experience on different devices.
-This concept is a methodology of work which allows users to start, or continue a working session, over multiple devices and locations, without any significant loss of data.
-This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since company data borders have changed in the last years.
-Therefore, now the users can access important data from outside the enterprise, and possibly through a non completely secure channel.
-%Antares - Yo quitaba lo de significant loss of data, ya que significant se repite después.
+Policies \cite{Opp_Security11}; allowing a BYOD environment implies
+taking care of the risks that the use of personal devices can bring to
+the company \cite{gangula2013survey}. For instance, the mixture
+between personal and professional information in these devices would
+allow the user to navigate inside social networks, where important
+data could be leaked in the event of a security incident.
+
+In this scenario several solutions that manage corporate security have
+appeared. Most of them are geared for both smartphones and desktop
+PCs, although some are implemented only for a certain platform. However,
+almost all of them try to be non-intrusive with regards to users'
+personal data, friendly, and easy to use.
+
+Even with the help of those solutions, it has been demonstrated that
+employees who ignore company security policies are the main hazard for
+company security \cite{Adams_Users05}. In this situation, the tools
+that are appearing in the market aim to cope with the concept of
+seamless working experience on different devices. This concept is a
+methodology of work which allows users to start, or continue a working
+session, over multiple devices and locations, without any significant
+loss of data. This new situation has a big impact from the point of
+view of the security \cite{Schu_SecPatterns05}, since company data
+borders have changed in the last years. Therefore, now the users can
+access important data from outside the enterprise, and possibly
+through a non completely secure channel. %Antares - Yo quitaba lo de
+                                %significant loss of data, ya que
+                                %significant se repite después. 
 %Cambiado
@@
 the implementation was in its early stages when those papers were
-published.
-Also, an additional work on applying data mining and machine learning techniques was conducted in \cite{mora14:urls}.
-It presented a study over a dataset similar to those that MUSES manages, but not the same, since the prototype of MUSES had not still been released.
+published. Also, an additional work on applying data mining and
+machine learning techniques was conducted in \cite{mora14:urls}. This
+last paper presented a study over a dataset similar to those that MUSES manages, but not the same, since the prototype of MUSES had not still been released.
 Thus, a set of URL connection logs were provided by a Spanish security company, % [Pedro] quizás decir que es una empresa de seguridad o algo así % Añadido, gracias!
@@
 
-The rest of the paper is organized as follows.
-First, some background situation about enterprise security is presented in Section \ref{sec:preliminaryconcepts}, explaining how BYOD philosophy affects it.
-The main solutions or tools are detailed in Section \ref{sec:toolsreview}, even if they are still in development.
-Section \ref{sec:muses} presents the Multi-platform Usable Endpoint Security System, with its architecture and the soft computing techniques it makes uses of.
-Advantages and benefits of the proposed system are compared to other solutions found in bibliography in Section \ref{sec:comparison}.
-Finally, the reached conclusions are discussed in Section \ref{sec:conclusions}, followed by future work.
+The rest of the paper is organized as follows. First, some background
+material about enterprise security is presented in Section
+\ref{sec:preliminaryconcepts}, explaining how the BYOD philosophy
+affects it. The main solutions or tools available or in development
+are detailed in Section \ref{sec:toolsreview}.
+Section \ref{sec:muses} presents the Multi-platform Usable Endpoint
+Security System, with its architecture and the soft computing
+techniques it makes uses of. Advantages and benefits of the proposed
+system are compared to other solutions found in bibliography in
+Section \ref{sec:comparison}. 
+Finally, the reached conclusions are discussed in Section
+\ref{sec:conclusions}, followed by future work.
 

### 2015-07-09 Response to reviewers - r2.tex
Paper structure revised
And specific comments by the reviewer addressed. Closes #26.

@@
 
-\textcolor{blue}{TODO}
+The paper structure has been completely redefined, with an introducion
+that presents the work, a section that introduces preliminary concepts
+followed by the state of the art in corporate mobile security and,
+eventually, the description of the framework that is the main point of
+the paper. Changes have been too extensive to include here, but great
+care has been taken to talk about concepts only when defined
+previously. For instance, the concept of MUSES-Aware apps is now
+introduced in the context of the API in section 3.5 and only used
+later on, from Section 3.6.4, in the context of other tool. The
+concept of data
+mining is presented along with machine learning in section 4.3.1.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Paper structure revised
And specific comments by the reviewer addressed. Closes #26.

@@
 For example, in \cite{Armando14metamarket} a meta-market application is used to supervise the installation of new applications, using static analysis and code instrumentation techniques, taking into account the organizational security policies.
-A meta-market prototype is tested with Google Play market using a real world BYOD security policy \footnote{The US Government BYOD security guidelines}.
+A meta-market prototype is tested with Google Play market using a real world BYOD security policy \footnote{The US Government BYOD security guidelines.}.
 
@@
 IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure.
-They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognize new vulnerabilities - or threats - with enough accuracy.
+They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognize new vulnerabilities or threats with enough accuracy.
 
@@
 MUSES has been compared to other existing solutions with a similar aim: enduring the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
-Main advantages of MUSES with respect to the other solutions have been discussed, remarking its advances beyond the state of the art that define these tools.
+The main advantages of MUSES with respect to the other solutions have
+been discussed, remarking its advances beyond the state of the art
+that define these tools. %¿El estado del arte que define a estas
+                         %herramientas? ¿Qué es eso? - JJ
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Filling and finishing @deantares tables. Closes #37

@@
      \arrayrulecolor[gray]{0.6}\hline
-    Samsung Knox & \cmark & \nmark & \cmark & \nmark & \cmark\\
+    Samsung Knox & \cmark & \xmark & \cmark & \cmark & \cmark\\
      \arrayrulecolor[gray]{0.6}\hline
-     Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \cmark\\
+     Blackbery Balance & \xmark & \xmark & \cmark & \cmark & \cmark\\
      \arrayrulecolor[gray]{0.6}\hline
-    Blackphone & \nmark & \nmark & \cmark & \cmark & \nmark\\
+    Blackphone & \nmark & \nmark & \cmark & \cmark & \cmark\\
      \arrayrulecolor[gray]{0.6}\hline
-    Android for Work & \xmark & \xmark & \cmark & \xmark & \cmark\\
+    Android for Work & \cmark & \xmark & \cmark & \cmark & \cmark\\
     \bottomrule
@@
 \end{footnotesize}
-  \caption{Features of the analyzed tools regarding the proposed taxonomy to classify BYOD systems (see Section \ref{sec:toolsreview}).}
+  \caption{Features of the analyzed tools with regard to the proposed taxonomy to classify BYOD systems (see Section \ref{sec:toolsreview}).}
   \label{tab:taxonomy}
@@
        \midrule
-    MUSES & OpenSource &  & Free  \\
+    MUSES & OpenSource & Android, Windows 8.1, Windows Phone, iOS & Free  \\
        \arrayrulecolor[gray]{0.8}\hline
@@
 \end{footnotesize}
-  \caption{Features of the analyzed products considering licenses, type of devices and price.}
+  \caption{Features of the analyzed products considering licenses, type of devices and OS, and price.}
   \label{tab:features}

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Reviewing @amorag new section 4, and completing with limitations. Closes #24

@@
 
-A MUSES first prototype, implemented on Android devices, has been tested recently.
-These trials have been conducted in an actual Spanish company (a partner in the European Project where the system is being developed), with 50 employees using the system on their own devices.
+A MUSES first prototype, implemented for Android devices, has been recently tested.
+These trials have been conducted in an actual Spanish company, with 50 employees using the system on their own devices.
+% He quitado "(a partner in the European Project where the system is being developed)" porque creo que es irrelevante, y si no se puede redactar de manera que esté fuera de los paréntesis, no debería estar.
 The trials were divided in two phases: \textit{silent} and \textit{verbose}, 1 month duration each.
@@
 
-As a results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 before the trials period finished.
-Thus, we can assume that MUSES is an effective tool.
+As results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 even before the trials period finished.
+Thus, we can assume that MUSES is an effective tool, even though it has the aforementioned limitation of needing an initial set of defined rules to start working.
+For this, MUSES also includes a set of guidelines for the companies to build adequate security policies.
+For instance, the set of initially defined rules used for the trial included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.
 

### 2015-07-09 Response to reviewers - r2.tex
Mejorando la respuesta al primer revisor (#2)
Completada con más cosas. Mirad si podéis añadir algo más.

@@
 
-% Antonio - Voy a sustituir el Verbatim por un cambio de color en las
-% respuestas porque al compilarlo no hace los saltos de lÌnea si no se
-% los especificas y el texto se sale del margen. 
 % Es quotation, no verbatim, øno?
+% Antonio - con quotation no se distinguÌa bien el texto del revisor y el de la respuesta. SÛlo hacÌa un sangrado. Creo que asÌ se ve mejor.
 
@@
 \begin{itemize}
-\item We have described in a more detailed way our previously published papers in this scope, clarifying the differences and contributions of this work with respect to them.
-\item Section 2 has been deeply improved adding a much more complete State of the Art in the scope of this work... 
+\item We have described in a more detailed way our previously published papers in this scope (in Section 1), clarifying the differences and contributions of this work with respect to them.
+\item Section 2 has been deeply improved adding a much more complete state of the art in the scope of this work.
+To this end, several works have been read and commented in that section and along the text.
 % Antonio - TODO: Fergu, completa esto t˙ que tienes la idea global de lo nuevo en el SotA, por favor.
-%The reviewer can see the set of new references added by the end of this response letter.
-New references added after the review can be found at the end of this document
-\item The description of MUSES system has been improved.
+New references added after the review can be found at the end of this letter.
+
+\item Section 3 has been rewritten in a big part, including a new taxonomy for the analyzed systems at the beginning of the section.
+Some new tools have been revised and better classified considering the defined taxonomy.
+% Antonio - TODO: extender esto de la secciÛn 3 y 5 un poco m·s.
+
+\item The description of MUSES system has been also improved.
 Several points have been clarified and better explained in Section 4.
 Moreover, a prototype of the system has been tested in an actual company with success, according to the obtained results.
-This is also commented by the end of that section.
-% Antonio - TODO: Revisar que esto se haya dicho/hecho en el paper
-\item Section 3 has been rewritten in a big part, including a new taxonomy for the analyzed systems, along with a better comparison with MUSES in Section 5.
-% Antonio - TODO: extender esto de la secciÛn 3 y 5 un poco m·s.
-\item A complete proof-editing process has been done, reviewing the English grammar and rewriting several paragraphs for a better comprehension.
+This is explained in the new Section 4.4 (page XX), where the results of some trials are presented.
+
+\item Section 5 has been also completed and enhanced with respect to previous version.
+It includes a better comparison between MUSES and the rest of tools.
+Two new tables (1 and 2) have been added summarizing the main features of the systems, for the sake of clarity.
+
+\item A complete proof-editing process has been done, reviewing the English grammar and rewriting several paragraphs for a better comprehension and flow.
+
 \end{itemize}
 % Antonio - TODO: AÒadir m·s cosas (medianamente relevantes) que se hayan hecho
-%
-These changes are better described in the responses to the others reviewers, so we encourage this reviewer to read them to have a better idea of their impact in the new version of the manuscript.
+
+These changes are better described in the responses to the others reviewers, so we strongly suggest this reviewer to read them to have a better idea of their impact in the new version of the manuscript.
 

### 2015-07-09 Response to reviewers - r2.tex
Cambios en el artículo propuesto por @fergunet
Y un par de correcciones tontas

@@
 
-These changes are better described in the responses to the others reviewers, so we strongly suggest this reviewer to read them to have a better idea of their impact in the new version of the manuscript.
+These changes are better described in the responses to the others reviewers, so we strongly suggest this reviewer to read them in order to have a better idea of their impact in the new version of the manuscript.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Cambios en el artículo propuesto por @fergunet
Y un par de correcciones tontas

@@
 %FERGU: citad este trabajo cuando digáis que es bueno no modificar el OS
+% Antonio - hecho.
 
@@
 Usually, they can be accessed through the OS.
-But the type of information to gather from them and also the type of actions to do over them strongly vary depending on the OS.
+But the type of information to gather from them and also the type of actions to do over them strongly vary depending on the OS, which should not be modified according to  \cite{Gessner13userfriendly}.
 As was already mentioned, when MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user.

### 2015-07-09 Response to reviewers - r2.tex
Cambios en el paper y en las revisiones
Con comentarios

@@
 
-The paper structure has been completely redefined, with an introducion
+The paper structure has been completely redefined, with an introduction
 that presents the work, a section that introduces preliminary concepts
@@
 previously. For instance, the concept of MUSES-Aware apps is now
-introduced in the context of the API in section 3.5 and only used
+introduced in the context of the API in Section 3.5 and only used
 later on, from Section 3.6.4, in the context of other tool. The
-concept of data
-mining is presented along with machine learning in section 4.3.1.
+concept of data mining is presented along with machine learning in section 4.3.1. 
+We have also added some tables (in Section 5) as an additional summary of information, for the sake of clarity.
 
@@
 
-We agree with what the reviewer remarks, and so we have included, at the end of the Introduction section, the ratio of security violations detected by the system in a prototype trials period.
-Also, a little description of the conditions of the trials has been included, for we consider that a deep description of these trials is not in the scope of the paper.
+We agree with what the reviewer remarks, and so we have created a new Section (4.4, in page XX), describing the trials that have been conducted with the first prototype of MUSES.
+In that section there are commented the ratio of security violations detected and how the system has influenced in the complete reduction of this number to 0.
+This has been also commented in the Introduction of the paper.
+
+The main limitation of MUSES, also commented in Section 4.4, is the need of an initial set of defined security rules to start working.
+The other limitation comes from the set of deployed sensors, which are the only source of data for the system, so it cannot manage security violations happened by different ways.
+
+To avoid this in part, there is a set of guidelines for the companies to build adequate security policies.
+For instance, the set of initially defined rules used for the trial included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.
+
+\textcolor{blue}{TODO - computational costs?
+Al menos en el cliente, y la correlaciÛn + risk and trust en el servidor, ya que no se ha llegado a aplicar lo del KRS.
+Aunque sea muy aproximado (segundos, milisegundos)}
 
@@
 
-Following the reviewer's suggestion we have introduced a taxonomy for the analyzed systems, according to the works that we have revised in the state of the art section.
+Following the reviewer's suggestion we have introduced a taxonomy for the analyzed systems, according to the works that we have revised in the state of the art (Section 2).
 This taxonomy is described at the beginning of Section 3 (second paragraph, page XX).
+All the tools have been included in the types defined by the taxonomy.
 % Antonio - completar con el n˙mero de p·gina final

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Cambios en el paper y en las revisiones
Con comentarios

@@
 On the contrary, the MUSES system proposed in this work is designed as device-independent.
-Furthermore, the lack of information about this system makes difficult to determine its real qualities.
+Furthermore, the lack of information about this system makes it difficult to determine its real qualities.
 
@@
 
-\begin{description}
-  \item[Connectivity sensor:] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
+% Antonio - pongo esto como lista de items, ya que era la única lista diferente
+\begin{itemize}
+  \item \textit{Connectivity sensor:} It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item[Device protection sensor:] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
+  \item \textit{Device protection sensor:} Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
 This security mechanism adds the possibility of detecting security violations even if the user is not doing a specific action.
-  \item[Location sensor:] User location can be obtained using the device GPS.
+  \item \textit{Location sensor:} User location can be obtained using the device GPS.
 Although, this might be taken against the preservation of user privacy.
 This is why MUSES allows the definition of a number of `zones', and therefore it only checks if the user is inside them or not, acting in consequence.
-  \item[Mail sensor:] If the user is writing an email, MUSES client sensor can also check the email attributes.
+  \item \textit{Mail sensor:} If the user is writing an email, MUSES client sensor can also check the email attributes.
 Thus, it can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
@@
 ¿Cómo lo veis?
-  \item[File sensor:] The type of file, also called \textit{asset}, is also very important for the application of security rules.
+  \item \textit{File sensor:} The type of file, also called \textit{asset}, is also very important for the application of security rules.
 Thus, this sensor aims to detect if some files might need more strict security policies, also depending on the rest of sensors.
-  \item[App sensor:] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
+  \item \textit{App sensor:} It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
 Additionally, this sensor gathers information about the applications which the user tries to install or uninstall.
-\end{description}
+\end{itemize}
 
@@
 As results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 even before the trials period finished.
-Thus, we can assume that MUSES is an effective tool, even though it has the aforementioned limitation of needing an initial set of defined rules to start working.
+Thus, we can assume that MUSES is an effective tool, even though it has the aforementioned limitation of needing an initial set of defined security rules to start working.
 For this, MUSES also includes a set of guidelines for the companies to build adequate security policies.
@@
        \arrayrulecolor[gray]{0.8}\hline
-    IBM Mobile Security & Proprietary & IOS, Android, Windows Phone, Blackberry  &  By Request\\\\
+    IBM Mobile Security & Proprietary & iOS, Android, Windows Phone, Blackberry  &  By Request\\\\
         \arrayrulecolor[gray]{0.8}\hline
-    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
+    Sophos Mobile Control & Proprietary & iOS, Android, Windows Phone  &  By Request\\
         \arrayrulecolor[gray]{0.8}\hline
-    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
+    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and iOS & 12\$ per year/device \\
         \arrayrulecolor[gray]{0.8}\hline

### 2015-07-09 Response to reviewers - r2.tex
Respuestas al segundo revisor completas también
Y nuevas cosas en el artículo

@@
 
-Include an overview of all changes made in the paper.
 \end{verbatim}
@@
 The new references can be consulted b the end of this letter.
+
+In addition to this, we have addressed all the requests and suggestions by the reviewers. The responses are included below in this document.
 
@@
 potential security incidents that the company aims to detect. MUSES
-would be able to define new rules by means of refinement which could
+would be able to define new rules, by means of refinement, which could
 be labelled, i.e. assigned a decision, after the corresponding events
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{TODO - Justificar su valÌa.
+Las empresas querr·n MUSES y querr·n que sus empleados utilicen MUSES-Aware Apps porque les garantizar·n un control sobre lo que se hace en la empresa y los posibles incidentes de seguridad.}
+
+With respect to the experimental results, a new section (4.4, in page XX) has been included describing some trials conducted in an actual company, using a prototype of MUSES on Android devices.
+The results show the effectiveness of this system, which has roughly reduced from 23000 security violations in the first stages to 0 in a few weeks.
+
+% Antonio - completar algo m·s, si alguien quiere
 
@@
 
-A more detailed definition and description of the sensors has been included. In addition, a discussion on how the case the reviewer mentions could affect the system has been added, as:
+To clarify this point, a more detailed definition and description of the sensors has been included in Section 4.1 (page XX).
+In addition, a discussion on how the case the reviewer mentions could affect the system has been added just below the list of sensors, as:
 
@@
 
-The paper structure has been completely redefined, with an introduction
-that presents the work, a section that introduces preliminary concepts
-followed by the state of the art in corporate mobile security and,
-eventually, the description of the framework that is the main point of
-the paper. Changes have been too extensive to include here, but great
+Following the reviewer's suggestion, the paper structure has been redefined, with an introduction that presents the work, a section that introduces preliminary concepts followed by the state of the art in corporate mobile security and, eventually, the description of the framework that is the main point of the paper.
+Changes have been too extensive to include here, but great
 care has been taken to talk about concepts only when defined
@@
 We have also added some tables (in Section 5) as an additional summary of information, for the sake of clarity.
+
+% Antonio - Mejorar un poco esta justificaciÛn, si hay tiempo
 
@@
 Although several works have been cited in other sections of the work, a proper discussion on research on BYOD was necessary.
-Therefore, we have analysed the papers suggested by the reviewer, along with several new relevant ones.
-These new references also have been also cited in other sections of the work to justify MUSES features; for example, the set of best practices for BYOD security proposed by H.
+Therefore, we have analysed the papers suggested by the reviewer, along with several new relevant ones in Section 2 (page XX).
+These new references have been also cited in other sections of the work in order to justify MUSES features; for example, the set of best practices for BYOD security proposed by H.
 Romer.
-These works have been also considered to propose the new taxonomy included in the paper (Section X, Page XX).
+
+These works have been also considered to propose the new taxonomy included in the paper (beginning of Section 3, page XX).
 These references are \cite{Garba15organisational,Scarfo12survey,Gessner13userfriendly,Armando14metamarket,Haejung12Door,Samaras13SaaS,Miller12Privacy,Romer14BestPractices}, and can be found at the end of this document.
@@
 The main limitation of MUSES, also commented in Section 4.4, is the need of an initial set of defined security rules to start working.
-The other limitation comes from the set of deployed sensors, which are the only source of data for the system, so it cannot manage security violations happened by different ways.
+The other limitation comes from the set of deployed sensors, which are the only input of data in the system, so it cannot manage security violations happened by different ways.
 
@@
 
-\textcolor{blue}{TODO - computational costs?
-Al menos en el cliente, y la correlaciÛn + risk and trust en el servidor, ya que no se ha llegado a aplicar lo del KRS.
-Aunque sea muy aproximado (segundos, milisegundos)}
+With respect to the computational costs, in this first prototype they are around 0.3 - 0.5 seconds in the client side, if there is already a decision in the local table for the event.
+If there is need to ask the server to make a decision (by means of Event Correlation + Risk and Trust Analysis), the time grows up to 2 - 2.5 seconds in the worst case.
+This has been also commented in Section 4.4.
+
+% Antonio - completo con cifras que me ha dado Sergio.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Respuestas al segundo revisor completas también
Y nuevas cosas en el artículo

@@
 For instance, the set of initially defined rules used for the trial included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.
+
+With respect to the computational costs, in this first prototype it takes less than 0.5 seconds in the client side, if there is already a decision in the local table for the happened event.
+Otherwise, i.e.
+if there is need to ask the server to make a decision (by means of Event Correlation + Risk and Trust Analysis), the time grows up to 2.5 seconds in the worst case.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Changed all British words to the colonies barbaric language (aka American)

@@
 set of security rules defined as specifications of the Corporate
-Security Policies. In addition, it has the ability of `learning' from the user's past behaviour and adapt the set of existing rules, or even inferring new ones,
+Security Policies. In addition, it has the ability of `learning' from the user's past behavior and adapt the set of existing rules, or even inferring new ones,
 in order to deal with potential security incidents that users might cause in the future. 
@@
 
-To this end, MUSES analyses the users' behaviour by means of Data
+To this end, MUSES analyses the users' behavior by means of Data
 Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
@@
 With regard to compliance enforcement, the main goal of this Mobile Control tool is to give more importance to company security, instead of giving more flexibility to the users.
-But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behaviour, even if it was not on purpose.
+But it has been demonstrated by Herath and Rao in \cite{SecPolPenalty09} that this practise can result in bad users' behavior, even if it was not on purpose.
 Thus, the company BYOD initiative should include an acceptable use policy to ensure that the users are aware of the measures that the company would take if a device breaches any ISPs.
@@
 
-Althoug this tool also includes features such as device location, remote wipe, or encrypt storage, its main disadvantage is that it does not work in offline mode.
+Although this tool also includes features such as device location, remote wipe, or encrypt storage, its main disadvantage is that it does not work in offline mode.
 In the documentation \footnote{\url{https://docs.wso2.com/display/EMM200/Working+with+Policies}}, it is clearly stated that the policy compliance can be monitored while the devices are connected to the WSO2 EMM server.
@@
 A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorized devices, or for providing access to secure collaboration solutions (email, documents, calendar), the intranet, and both in-house or third-party mobile applications.
-Finally, Good offers best practise recommendations to help the company developing BYOD policies.
+Finally, Good offers best practice recommendations to help the company developing BYOD policies.
 A document can be accessed from Good's webpage \cite{Good_tool}, which contains several questions about ISPs and how to cope with all of them.
@@
 As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}.
-The former consists of a number of implemented \textit{sensors} in the device, which monitor the environment and the users' behaviour \footnote{Which has been introduced as the `context' of an event.}.
+The former consists of a number of implemented \textit{sensors} in the device, which monitor the environment and the users' behavior \footnote{Which has been introduced as the `context' of an event.}.
 Then, the user's actions, as well as device configuration, or connection properties, are translated into a sequence of events.
@@
 % Antonio - "values of the assets"
-  \item  The \textit{Privacy Enhancing System}, which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system.
+  \item  The \textit{Privacy Enhancing System}, which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymization and retaining of these data in the system.
 There are three important points with relation to this matter \cite{deliverable72}.
@@
 Then, the model learns from events that, according to the ISPs, had been previously marked as `allowed' or `denied'.
-When a new event arrives to the server, if it has not an assigned decision, the classifier should provide one based on the similarity with previous, and already labelled, patterns.
+When a new event arrives to the server, if it has not an assigned decision, the classifier should provide one based on the similarity with previous, and already labeled, patterns.
 
@@
 \item \textit{Data Analysis}: 
-This provides the CSO with mechanisms to visualize interesting facts about the data, such as most frequent events, dangerous or suspicious users according to their behaviour, most triggered rules, etc.
+This provides the CSO with mechanisms to visualize interesting facts about the data, such as most frequent events, dangerous or suspicious users according to their behavior, most triggered rules, etc.
 All this information is shown to the CSO via the mentioned graphical interface, implemented in the server.
@@
 
-\item User-related information, and context information in general, corresponding to those anomalous or unlabelled events.
+\item User-related information, and context information in general, corresponding to those anomalous or unlabeled events.
 Thus, the user's location zone, role, or device settings, for instance, can be considered in order to select the applicable set of rules for those conditions.
@@
 
-\item The information about the user behaviour with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
+\item The information about the user behavior with respect to system messages, whether the users acts in consequence or against MUSES advice, as well as user feedback.
 The user feedback has been measured in the MUSES trials by making interviews with the people who have used MUSES, but it can also be measured by pop-up messages, such as ``has this information been useful?''.
@@
 The evaluation of these rules is done by considering the information that has been described.
-Thus, it is possible to `simulate' the whole system behaviour when the new rule is included.
+Thus, it is possible to `simulate' the whole system behavior when the new rule is included.
 Therefore, the system gets a value of its performance in terms of, for instance, how many of the events that were not classified or misclassified, are covered now.
@@
 
-With regard to the scientific contribution of the system, one of the main differences with respect to previous works is the consideration of security threats `brought' by the user's behaviour inside the system, i.e.
+With regard to the scientific contribution of the system, one of the main differences with respect to previous works is the consideration of security threats `brought' by the user's behavior inside the system, i.e.
 through interaction or events, rather than more general and external threats.

### 2015-07-09 Response to reviewers - r2.tex
Rewriting data security paragraph and writing response to remark ir. Closes #36

@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We agree with the reviewer about this paragraph not being clear, which is why it has been rewritten and clarified.
+At the end of the introduction of Section 4 (page XX) we have improved the explanation about MUSES data security and authentication.}
+
+\textcolor{blue}{The MUSES system also performs an authentication process when the user logs in.
+The MUSES server authenticates to the MUSES client by means of a self-signed certificate.
+The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications.
+When the user connects to the MUSES server for the first time, the MUSES client asks the server for the cerfiticate, wich is sent and installed in the client local database if the user credentials are right.
+As the user credentials are also stored in the MUSES client local database, the user can also log in to MUSES, and it therefore can apply the Device Policies.
+With regard to internal data security, MUSES makes use of the advantages that the OSs themselves offer to developers.
+More concretely, the first prototype for Android includes functionalities provided by the Android Application Sandbox \cite{blasing2010android}.
+This means that other applications cannot access MUSES data, nor even other developers.
+The only way to do this is by rooting the device, which is a state that MUSES can detect, and therefore warn about its implications.
+With regard to the encryption of the rest of the device data, MUSES stands for having a security policy which advices about the installation of existing open source tools \footnote{For instance, \url{https://github.com/neurodroid/cryptonite/blob/master/README.md}}, instead of having an own implementation.}
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Rewriting data security paragraph and writing response to remark ir. Closes #36

--- 2015-07-09 MUSES_vs_BYOD_solutions.tex
@@
 
-All flows of information in MUSES are encrypted using AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations of the Fact Sheet on Suite B Cryptography \cite{salter2012suite}.
-Also, the MUSES server authenticates to the MUSES client by means of a self-signed certificate.
+The MUSES system also performs an authentication process when the user logs in.
+The MUSES server authenticates to the MUSES client by means of a self-signed certificate.
 The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications.
-And finally, MUSES makes use of the fact that current OS for mobile devices provide encrypted data containers by default, like the feature used in Android Work.
+When the user connects to the MUSES server for the first time, the MUSES client asks the server for the cerfiticate, wich is sent and installed in the client local database if the user credentials are right.
+As the user credentials are also stored in the MUSES client local database, the user can also log in to MUSES, and it therefore can apply the Device Policies.
+With regard to internal data security, MUSES makes use of the advantages that the OSs themselves offer to developers.
+More concretely, the first prototype for Android includes functionalities provided by the Android Application Sandbox \cite{blasing2010android}.
+This means that other applications cannot access MUSES data, nor even other developers.
+The only way to do this is by rooting the device, which is a state that MUSES can detect, and therefore warn about its implications.
+With regard to the encryption of the rest of the device data, MUSES stands for having a security policy which advices about the installation of existing open source tools \footnote{For instance, \url{https://github.com/neurodroid/cryptonite/blob/master/README.md}}, instead of having an own implementation.
 
@@
 For this, MUSES also includes a set of guidelines for the companies to build adequate security policies.
-For instance, the set of initially defined rules used for the trial included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.
+For instance, the set of initially defined rules used for the trials included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Including WHY did we chose these tools

@@
 Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art.
+The products that have been reviewed were chosen either because they have appeared in top-10 web articles \footnote{\url{http://www.networkworld.com/article/2357899/data-center/108866-10-Mobile-Device-Management-Leaders-That-Help-IT-Control-BYOD.html#slide11}}, or they have been developed for the main smartphone platforms \footnote{\url{http://www.idc.com/prodserv/smartphone-os-market-share.jsp}}.
+Actually, the selection process have been diffiicult, as some of the initially found tools or companies in the web were bought by others that we do review here.
+Also, because this market is still growing, there are not many solutions to review, and here we display the ones more alike to MUSES.
 This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.

### 2015-07-09 Response to reviewers - r2.tex
Addressing some @amorag questions in response letter for issue #40

--- 2015-07-09 Response to reviewers - r2.tex
@@
 \item Section 2 has been deeply improved adding a much more complete state of the art in the scope of this work.
-To this end, several works have been read and commented in that section and along the text.
-% Antonio - TODO: Fergu, completa esto t˙ que tienes la idea global de lo nuevo en el SotA, por favor.
+To this end, several research works have been read and commented in that section and along the text.
+This has helped us to better compare our system against the other products available in the market.
+Also, an analysis of the best practices for BYOD have been applied for each product and our system.
+% Antonio - TODO: Fergu, completa esto t˙ que tienes la idea global de lo nuevo en el SotA, por favor. FERGU: Hecho. Metido tambiÈn lo de las best practices
 New references added after the review can be found at the end of this letter.
@@
 \item Section 3 has been rewritten in a big part, including a new taxonomy for the analyzed systems at the beginning of the section.
-Some new tools have been revised and better classified considering the defined taxonomy.
-% Antonio - TODO: extender esto de la secciÛn 3 y 5 un poco m·s.
+This taxonomy has been created taking into account the expertise extracted from the new references of the state of the art, such as the best practices by Romer \cite{Romer14BestPractices} or the hands-off/hands-on classification by Scarfo et al.
+\cite{Scarfo12survey}, among others.
+Furthermore, some new tools have been added, and all the products have been better classified considering the defined taxonomy.
+% Antonio - TODO: extender esto de la secciÛn 3 y 5 un poco m·s. FERGU: Done
 
@@
 would be able to define new rules, by means of refinement, which could
-be labelled, i.e. assigned a decision, after the corresponding events
+be labeled, i.e. assigned a decision, after the corresponding events
 have happened. However, it can also infer or create new rules, which
@@
 \textit{However, MUSES presents a limitation regarding the enhancement of rules, since, in principle, it cannot predict (generate rules for dealing with) unexpected or unknown events which could lead to a security incident.
-The philosophy is that the initial set of rules, defined by the CSO, should be very restrictive regarding possible unexpected users' behaviours or events, in order to avoid as much security incidents as possible.
+The philosophy is that the initial set of rules, defined by the CSO, should be very restrictive regarding possible unexpected users' behaviors or events, in order to avoid as much security incidents as possible.
 As the system works, MUSES would be able to define new rules (through refinement) which could get an associated decision after the corresponding events have happened.
@@
 the references mentioned by the referee, including new products, have
-been considered in the study. Tools have been described 
+been considered in the study. The different IBM tools and services have been described 
 (end of Section 3.1, in page XX), and compared to MUSES in Section 5.
@@
 % [Pedro] he cambiado un poco la redacciÛn   ;)
+% FERGU: Bueno, al final estos productos forman parte del "Entorno IBM" en general, que sÌ se ha comparado con MUSES. Paloma ha reescrito tambiÈn la secciÛn y quitado lo que sobraba.
 
@@
 
-Following the reviewer's suggestion we have introduced a taxonomy for the analyzed systems, according to the works that we have revised in the state of the art (Section 2).
+Following the reviewer's suggestion we have introduced a taxonomy for BYOD, according to the works that we have revised in the state of the art (Section 2).
+Different concepts mentioned in this improved state of the art, such as the hands-off/hand-off differentiation or BYOD best practices, have been taken into account to justify the proposed taxonomy.
 This taxonomy is described at the beginning of Section 3 (second paragraph, page XX).
-All the tools have been included in the types defined by the taxonomy.
+Then, all the tools, including MUSES, have been classified in the types defined by the taxonomy, and summarized in Table 1.
 % Antonio - completar con el n˙mero de p·gina final
 % Antonio - TODO: decir si MUSES y el resto de sistemas se han encuadrado dentro de esa taxonomÌa
+% FERGU: completado lo de la taxonomia (falta lo de los n˙meros de p·gina a˙n!) TODO
 
@@
 We have rewritten several parts of the paper and included new sections, subsections, tables and lists in order to improve the structure, contents and fluency of the text.
+Moreover, some paragraphs have been also rewritten to avoid large phrases, the inadequate use of parentheses, or the misunderstanding of some concepts.
 % Antonio - Por favor, completad esta justificaciÛn mejor.

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Lista como descripciones

--- 2015-07-09 MUSES_vs_BYOD_solutions.tex
@@
 
-% Antonio - pongo esto como lista de items, ya que era la única lista diferente
-\begin{itemize}
-  \item \textit{Connectivity sensor:} It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
+\begin{description}
+  \item[Connectivity sensor:] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours.
 This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough.
-  \item \textit{Device protection sensor:} Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
+  \item[Device protection sensor:] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}.
 This security mechanism adds the possibility of detecting security violations even if the user is not doing a specific action.
-  \item \textit{Location sensor:} User location can be obtained using the device GPS.
+  \item[Location sensor:] User location can be obtained using the device GPS.
 Although, this might be taken against the preservation of user privacy.
 This is why MUSES allows the definition of a number of `zones', and therefore it only checks if the user is inside them or not, acting in consequence.
-  \item \textit{Mail sensor:} If the user is writing an email, MUSES client sensor can also check the email attributes.
+  \item[Mail sensor:] If the user is writing an email, MUSES client sensor can also check the email attributes.
 Thus, it can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
@@
 ¿Cómo lo veis?
-  \item \textit{File sensor:} The type of file, also called \textit{asset}, is also very important for the application of security rules.
+  \item[File sensor:] The type of file, also called \textit{asset}, is also very important for the application of security rules.
 Thus, this sensor aims to detect if some files might need more strict security policies, also depending on the rest of sensors.
-  \item \textit{App sensor:} It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
+  \item[App sensor:] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications.
 Additionally, this sensor gathers information about the applications which the user tries to install or uninstall.
-\end{itemize}
+\end{description}
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Añadidas referencias a la taxonomia en abstract, intro y conclusiones

--- 2015-07-09 MUSES_vs_BYOD_solutions.tex
@@
 can be implemented in a secure way and comply with the Security Policies
-mentioned above. In this paper we present an overview of BYOD security
-solutions along with a novel, adaptive and free software system named
+mentioned above. In this paper we propose a  taxonomy to classify the features
+of BYOD systems. This taxonomy is used to present an overview of BYOD security
+solutions.
+
+Also, we describe a novel, adaptive and free software system named
 MUSES (Multi-platform Usable Endpoint Security), able 
@@
 enterprise security policies, but as a user-centric tool. It considers
-users' behaviour in order to adapt, improve, and even increase the
+users' behavior in order to adapt, improve, and even increase the
 defined set of security rules. To do this, the system applies Machine
@@
 So we now have a clear idea of its capabilities.
-Thus, in this paper we present an overview of the main existing solutions in the BYOD environment.
+Thus, in this paper we propose a taxonomy to classify the features of BYOD systems.
+This taxonomy is applied on the main existing solutions in the BYOD environment.
 Then, a comparison between these tools and MUSES is conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES.
@@
 \ref{sec:preliminaryconcepts}, explaining how the BYOD philosophy
-affects it. The main solutions or tools available or in development
+affects it. A taxonomy of BYOD systems, with the main solutions or tools available
 are detailed in Section \ref{sec:toolsreview}.
@@
 
-MUSES has been compared to other existing solutions with a similar aim: enduring the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
+A taxonomy has been proposed to compare MUSES with other existing solutions with a similar aim: enduring the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
 The main advantages of MUSES with respect to the other solutions have
-been discussed, remarking its advances beyond the state of the art
-that define these tools. %¿El estado del arte que define a estas
-                         %herramientas? ¿Qué es eso? - JJ
+been discussed, remarking its advances beyond the state of the art. %¿El estado del arte que define a estas
+                         %herramientas? ¿Qué es eso? - JJ FERGU: fuera
 

### 2015-07-09 Response to reviewers - r2.tex
Response to reviewers about all my changes... I think. Am i done? please? please :_

--- 2015-07-09 Response to reviewers - r2.tex
@@
 As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, stored, and processed on the server.
-In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will mean a significant change in the patterns.
+In case the device gets infected with rootkit-type malware (53), a sudden change in the values of the sensors will mean a significant change in the patterns.
 Then, this change in the patterns will be noticed by the server, which will immediately warn the user, and decrease the device trust value.}
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We agree with the reviewer and we have re-formulated this statement, as what actually happened was that these two tools had many problems.
+We explained why in the previous version of this work.
+Also, we have included new aspects of these tools, in order to classify them in the newly added taxonomy in section 3.
+Therefore:}
+
+\textcolor{blue}{Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they found problems in the market in spite of their features.
+On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.
+On the other hand, Samsung revealed at the Barcelona Mobile World Congress 2013 the KNOX application \cite{Samsung_mwc13}, which was expected to be available for its last Galaxy smartphone generation.
+Then, it was delayed and again presented in the same congress in 2014 \cite{Samsung_mwc14}, but still remained delayed until it was apparently found insecure \cite{Samsung_insecure}.
+Finally, Samsung decided to collaborate with Google in Android Work \cite{Samsung_android}, as mentioned in Section \ref{subsec:androidwork}.
+
+With regard to their features, Samsung KNOX, as well as Blackberry Balance, are more focused on the device side, while the solutions mentioned in previous subsections were more centered in being tools for CSOs.
+This also means that they are not device-independent, as KNOX is only for Samsung devices and Balance is integrated in BlackBerry 10 \cite{Blackberry_tool}.
+Looking at their situation and problems, it could be thought that making a BYOD solution platform-dependent is counteractive, which is why MUSES is independent of the device platform.}
 
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{The reviewer is right and it is true that WSO2 is a better competitor for MUSES than other tools, as is open source and multiplatform.
+However, it does not include offline working mode neither is able to refine policies.
+We have explained this in its section:}
+
+\textcolor{blue}{Although this tool also includes features such as device location, remote wipe, or encrypt storage, its main disadvantage is that it does not work in offline mode.
+In the documentation \footnote{\url{https://docs.wso2.com/display/EMM200/Working+with+Policies}}, it is clearly stated that the policy compliance can be monitored while the devices are connected to the WSO2 EMM server.
+}
 
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We have made clear that Worx is an SDK, which is a development environment, and also completed the explanation of ``Worx-enable application'' by comparing it with the concept of MUSES Aware applications.}
+
+\textcolor{blue}{XenMobile with the development environment called Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions \cite{WorxSDK}.
+For example using the mobile phone camera, GPS, or microphone.
+These policies can be turned on or off using its own GUI.
+Citrix is framework-enabled, and it is aware of the apps installed on the device.
+All the apps that are Worx-enabled are capable of interacting, and thus offering the user a better experience.
+This concept is similar to the `MUSES Aware' one, which was mentioned earlier in this section, and consists of adapting the applications to allow communications with the BYOD tools.}
 
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We understand that this might needed some clarification, so we included two references to web articles.
+First, to a top 10 of BYOD applications, the most recent we have found, and yet it is from 2013.
+As consequence, we found that some of the reviewed tools in the website ceased to exist or were acquired by other companies.
+As the other tools concern, we considered the most important manufacturers, companies, OSs, and devices, with regard to their sales.}
+
+\textcolor{blue}{The products that have been reviewed were chosen either because they have appeared in top-10 web articles \footnote{\url{http://www.networkworld.com/article/2357899/data-center/108866-10-Mobile-Device-Management-Leaders-That-Help-IT-Control-BYOD.html#slide11}}, or they have been developed for the main smartphone platforms \footnote{\url{http://www.idc.com/prodserv/smartphone-os-market-share.jsp}}.
+Actually, the selection process have been difficult, as some of the initially found tools or companies in the web were bought by others that we do review here.
+Also, because this market is still growing, there are not many solutions to review, and here we display the ones more alike to MUSES.
+This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.}
 
@@
 
-\textcolor{blue}{TODO - describir las limitaciones de MUSES en cada sistema}
+\textcolor{blue}{We agree and therefore we have included in section 4 that MUSES has been developed for Android, Windows PCs and phones, and that an iOS client is being developed.
+The same sensors are available in Android and Windows, but there is a strong limitation with monitoring iOS devices if they were not been \textit{jailbroken}.
+This means that if an iOS device has not been rooted, MUSES could not monitor every proccess in the device, and also it would have access only to some sensors.
+However, to be rooted is one of the situations that MUSES tries to avoid, which is why it depends on MUSES Aware apps.
+Thus:}
+
+\textcolor{blue}{MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development.
+The same sensors are available in Android and Windows, but there is a strong limitation with monitoring iOS devices if they were not been \textit{jailbroken}.
+This means that if an iOS device has not been rooted, MUSES could not monitor every proccess in the device, and also it would have access only to some sensors.
+However, to be rooted is one of the situations that MUSES tries to avoid, which is why it depends on MUSES Aware apps.
+As far as the server is concerned, it has been developed using Java to be installed with an Apache Tomcat in the corporate
+server, independently of its OS. Both sides are connected through a secure channel using HTTPS over the Internet.}
 
@@
 \textcolor{blue}{We agree with the reviewer about this paragraph not being clear, which is why it has been rewritten and clarified.
-At the end of the introduction of Section 4 (page XX) we have improved the explanation about MUSES data security and authentication.}
+At the end of the introduction of Section 4 (page XX) we have improved the explanation about MUSES data security and authentication, and added a new reference \cite{blasing2010android}.}
 
@@
 With regard to internal data security, MUSES makes use of the advantages that the OSs themselves offer to developers.
-More concretely, the first prototype for Android includes functionalities provided by the Android Application Sandbox \cite{blasing2010android}.
+More concretely, the first prototype for Android includes functionalities provided by the Android Application Sandbox (51).
 This means that other applications cannot access MUSES data, nor even other developers.
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We strongly agree and therefore we extended the explanation of the particular concept of MUSES API, in Section 4.1.
+We agree that this was necessary because the MUSES API is not a typical API which is used for developing part of third party applications.
+Instead, the MUSES API provides the necessary resources to make those third party applications able to communicate and deeply interact with MUSES.
+Then:}
+
+\textcolor{blue}{On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interact with it.
+This application must be implemented using the MUSES API (Application Program Interface).
+It should be noted that MUSES is an application that is running in the background, and third party apps can communicate with MUSES and ask for a response.
+Then, the MUSES API is not a normal API for building the third party application, but a collection of methods to allow this communication\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
+The main advantage of having MUSES Aware applications, is because actuator is able to actually forbid the users for doing something, if it implies a big risk for the company.}
 
@@
 
-\textcolor{blue}{TODO - Incluir justificaciÛn de Big Data Processing considerando el n˙mero de eventos generados en las Trials y extrapol·ndolo a muchos meses (al menos los 6 del hard limit)}.
+\textcolor{blue}{The justification for using Big Data techniques has been completed in section 4.3.1 with results of the first MUSES prototype trials.
+Then, these results have been extrapolated to an example case of a medium sized company, and by considering 6 months as the maximum period for storing the data.
+This way:}
+
+\textcolor{blue}{The set of data is composed by the so-called patterns, which consist of an occurred event and all the related information to that event.
+This means that the context in which the event was, is translated into a number of \textit{attributes} of the pattern.
+Moreover, a lot of attributes are extracted from the events, for obtaining the more information as possible.
+During the first trials, a mean of 201 events per day and user was observed.
+By considering just a medium size company, of 250 employees, that would make an average of 50300 events per day, of which a high number of features are extracted.
+Furthermore, if for instance 6 months are considered for the `hard limit' (see previous section), the amount of events to be processed would exponentially grow, until reaching the 9 millon events.
+For even bigger companies, this all result in huge datasets, so that MUSES makes use of several Big Data processing methods (48), such as: [...]}
 
@@
 
-\textcolor{blue}{TODO - no sÈ a quÈ 'bullets' se refiere}
+\textcolor{blue}{Agreeing with the reviewer, the refinement process inside MUSES has been explained with more detail in Section 4.3.
+Also, it has been included how the three Evolutionary Computation techniques depend, or not, one from each other.
+We agree that this is mandatory because is one of the most important features of the system and should be completely clear for the readers.
+Additionally, the concept of ``server graphical interface'' has been introduced and explained, as it is a tool for the CSO to interact with the system, define rules, consult the system status, and control the rule refinement, among other useful features.
+Thus:}
+
+\textcolor{blue}{Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with.
+Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
+The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.}
+
+\textcolor{blue}{In addition, we added how every information that the Knowledge Refinement System module manages is used by every technique:}
+
+\textcolor{blue}{As the rule refinement process is considered of the same importance as inferring new ones, the following three approaches have been implemented:
+
+\begin{itemize}
+
+\item A \textit{GP rule inference} method, which generates new rules in order to `cover' those situations that have been not contemplated in the current set of rules.
+Thus, a new rule would be created for dealing with the patterns to which the classifier could not assign a class.
+The generation of new rules is done by considering the so-called \textit{dictionary}, i.e.
+a set of terms corresponding to all the possible context situations and user actions in the system, which are the antecedents and consequents \footnote{The antecedents are the conditions of a rule that have to be met to apply the consequents.} of the security rules to be inferred.
+The evaluation of these rules is done by considering the information that has been described.
+Thus, it is possible to `simulate' the whole system behavior when the new rule is included.
+Therefore, the system gets a value of its performance in terms of, for instance, how many of the events that were not classified or misclassified, are covered now.
+As was also mentioned, the user or device trust values influence the creation of the rules.
+Finally, the inferred rules are proposed to the CSO as ``new, but not yet refined'', along with their evaluated performance.
+
+\item A \textit{GP rule refinement} approach, which optimizes the current set of rules, adjusting the values in the conditions.
+The set of rules that could be refined is composed by the new rules from the GP-based inference, but also by the original set of rules which was already completed by the Data Miner.
+Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specializations or generalizations of existing rules which could lead to a better performance.
+The evaluation of the whole set of security rules is done by considering the number of unlabelled patterns that are `covered' after the adjustments.
+Again, the rules at the end of this step are presented to the CSO as ``refined''.
+The CSO is the one who decides, according to the performance simulation results, if an inferred rule, or the refined one, is the rule which is finally included in the system.
+
+\item A \textit{GA optimization} algorithm for adapting the values of the assets.
+These are numerical representations of the importance of the corporate assets, and are considered in the Real-Time Risk and Trust Analysis process, in order to assign a risk value to every potential decision that can be made by the system.
+By evaluating the partial solutions proposed by the GA, this approach provides the CSO, who is in charge of assigning and adjusting these values over time, with information about the most dangerous situations for certain assets.
+In this process, then, the context information that is gathered by the system is very important.
+The adaptation or adjustment concerns the change in the value that an asset has due to a loss of importance, for instance, for being an out-to-date document.
+
+\end{itemize}
+
+As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting values of the assets.
+Both the inferred rules and the refined rules are presented to the CSO, who includes them or not in the system, and this acceptance or rejection acts itself as a feedback for future rule inference.}
 
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We agree with this, so the way MUSES creates new rules through classification and also refinement, has been better explained in Section 4.3.
+Also, in section 5 this has been remarked, as well as completed by explaining that the rule creation process is aimed by a risk and trust analysis in real-time.
+The reviewer can consult the test in the response to the previous statement.
+Also, of Section 5:}
+
+\textcolor{blue}{Also related to this issue, a very big advantage of the MUSES system that is not present in the other solutions is its self-adaptivity power.
+The proposed system uses different methods to create new security rules, being their aim to cover new vulnerabilities or threats.
+Thus, MUSES is able to adapt to changes by applying classification techniques to create new rules, and then refining the whole set of existing policies.
+Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis plus a classifier trained with all the occurred events in the system.}
 
@@
 
-\textcolor{blue}{TODO}
+\textcolor{blue}{We agree that it was not clear how MUSES contributes to the State of The Art about HCI.
+Therefore, it has been explained in section 5 how MUSES tries to have an influence in the user bevahiour through the warnings, as long as securing by adaptation of the security rules.
+Then:}
+
+\textcolor{blue}{As far as the HCI is concerned, in Section 2 we talked about how it has been demonstrated by Shaw et al.
+(21) and Herath et al.
+(22) that the compliance of the employees of a company, with respect to the security policies, increases by educating them and decreases by punishing them.
+Therefore, the fact that MUSES is focused in avoiding security incidents due to users' unawareness of the ISPs, it sets up a significant advance in the state of the art.
+This is because not only the incident is avoided, but the user is educated, which at the same time avoids future risky situations.
+With regard to device monitoring, MUSES  also take into account the so-called context observation, by which private or professional scenarios can be detected, or predicted, based on advanced machine learning techniques.
+Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it  contributes to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.}
 
@@
 \textcolor{blue}{TODO}
+% Paloma - Esto creo que lo he respondido antes...
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Response to reviewers about all my changes... I think. Am i done? please? please :_

--- 2015-07-09 MUSES_vs_BYOD_solutions.tex
@@
 Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art.
+The products that have been reviewed were chosen either because they have appeared in top-10 web articles \footnote{\url{http://www.networkworld.com/article/2357899/data-center/108866-10-Mobile-Device-Management-Leaders-That-Help-IT-Control-BYOD.html#slide11}}, or they have been developed for the main smartphone platforms \footnote{\url{http://www.idc.com/prodserv/smartphone-os-market-share.jsp}}.
+Actually, the selection process have been difficult, as some of the initially found tools or companies in the web were bought by others that we do review here.
+Also, because this market is still growing, there are not many solutions to review, and here we display the ones more alike to MUSES.
 This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.
@@
 In the documentation \footnote{\url{https://docs.wso2.com/display/EMM200/Working+with+Policies}}, it is clearly stated that the policy compliance can be monitored while the devices are connected to the WSO2 EMM server.
+In addition, this tool seems to be only an MDM, without any refinement of the security policies.
 
@@
 
-XenMobile with Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions \cite{WorxSDK}.
+XenMobile with the development environment called Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions \cite{WorxSDK}.
 For example using the mobile phone camera, GPS, or microphone.
@@
 MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development.
+The same sensors are available in Android and Windows, but there is a strong limitation with monitoring iOS devices if they were not been \textit{jailbroken}.
+This means that if an iOS device has not been rooted, MUSES could not monitor every proccess in the device, and also it would have access only to some sensors.
+However, to be rooted is one of the situations that MUSES tries to avoid, which is why it depends on MUSES Aware apps.
 % [Pedro] ¿qué tal decir: "MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development."
@@
 By considering just a medium size company, of 250 employees, that would make an average of 50300 events per day, of which a high number of features are extracted.
-For even bigger companies, this results in huge datasets, so that MUSES makes use of several Big Data processing methods \cite{BigData_11}, such as:
+Furthermore, if for instance 6 months are considered for the `hard limit' (see previous section), the amount of events to be processed would exponentially grow, until reaching the 9 millon events.
+For even bigger companies, this all result in huge datasets, so that MUSES makes use of several Big Data processing methods \cite{BigData_11}, such as:
 

### 2015-07-09 Response to reviewers - r2.tex
Actualización en las respuestas

@@
 
-\textcolor{blue}{We agree with the reviewer and we have re-formulated this statement, as what actually happened was that these two tools had many problems.
+We agree with the reviewer and we have re-formulated this statement, as what actually happened was that these two tools had many problems.
 We explained why in the previous version of this work.
 Also, we have included new aspects of these tools, in order to classify them in the newly added taxonomy in section 3.
-Therefore:}
+Therefore:
 
-\textcolor{blue}{Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they found problems in the market in spite of their features.
+Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation, as they found problems in the market in spite of their features.
 On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.
@@
 This also means that they are not device-independent, as KNOX is only for Samsung devices and Balance is integrated in BlackBerry 10 \cite{Blackberry_tool}.
-Looking at their situation and problems, it could be thought that making a BYOD solution platform-dependent is counteractive, which is why MUSES is independent of the device platform.}
+Looking at their situation and problems, it could be thought that making a BYOD solution platform-dependent is counteractive, which is why MUSES is independent of the device platform.
 
@@
 
-\textcolor{blue}{The reviewer is right and it is true that WSO2 is a better competitor for MUSES than other tools, as is open source and multiplatform.
+The reviewer is right and it is true that WSO2 is a better competitor for MUSES than other tools, as is open source and multiplatform.
 However, it does not include offline working mode neither is able to refine policies.
-We have explained this in its section:}
+We have explained this in its section:
 
-\textcolor{blue}{Although this tool also includes features such as device location, remote wipe, or encrypt storage, its main disadvantage is that it does not work in offline mode.
+Although this tool also includes features such as device location, remote wipe, or encrypt storage, its main disadvantage is that it does not work in offline mode.
 In the documentation \footnote{\url{https://docs.wso2.com/display/EMM200/Working+with+Policies}}, it is clearly stated that the policy compliance can be monitored while the devices are connected to the WSO2 EMM server.
-}
 
@@
 
-\textcolor{blue}{We have made clear that Worx is an SDK, which is a development environment, and also completed the explanation of ``Worx-enable application'' by comparing it with the concept of MUSES Aware applications.}
+We have made clear that Worx is an SDK, which is a development environment, and also completed the explanation of ``Worx-enable application'' by comparing it with the concept of MUSES Aware applications.
 
-\textcolor{blue}{XenMobile with the development environment called Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions \cite{WorxSDK}.
+XenMobile with the development environment called Worx App SDK, made by Citrix Systems, provides BYOD security services to companies using fine-grained policies to prevent users from performing unallowed actions \cite{WorxSDK}.
 For example using the mobile phone camera, GPS, or microphone.
@@
 All the apps that are Worx-enabled are capable of interacting, and thus offering the user a better experience.
-This concept is similar to the `MUSES Aware' one, which was mentioned earlier in this section, and consists of adapting the applications to allow communications with the BYOD tools.}
+This concept is similar to the `MUSES Aware' one, which was mentioned earlier in this section, and consists of adapting the applications to allow communications with the BYOD tools.
 
@@
 
-\textcolor{blue}{We understand that this might needed some clarification, so we included two references to web articles.
+We understand that this might needed some clarification, so we included two references to web articles.
 First, to a top 10 of BYOD applications, the most recent we have found, and yet it is from 2013.
 As consequence, we found that some of the reviewed tools in the website ceased to exist or were acquired by other companies.
-As the other tools concern, we considered the most important manufacturers, companies, OSs, and devices, with regard to their sales.}
+As the other tools concern, we considered the most important manufacturers, companies, OSs, and devices, with regard to their sales.
 
-\textcolor{blue}{The products that have been reviewed were chosen either because they have appeared in top-10 web articles \footnote{\url{http://www.networkworld.com/article/2357899/data-center/108866-10-Mobile-Device-Management-Leaders-That-Help-IT-Control-BYOD.html#slide11}}, or they have been developed for the main smartphone platforms \footnote{\url{http://www.idc.com/prodserv/smartphone-os-market-share.jsp}}.
+The products that have been reviewed were chosen either because they have appeared in top-10 web articles \footnote{\url{http://www.networkworld.com/article/2357899/data-center/108866-10-Mobile-Device-Management-Leaders-That-Help-IT-Control-BYOD.html#slide11}}, or they have been developed for the main smartphone platforms \footnote{\url{http://www.idc.com/prodserv/smartphone-os-market-share.jsp}}.
 Actually, the selection process have been difficult, as some of the initially found tools or companies in the web were bought by others that we do review here.
 Also, because this market is still growing, there are not many solutions to review, and here we display the ones more alike to MUSES.
-This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.}
+This section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.
 
@@
 
-\textcolor{blue}{We agree and therefore we have included in section 4 that MUSES has been developed for Android, Windows PCs and phones, and that an iOS client is being developed.
+We agree and therefore we have included in section 4 that MUSES has been developed for Android, Windows PCs and phones, and that an iOS client is being developed.
 The same sensors are available in Android and Windows, but there is a strong limitation with monitoring iOS devices if they were not been \textit{jailbroken}.
@@
 However, to be rooted is one of the situations that MUSES tries to avoid, which is why it depends on MUSES Aware apps.
-Thus:}
+Thus:
 
-\textcolor{blue}{MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development.
+MUSES client is available up to date to be used in Android devices as well as in Windows mobile devices and PCs; the iOS client is under development.
 The same sensors are available in Android and Windows, but there is a strong limitation with monitoring iOS devices if they were not been \textit{jailbroken}.
@@
 As far as the server is concerned, it has been developed using Java to be installed with an Apache Tomcat in the corporate
-server, independently of its OS. Both sides are connected through a secure channel using HTTPS over the Internet.}
+server, independently of its OS. Both sides are connected through a secure channel using HTTPS over the Internet.
 
@@
 
-\textcolor{blue}{We agree with the reviewer about this paragraph not being clear, which is why it has been rewritten and clarified.
-At the end of the introduction of Section 4 (page XX) we have improved the explanation about MUSES data security and authentication, and added a new reference \cite{blasing2010android}.}
+We agree with the reviewer about this paragraph not being clear, which is why it has been rewritten and clarified.
+At the end of the introduction of Section 4 (page XX) we have improved the explanation about MUSES data security and authentication, and added a new reference \cite{blasing2010android}.
 
-\textcolor{blue}{The MUSES system also performs an authentication process when the user logs in.
+The MUSES system also performs an authentication process when the user logs in.
 The MUSES server authenticates to the MUSES client by means of a self-signed certificate.
@@
 The only way to do this is by rooting the device, which is a state that MUSES can detect, and therefore warn about its implications.
-With regard to the encryption of the rest of the device data, MUSES stands for having a security policy which advices about the installation of existing open source tools \footnote{For instance, \url{https://github.com/neurodroid/cryptonite/blob/master/README.md}}, instead of having an own implementation.}
+With regard to the encryption of the rest of the device data, MUSES stands for having a security policy which advices about the installation of existing open source tools \footnote{For instance, \url{https://github.com/neurodroid/cryptonite/blob/master/README.md}}, instead of having an own implementation.
 
@@
 
-\textcolor{blue}{We strongly agree and therefore we extended the explanation of the particular concept of MUSES API, in Section 4.1.
+We strongly agree and therefore we extended the explanation of the particular concept of MUSES API, in Section 4.1.
 We agree that this was necessary because the MUSES API is not a typical API which is used for developing part of third party applications.
 Instead, the MUSES API provides the necessary resources to make those third party applications able to communicate and deeply interact with MUSES.
-Then:}
+Then:
 
-\textcolor{blue}{On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interact with it.
+On the one hand, the \textit{MUSES Aware App} is an application adapted to MUSES, so the system can directly interact with it.
 This application must be implemented using the MUSES API (Application Program Interface).
@@
 Then, the MUSES API is not a normal API for building the third party application, but a collection of methods to allow this communication\footnote{The MUSES API is defined in the project, so for every application desired to be MUSES Aware, it should be implemented using this.}.
-The main advantage of having MUSES Aware applications, is because actuator is able to actually forbid the users for doing something, if it implies a big risk for the company.}
+The main advantage of having MUSES Aware applications, is because actuator is able to actually forbid the users for doing something, if it implies a big risk for the company.
 
@@
 
-\textcolor{blue}{The justification for using Big Data techniques has been completed in section 4.3.1 with results of the first MUSES prototype trials.
+The justification for using Big Data techniques has been completed in section 4.3.1 with results of the first MUSES prototype trials.
 Then, these results have been extrapolated to an example case of a medium sized company, and by considering 6 months as the maximum period for storing the data.
-This way:}
+This way:
 
-\textcolor{blue}{The set of data is composed by the so-called patterns, which consist of an occurred event and all the related information to that event.
+The set of data is composed by the so-called patterns, which consist of an occurred event and all the related information to that event.
 This means that the context in which the event was, is translated into a number of \textit{attributes} of the pattern.
@@
 Furthermore, if for instance 6 months are considered for the `hard limit' (see previous section), the amount of events to be processed would exponentially grow, until reaching the 9 millon events.
-For even bigger companies, this all result in huge datasets, so that MUSES makes use of several Big Data processing methods (48), such as: [...]}
+For even bigger companies, this all result in huge datasets, so that MUSES makes use of several Big Data processing methods (48), such as: [...]
 
@@
 
-\textcolor{blue}{Agreeing with the reviewer, the refinement process inside MUSES has been explained with more detail in Section 4.3.
+Agreeing with the reviewer, the refinement process inside MUSES has been explained with more detail in Section 4.3.
 Also, it has been included how the three Evolutionary Computation techniques depend, or not, one from each other.
@@
 Additionally, the concept of ``server graphical interface'' has been introduced and explained, as it is a tool for the CSO to interact with the system, define rules, consult the system status, and control the rule refinement, among other useful features.
-Thus:}
+Thus:
 
-\textcolor{blue}{Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with.
+Another important fact is that MUSES functionalities are completed by a human controller, normally the CSO, who supervises the system activity by means of a graphic interface they can interact with.
 Thus, adapted and inferred security rules are not directly added to the current set of rules, but they are proposed instead as draft rules to this human controller, in order to be accepted if they are interesting and useful.
-The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.}
+The system also uses the acceptance or rejection of new rules as `feedback`, learning from these decisions, and refining the rules according to this.
 
-\textcolor{blue}{In addition, we added how every information that the Knowledge Refinement System module manages is used by every technique:}
+In addition, we added how every information that the Knowledge Refinement System module manages is used by every technique:
 
-\textcolor{blue}{As the rule refinement process is considered of the same importance as inferring new ones, the following three approaches have been implemented:
+As the rule refinement process is considered of the same importance as inferring new ones, the following three approaches have been implemented:
 
@@
 As a summary, the Knowledge Compiler module uses two EC-based processes for inferring and refining rules, plus another one for adjusting values of the assets.
-Both the inferred rules and the refined rules are presented to the CSO, who includes them or not in the system, and this acceptance or rejection acts itself as a feedback for future rule inference.}
+Both the inferred rules and the refined rules are presented to the CSO, who includes them or not in the system, and this acceptance or rejection acts itself as a feedback for future rule inference.
 
@@
 
-\textcolor{blue}{We agree with this, so the way MUSES creates new rules through classification and also refinement, has been better explained in Section 4.3.
+We agree with this, so the way MUSES creates new rules through classification and also refinement, has been better explained in Section 4.3.
 Also, in section 5 this has been remarked, as well as completed by explaining that the rule creation process is aimed by a risk and trust analysis in real-time.
 The reviewer can consult the test in the response to the previous statement.
-Also, of Section 5:}
+Also, of Section 5:
 
-\textcolor{blue}{Also related to this issue, a very big advantage of the MUSES system that is not present in the other solutions is its self-adaptivity power.
+Also related to this issue, a very big advantage of the MUSES system that is not present in the other solutions is its self-adaptivity power.
 The proposed system uses different methods to create new security rules, being their aim to cover new vulnerabilities or threats.
 Thus, MUSES is able to adapt to changes by applying classification techniques to create new rules, and then refining the whole set of existing policies.
-Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis plus a classifier trained with all the occurred events in the system.}
+Additionally, MUSES is able to discover new threats by a combination of real-time risk and trust analysis plus a classifier trained with all the occurred events in the system.
 
@@
 
-\textcolor{blue}{We agree that it was not clear how MUSES contributes to the State of The Art about HCI.
+We agree that it was not clear how MUSES contributes to the State of The Art about HCI.
 Therefore, it has been explained in section 5 how MUSES tries to have an influence in the user bevahiour through the warnings, as long as securing by adaptation of the security rules.
-Then:}
+Then:
 
-\textcolor{blue}{As far as the HCI is concerned, in Section 2 we talked about how it has been demonstrated by Shaw et al.
+As far as the HCI is concerned, in Section 2 we talked about how it has been demonstrated by Shaw et al.
 (21) and Herath et al.
@@
 With regard to device monitoring, MUSES  also take into account the so-called context observation, by which private or professional scenarios can be detected, or predicted, based on advanced machine learning techniques.
-Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it  contributes to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.}
+Finally, the project is concerned about legal compliance in regards of Information Security Policies, so that it  contributes to the proposal for the EU Data Protection: legal binding force and legal certainty of company policies, and end-user responsibility.
 
@@
 % Paloma - Esto creo que lo he respondido antes...
+% Antonio - por favor, dÌ eso mismo al revisor.
+% DirÌgelo a la respuesta que sea o repite de otra forma lo mismo.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Adding explanation why 'other tools' section is such and closes #47
Changing another word from British to Colonial, thanks to @draxus twitt :)

@@
 
-To this end, MUSES analyses the users' behavior by means of Data
+To this end, MUSES analyzes the users' behavior by means of Data
 Mining (DM) techniques \cite{DataMining_Lee01} and Machine Learning
@@
 
-There exist other corporate security-aimed tools inside the BYOD philosophy, such as:
+There exist other corporate security-aimed tools inside the BYOD philosophy, of which there are less references on the Internet, but still we consider important for having similar features as MUSES.
+These tools are:
 

### 2015-07-09 Response to reviewers - r2.tex
resuelto un TODO de las respuestas

@@
 
-\textcolor{blue}{TODO - Justificar su valÌa.
+% [Pedro] traducido e incluido a continuaciÛn => \textcolor{blue}{TODO - Justificar su valÌa.
 Las empresas querr·n MUSES y querr·n que sus empleados utilicen MUSES-Aware Apps porque les garantizar·n un control sobre lo que se hace en la empresa y los posibles incidentes de seguridad.}
+
+Due to its functionality, proposed system might be of interest for many companies as using MUSES-aware Apps they could control any operation that a person can do with their mobile or desktop devices.
 

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Re-Revisadas las respuestas a #2 y #3
Y algunos cambios en el artículo

@@
 As results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 even before the trials period finished.
-Thus, we can assume that MUSES is an effective tool, even though it has the aforementioned limitation of needing an initial set of defined security rules to start working.
+Thus, we can assume that MUSES is an effective tool, even though it has the limitation of needing an initial set of defined security rules to start working (this will be better explained in Section \ref{sec:comparison}).
 For this, MUSES also includes a set of guidelines for the companies to build adequate security policies.

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Version final (espero) de artículo y respuestas

@@
 Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art.
+
 The products that have been reviewed were chosen either because they have appeared in top-10 web articles \footnote{\url{http://www.networkworld.com/article/2357899/data-center/108866-10-Mobile-Device-Management-Leaders-That-Help-IT-Control-BYOD.html#slide11}}, or they have been developed for the main smartphone platforms \footnote{\url{http://www.idc.com/prodserv/smartphone-os-market-share.jsp}}.
@@
 The same sensors are available in Android and Windows, but there is a strong limitation with monitoring iOS devices if they were not been \textit{jailbroken}.
-This means that if an iOS device has not been rooted, MUSES could not monitor every proccess in the device, and also it would have access only to some sensors.
+This means that if an iOS device has not been rooted, MUSES could not monitor every process in the device, and also it would have access only to some sensors.
 However, to be rooted is one of the situations that MUSES tries to avoid, which is why it depends on MUSES Aware apps.
@@
 The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications.
-When the user connects to the MUSES server for the first time, the MUSES client asks the server for the cerfiticate, wich is sent and installed in the client local database if the user credentials are right.
+When the user connects to the MUSES server for the first time, the MUSES client asks the server for the certificate, which is sent and installed in the client local database if the user credentials are right.
 As the user credentials are also stored in the MUSES client local database, the user can also log in to MUSES, and it therefore can apply the Device Policies.
@@
 By considering just a medium size company, of 250 employees, that would make an average of 50300 events per day, of which a high number of features are extracted.
-Furthermore, if for instance 6 months are considered for the `hard limit' (see previous section), the amount of events to be processed would exponentially grow, until reaching the 9 millon events.
+Furthermore, if for instance 6 months are considered for the `hard limit' (see previous section), the amount of events to be processed would exponentially grow, until reaching the 9 million events.
 For even bigger companies, this all result in huge datasets, so that MUSES makes use of several Big Data processing methods \cite{BigData_11}, such as:

### 2015-07-12 MUSES_vs_BYOD_solutions.tex
Quito Keywords por requisitos de la revista

@@
 \begin{keyword}
-Corporate mobile security \sep End-to-end security solutions \sep User-centric systems \sep Self-adaptation \sep Multi-platform \sep Security Policies \sep Data security and data privacy \sep BYOD
+Corporate mobile security \sep User-centric systems \sep Self-adaptation \sep Multi-platform \sep BYOD
 \end{keyword}
